### 2016-03-02 report/draft1.tex
Backup 02/03/16

\documentclass{article}
\usepackage{graphicx}
\graphicspath{ {graphs/} }
\begin{document}
\begin{titlepage}
    \begin{center}
        \vspace*{1cm}

        \Huge
        \textbf{Reconstruction of Charge Number of Heavy Cosmic Rays using Cherenkov Light}

        \LARGE

        \vspace{1cm}

        \textbf{Robert Stein}\\
        \textbf{CID 00819615}

        \vspace{1cm}
        \includegraphics[width=0.4\textwidth]{Imperial_College_London_logo} 
        \hspace{0.5cm}
        \includegraphics[width=0.4\textwidth]{hamburglogo}

        \vspace{1cm}

        Supervisor: Professor Dieter Horns

        \large
        \vspace{1.0cm}

        A thesis presented for the degree of\\
        \textbf{Master in Science}

        \vspace{0.5cm}

        Physics Department\\
        Imperial College London

        \vspace{0.5cm}

        \today

    \end{center}
\end{titlepage}
\section*{Abstract}
Between impact with the upper atmosphere and decay into a charged particle shower, heavy cosmic ray elements such as Iron emit Cherenkov Light at an angle determined by the Refractive Index of the air and the energy per nucleon. This direct Cherenkov Light forms a characteristic circular light distribution on the Earth's surface with an intensity proportional to the square of the cosmic ray charge. A new method has been developed to reconstruct this charge number, by fitting the received Cherenkov Photons to the characteristic Lateral Photon Distribution. The expected performance for various existing and planned installations will be discussed.

\section*{Zusammenfassung}
Between impact with the upper atmosphere and decay into a charged particle shower, heavy cosmic ray elements such as Iron emit Cherenkov Light at an angle determined by the Refractive Index of the air and the energy per nucleon. This direct Cherenkov Light forms a characteristic circular light distribution on the Earth's surface with an intensity proportional to the square of the cosmic ray charge. A new method has been developed to reconstruct this charge number, by fitting the received Cherenkov Photons to the characteristic Lateral Photon Distribution. The expected performance for various existing and planned installations will be discussed.
\newpage
\tableofcontents
\newpage
\section{Introduction}
There are numerous Telescope Arrays which image the Cherenkov Light emitted by Cosmic Rays in the atmosphere, including the HESS, Magic and Veritas Experiments. All such Imaging Atmospheric Cherenkov Telescopes (IACTs) rely on Hillas Analysis for event reconstruction.Hillas Analysis extracts parameters from each of the camera images in order to reconstruct the events. However, heavy blurring of the events by atmospheric effects means that resolution of reconstruction  is very poor. For a typical Iron Nucleus event \cite{hess07}, the core position resolution is roughly $d \approx 20 m $, and the charge would be reconstructed as \[Z \approx 26 \pm 5 \]

Cosmic Rays that are imaged by these telescopes have energies between $13 $TeV and $200 $TeV. At present, no study of the relative abundance of different cosmic ray elemental abundances exists, although it could provide important clues regarding the mechanism of Cosmic Ray formation and propagation in the galaxy. Unfortunately, current charge resolution from Hillas Analysis is not small enough to undertake such a study.

Instead of Hillas Analysis, we consider a new method for event reconstruction, in which we fit the known Direct Cherenkovn (DC) Light observed by each telescope to a characteristic Lateral Photon Distribution (LPD) function. This new technique is valid both for currently running experiments, as well as planned experiments such as the Cherenkov Telescope Array (CTA). It uses only the information from the DC Pixel identified in the shower images.

A theoretical study by Kieda in 2001 \cite{kieda01} suggested that for a core position resolution of $d \approx 5 $ m , we could expect to see a charge resolution of $ \sigma_{Z} \approx 1 $ for elements of $Z = 20$ or higher. In this case the core resolution would be the limiting value. Thus, if the LPD method can achieve this core position resolution, then charge resolution will become sufficiently good enough to extract the abundances of the different Cosmic Ray Elements. This the prime motivation for the new LPD technique.

\section{Lateral Photon Distribution Method}
In order to reconstruct events using the LPD method, we require the Energy of the Cosmic Ray lie in the saturated region, and that the event can be seen by at least 4 telescopes. These restrictions confine us to Cosmic Rays with specific characteristics.

\subsection{Cherenkov Light Emission}
Cosmic Rays follow a well-defined power law where $ \frac{dN_{E}}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ? $. Consequently higher energy Cosmic Rays are heavily suppressed.

The energy Threshold as a function of height is illustrated in

Once a Cosmic Ray crosses the Threshold Energy, it will begin emitting Cherenkov Light, and will stop emitting Cherenkov Light when it first interacts at a height $h$. For a given Telescope Array altitude above sea level, simple trigonometry yields:
\[ Radius(height = altitude_{array}) = \tan (\theta_{C}(h)) \times (h - altitude_{array})\]
As the Refractive Index of the Earth increases as height decreases, the angle $\theta_{C}$ increases with decreasing height. Thus the upper earlier emission contributes to the inner LPD, while the later emission contributes to the high-radius LPD.

In figure Y, we see ground emission radius as a function of height. It is clear that the high-radius emission, (occurring near the first interaction region) is virtually unchanged for different Energies. We deem this to be 'saturated emission'.

\subsection{Nuclear Charge}
In figure Z we see that the height of the 'signal' LPD varies with \[ \rho_{DC}  = f(r) \times Z^{2}\]

Thus the height of the LPD is proportional to the charge of the Cosmic Ray, enabling the Charge to be determined from the DC emission. This is the basis for charge reconstruction in the LPD method.

\subsection{Iterative Log Likelihood Minimisation}
In order to reconstruct an event, we need to find the x/y core position, the Energy per Nucleon, the first interaction height and the charge. However, if one telescope in a five-telescope array does not observe DC light, this data point can be used to constrain the core position. Thus, for the LPD method to be applied, we require a minimum of five telescopes, four or more of which must image the DC light.

We consider the amount of DC light that each telescope receives to be Poissonian \[  P_{i} ( N_{i, Received} \mid X, Y, Z, height, Epn )  =  \frac{ e^{- \lambda_{i} } \times \lambda_{i} ^{N_{i}} }{N_{i}!} \]

In order to reduce computing time, we can use Stirling's Approximation $ln( N! )  \approx  N ln(N) - N + \frac{1}{2} ln(2 \pi N)$. Pure night sky background requires that there be more that X photons in a DC pixel, and for this Stirling's Approximation has an error of just Y?. We then minimise the Log Likelihood function \[ - Ln(L) = - \sum_{i=1}^{n} [P_{i}] \approx  \sum_{i=1}^{n} [\lambda _{i} - N_{i} ln(\lambda _{i}) + N_{i} ln(N_{i}) - N_{i} + \frac{1}{2} ln(2 \pi N_{i})]  \]
where n is the total number of telescopes in the array.

Unfortunately, as a result of varying Threshold Energies and the sharp drop in the LDF above the maximum radius, the Log likelihood is discontinuous in many places. Consequently, a Minuit-type minimisation algorithm will only be able to find a local minimum near the starting values for the fit parameters.

\section{HESS-type Event Reconstruction}

\subsection{First Interaction Height}
Cosmic Rays survival in from the top of the atmosphere follows an exponential decay with the number of 'interaction lengths' passed. The interaction length is dependent on the interaction cross section, which increases with density. Thus the number of interaction lengths increases exponentially as height decreases .

The resultant decays occur most often at a height of $h \approx 40 \pm 10$ km. However, when the HESS layout is simulated, the 4 telescope events have a mean height of $h \approx 24 \pm 4$ km, as shown in \ref{fig:Height Statistics}.

\begin{figure}
\begin{center}
\includegraphics[height=0.9\textheight]{height}
\caption{The integrated interaction lengths increases as height decreases. Thus the decay probability follows a exponentially increasing distribution. The first interaction height for all events peaks at around 40000m. However the mean first interaction height for 4 telescope events is 23000m}
\label{fig:Height Statistics}
\end{center}
\end{figure}

\subsection{HESS Energy saturation region}
It be like 0.7 Tev per Nucleon!

However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon fig Y! The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...

\subsection{Extended Air Shower Background}
A typical HESS image is shown in \ref{fig:hess}, with the DC pixel visible. The Extended Air Shower (EAS) produced after the first interaction of the Cosmic Ray overlaps the DC pixel, leading to background in the LPD. As the Energy of the Cosmic Ray increases, the EAS speads over a larger angular area, and at smaller radii, the EAS-DC-shower direction axis contracts, leading to more overlap. Thus the background in the DC pixel increases with decreasing radius and increasing Energy.

\begin{figure}
\begin{center}
\includegraphics[width=0.9\textwidth]{hess}
\caption{A 4-camera HESS event. The shower direction is marked with a white cross, and the DC pixel is indicated with a white arrow. The shower axis passes through the shower direction, the DC pixel, and the center of the Extensive Air Shower region lying beyond the DC pixel.}
\label{fig:hess}
\end{center}
\end{figure}

In addition, we have a fixed night sky background with 7 photons $m^{-2}$. We thus parameterise the background with 
\[ \rho_{bkg}  = 7 + 5E\]
The modeled background LPD is shown in X. It begins to dominate above roughly 1 TeV per Nucleon, particularly in the case of smaller radii.

\section{Optimised Telescope Array}
NO Background!!!!!
\subsection{Count Rates}

\subsection{Saturation Region Energies}

\section{Conclusion}
End
\bibliographystyle{plain}
\bibliography{report}
\end{document}

### 2016-03-02 positioning/epnstatistics.py

@@ -131,19 +131,19 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, layout="five", numbe
 	
 	#Plot variables Etheshold and Ring Radius againist height
 	
-	ax3 = plt.subplot(122)
+	ax3 = plt.subplot(111)
 	
 	rawheights=[]
 	emin=[]
 	rmax = []
 	
-	Erange = [3571, 850, 231]
+	Erange = [3571, 850]
 	
 	labels = [" = Infinity "]
 	for e in Erange:
 		labels.append(" = " + str(e))
 		
-	colors=["k", "r", "g", "b"]
+	colors=["k", "r", "g"]
 	
 	nucleonmass = 0.93827 
 	
@@ -201,15 +201,17 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, layout="five", numbe
 	for j in range (0, len(betarange)):
 		print j, len(curves[j]), len(rawheights[j])
 		label = "Radius (m) for E" + str(labels[j])
-		ax3.plot(curves[j], rawheights[j], color = colors[k], label=label)
-	plt.axhline(y=22000, color='m')
-	ax3.plot(emin,rawheights[0],  color='c', label="Threshold Energy (TeV per Nucleon)")	
+		ax3.plot(curves[j], rawheights[j], color = colors[j], label=label, linewidth=3.0)
+	plt.axhspan(19000, 26000, color='m', alpha=0.5)
+	ax3.plot(emin,rawheights[0],  color='b', linewidth=3.0, label="Threshold Energy (TeV per Nucleon)")	
 	
 	
 	plt.xscale('log')
 	
-	plt.ylabel('Height', labelpad=0)
+	plt.ylabel('Height', labelpad=0, fontsize=30)
 	plt.legend(loc=2)
+	
+	ax3.tick_params(labelsize=30)
 	
 	print "Maximum Radius is", max(curves[0])
 	
@@ -218,26 +220,14 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, layout="five", numbe
 	
 	#Option to produce a full size graph, for use in presentations etc.
 	
-	#~ ax3 = plt.subplot(111)
-	#~ 
-	#~ ax3.plot(emin,rawheights,  label="Threshold Energy (TeV per Nucleon)")
-	#~ ax3.plot(rmax, rawheights, label="Maximum Radius (m)")
-	#~ plt.xscale('log')
[…]

### 2016-03-02 positioning/optimiselayout.py

@@ -31,10 +31,10 @@ def run(numberofhours):
 	lowerbincount = 20
 	upperbincount = 10
 	
-	lowerrange = [lowerlim, midlim-0.01, lowerbincount]
+	lowerrange = [lowerlim, midlim, lowerbincount]
 	ranges.append(lowerrange)
 	
-	upperrange = [midlim+0.01, upperlim, upperbincount]
+	upperrange = [midlim, upperlim, upperbincount]
 	ranges.append(upperrange)
 	
 	fullcount = []
@@ -51,8 +51,15 @@ def run(numberofhours):
 		upper = entry[1]
 		bins = entry[2]
 		
-		telescopegap = np.linspace(lower, upper, bins)
-		edges.extend(np.linspace(lower-0.01, upper+0.01, bins+1))
+		
+		edge = np.linspace(lower, upper, bins)
+		edges.extend(edge)
+		telescopegap = (edge[1:] + edge[:-1])*0.5
+		
+		print edge
+		print telescopegap
+		
+		
 		simlim = (upper + 150)
 		
 		area = 4*(simlim**2)
@@ -148,8 +155,8 @@ def run(numberofhours):
 	print bins
 
 	plt.legend(loc=2)
-	plt.xlabel('Grid width (m)', labelpad=0)
-	plt.ylabel('Count', labelpad=0)
+	plt.xlabel('Grid width (m)', fontsize=20, labelpad=0)
+	plt.ylabel('Count', fontsize=20, labelpad=0)
 	
 	ax2 = plt.subplot(212)
 	
@@ -202,9 +209,12 @@ def run(numberofhours):
 		
 	plt.legend()
 	
-	plt.xlabel('Grid width (m)', labelpad=0)
-	plt.ylabel('Count', labelpad=0)
+	plt.xlabel('Grid width (m)', fontsize=20, labelpad=0)
+	plt.ylabel('Count', fontsize=20, labelpad=0)
 	plt.yscale('log')
+	
+	ax1.tick_params(labelsize=20)
+	ax2.tick_params(labelsize=20)
 	
 	title = "Telescope Observations for " +str(numberofhours) + " hours"
 	
@@ -214,3 +224,4 @@ def run(numberofhours):
 	figure.set_size_inches(20, 15)	
 	
 	plt.savefig('graphs/stats/optimiselayout.pdf')
+	plt.savefig('/afs/desy.de/user/s/steinrob/Documents/DESY/presentations/dpg presentation/optimiselayout.png')

### 2016-03-02 positioning/optimisez.py

@@ -39,11 +39,11 @@ def run(source, detectorcount, mindetections, graph=False):
 		
 		frac=0
 		
-		for i in range(2, len(llrange)):
+		for i in range(1, len(llrange)):
 			ll = llrange[i]
 			currentsigma = 5		
 			best=['nope']
-			for k in range(0, i-2):
+			for k in range(i-10, i-1):
 				specificcount = []
 				minll=llrange[k]	
 				with open("/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/reconstructeddata/"+ str(source) +".csv", 'rb') as csvfile:
@@ -92,17 +92,29 @@ def run(source, detectorcount, mindetections, graph=False):
 						lowerz = specificcount[0]
 						upperz = specificcount[total-1]
 						meansigma = (float(upperz)-float(lowerz))/(2*sigmas)
+
+						#~ lower = int(total*0.16)
+						#~ upper = int(total*0.84)
+						#~ 
+						#~ lowerz = specificcount[lower]
+						#~ upperz = specificcount[upper]
+						#~ sixtyeightsigma = (upperz-lowerz) * 0.5
+						
+						#~ if extremesigma < sixtyeightsigma:
+							#~ meansigma = sixtyeightsigma
+						#~ else:
+							#~ meansigma = extremesigma
 						
 						
 						if float(meansigma) > float(currentsigma):
 							pass
 							
-						elif fraction > 0.3:
+						elif fraction > 0.05:
 							if int(lowerz) > int(26):
 								pass
 							elif int(26) > int(upperz):
 								pass
-							else: 
+							else:
 								best = [meansigma, sigmas, ll, minll, total, specificcount, fraction]
 							
 			if len(best) > 1:

### 2016-03-03 report/draft1.tex
Backup 3/3/16

@@
 \section{Lateral Photon Distribution Method}
-In order to reconstruct events using the LPD method, we require the Energy of the Cosmic Ray lie in the saturated region, and that the event can be seen by at least 4 telescopes.
+In order to reconstruct events using the LPD method, we require saturation of the Cosmic Ray Energy, and that the event can be seen by at least 4 telescopes.
 These restrictions confine us to Cosmic Rays with specific characteristics.
 
-\subsection{Cherenkov Light Emission}
-Cosmic Rays follow a well-defined power law where $ \frac{dN_{E}}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ? $. Consequently higher energy Cosmic Rays are heavily suppressed.
+\subsection{First Interaction Height}
+Cosmic Rays survival in from the top of the atmosphere follows an exponential decay with the number of 'interaction lengths' passed.
+The interaction length is dependent on the interaction cross section, which increases with density.
+Thus the number of interaction lengths increases exponentially as height decreases.
+The resultant decays occur most often at a height of $h \approx 40 \pm 10$ km , as seen in \ref{fig:generalheight}.
 
-The energy Threshold as a function of height is illustrated in
+\begin{figure}
+\begin{center}
+\includegraphics[height=0.9\textheight]{generalheight}
+\caption{The integrated interaction lengths increases as height decreases.
+Thus the decay probability follows a exponentially increasing distribution.
+The mean first interaction height for all events is roughly 40km above sea level.}
+\label{fig:generalheight}
+\end{center}
+\end{figure}
 
-Once a Cosmic Ray crosses the Threshold Energy, it will begin emitting Cherenkov Light, and will stop emitting Cherenkov Light when it first interacts at a height $h$.
-For a given Telescope Array altitude above sea level, simple trigonometry yields:
-\[ Radius(height = altitude_{array}) = \tan (\theta_{C}(h)) \times (h - altitude_{array})\]
+\subsection{Energy Considerations}
+Cosmic Rays follow a well-defined power law where $ \frac{dN(E)}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ?
+$.
+Consequently higher energy Cosmic Rays are heavily suppressed.
+The Energy Threshold for Cherenkov Light Emission as a function of height is illustrated in \ref{fig:generalenergy}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=0.9\textheight]{logenergyradius}
+\caption{The Threshold Energy for Cherenkov Emission is marked in blue.
+With the assumption of $\beta=1$, the maximum emission radius is marked in black.
+The red and green and magenta line show the emission radius at 3.57 and 0.75 and 0.23 TeV per Nucleon respectively.
+The Green line is sufficiently close to the background to be saturated at 24km, while the magenta line is not.}
+\label{fig:generalenergy}
+\end{center}
+\end{figure}
+
+Once the Energy Threshold falls below the Cosmic Ray Energy, the Nucleus will begin emitting Cherenkov Light.
+It will stop emitting when it first interacts, at a randomly distributed height we call $h$.
+Then for a given Telescope Array altitude above sea level, simple trigonometry yields:
+\[ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})\]
 As the Refractive Index of the Earth increases as height decreases, the angle $\theta_{C}$ increases with decreasing height.
@@
 
-In figure Y, we see ground emission radius as a function of height.
-It is clear that the high-radius emission, (occurring near the first interaction region) is virtually unchanged for different Energies.
-We deem this to be 'saturated emission'.
+We can also see ground emission radius as a function of height in \ref{fig:generalenergy}.
+It is clear that the high-radius emission, (occurring near the first interaction region) is virtually unchanged for high Energies.
+We deem this to be \textquoteleft saturated emission\textquoteright.
 
@@
 
+To overcome this problem, we can iterate over a series of starting values for the parameters, with the aim of scanning the true minimum among the many found.
+To simplify matters, we can scan only the integer Z values over the range $ 20 \leq Z \leq 32 $, rather than considering the charge to be a free floating parameter.
+
+In order to reduce the number of calculations needed, we can consider the core position region derived from camera images, as in Hillas Analysis.
+Each telescope will have a Gaussian smeared central axis indicating the direction of the core.
+We overlay the simulated telescope array with a grid of points with grid width 1m.
+Then we select all points satisfy the condition of lying within the shower axis direction confidence interval for every telescope.
+The angular width of the confidence interval from the shower axis will be determined by the precision of the telescopes.
+
+Having determined the relevant Height and Energy ranges, we can then consider combinations of Energy and Height for which the Energy is above the Cherenkov Emission Threshold (and is saturated!).
+This gives us a second set of starting \textquoteleft Coordinates \textquoteright.
+
+The Z value is fixed and the LL function is then minimised with the assigned starting values, with the other four variables allowed to float freely.
+Minimisation typically scans 13 Z values, 10 core position coordinates, and 50 Height/Energy coordinates, yielding $ 13 \times 10 \times 50 = 6500$ minimisations in total.
+Such a techinique is resource intensive but reduces $\sigma_{Z}$ by a factor of 5 or more.
+(CHECK this quantitatively and get a graph yo.
+Want to see some plateauing of sigma Z!).
+
+\subsection{Extracting Charge Resolution}
+
+Having reconstructed many events, we can then consider the $\sigma_{Z}$ of the dataset.
+The Z distribution is a binned Gaussian, but due to the Integer nature of the reconstruction, a standard 68\% values method will be constrained to half integer values for $\sigma_{Z}$.
+
+A large Monte Carlo simulation can also provide optimised values for Log Likelihood cuts that can be applied to datasets, reducing the $\sigma_{Z}$ further.
+
 \section{HESS-type Event Reconstruction}
 
-\subsection{First Interaction Height}
-Cosmic Rays survival in from the top of the atmosphere follows an exponential decay with the number of 'interaction lengths' passed.
-The interaction length is dependent on the interaction cross section, which increases with density.
-Thus the number of interaction lengths increases exponentially as height decreases .
-
-The resultant decays occur most often at a height of $h \approx 40 \pm 10$ km.
-However, when the HESS layout is simulated, the 4 telescope events have a mean height of $h \approx 24 \pm 4$ km, as shown in \ref{fig:Height Statistics}.
+\subsection{First Interaction and Energy Saturation}
+The mean first interaction height for all Cherenkov Emitting Cosmic Rays in the atmosphere is 40km???, and neglecting variations in atmospheric density profiles around the Earth, this can be considered independent of experimental array.
+However, the multiplicity of event is determined by equipment efficiencies, altitude and telescope layout.
+When the HESS layout is simulated, we find that the 4 telescope events have a mean height of $h \approx 23 \pm 5$ km, as shown in \ref{fig:Hessheight}.
 
@@
 \begin{center}
-\includegraphics[height=0.9\textheight]{height}
-\caption{The integrated interaction lengths increases as height decreases.
-Thus the decay probability follows a exponentially increasing distribution.
-The first interaction height for all events peaks at around 40000m.
-However the mean first interaction height for 4 telescope events is 23000m}
-\label{fig:Height Statistics}
+\includegraphics[height=0.9\textheight]{hessheight}
+\caption{The mean first interaction height for all Cherenkov Events is 40km???. The mean first interaction height for 4 telescope events in the HESS array is 23km}
+\label{fig:Hessheight}
 \end{center}
@@
 \subsection{HESS Energy saturation region}
-It be like 0.7 Tev per Nucleon!
-
 However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon fig Y!
@@
 \subsection{Count Rates}
+We can consider a 3x3 array of Cherenkov Telescopes of 12m diameter, which we want to use for identifying Cosmic Ray Elements accurately.
+In \ref{fig:optmiselayout} we see that the \textquoteleft Good Count Rate' of events observed by sufficient telescopes falls with increasing grid separation.
+We can clearly see that the optimum grid spacing will lie in the 20-50m region to provide a reasonable count rate.
+
+Competing with this effect is the reliance of LPD reconstruction on sampling the entire lateral distribution. Thus the charge resolution will increase as Grid Width decreases.
+
+A further analysis of $\sigma_{Z}$ in this region is required to determine the true optimum.
+
+Other shapes?
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{optimiselayout}
+\caption{A simulation of 50 hours of run time for various grid spacing for a 3x3 telescope array.
+Although raw count rate increases with increasing grid width, the \textquoteleft good count' rate of events observed by sufficient telescopes falls rapidly with increasing grid width}
+\label{fig:optmiselayout}
+\end{center}
+\end{figure}
 

### 2016-03-03 positioning/epnstatistics.py

@@ -13,11 +13,13 @@ import atmosphere as atm
 import cherenkovradius as cr
 from matplotlib.patches import Ellipse
 
+altitude = 1800
+
 def run(eff, rowcount, mincount=4, text=False, graph=False, layout="five", number=1, nh=1):
 	
 	#Create a subplot for the fractional abundance
 
-	ax1 = plt.subplot(221)
+	ax1 = plt.subplot(211)
 	
 	#Define number of bins, maximum Epn
 	
@@ -118,7 +120,7 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, layout="five", numbe
 	
 	#plot the histogram scaled with E^-2.7 distribution to the second subplot
 	
-	ax2 = plt.subplot(223)
+	ax2 = plt.subplot(212)
 		
 	plt.hist([mT, bT, nDC], weights=[wmT, wbT, wnDC], log=True, bins=Erange, histtype='bar',range=limits, label=labels)
 
@@ -129,21 +131,34 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, layout="five", numbe
 	plt.ylabel('Scaled Count')
 	plt.legend()
 	
+	fig = plt.gcf() # get current figure
+	title = 'Epn Statistics for ' + str(float(nh)*float(bincount)) + " hours"
+	st = plt.suptitle(title, fontsize=20)
+	st.set_y(0.98)
+	fig.set_size_inches(10, 15)
+	fig.tight_layout()
+	fig.subplots_adjust(top=0.95)
+	
+	plt.savefig('/afs/desy.de/user/s/steinrob/Documents/DESY/report/graphs/energystats.png')
+	
+	plt.close()
+
+	
 	#Plot variables Etheshold and Ring Radius againist height
 	
-	ax3 = plt.subplot(111)
+	ax3 = plt.subplot(211)
 	
 	rawheights=[]
 	emin=[]
 	rmax = []
 	
-	Erange = [3571, 850]
+	Erange = [3521, 750, 232]
 	
 	labels = [" = Infinity "]
 	for e in Erange:
 		labels.append(" = " + str(e))
 		
-	colors=["k", "r", "g"]
+	colors=["k", "r", "g", "m", "c", "b"]
 	
 	nucleonmass = 0.93827 
 	
@@ -179,14 +194,12 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, layout="five", numbe
 				
[…]

### 2016-03-22 report/summary.tex
Backup 22/3/16

--- 2016-03-02 report/draft1.tex
@@
 \graphicspath{ {graphs/} }
+\usepackage{geometry}
+\geometry{a4paper, portrait, margin=1in}
 \begin{document}
-\begin{titlepage}
-    \begin{center}
-        \vspace*{1cm}
+\title{Reconstruction of Charge Number of Heavy Cosmic Rays using Cherenkov Light}
+\author{Robert Stein}
+\maketitle
+\section{Introduction}
+There are numerous Telescope Arrays which image the Cherenkov Light emitted by Cosmic Rays (CRs) in the atmosphere, all relying on Hillas Analysis for event reconstruction.
+Hillas Analysis extracts parameters from each of the camera images in order to reconstruct the events, but heavy blurring of the events by atmospheric effects means that resolution is very poor.
+For a typical Iron Nucleus event \cite{hess07}, the charge would be reconstructed as $Z \approx 26 \pm 5 $.
 
-        \Huge
-        \textbf{Reconstruction of Charge Number of Heavy Cosmic Rays using Cherenkov Light}
+The imaged CRs have energies between $13 $TeV and $200 $TeV and, at present, no study of the relative abundance of different cosmic ray elemental abundances exists for these energies.
+It could provide important clues regarding the mechanism of CR formation and propagation in the galaxy but current charge resolution from Hillas Analysis is not small enough to undertake such a study.
 
-        \LARGE
-
-        \vspace{1cm}
-
-        \textbf{Robert Stein}\\
-        \textbf{CID 00819615}
-
-        \vspace{1cm}
-        \includegraphics[width=0.4\textwidth]{Imperial_College_London_logo} 
-        \hspace{0.5cm}
-        \includegraphics[width=0.4\textwidth]{hamburglogo}
-
-        \vspace{1cm}
-
-        Supervisor: Professor Dieter Horns
-
-        \large
-        \vspace{1.0cm}
-
-        A thesis presented for the degree of\\
-        \textbf{Master in Science}
-
-        \vspace{0.5cm}
-
-        Physics Department\\
-        Imperial College London
-
-        \vspace{0.5cm}
-
-        \today
-
-    \end{center}
-\end{titlepage}
-\section*{Abstract}
-Between impact with the upper atmosphere and decay into a charged particle shower, heavy cosmic ray elements such as Iron emit Cherenkov Light at an angle determined by the Refractive Index of the air and the energy per nucleon.
-This direct Cherenkov Light forms a characteristic circular light distribution on the Earth's surface with an intensity proportional to the square of the cosmic ray charge.
-A new method has been developed to reconstruct this charge number, by fitting the received Cherenkov Photons to the characteristic Lateral Photon Distribution.
-The expected performance for various existing and planned installations will be discussed.
-
-\section*{Zusammenfassung}
-Between impact with the upper atmosphere and decay into a charged particle shower, heavy cosmic ray elements such as Iron emit Cherenkov Light at an angle determined by the Refractive Index of the air and the energy per nucleon.
-This direct Cherenkov Light forms a characteristic circular light distribution on the Earth's surface with an intensity proportional to the square of the cosmic ray charge.
-A new method has been developed to reconstruct this charge number, by fitting the received Cherenkov Photons to the characteristic Lateral Photon Distribution.
-The expected performance for various existing and planned installations will be discussed.
-\newpage
-\tableofcontents
-\newpage
-\section{Introduction}
-There are numerous Telescope Arrays which image the Cherenkov Light emitted by Cosmic Rays in the atmosphere, including the HESS, Magic and Veritas Experiments.
-All such Imaging Atmospheric Cherenkov Telescopes (IACTs) rely on Hillas Analysis for event reconstruction.Hillas Analysis extracts parameters from each of the camera images in order to reconstruct the events.
-However, heavy blurring of the events by atmospheric effects means that resolution of reconstruction  is very poor.
-For a typical Iron Nucleus event \cite{hess07}, the core position resolution is roughly $d \approx 20 m $, and the charge would be reconstructed as \[Z \approx 26 \pm 5 \]
-
-Cosmic Rays that are imaged by these telescopes have energies between $13 $TeV and $200 $TeV.
-At present, no study of the relative abundance of different cosmic ray elemental abundances exists, although it could provide important clues regarding the mechanism of Cosmic Ray formation and propagation in the galaxy.
-Unfortunately, current charge resolution from Hillas Analysis is not small enough to undertake such a study.
-
-Instead of Hillas Analysis, we consider a new method for event reconstruction, in which we fit the known Direct Cherenkovn (DC) Light observed by each telescope to a characteristic Lateral Photon Distribution (LPD) function.
-This new technique is valid both for currently running experiments, as well as planned experiments such as the Cherenkov Telescope Array (CTA).
-It uses only the information from the DC Pixel identified in the shower images.
-
-A theoretical study by Kieda in 2001 \cite{kieda01} suggested that for a core position resolution of $d \approx 5 $ m , we could expect to see a charge resolution of $ \sigma_{Z} \approx 1 $ for elements of $Z = 20$ or higher.
-In this case the core resolution would be the limiting value.
-Thus, if the LPD method can achieve this core position resolution, then charge resolution will become sufficiently good enough to extract the abundances of the different Cosmic Ray Elements.
-This the prime motivation for the new LPD technique.
+We consider a new method for event reconstruction, in which we fit the known Direct Cherenkovn (DC) Light observed by each telescope to a characteristic Lateral Photon Distribution (LPD) function.
+If the LPD method can achieve a resolution $ \sigma_{Z} \approx 1 $ for elements of $Z = 20$ or higher, this will be precise enough to extract the abundances of the different CR Elements.
+This the prime motivation for introducing the new LPD technique.
 
 \section{Lateral Photon Distribution Method}
-In order to reconstruct events using the LPD method, we require the Energy of the Cosmic Ray lie in the saturated region, and that the event can be seen by at least 4 telescopes.
+In order to reconstruct events using the LPD method, we require saturation of the Cosmic Ray Energy, and that the event can be seen by at least 4 telescopes.
 These restrictions confine us to Cosmic Rays with specific characteristics.
 
-\subsection{Cherenkov Light Emission}
-Cosmic Rays follow a well-defined power law where $ \frac{dN_{E}}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ? $. Consequently higher energy Cosmic Rays are heavily suppressed.
-
-The energy Threshold as a function of height is illustrated in
-
-Once a Cosmic Ray crosses the Threshold Energy, it will begin emitting Cherenkov Light, and will stop emitting Cherenkov Light when it first interacts at a height $h$.
-For a given Telescope Array altitude above sea level, simple trigonometry yields:
-\[ Radius(height = altitude_{array}) = \tan (\theta_{C}(h)) \times (h - altitude_{array})\]
+Cosmic Rays interactions occur most often at a height of $h \approx 40 \pm 10$ km, and neglecting variations in atmospheric density profiles around the Earth, this can be considered independent of experimental array.
+The CR energies follow a well-defined power law where $ \frac{dN(E)}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ?
+$.
+Consequently higher energy CRs are heavily suppressed.
+Once the Energy Threshold falls below the CR Energy, the Nucleus will begin emitting Cherenkov Light.
+It will stop emitting when it first interacts, at a randomly distributed height we call $h$.
+Then for a given Telescope Array altitude above sea level, simple trigonometry yields:
+\[ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})\]
 As the Refractive Index of the Earth increases as height decreases, the angle $\theta_{C}$ increases with decreasing height.
 Thus the upper earlier emission contributes to the inner LPD, while the later emission contributes to the high-radius LPD.
+We find that the high-radius emission, (occurring near the first interaction region) varies little between different high energies.
+We deem this to be \textquoteleft saturated emission\textquoteright.
 
-In figure Y, we see ground emission radius as a function of height.
-It is clear that the high-radius emission, (occurring near the first interaction region) is virtually unchanged for different Energies.
-We deem this to be 'saturated emission'.
+We see that the amplitude of the 'signal' LPD varies with $ \rho_{DC}  = f(r) \times Z^{2}$.
+Thus the amplitude of the LPD is proportional to the charge of the Cosmic Ray, enabling the Charge to be determined from the DC emission.
+This is the basis for charge reconstruction in the LPD method.
 
-\subsection{Nuclear Charge}
-In figure Z we see that the height of the 'signal' LPD varies with \[ \rho_{DC}  = f(r) \times Z^{2}\]
-
-Thus the height of the LPD is proportional to the charge of the Cosmic Ray, enabling the Charge to be determined from the DC emission. This is the basis for charge reconstruction in the LPD method.
-
-\subsection{Iterative Log Likelihood Minimisation}
 In order to reconstruct an event, we need to find the x/y core position, the Energy per Nucleon, the first interaction height and the charge.
@@
 
-We consider the amount of DC light that each telescope receives to be Poissonian \[  P_{i} ( N_{i, Received} \mid X, Y, Z, height, Epn )  =  \frac{ e^{- \lambda_{i} } \times \lambda_{i} ^{N_{i}} }{N_{i}!} \]
-
-In order to reduce computing time, we can use Stirling's Approximation $ln( N!
-)  \approx  N ln(N) - N + \frac{1}{2} ln(2 \pi N)$.
-Pure night sky background requires that there be more that X photons in a DC pixel, and for this Stirling's Approximation has an error of just Y?.
+We consider the amount of DC light that each telescope receives to be Poissonian and can use Stirling's Approximation to reduce computing time.
 We then minimise the Log Likelihood function \[ - Ln(L) = - \sum_{i=1}^{n} [P_{i}] \approx  \sum_{i=1}^{n} [\lambda _{i} - N_{i} ln(\lambda _{i}) + N_{i} ln(N_{i}) - N_{i} + \frac{1}{2} ln(2 \pi N_{i})]  \]
@@
 Consequently, a Minuit-type minimisation algorithm will only be able to find a local minimum near the starting values for the fit parameters.
+To overcome this problem, we can iterate over a series of starting values for the parameters, with the aim of scanning the true minimum among the many found.
+To simplify matters, we can scan only the integer Z values over the range $ 20 \leq Z \leq 32 $, rather than considering the charge to be a free floating parameter.
+
+The Z value is fixed and the LL function is then minimised with the assigned starting values, with the other four variables allowed to float freely.
+Minimisation typically scans 13 Z values, 10 core position coordinates, and 50 Height/Energy coordinates, yielding $ 13 \times 10 \times 50 = 6500$ minimisations in total.
+Such a technique is very resource intensive but reduces $\sigma_{Z}$ by a factor of 5 or more.
+
+Having reconstructed many events, we can then consider the $\sigma_{Z}$ of the dataset.
+A large Monte Carlo simulation can also provide optimised values for Log Likelihood cuts that can be applied to datasets, reducing the $\sigma_{Z}$ further.
 
 \section{HESS-type Event Reconstruction}
+We can consider a simulation of the HESS Cherenkov Telescope Array to verify the accuracy of the technique.
+When the HESS layout is simulated, we find that the 4 telescope events have a mean height of $h \approx 23 \pm 5$ km.
 
-\subsection{First Interaction Height}
-Cosmic Rays survival in from the top of the atmosphere follows an exponential decay with the number of 'interaction lengths' passed.
-The interaction length is dependent on the interaction cross section, which increases with density.
-Thus the number of interaction lengths increases exponentially as height decreases .
-
-The resultant decays occur most often at a height of $h \approx 40 \pm 10$ km.
-However, when the HESS layout is simulated, the 4 telescope events have a mean height of $h \approx 24 \pm 4$ km, as shown in \ref{fig:Height Statistics}.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=0.9\textheight]{height}
-\caption{The integrated interaction lengths increases as height decreases.
-Thus the decay probability follows a exponentially increasing distribution.
-The first interaction height for all events peaks at around 40000m.
-However the mean first interaction height for 4 telescope events is 23000m}
-\label{fig:Height Statistics}
-\end{center}
-\end{figure}
-
-\subsection{HESS Energy saturation region}
-It be like 0.7 Tev per Nucleon!
-
-However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon fig Y!
+However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon.
 The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...
 
-\subsection{Extended Air Shower Background}
-A typical HESS image is shown in \ref{fig:hess}, with the DC pixel visible.
 The Extended Air Shower (EAS) produced after the first interaction of the Cosmic Ray overlaps the DC pixel, leading to background in the LPD.
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{hess}
-\caption{A 4-camera HESS event.
-The shower direction is marked with a white cross, and the DC pixel is indicated with a white arrow.
-The shower axis passes through the shower direction, the DC pixel, and the center of the Extensive Air Shower region lying beyond the DC pixel.}
-\label{fig:hess}
-\end{center}
-\end{figure}
+In addition, we have a fixed night sky background with 7 photons $m^{-2}$. We thus parameterise the background with 
+$ \rho_{bkg}  = (7 + 5E) m^{-2}$. It begins to dominate above roughly 1 TeV per Nucleon, particularly in the case of smaller radii.
 
-In addition, we have a fixed night sky background with 7 photons $m^{-2}$. We thus parameterise the background with 
-\[ \rho_{bkg}  = 7 + 5E\]
-The modeled background LPD is shown in X. It begins to dominate above roughly 1 TeV per Nucleon, particularly in the case of smaller radii.
+In the preliminary HESS simulation, it was found that the 4 telescope event reconstruction had a charge resolution of $\sigma_{Z} = 2.4$.
+However, requiring that the Log Likelihood satisfied $L.L < 23.5$ removed just $17 \%$ of events, while reducing the Charge resolution to $\sigma_{Z} = 0.4$ .
+With this cut, core position resolution was $d \approx 2 m $.
+
+For 5 telescope events, it was found that the charge resolution was $\sigma_{Z} = 1.0$.
+However, requiring that the Log Likelihood satisfied $L.L < 23.0$ removed $47 \%$ of events, including all wrongly reconstructed ones.
+This placed an upper limit on the charge resolution to $\sigma_{Z} < 0.3$ .
+With this cut, core position resolution was $d \approx 1 m $.
 
 \section{Optimised Telescope Array}
-NO Background!!!!!
-\subsection{Count Rates}
 
-\subsection{Saturation Region Energies}
+We can consider a 3x3 array of Cherenkov Telescopes of 12m diameter, which we want to use for identifying Cosmic Ray Elements accurately.
+The \textquoteleft Good Count Rate' of events observed by sufficient telescopes falls with increasing grid separation.
+We can clearly see that the optimum grid spacing will lie in the 20-50m region to provide a reasonable count rate.
+
+Competing with this effect is the reliance of LPD reconstruction on sampling the entire lateral distribution.
+Thus the charge resolution will increase as Grid Width decreases.
+A further analysis of $\sigma_{Z}$ in this region is required to determine the true optimum.
 

### 2016-03-22 cluster_input/execute41.py

@@ -1,0 +1,42 @@
+n = 41
+
+import initialise as i
+numberofhours, mincount, reconstructiongridwidth, orientation, eff, flux, area, solidangle, selectionefficiency = i.run()
+
+import sys
+
+sys.path.append('/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/')
+
+import argparse, math, random, time
+import csv
+import numpy as np
+import simulate as s
+import batchprocessing as bp
+import batchreconstruction as br
+
+sourcedata="executedefault" + str(n)
+processdata="executeprocess" + str(n)
+reconstructdata="executereconstructed" + str(n)
+
+
+detectedflux = float(flux)*float(area)*float(solidangle)*float(selectionefficiency)
+rateperhour = detectedflux * 60 * 60
+n = int(rateperhour*float(numberofhours))
+print time.asctime(time.localtime()),"Cosmic Ray Iron Flux is", flux, "Simulated Area is", area, "Field of View is", solidangle, "Detected Flux is", detectedflux
+print time.asctime(time.localtime()),"Rate per hour", rateperhour, "Simulated Hours", numberofhours, "Simulated Events", n 
+
+with open("/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/orientations/"+ orientation +".csv", 'rb') as csvfile:
+	reader = csv.reader(csvfile, delimiter=',', quotechar='|')
+	rowcount = 0
+	for row in reader:
+		rowcount +=1
+
+s.run(eff, rowcount, mincount=mincount, text=False, graph=False, output=sourcedata, layout=orientation, number = n)
+bp.run(sourcedata, processdata, int(mincount), rowcount, text=False)
+br.run(processdata, reconstructdata, rowcount, reconstructiongridwidth, eff)
+
+message = str(time.asctime(time.localtime())) + " Completed simulation of " + str(n) + " events!"
+import os, sys
+import sendemail as se
+name = os.path.basename(__file__)
+se.send(name, message, False)

### 2016-03-22 cluster_input/execute47.py

@@ -1,0 +1,42 @@
+n = 47
+
+import initialise as i
+numberofhours, mincount, reconstructiongridwidth, orientation, eff, flux, area, solidangle, selectionefficiency = i.run()
+
+import sys
+
+sys.path.append('/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/')
+
+import argparse, math, random, time
+import csv
+import numpy as np
+import simulate as s
+import batchprocessing as bp
+import batchreconstruction as br
+
+sourcedata="executedefault" + str(n)
+processdata="executeprocess" + str(n)
+reconstructdata="executereconstructed" + str(n)
+
+
+detectedflux = float(flux)*float(area)*float(solidangle)*float(selectionefficiency)
+rateperhour = detectedflux * 60 * 60
+n = int(rateperhour*float(numberofhours))
+print time.asctime(time.localtime()),"Cosmic Ray Iron Flux is", flux, "Simulated Area is", area, "Field of View is", solidangle, "Detected Flux is", detectedflux
+print time.asctime(time.localtime()),"Rate per hour", rateperhour, "Simulated Hours", numberofhours, "Simulated Events", n 
+
+with open("/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/orientations/"+ orientation +".csv", 'rb') as csvfile:
+	reader = csv.reader(csvfile, delimiter=',', quotechar='|')
+	rowcount = 0
+	for row in reader:
+		rowcount +=1
+
+s.run(eff, rowcount, mincount=mincount, text=False, graph=False, output=sourcedata, layout=orientation, number = n)
+bp.run(sourcedata, processdata, int(mincount), rowcount, text=False)
+br.run(processdata, reconstructdata, rowcount, reconstructiongridwidth, eff)
+
+message = str(time.asctime(time.localtime())) + " Completed simulation of " + str(n) + " events!"
+import os, sys
+import sendemail as se
+name = os.path.basename(__file__)
+se.send(name, message, False)

### 2016-03-22 positioning/batchreconstruction.py

@@ -8,7 +8,7 @@ import calculateellipse as ce
 def run(source, outputfile, detectorcount, rgw, eff):
 	with open("/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/reconstructeddata/" + str(outputfile) + ".csv", 'wb') as csvout:
 		writer = csv.writer(csvout, delimiter=',', quotechar='|')
-		writer.writerow(["Detections","X","Y","Energy Per Nucleon","Z","Height","True X","True Y","True Energy per nucleon","True Z","True Height", "Phi", "Epsilon", "Theta", "Guess Log Likelihood", "True Log Likelihood"])
+		writer.writerow(["Detections","X","Y","Energy Per Nucleon","Z","Height","True X","True Y","True Energy per nucleon","True Z","True Height", "Phi", "Epsilon", "Guess Log Likelihood", "True Log Likelihood"])
 		with open("/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/data/"+ str(source) +".csv", 'rb') as csvfile:
 			reader = csv.reader(csvfile, delimiter=',', quotechar='|')
 			i = 0

### 2016-03-22 positioning/optimisez.py

@@ -5,57 +5,51 @@ import matplotlib.pyplot as plt
 from scipy.optimize import curve_fit
 import scipy.stats
 
-def run(source, detectorcount, mindetections, graph=False):
+def run(source, detectorcount, mindetections, graph=False, allcounts=None):
+
+	plt.figure()
 
 	i=1
 
 	Z = 26
 	
-	upperlim = 150
-	lowerlim = 18
-	bincount=(upperlim-lowerlim)*2 + 1
-	
-	zrange = [19.5, 32.5]
-	reconvalues = np.linspace(zrange[0]+0.5, zrange[1]-0.5, bincount)
-	
-	llrange = np.linspace(lowerlim, upperlim, bincount)
+	BDTrange = np.linspace(0.0, 1.0, 51)
 	annotation = ""
-	llcuts = []
-	llmins=[]
+	
+	optimumcuts = []
 	
 	for j in range (detectorcount, mindetections -1, -1):
-		lowestsigma = 5
-		dataset = 0
-		datawidth = 0
-		text = ""
-		optimumll = 500
-		optimummin=0
-		mincount = 5
-		meansigmas=[]
-		llvalues =[]
+			
+		count = allcounts[detectorcount-j]
 		
-		limitsigmas = []
-		overflowvalues = []
+		testcount = int(float(count)/4.) 
 		
-		frac=0
-		
-		for i in range(1, len(llrange)):
-			ll = llrange[i]
-			currentsigma = 5		
-			best=['nope']
-			for k in range(i-10, i-1):
-				specificcount = []
-				minll=llrange[k]	
+		if int(testcount) > int(1):
+			
+			lowestsigma = 5
+			optimumbdt = 0.0
+			optimumpassing = 1.0
+			
+			meansigmas=[]
+			
+			bdtcuts =[]
+			
+			frac=0
+			
+			
+			for i in range(0, len(BDTrange)):
+				BDTcut = BDTrange[i]
+				
+				currentsigma = 5
+				specificcount = []	
 				with open("/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/reconstructeddata/"+ str(source) +".csv", 'rb') as csvfile:
 					reader = csv.reader(csvfile, delimiter=',', quotechar='|')
 					full = 0
 					passing = 0
 					
-					i=0
+					i=-1
 					for row in reader:
-						if i == 0:
-							i = 1
-						else:
+						if testcount < i < (2*testcount):
 							detections = row[0]
[…]

### 2016-03-22 positioning/reconstruction.py

@@ -1,4 +1,4 @@
-import argparse, math, random, time
+import argparse, math, random, time, sys
 import csv
 import numpy as np
 import simulate as s
@@ -16,6 +16,7 @@ import lightstatistics as ls
 import plotlikelihood as pl
 import optimisez as oz
 import optimiselayout as ol
+import categorycounts as cc
 
 parser = argparse.ArgumentParser(description='Create a canvas for positions of telescopes')
 parser.add_argument("-o", "--orientation", default="five")
@@ -49,9 +50,9 @@ n = int(rateperhour*float(cfg.numberofhours))
 defaultcuts = [500, 500]
 
 if cfg.data == "default":
-	sourcedata="simulated" + str(cfg.mincount)
-	processdata = "processed"+ str(cfg.mincount)
-	reconstructdata = "reconstructed"+ str(cfg.mincount)
+	sourcedata="executesimulated_combined"
+	processdata = "executeprocessed_combined"
+	reconstructdata = "executereconstructed_combined"
 	
 else:
 	sourcedata= str(cfg.data) + "simulated" + str(cfg.mincount)
@@ -78,12 +79,19 @@ if cfg.simulate:
 	se.send(name, message)
 	
 if cfg.plotcut:
-	llcuts = oz.run(reconstructdata, rowcount, int(cfg.mincount), cfg.graph)
-	pl.run(reconstructdata, cfg.graph, llcuts)
-	pz.run(reconstructdata, rowcount, int(cfg.mincount), cfg.graph, llcuts)
-	pp.run(reconstructdata, rowcount, int(cfg.mincount), cfg.graph, llcuts)
-	pe.run(reconstructdata, rowcount, int(cfg.mincount), cfg.graph, llcuts)
-	ph.run(reconstructdata, rowcount, int(cfg.mincount), cfg.graph, llcuts)
+	allcounts = cc.run(reconstructdata, rowcount, int(cfg.mincount))
+	
+	sys.path.append('/home/steinrob/Documents/DESY/BDT')
+	import BDT
+	BDT.run(reconstructdata, rowcount, int(cfg.mincount), allcounts)
+	
+	llcuts = oz.run(reconstructdata + "_BDT", rowcount, int(cfg.mincount), cfg.graph, allcounts)
+	print llcuts
[…]

### 2016-03-22 report/summary.tex
Backup 22/3/16

@@
 
-We consider a new method for event reconstruction, in which we fit the known Direct Cherenkovn (DC) Light observed by each telescope to a characteristic Lateral Photon Distribution (LPD) function.
+We consider a new method for event reconstruction, in which we fit the known Direct Cherenkov (DC) Light observed by each telescope to a characteristic Lateral Photon Distribution (LPD) function.
 If the LPD method can achieve a resolution $ \sigma_{Z} \approx 1 $ for elements of $Z = 20$ or higher, this will be precise enough to extract the abundances of the different CR Elements.
@@
 \section{Lateral Photon Distribution Method}
-In order to reconstruct events using the LPD method, we require saturation of the Cosmic Ray Energy, and that the event can be seen by at least 4 telescopes.
+In order to reconstruct events using the LPD method, we require saturation of the CR Energy, and that the event can be seen by at least 4 telescopes.
 These restrictions confine us to Cosmic Rays with specific characteristics.

### 2016-03-22 cluster_input/combinedatasets.py

@@ -1,6 +1,7 @@
 #!/bin/env python
 
 import sys
+import os.path
 
 afspath = '/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/'
 
@@ -10,7 +11,7 @@ import argparse, math, random, time
 import csv
 import numpy as np
 
-nparrallel = 30
+nparrallel = 50
 
 targetfolder = "reconstructeddata/"
 
@@ -26,21 +27,23 @@ with open(afspath + targetfolder + batchname + "_combined.csv", 'wb') as csvout:
 		filename= batchname + str(i)
 		path = afspath + targetfolder + filename + ".csv"
 		
-		print "Adding", path
-
-		with open(path, 'rb') as csvfile:
-			reader = csv.reader(csvfile, delimiter=',', quotechar='|')
-			
-			for row in reader:
-				if j == -1:
-					writer.writerow(row)
-					j = 1
-				elif j == 1:
-					writer.writerow(row)
-				elif j == 0:
-					j = 1
-					pass
-			
+		if os.path.isfile(path):
+		
+			print "Adding", path
+	
+			with open(path, 'rb') as csvfile:
+				reader = csv.reader(csvfile, delimiter=',', quotechar='|')
+				
+				for row in reader:
+					if j == -1:
+						writer.writerow(row)
+						j = 1
+					elif j == 1:
+						writer.writerow(row)
+					elif j == 0:
+						j = 1
+						pass
+				
 			j = 0
 			
 	filename= batchname + "_saved"

### 2016-03-22 cluster_input/plotcombined.py

@@ -21,9 +21,13 @@ import plotangle as pa
 import plotheight as ph
 import plotlikelihood as pl
 import optimisez as oz
+import categorycounts as cc
 
 import initialise as i
 numberofhours, mincount, reconstructiongridwidth, orientation, eff, flux, area, solidangle, selectionefficiency = i.run()
+
+sys.path.append('/home/steinrob/Documents/DESY/BDT')
+import BDT
 
 with open(afspath + "/orientations/"+ orientation +".csv", 'rb') as csvfile:
 	reader = csv.reader(csvfile, delimiter=',', quotechar='|')
@@ -33,12 +37,17 @@ with open(afspath + "/orientations/"+ orientation +".csv", 'rb') as csvfile:
 		
 reconstructdata = batchname + "_combined"
 
-llcuts, llmins = oz.run(reconstructdata, rowcount, int(mincount), graph=False)
+
+pz.run(reconstructdata, rowcount, int(mincount), graph=False, cuts=None)	
+allcounts = cc.run(reconstructdata, rowcount, int(mincount))
+print allcounts
+
+BDT.run(reconstructdata, rowcount, int(mincount), allcounts)
+
+llcuts = oz.run(reconstructdata + "_BDT", rowcount, int(mincount), graph=False, allcounts=allcounts)
 print llcuts
-print llmins
-pl.run(reconstructdata, rowcount, int(mincount), graph=False, llcuts=llcuts, llmins=llmins)
-pz.run(reconstructdata, rowcount, int(mincount), graph=False, llcuts=None)
-pz.run(reconstructdata, rowcount, int(mincount), graph=False, llcuts=llcuts, llmins=llmins)
-pp.run(reconstructdata, rowcount, int(mincount), graph=False, llcuts=llcuts)
-pe.run(reconstructdata, rowcount, int(mincount), graph=False, llcuts=llcuts)
-ph.run(reconstructdata, rowcount, int(mincount), graph=False, llcuts=llcuts)
+pl.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
+pz.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
+pp.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
[…]

### 2016-03-22 positioning/plotepn.py

@@ -3,20 +3,31 @@ import csv
 import numpy as np
 import matplotlib.pyplot as plt
 
-def run(source, detectorcount, mindetections, graph, llcuts):
+def run(source, detectorcount, mindetections, graph, cuts, allcounts):
 	fullcount=[]
 	labels=[]
 	info = ""
 	k=0
 	for j in range (detectorcount, mindetections -1, -1):
 		specificcount=[]
+		if allcounts != None:
+			count = allcounts[detectorcount-j]
+			testcount = int(float(count)/4.) 
+					
+		else:
+			testcount = 0
+		
 		with open("/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/reconstructeddata/"+ str(source) +".csv", 'rb') as csvfile:
 			reader = csv.reader(csvfile, delimiter=',', quotechar='|')
-			i = 0
-			upperll=llcuts[k]
+			specificcount = []
+			
+			i = -1
+			
+			bdtmin = cuts[k]
+
 			for row in reader:
-				if i == 0:
-					i = 1
+				if i < (2*testcount):
+					i += 1
 				else:
 					detections = row[0]
 					reconx = float(row[1])
@@ -30,9 +41,10 @@ def run(source, detectorcount, mindetections, graph, llcuts):
 					trueZ = row[9]
 					trueHeight = row[10]
 					likelihood = row[13]
+					BDT = row[15]
 					
 					if int(detections) == int(j):
-						if float(likelihood) < float(upperll):
+						if float(BDT) < float(bdtmin):
 							difference = (reconEPN-trueEPN)/trueEPN
 							specificcount.append(difference)
 

### 2016-03-22 positioning/plotz.py

@@ -16,7 +16,7 @@ def run(source, detectorcount, mindetections, graph, cuts=None, allcounts=None):
 	reconvalues = np.linspace(zrange[0]+0.5, zrange[1]-0.5, bincount)
 	
 	if cuts == None:
-		cuts = np.ones(1 + detectorcount-mindetections)*500
+		cuts = np.zeros(1 + detectorcount-mindetections)
 		path = '/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/graphs/rawZ.pdf'
 	else:
 		path = '/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/graphs/Z.pdf'
@@ -41,9 +41,14 @@ def run(source, detectorcount, mindetections, graph, cuts=None, allcounts=None):
 		
 		for j in range (detectorcount, mindetections -1, -1):
 			
-			count = allcounts[detectorcount-j]
+			if allcounts != None:
+				count = allcounts[detectorcount-j]
+				testcount = int(float(count)/4.) 
+						
+			else:
+				testcount = 0
 		
-			testcount = int(float(count)/4.) 
+			print j
 			
 			with open("/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/reconstructeddata/"+ str(source) +".csv", 'rb') as csvfile:
 				reader = csv.reader(csvfile, delimiter=',', quotechar='|')
@@ -72,18 +77,23 @@ def run(source, detectorcount, mindetections, graph, cuts=None, allcounts=None):
 						trueZ = row[9]
 						trueHeight = row[10]
 						likelihood = row[13]
-						BDT=row[15]
+						
+						if allcounts != None:
+							BDT=row[15]
+						
+						else:
+							BDT = 1.0
 						
 						
 						if int(detections) == int(j):
 							if int(z) == int(trueZ):
 								full += 1
-								if float(bdtmin) < float(BDT):
+								if float(bdtmin) > float(BDT):
 									passing += 1
 									specificcount.append(float(reconZ))
 											
 				label = str(j) + " detections"
-					
+
 				fullcount.append(specificcount)
 				labels.append(label)
 				
@@ -162,6 +172,7 @@ def run(source, detectorcount, mindetections, graph, cuts=None, allcounts=None):
 	plt.legend()
 	
 	plt.savefig(path)
+	print "saving to", path
 		
 	if graph:
 		plt.show()

### 2016-03-29 report/summary.tex
Backup 29/3/16

@@
 \usepackage{geometry}
-\geometry{a4paper, portrait, margin=1in}
+\geometry{a4paper, portrait, margin=1.0in}
 \begin{document}
@@
 \section{Lateral Photon Distribution Method}
-In order to reconstruct events using the LPD method, we require saturation of the CR Energy, and that the event can be seen by at least 4 telescopes.
-These restrictions confine us to Cosmic Rays with specific characteristics.
+Once the Cherenkov Energy Threshold of the atmosphere falls below the CR Energy, the Nucleus will begin emitting a ring of Cherenkov Light.
+It will stop emitting when it first interacts, at a randomly distributed height we call $h$.
+Then for a given Telescope Array altitude above sea level, simple trigonometry yields $ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})$.
 
-Cosmic Rays interactions occur most often at a height of $h \approx 40 \pm 10$ km, and neglecting variations in atmospheric density profiles around the Earth, this can be considered independent of experimental array.
-The CR energies follow a well-defined power law where $ \frac{dN(E)}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ?
-$.
-Consequently higher energy CRs are heavily suppressed.
-Once the Energy Threshold falls below the CR Energy, the Nucleus will begin emitting Cherenkov Light.
-It will stop emitting when it first interacts, at a randomly distributed height we call $h$.
-Then for a given Telescope Array altitude above sea level, simple trigonometry yields:
-\[ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})\]
-As the Refractive Index of the Earth increases as height decreases, the angle $\theta_{C}$ increases with decreasing height.
-Thus the upper earlier emission contributes to the inner LPD, while the later emission contributes to the high-radius LPD.
-We find that the high-radius emission, (occurring near the first interaction region) varies little between different high energies.
-We deem this to be \textquoteleft saturated emission\textquoteright.
+The Refractive Index of the atmosphere, and thus the angle $\theta_{C}$, increases as the height decreases.
+Thus the upper atmosphere emission contributes to the inner LPD, while the lower atmosphere emission contributes to the outer LPD.
+We find that the high-radius emission (occurring near the first interaction region) varies little between different high energies.
+We deem this to be \textquoteleft Saturated Emission\textquoteright.
 
-We see that the amplitude of the 'signal' LPD varies with $ \rho_{DC}  = f(r) \times Z^{2}$.
+We see that the amplitude of the LPD varies with $ \rho_{DC}  = f(r) \times Z^{2}$.
 Thus the amplitude of the LPD is proportional to the charge of the Cosmic Ray, enabling the Charge to be determined from the DC emission.
@@
 
-Unfortunately, as a result of varying Threshold Energies and the sharp drop in the LDF above the maximum radius, the Log likelihood is discontinuous in many places.
+\section{Reconstruction Optimisation}
+Having reconstructed many events, we can then derive the $\sigma_{Z}$ of the dataset by assuming a Gaussian Distribution, giving us a number to directly compare the quality of event reconstruction.
+
+We find that the LPD initially provides very poor event reconstruction because, as a result of varying Threshold Energies and the sharp drop in the LDF above the maximum radius, the Log Likelihood is frequently discontinuous.
 Consequently, a Minuit-type minimisation algorithm will only be able to find a local minimum near the starting values for the fit parameters.
-To overcome this problem, we can iterate over a series of starting values for the parameters, with the aim of scanning the true minimum among the many found.
+To overcome this problem, we can iterate over a series of starting values for the parameters, with the aim of scanning the true minimum among the many minima found.
 To simplify matters, we can scan only the integer Z values over the range $ 20 \leq Z \leq 32 $, rather than considering the charge to be a free floating parameter.
 
-The Z value is fixed and the LL function is then minimised with the assigned starting values, with the other four variables allowed to float freely.
+The Z value is fixed and the LL function is then minimised with the assigned starting values, allowing the other four variables to float freely.
 Minimisation typically scans 13 Z values, 10 core position coordinates, and 50 Height/Energy coordinates, yielding $ 13 \times 10 \times 50 = 6500$ minimisations in total.
-Such a technique is very resource intensive but reduces $\sigma_{Z}$ by a factor of 5 or more.
+Such a technique is very resource intensive but typically reduces $\sigma_{Z}$ of a dataset by a factor of 5 or more.
 
-Having reconstructed many events, we can then consider the $\sigma_{Z}$ of the dataset.
-A large Monte Carlo simulation can also provide optimised values for Log Likelihood cuts that can be applied to datasets, reducing the $\sigma_{Z}$ further.
+Using one quarter of a large sample of Monte Carlo data, we can train a Boosted Decision Tree (BDT) for a given telescope multiplicity, using the reconstructed x/y core position, height and energy, as well as the Log Likelihood.
+The BDT is told whether each event is \textquoteleft signal' (correctly reconstructed) or \textquoteleft background' (incorrectly reconstructed).
+For every simulated event, this trained BDT can then be used to assign a \textquoteleft Signal Probability'.
+On a second quarter of the dataset we can optimise a cut on the minimum \textquoteleft Signal Probability', in order to maximise the ratio of signal to background.
+We find that the $\sigma_{Z}$ of the remaining \textquoteleft Test' Monte Carlo data is reduced when the same BDT cut is applied.
 
 \section{HESS-type Event Reconstruction}
-We can consider a simulation of the HESS Cherenkov Telescope Array to verify the accuracy of the technique.
-When the HESS layout is simulated, we find that the 4 telescope events have a mean height of $h \approx 23 \pm 5$ km.
-
-However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon.
-The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...
-
+We can consider a simulation of the HESS Cherenkov Telescope Array to verify the accuracy of the technique, with a 5 telescope array.
 The Extended Air Shower (EAS) produced after the first interaction of the Cosmic Ray overlaps the DC pixel, leading to background in the LPD.
@@
 Thus the background in the DC pixel increases with decreasing radius and increasing Energy.
-
-In addition, we have a fixed night sky background with 7 photons $m^{-2}$. We thus parameterise the background with 
+In addition, we have a fixed night sky background with 7 photons $m^{-2}$.
+We thus parameterise the background with
 $ \rho_{bkg}  = (7 + 5E) m^{-2}$. It begins to dominate above roughly 1 TeV per Nucleon, particularly in the case of smaller radii.
 
-In the preliminary HESS simulation, it was found that the 4 telescope event reconstruction had a charge resolution of $\sigma_{Z} = 2.4$.
-However, requiring that the Log Likelihood satisfied $L.L < 23.5$ removed just $17 \%$ of events, while reducing the Charge resolution to $\sigma_{Z} = 0.4$ .
-With this cut, core position resolution was $d \approx 2 m $.
+In the preliminary HESS simulation, it was found that the 4 telescope event reconstruction had a charge resolution of $\sigma_{Z} = 1.4$.
+However, requiring that the BDT signal Probability satisfied $P < 0.81$ removed $75 \%$ of events, while reducing the Charge resolution to $\sigma_{Z} = 0.9$ .
+With this cut, core position resolution was $d \approx 1.4 m $.
+For 5 telescope events, it was found that the charge resolution was also $\sigma_{Z} = 1.4$.
+However, requiring that the Log Likelihood satisfied $P < 0.05$ removed $53 \%$ of events, including all wrongly reconstructed ones.
+This placed an upper limit on the charge resolution of $\sigma_{Z} < 0.35$ .
+With this cut, core position resolution was $d \approx 0.8 m $.
 
-For 5 telescope events, it was found that the charge resolution was $\sigma_{Z} = 1.0$.
-However, requiring that the Log Likelihood satisfied $L.L < 23.0$ removed $47 \%$ of events, including all wrongly reconstructed ones.
-This placed an upper limit on the charge resolution to $\sigma_{Z} < 0.3$ .
-With this cut, core position resolution was $d \approx 1 m $.
-
-\section{Optimised Telescope Array}
+\section{Telescope Array Optimisation}
 

### 2016-03-29 cluster_input/plotcombined.py

@@ -37,17 +37,18 @@ with open(afspath + "/orientations/"+ orientation +".csv", 'rb') as csvfile:
 		
 reconstructdata = batchname + "_combined"
 
-
-pz.run(reconstructdata, rowcount, int(mincount), graph=False, cuts=None)	
 allcounts = cc.run(reconstructdata, rowcount, int(mincount))
 print allcounts
+
 
 BDT.run(reconstructdata, rowcount, int(mincount), allcounts)
 
 llcuts = oz.run(reconstructdata + "_BDT", rowcount, int(mincount), graph=False, allcounts=allcounts)
 print llcuts
+pz.run(reconstructdata + "_BDT", rowcount, int(mincount), graph=False, cuts=None, allcounts=allcounts)	
+
 pl.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
 pz.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
 pp.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
 pe.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
-ph.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, llcuts=None)
+ph.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)

### 2016-03-29 positioning/cherenkovradius.py

@@ -47,5 +47,13 @@ def runemin(ri):
 	
 	return Epn
 	
+def runbetaeta(Epn, height, fit=False):
+	gamma = (Epn/nucleonmass) + 1
+	beta = math.sqrt(1 - (1/gamma**2))
+	
+	refractiveindex = atm.runindex(height)
+	
+	return beta, refractiveindex
+	
 	
 	

### 2016-03-29 positioning/lightstatistics.py

@@ -46,7 +46,7 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 	
 		ax1.plot(rrange, sdensity, label=label)
 	
-	plt.yscale('log')
+	#~ plt.yscale('log')
 	plt.ylabel('Photons per m$^2$', fontsize=20)
 	plt.xlabel('Radius (m)', fontsize=20)
 	plt.title('No background, Rmax=100', fontsize=20)
@@ -114,7 +114,7 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 		ax2.plot(rrange, sigdensity, '--', color=color)
 		ax2.plot(rrange, density, color=color, label=label, linewidth=3.0)
 	
-	plt.yscale('log')
+	#~ plt.yscale('log')
 	plt.ylabel('Photons per m$^2$', fontsize=20)
 	plt.xlabel('Radius (m)', fontsize=20)
 	plt.title('Height = ' + str(height) + ', Z = 26', fontsize=20)
@@ -130,7 +130,6 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 	figure.set_size_inches(20, 15)
 	
 	plt.savefig('graphs/stats/Light.pdf')
-	plt.savefig('/afs/desy.de/user/s/steinrob/Documents/DESY/presentations/dpg presentation/Light.png')
 		
 	if graph:
 		plt.show()

### 2016-03-31 report/summary.tex
Backup 31/03/16

@@
 There are numerous Telescope Arrays which image the Cherenkov Light emitted by Cosmic Rays (CRs) in the atmosphere, all relying on Hillas Analysis for event reconstruction.
-Hillas Analysis extracts parameters from each of the camera images in order to reconstruct the events, but heavy blurring of the events by atmospheric effects means that resolution is very poor.
-For a typical Iron Nucleus event \cite{hess07}, the charge would be reconstructed as $Z \approx 26 \pm 5 $.
-
+Hillas Analysis extracts parameters from each of the camera images in order to reconstruct the events, but heavy atmospheric blurring means that charge resolution is very poor.
+For Iron Nucleus events, we would expect to reconstruct $Z \approx 26 \pm 5 $ \cite{hess07}.
 The imaged CRs have energies between $13 $TeV and $200 $TeV and, at present, no study of the relative abundance of different cosmic ray elemental abundances exists for these energies.
@@
 
-We consider a new method for event reconstruction, in which we fit the known Direct Cherenkov (DC) Light observed by each telescope to a characteristic Lateral Photon Distribution (LPD) function.
-If the LPD method can achieve a resolution $ \sigma_{Z} \approx 1 $ for elements of $Z = 20$ or higher, this will be precise enough to extract the abundances of the different CR Elements.
-This the prime motivation for introducing the new LPD technique.
+We consider a new method for event reconstruction, in which we fit the known Direct Cherenkov (DC) Light observed by each telescope to a characteristic Lateral Distribution Function (LDF) function.
+If the LDF method can achieve a resolution $ \sigma_{Z} \approx 1 $ for elements of $Z = 20$ or higher, the precision will be sufficient to extract the abundances of the different CR Elements.
+This the prime motivation for introducing the new LDF technique.
 
 \section{Lateral Photon Distribution Method}
-Once the Cherenkov Energy Threshold of the atmosphere falls below the CR Energy, the Nucleus will begin emitting a ring of Cherenkov Light.
-It will stop emitting when it first interacts, at a randomly distributed height we call $h$.
-Then for a given Telescope Array altitude above sea level, simple trigonometry yields $ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})$.
-
-The Refractive Index of the atmosphere, and thus the angle $\theta_{C}$, increases as the height decreases.
-Thus the upper atmosphere emission contributes to the inner LPD, while the lower atmosphere emission contributes to the outer LPD.
+Once the Energy of a CR exceeds the local Cherenkov Energy Threshold of the atmosphere, the Nucleus will begin emitting a ring of Cherenkov Light, and continues emitting until a randomly distributed first interaction with the atmosphere.
+The Refractive Index of the atmosphere, and thus the Cherenkov angle $\theta_{C}$, increases as the altitude decreases.
+Thus the upper atmosphere emission contributes to the inner LDF, while the lower atmosphere emission contributes to the outer LDF.
 We find that the high-radius emission (occurring near the first interaction region) varies little between different high energies.
@@
 
-We see that the amplitude of the LPD varies with $ \rho_{DC}  = f(r) \times Z^{2}$.
-Thus the amplitude of the LPD is proportional to the charge of the Cosmic Ray, enabling the Charge to be determined from the DC emission.
-This is the basis for charge reconstruction in the LPD method.
+We see that the amplitude of the LDF varies with $ \rho_{DC}  = f(r) \times Z^{2}$.
+Thus the amplitude of the LDF is proportional to the charge of the Cosmic Ray, enabling the Charge to be determined from the DC emission.
+This is the basis for charge reconstruction in the LDF method.
 
-In order to reconstruct an event, we need to find the x/y core position, the Energy per Nucleon, the first interaction height and the charge.
+In order to fully reconstruct an event, we need to find the x/y core position, the Energy per Nucleon, the first interaction height and the charge.
 However, if one telescope in a five-telescope array does not observe DC light, this data point can be used to constrain the core position.
-Thus, for the LPD method to be applied, we require a minimum of five telescopes, four or more of which must image the DC light.
+Thus, for the LDF method to be applied, we require a minimum of five telescopes, four or more of which must image the DC light.
 
 We consider the amount of DC light that each telescope receives to be Poissonian and can use Stirling's Approximation to reduce computing time.
-We then minimise the Log Likelihood function \[ - Ln(L) = - \sum_{i=1}^{n} [P_{i}] \approx  \sum_{i=1}^{n} [\lambda _{i} - N_{i} ln(\lambda _{i}) + N_{i} ln(N_{i}) - N_{i} + \frac{1}{2} ln(2 \pi N_{i})]  \]
+We then minimise the Log Likelihood function \[ - Ln(L) = - \sum_{i=1}^{n} Ln [P_{i}] \approx  \sum_{i=1}^{n} [\lambda _{i} - N_{i} ln(\lambda _{i}) + N_{i} ln(N_{i}) - N_{i} + \frac{1}{2} ln(2 \pi N_{i})]  \]
 where n is the total number of telescopes in the array.
 
-\section{Reconstruction Optimisation}
 Having reconstructed many events, we can then derive the $\sigma_{Z}$ of the dataset by assuming a Gaussian Distribution, giving us a number to directly compare the quality of event reconstruction.
-
-We find that the LPD initially provides very poor event reconstruction because, as a result of varying Threshold Energies and the sharp drop in the LDF above the maximum radius, the Log Likelihood is frequently discontinuous.
+We find that the LDF method initially provides very poor event reconstruction because, as a result of varying Threshold Energies and the sharp drop in the LDF above the maximum radius, the Log Likelihood is frequently discontinuous.
 Consequently, a Minuit-type minimisation algorithm will only be able to find a local minimum near the starting values for the fit parameters.
 To overcome this problem, we can iterate over a series of starting values for the parameters, with the aim of scanning the true minimum among the many minima found.
-To simplify matters, we can scan only the integer Z values over the range $ 20 \leq Z \leq 32 $, rather than considering the charge to be a free floating parameter.
-
-The Z value is fixed and the LL function is then minimised with the assigned starting values, allowing the other four variables to float freely.
 Minimisation typically scans 13 Z values, 10 core position coordinates, and 50 Height/Energy coordinates, yielding $ 13 \times 10 \times 50 = 6500$ minimisations in total.
@@
 For every simulated event, this trained BDT can then be used to assign a \textquoteleft Signal Probability'.
-On a second quarter of the dataset we can optimise a cut on the minimum \textquoteleft Signal Probability', in order to maximise the ratio of signal to background.
+On a second quarter of the dataset we can optimise a cut on the minimum signal probability, in order to maximise the ratio of signal to background.
 We find that the $\sigma_{Z}$ of the remaining \textquoteleft Test' Monte Carlo data is reduced when the same BDT cut is applied.
@@
 \section{HESS-type Event Reconstruction}
-We can consider a simulation of the HESS Cherenkov Telescope Array to verify the accuracy of the technique, with a 5 telescope array.
-The Extended Air Shower (EAS) produced after the first interaction of the Cosmic Ray overlaps the DC pixel, leading to background in the LPD.
-As the Energy of the Cosmic Ray increases, the EAS speads over a larger angular area, and at smaller radii, the EAS-DC-shower direction axis contracts, leading to more overlap.
+With a simulation of the HESS Cherenkov 5-Telescope Array we can verify the effectiveness of the technique.
+For HESS cameras, the Extended Air Shower (EAS) produced after the first interaction of the CR overlaps the DC pixel and thus provides background in the LDF.
+As the Energy of the CR increases, the EAS speads over a larger angular area, and at smaller radii, the EAS-DC-shower direction axis contracts, leading to more overlap.
 Thus the background in the DC pixel increases with decreasing radius and increasing Energy.
 In addition, we have a fixed night sky background with 7 photons $m^{-2}$.
-We thus parameterise the background with
-$ \rho_{bkg}  = (7 + 5E) m^{-2}$. It begins to dominate above roughly 1 TeV per Nucleon, particularly in the case of smaller radii.
+We thus parameterise the background with $ \rho_{bkg}  = (7 + 5E) m^{-2}$.
+It begins to dominate above roughly 1 TeV per Nucleon, particularly in the case of smaller radii.
 
 In the preliminary HESS simulation, it was found that the 4 telescope event reconstruction had a charge resolution of $\sigma_{Z} = 1.4$.
-However, requiring that the BDT signal Probability satisfied $P < 0.81$ removed $75 \%$ of events, while reducing the Charge resolution to $\sigma_{Z} = 0.9$ .
+However, requiring that the BDT signal probability satisfied $P > 0.81$ removed $75 \%$ of events, while reducing the Charge resolution to $\sigma_{Z} = 0.9$ .
 With this cut, core position resolution was $d \approx 1.4 m $.
 For 5 telescope events, it was found that the charge resolution was also $\sigma_{Z} = 1.4$.
-However, requiring that the Log Likelihood satisfied $P < 0.05$ removed $53 \%$ of events, including all wrongly reconstructed ones.
+However, requiring that the signal probability satisfied $P > 0.05$ removed $53 \%$ of events, including all wrongly reconstructed ones.
 This placed an upper limit on the charge resolution of $\sigma_{Z} < 0.35$ .
@@
 \section{Telescope Array Optimisation}
+In order to improve the count rate of high-multiplicity events, we can consider a 3x3 array of Cherenkov Telescopes, which we want to use for identifying Cosmic Ray Elements accurately.
+The \textquoteleft High Multiplicity Count Rate' of events observed by sufficient telescopes falls with increasing grid separation.
+We find that the optimum grid spacing will lie in the 20-50m region to provide a reasonable count rate.
+Competing with this effect is the reliance of LDF reconstruction on sampling the entire lateral distribution.
+Thus the charge resolution will increase as Grid Width decreases.
+Further study of $\sigma_{Z}$ in this region is required to determine the true optimum layout and grid spacing for event reconstruction.
 
-We can consider a 3x3 array of Cherenkov Telescopes of 12m diameter, which we want to use for identifying Cosmic Ray Elements accurately.
-The \textquoteleft Good Count Rate' of events observed by sufficient telescopes falls with increasing grid separation.
-We can clearly see that the optimum grid spacing will lie in the 20-50m region to provide a reasonable count rate.
-
-Competing with this effect is the reliance of LPD reconstruction on sampling the entire lateral distribution.
-Thus the charge resolution will increase as Grid Width decreases.
-A further analysis of $\sigma_{Z}$ in this region is required to determine the true optimum.
+By definition, the EAS shower will arrive on the ground shortly before the DC light.
+There are currently several high-speed Cherenkov telescopes capable of distinguishing between these, allowing a background-free LDF to be fitted.
+Additional study of alternative energy regimes and grid spacings will also be considered for the case of a high-speed imaging telescope array.
 
 \section{Conclusion}
-End
+Preliminary results suggest that the LDF reconstruction technique will significantly improve charge reconstruction, to a level sufficient for cosmic ray abundance studies.
+However, reliance on high-multiplicity events means that although applicable to current experiments such as HESS, a new optimised telescope array would be required for a statistical analysis.
+Such an array may have a grid spacing of 20-50m, although further study is needed to determine the ideal layout.
 \bibliographystyle{plain}

### 2016-03-31 positioning/lateralphotondistribution.py

@@ -12,26 +12,31 @@ import looptelescopes as lt
 import atmosphere as atm
 import matplotlib.pyplot as plt
 
+eff=1.0
+
 radii = []
 weights = []
 labels=[]
 colors=[]
 		
-Epns = [50000./56., 40000./56., 30000./56., 20000./56.]
+Epns = np.linspace(15, 65, 5)
 height = 25000
 
 wl=450*(10**-9)
 Z = 26
 alpha=float(1)/float(137)
-ewidth = 1.6*(10**-19)
-scaling= (Z**2) * alpha * ewidth * math.pi * 2/(wl**2)
+ewidth = 0.7
+#~ scaling= (Z**2) * alpha * ewidth * math.pi * 2/(wl**2)
+scaling = 370 * (Z**2) * 100 * ewidth
 
-for Epn in Epns:
+for tev in Epns:
+	
+	Epn = tev*1000./56.
 	
 	r=[]
 	w=[]
 
-	print Epn, height
+	print tev, "TeV", height, Epn
 	
 	h = 65000
 	
@@ -51,43 +56,59 @@ for Epn in Epns:
 		if float(beta) > (float(1)/float(ri)):
 			radius, theta = cr.run(Epn, h, sinphi=1)
 			
-			n = (1-(1/(ri*beta)**2))
+			n = scaling*(math.sin(theta)**2)
+			
+			DeltaE = (10**-9)*(n*2.74)/56.
 			
 			oldradius, oldtheta = cr.run(Epn, h+1, sinphi=1)
 			
 			deltar =  float(radius)- float(oldradius)
 			
-			area= deltar * math.pi * ((2*radius) + deltar) 
+			area= math.pi * ((radius**2) -(oldradius**2))
 			
-			density = scaling*n/area
+			frac = atm.runabsorption(h)
+			frac=1
+			
+			density = frac*eff*n/area
 			
 			r.append(radius)
 			w.append(density)
 			rmax=radius
 			
+			Epn += -DeltaE
+	
+	r.append(radius+0.01)
+	w.append(1)
+		
 	radii.append(r)
 	weights.append(w)
-	labels.append(str(Epn))
+	labels.append(str(tev) + " TeV")
 	colors.append("k")
 		
-plt.subplot(2,1,1)
+plt.subplot(3,1,1)
 plt.plot(heights, ris, label="Exponential")
 plt.plot(heights, linears, label="Linear", color='r')
 plt.yscale("Log")
 plt.legend()
[…]

### 2016-03-31 positioning/lightstatistics.py

@@ -35,7 +35,7 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 		
 		for r in rrange:
 			
-			sig, bkg = ld.run(r, 0, Z, Rmax, 1)
+			sig, bkg = ld.run(r, 0, Z, Rmax, eff)
 			
 			if sig > 1:
 				sdensity.append(sig)
@@ -46,7 +46,7 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 	
 		ax1.plot(rrange, sdensity, label=label)
 	
-	#~ plt.yscale('log')
+	plt.yscale('log')
 	plt.ylabel('Photons per m$^2$', fontsize=20)
 	plt.xlabel('Radius (m)', fontsize=20)
 	plt.title('No background, Rmax=100', fontsize=20)
@@ -89,7 +89,7 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 		
 		for r in rrange:
 			
-			sig, bkg = ld.run(r, Epn, Z, rmax, 1)
+			sig, bkg = ld.run(r, Epn, Z, rmax, eff)
 			
 			count = sig + bkg
 			
@@ -114,7 +114,7 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 		ax2.plot(rrange, sigdensity, '--', color=color)
 		ax2.plot(rrange, density, color=color, label=label, linewidth=3.0)
 	
-	#~ plt.yscale('log')
+	plt.yscale('log')
 	plt.ylabel('Photons per m$^2$', fontsize=20)
 	plt.xlabel('Radius (m)', fontsize=20)
 	plt.title('Height = ' + str(height) + ', Z = 26', fontsize=20)

### 2016-04-01 report/draft1.tex
Backup 1/4/16

@@
 \graphicspath{ {graphs/} }
+\usepackage{geometry}
+\geometry{a4paper, portrait, margin=1.0in}
+\usepackage{gensymb}
 \begin{document}
@@
 There are numerous Telescope Arrays which image the Cherenkov Light emitted by Cosmic Rays in the atmosphere, including the HESS, Magic and Veritas Experiments.
-All such Imaging Atmospheric Cherenkov Telescopes (IACTs) rely on Hillas Analysis for event reconstruction.Hillas Analysis extracts parameters from each of the camera images in order to reconstruct the events.
-However, heavy blurring of the events by atmospheric effects means that resolution of reconstruction  is very poor.
-For a typical Iron Nucleus event \cite{hess07}, the core position resolution is roughly $d \approx 20 m $, and the charge would be reconstructed as \[Z \approx 26 \pm 5 \]
+All rely on Hillas Analysis with extracted parameters from each of the camera images being used to reconstruct the events, but heavy atmospheric blurring means that charge resolution is very poor.
+For Iron Nucleus events, we would expect to reconstruct \[Z \approx 26 \pm 5 \] with a core position resolution of the core position resolution is roughly $d \approx 20 m $ \cite{hess07}.
 
 Cosmic Rays that are imaged by these telescopes have energies between $13 $TeV and $200 $TeV.
-At present, no study of the relative abundance of different cosmic ray elemental abundances exists, although it could provide important clues regarding the mechanism of Cosmic Ray formation and propagation in the galaxy.
-Unfortunately, current charge resolution from Hillas Analysis is not small enough to undertake such a study.
+At present, no study of the relative abundance of different cosmic ray elemental abundances exists at these energies.It could provide important clues regarding the mechanism of CR formation and propagation in the galaxy but current charge resolution from Hillas Analysis is not small enough to undertake such a study.
 
@@
 
-A theoretical study by Kieda in 2001 \cite{kieda01} suggested that for a core position resolution of $d \approx 5 $ m , we could expect to see a charge resolution of $ \sigma_{Z} \approx 1 $ for elements of $Z = 20$ or higher.
-In this case the core resolution would be the limiting value.
-Thus, if the LPD method can achieve this core position resolution, then charge resolution will become sufficiently good enough to extract the abundances of the different Cosmic Ray Elements.
+A theoretical study by Kieda in 2001 \cite{kieda01} suggested that for a core position resolution of $d \approx 5 $ m, we could expect to see a charge resolution of $ \sigma_{Z} \approx 1 $ for elements of $Z = 20$ or higher.
+In this case the core position resolution would be the limiting value.
+Thus, if the LPD method can achieve this core position resolution, the precision will be sufficient to extract the abundances of the different Cosmic Ray Elements.
 This the prime motivation for the new LPD technique.
 
-\section{Lateral Photon Distribution Method}
+\section{Cosmic Ray Event Simulation}
 In order to reconstruct events using the LPD method, we require saturation of the Cosmic Ray Energy, and that the event can be seen by at least 4 telescopes.
@@
 The Energy Threshold for Cherenkov Light Emission as a function of height is illustrated in \ref{fig:generalenergy}.
+Once the Energy of a Cosmic Ray exceeds the local Cherenkov Energy Threshold of the atmosphere, the Nucleus will begin emitting a ring of Cherenkov Light.
+Emission continues until the first interaction with the atmosphere, occurring at a randomly distributed height we call $h$.
+Then for a given Telescope Array altitude above sea level, simple trigonometry yields the radius of the LDF on the ground:
+\[ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})\]
+
+The Refractive Index of the atmosphere, and thus the Cherenkov angle $\theta_{C}$, increases as the altitude decreases.
+Thus the upper atmosphere emission contributes to the inner LDF, while the lower atmosphere emission contributes to the outer LDF.
+We can also see ground emission radius as a function of height in \ref{fig:generalenergy}.
+We find that the high-radius emission (occurring near the first interaction region) varies little between different high energies.
+We deem this to be \textquoteleft Saturated Emission\textquoteright.
 
@@
 
-Once the Energy Threshold falls below the Cosmic Ray Energy, the Nucleus will begin emitting Cherenkov Light.
-It will stop emitting when it first interacts, at a randomly distributed height we call $h$.
-Then for a given Telescope Array altitude above sea level, simple trigonometry yields:
-\[ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})\]
-As the Refractive Index of the Earth increases as height decreases, the angle $\theta_{C}$ increases with decreasing height.
-Thus the upper earlier emission contributes to the inner LPD, while the later emission contributes to the high-radius LPD.
+\subsection{Nuclear Charge}
+Cherenkov Emission is determined by the Frank Tamm formula!!!!!
 
-We can also see ground emission radius as a function of height in \ref{fig:generalenergy}.
-It is clear that the high-radius emission, (occurring near the first interaction region) is virtually unchanged for high Energies.
-We deem this to be \textquoteleft saturated emission\textquoteright.
+Under the assumption of constant magnetic permittivity and a zenith angle of $90\degree$ we can use the approximate form \[ N_{photons} \approx (37000 \times Z^{2} \times \Delta_{h} \times \Delta_{E})\] where $\Delta_{h}$ is the vertical distance travelled in meters and $\Delta_{E}$ is the emission energy range in eV.
 
-\subsection{Nuclear Charge}
-In figure Z we see that the height of the 'signal' LPD varies with \[ \rho_{DC}  = f(r) \times Z^{2}\]
+If we divide the number of emitted photons by the area of the annulus between the ring radii at $h$ and $h - \Delta_{h}$, we retrieve the LDF shown in \ref{fig:lpd}, which varies with $ \rho_{DC}  = f(r) \times Z^{2}$ .
+Thus the amplitude of the LDF is proportional to the charge of the Cosmic Ray, enabling the Charge to be determined from the DC emission.
+This is the basis for charge reconstruction in the LDF method.
 
-Thus the height of the LPD is proportional to the charge of the Cosmic Ray, enabling the Charge to be determined from the DC emission. This is the basis for charge reconstruction in the LPD method.
+\begin{figure}
+\begin{center}
+\includegraphics[height=0.9\textheight]{simulatedlpd}
+\caption{The LPD obtained from simulation of an Iron Nucleus up to a first interaction height of 25km for a range of Core Energies.
+An altitude of 1.8km for the experimental array is assumed.
+Atmospheric absorption, although neglected, is broadly constant across the emission range leading to uniform amplitude scaling.}
+\label{fig:lpd}
+\end{center}
+\end{figure}
 
-\subsection{Iterative Log Likelihood Minimisation}
-In order to reconstruct an event, we need to find the x/y core position, the Energy per Nucleon, the first interaction height and the charge.
+\subsection{Energy saturation region}
+However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon as shown in \ref{fig:lpd}!
+The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...
+
+\subsection{Atmospheric Absorption}
+Cosmic Rays get absorbed and stuff.
+
+\section{LPD Event Reconstruction}
+
+\subsection{Log Likelihood Minimisation}
+In order to fully reconstruct an event, we need to find the x/y core position, the Energy per Nucleon, the first interaction height and the charge.
 However, if one telescope in a five-telescope array does not observe DC light, this data point can be used to constrain the core position.
-Thus, for the LPD method to be applied, we require a minimum of five telescopes, four or more of which must image the DC light.
-
+Thus, for the LDF method to be applied, we require a minimum of five telescopes, four or more of which must image the DC light.
 We consider the amount of DC light that each telescope receives to be Poissonian \[  P_{i} ( N_{i, Received} \mid X, Y, Z, height, Epn )  =  \frac{ e^{- \lambda_{i} } \times \lambda_{i} ^{N_{i}} }{N_{i}!} \]
 
-In order to reduce computing time, we can use Stirling's Approximation $ln( N!
-)  \approx  N ln(N) - N + \frac{1}{2} ln(2 \pi N)$.
+In order to reduce computing time, we can use Stirling's Approximation $\ln( N!
+)  \approx  N \ln(N) - N + \frac{1}{2} \ln(2 \pi N)$.
 Pure night sky background requires that there be more that X photons in a DC pixel, and for this Stirling's Approximation has an error of just Y?.
-We then minimise the Log Likelihood function \[ - Ln(L) = - \sum_{i=1}^{n} [P_{i}] \approx  \sum_{i=1}^{n} [\lambda _{i} - N_{i} ln(\lambda _{i}) + N_{i} ln(N_{i}) - N_{i} + \frac{1}{2} ln(2 \pi N_{i})]  \]
-where n is the total number of telescopes in the array.
+We then minimise the Log Likelihood function \[ - \ln(L) = - \sum_{i=1}^{n} \ln(P_{i}) \approx  \sum_{i=1}^{n} [\lambda _{i} - N_{i} \ln(\lambda _{i}) + N_{i} \ln(N_{i}) - N_{i} + \frac{1}{2} \ln(2 \pi N_{i})]  \] where n is the total number of telescopes in the array.
 
-Unfortunately, as a result of varying Threshold Energies and the sharp drop in the LDF above the maximum radius, the Log likelihood is discontinuous in many places.
+\subsection{Extracting Charge Resolution}
+Having reconstructed many events, we can then derive the $\sigma_{Z}$ of the dataset, giving us a number to directly compare the quality of event reconstruction.
+However, a simple Gaussian 68\% method will yield only half integer values of $\sigma_{Z}$ and very frequently 0.
+This will be unhelpful for comparisons of minor modifications of reconstruction methods.
+
+Instead, we can assume a Gaussian with tails at the highest and lowest reconstructed charge values in the dataset.
+The size of the dataset can be used to calculate the fraction of events that the extreme values represent, and this probability can be converted into a \textquoteleft number of standard deviations from mean'.
+Dividing the Gaussian total width by the number of standard deviations gives us a value for $\sigma$.
+Although this will in most cases tend to overestimate the spread of the data, it will also be sensitive to all increases in the proportion of correctly reconstructed events.
+
+\subsection{Iterative Scanning Minimisation}
+Through $\sigma_{Z}$ calculation, we find that the LDF method initially provides very poor charge reconstruction.
+This is as a result of varying Threshold Energies and the sharp drop in the LDF above the maximum radius, which means the Log Likelihood is frequently discontinuous within the parameter space.
 Consequently, a Minuit-type minimisation algorithm will only be able to find a local minimum near the starting values for the fit parameters.
 
-To overcome this problem, we can iterate over a series of starting values for the parameters, with the aim of scanning the true minimum among the many found.
+To overcome this problem, we can iterate over a series of starting values for the parameters, with the aim of scanning the true minimum among the many minima found.
 To simplify matters, we can scan only the integer Z values over the range $ 20 \leq Z \leq 32 $, rather than considering the charge to be a free floating parameter.
@@
 Minimisation typically scans 13 Z values, 10 core position coordinates, and 50 Height/Energy coordinates, yielding $ 13 \times 10 \times 50 = 6500$ minimisations in total.
-Such a techinique is resource intensive but reduces $\sigma_{Z}$ by a factor of 5 or more.
+Such a technique is resource intensive but reduces $\sigma_{Z}$ by a factor of 5 or more.
 (CHECK this quantitatively and get a graph yo.
@@
 
-\subsection{Extracting Charge Resolution}
+\subsection{Boosted Decision Trees}
+Using one quarter of a large sample of Monte Carlo data, we can train a Boosted Decision Tree (BDT) for a given telescope multiplicity, using the reconstructed x/y core position, height and energy, as well as the Log Likelihood.
+The BDT is told whether each event is \textquoteleft signal' (correctly reconstructed) or \textquoteleft background' (incorrectly reconstructed).
 
-Having reconstructed many events, we can then consider the $\sigma_{Z}$ of the dataset.
-The Z distribution is a binned Gaussian, but due to the Integer nature of the reconstruction, a standard 68\% values method will be constrained to half integer values for $\sigma_{Z}$.
-
-A large Monte Carlo simulation can also provide optimised values for Log Likelihood cuts that can be applied to datasets, reducing the $\sigma_{Z}$ further.
+For every simulated event, this trained BDT can then be used to assign a \textquoteleft Signal Probability'.
+On a second quarter of the dataset we can optimise a cut on the minimum signal probability, in order to maximise the ratio of signal to background.
+We find that the $\sigma_{Z}$ of the remaining \textquoteleft Test' Monte Carlo data is reduced when the same BDT cut is applied.
 
 \section{HESS-type Event Reconstruction}
-
+With a simulation of the HESS Cherenkov 5-Telescope Array we can verify the effectiveness of the technique. 
 \subsection{First Interaction and Energy Saturation}
-The mean first interaction height for all Cherenkov Emitting Cosmic Rays in the atmosphere is 40km???, and neglecting variations in atmospheric density profiles around the Earth, this can be considered independent of experimental array.
+The mean first interaction height for all Cherenkov Emitting Cosmic Rays in the atmosphere is 40km, and neglecting variations in atmospheric density profiles around the Earth, this can be considered independent of experimental array.
 However, the multiplicity of event is determined by equipment efficiencies, altitude and telescope layout.
@@
 
-\subsection{HESS Energy saturation region}
-However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon fig Y!
-The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...
-
 \subsection{Extended Air Shower Background}
 A typical HESS image is shown in \ref{fig:hess}, with the DC pixel visible.
-The Extended Air Shower (EAS) produced after the first interaction of the Cosmic Ray overlaps the DC pixel, leading to background in the LPD.
+For HESS cameras, the Extended Air Shower (EAS) produced after the first interaction of the Cosmic Ray overlaps the DC pixel and thus provides background in the LDF.
 As the Energy of the Cosmic Ray increases, the EAS speads over a larger angular area, and at smaller radii, the EAS-DC-shower direction axis contracts, leading to more overlap.
 Thus the background in the DC pixel increases with decreasing radius and increasing Energy.
+In addition, we have a fixed night sky background with 7 photons $m^{-2}$.
+We thus parameterise the background with \[ \rho_{bkg}  = 7 + 5E\].
+The modeled background LPD is shown as part of REF.
+It begins to dominate above roughly 1 TeV per Nucleon, particularly in the case of smaller radii.
 
@@
 
-In addition, we have a fixed night sky background with 7 photons $m^{-2}$. We thus parameterise the background with 
-\[ \rho_{bkg}  = 7 + 5E\]
-The modeled background LPD is shown in X. It begins to dominate above roughly 1 TeV per Nucleon, particularly in the case of smaller radii.
+\subsection{Reconstructed Charge Resolution}
+In the preliminary HESS simulation, it was found that the 4 telescope event reconstruction had a charge resolution of $\sigma_{Z} = 1.4$.
+However, requiring that the BDT signal probability satisfied $P > 0.81$ removed $75 \%$ of events, while reducing the Charge resolution to $\sigma_{Z} = 0.9$ .
+With this cut, core position resolution was $d \approx 1.4 m $.
+For 5 telescope events, it was found that the charge resolution was also $\sigma_{Z} = 1.4$.
+However, requiring that the signal probability satisfied $P > 0.05$ removed $53 \%$ of events, including all wrongly reconstructed ones.
+This placed an upper limit on the charge resolution of $\sigma_{Z} < 0.35$ .
+With this cut, core position resolution was $d \approx 0.8 m $.
+
+However, the simulated number of hours for the data was 1200?
+hours, and comparisons with HESS data show just 12 4-telescope events rather than 600.
+Thus, although the technique is valid and effective for HESS, the count rate will limit the potential to conduct any statistical analysis from this experiment.
 
@@
 \subsection{Count Rates}
-We can consider a 3x3 array of Cherenkov Telescopes of 12m diameter, which we want to use for identifying Cosmic Ray Elements accurately.
-In \ref{fig:optmiselayout} we see that the \textquoteleft Good Count Rate' of events observed by sufficient telescopes falls with increasing grid separation.
-We can clearly see that the optimum grid spacing will lie in the 20-50m region to provide a reasonable count rate.
 
-Competing with this effect is the reliance of LPD reconstruction on sampling the entire lateral distribution. Thus the charge resolution will increase as Grid Width decreases.
-
-A further analysis of $\sigma_{Z}$ in this region is required to determine the true optimum.
-
-Other shapes?
+In order to improve the count rate of high-multiplicity events, we can consider a 3x3 array of Cherenkov Telescopes, which we want to use for identifying CR Elements accurately.
+In \ref{fig:optmiselayout} we see that the \textquoteleft High Multiplicity Count Rate' of events observed by 4 or more telescopes falls with increasing grid separation.
+We can clearly see that the optimum grid spacing will likely lie in the 20-50m region to provide a reasonable count rate.
+Competing with this effect is the reliance of LDF reconstruction on sampling the entire lateral distribution.
+Thus the reconstruction quality will decrease as Grid Width decreases.
+Further study of $\sigma_{Z}$ in this region is required to determine the optimum layout (not necessarily be a grid) for event reconstruction.
 
@@
 
+\subsection{High Speed Telescopes}
+By definition, the EAS shower will arrive on the ground shortly before the DC light.
+There are currently several high-speed Cherenkov telescopes capable of distinguishing between these, allowing a background-free LDF to be fitted.
+Additional study of alternative energy regimes and layouts will also be considered for the case of a high-speed imaging telescope array.
+
 \section{Conclusion}
-End
+Preliminary results suggest that the LDF reconstruction technique will significantly improve charge reconstruction, to a level sufficient for cosmic ray abundance studies.
+However, reliance on high-multiplicity events means that although applicable to current experiments such as HESS, a new optimised telescope array would be required for a statistical analysis.
+Such an array may have a grid spacing of 20-50m, although further study is needed to determine the ideal layout.
 \bibliographystyle{plain}

### 2016-04-01 report/summary.tex
Backup 1/4/16

@@
 In addition, we have a fixed night sky background with 7 photons $m^{-2}$.
-We thus parameterise the background with $ \rho_{bkg}  = (7 + 5E) m^{-2}$.
+We thus parameterise the background with an exponential in height and radius added to a fixed background.
 It begins to dominate above roughly 1 TeV per Nucleon, particularly in the case of smaller radii.
@@
 \section{Telescope Array Optimisation}
-In order to improve the count rate of high-multiplicity events, we can consider a 3x3 array of Cherenkov Telescopes, which we want to use for identifying Cosmic Ray Elements accurately.
-The \textquoteleft High Multiplicity Count Rate' of events observed by sufficient telescopes falls with increasing grid separation.
-We find that the optimum grid spacing will lie in the 20-50m region to provide a reasonable count rate.
+In order to improve the count rate of high-multiplicity events, we can consider a 3x3 array of Cherenkov Telescopes, which we want to use for identifying CR Elements accurately.
+The \textquoteleft High Multiplicity Count Rate' of events observed by 4 or more telescopes falls with increasing grid separation.
+We find that the optimum grid spacing will likely lie in the 20-50m region to provide a reasonable count rate.
 Competing with this effect is the reliance of LDF reconstruction on sampling the entire lateral distribution.
-Thus the charge resolution will increase as Grid Width decreases.
-Further study of $\sigma_{Z}$ in this region is required to determine the true optimum layout and grid spacing for event reconstruction.
+Thus the reconstruction quality will decrease as Grid Width decreases.
+Further study of $\sigma_{Z}$ in this region is required to determine the optimum layout (not necessarily be a grid) for event reconstruction.
 
@@
 There are currently several high-speed Cherenkov telescopes capable of distinguishing between these, allowing a background-free LDF to be fitted.
-Additional study of alternative energy regimes and grid spacings will also be considered for the case of a high-speed imaging telescope array.
+Additional study of alternative energy regimes and layouts will also be considered for the case of a high-speed imaging telescope array.
 

### 2016-04-01 cluster_input/plotold.py

@@ -1,0 +1,52 @@
+import sys
+
+afspath = '/afs/desy.de/user/s/steinrob/Documents/DESY/positioning/'
+
+sys.path.append(afspath)
+
+import argparse, math, random, time
+import csv
+import numpy as np
+
+nparrallel = 10
+
+targetfolder = "reconstructeddata/"
+
+reconstructdata= "archive/9gridarchive"
+
+import plotz as pz
+import plotposition as pp
+import plotepn as pe
+import plotangle as pa
+import plotheight as ph
+import plotlikelihood as pl
+import optimisez as oz
+import categorycounts as cc
+
+import initialise as i
+orientation="ideal"
+mincount=5
+
+sys.path.append('/home/steinrob/Documents/DESY/BDT')
+import BDT
+
+with open(afspath + "/orientations/"+ orientation +".csv", 'rb') as csvfile:
+	reader = csv.reader(csvfile, delimiter=',', quotechar='|')
+	rowcount = 0
+	for row in reader:
+		rowcount +=1
+
+allcounts = cc.run(reconstructdata, rowcount, int(mincount))
+print allcounts
+
+BDT.run(reconstructdata, rowcount, int(mincount), allcounts)
+
+llcuts = oz.run(reconstructdata + "_BDT", rowcount, int(mincount), graph=False, allcounts=allcounts)
+print llcuts
+pz.run(reconstructdata + "_BDT", rowcount, int(mincount), graph=False, cuts=None, allcounts=allcounts)	
+
+pl.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
+pz.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
+pp.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
+pe.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
+ph.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)

### 2016-04-01 positioning/optimisez.py

@@ -84,7 +84,7 @@ def run(source, detectorcount, mindetections, graph=False, allcounts=None):
 					
 						frac = float(passing)/float(full)
 						
-						if float(frac) > float(0.05):
+						if float(frac) > float(0.2):
 							specificcount.sort()
 							
 							interval = (float(0.5)/float(total))

### 2016-04-01 positioning/plotepn.py

@@ -3,7 +3,7 @@ import csv
 import numpy as np
 import matplotlib.pyplot as plt
 
-def run(source, detectorcount, mindetections, graph, cuts, allcounts):
+def run(source, detectorcount, mindetections, graph, cuts, allcounts=None):
 	fullcount=[]
 	labels=[]
 	info = ""
@@ -56,13 +56,14 @@ def run(source, detectorcount, mindetections, graph, cuts, allcounts):
 								difference = (reconEPN-trueEPN)
 								specificcount.append(difference)
 
-		fullcount.append(specificcount)
-		label = str(j) + " detections"
-		labels.append(label)
-		
 		total = len(specificcount)
 		
 		if float(total) > float(0):
+			fullcount.append(specificcount)
+			label = str(j) + " detections"
+			labels.append(label)
+		
+			
 		
 			specificcount.sort()
 		
@@ -88,7 +89,7 @@ def run(source, detectorcount, mindetections, graph, cuts, allcounts):
 	
 	plt.annotate(info, xy=(0.05, 0.4), xycoords="axes fraction",  fontsize=10)
 			
-	n, bins, _ = plt.hist(fullcount, label=labels, histtype='bar', stacked=True)
+	n, bins, _ = plt.hist(fullcount, bins=30, label=labels, histtype='bar', stacked=True)
 	
 	mid = (bins[1:] + bins[:-1])*0.5
 	if isinstance(n[0], np.ndarray):

### 2016-04-01 positioning/plotposition.py

@@ -56,14 +56,13 @@ def run(source, detectorcount, mindetections, graph, cuts, allcounts=None):
 								distance = math.sqrt(((reconx-truex)**2)+(recony-truey)**2)
 								specificcount.append(distance)
 
-		fullcount.append(specificcount)
-		label = str(j) + " detections"
-		labels.append(label)
-		
 		total = len(specificcount)
 		
 		if float(total) > float(0):
-		
+			fullcount.append(specificcount)
+			label = str(j) + " detections"
+			labels.append(label)
+
 			specificcount.sort()
 		
 			lower = int(0)

### 2016-04-22 report/draft1.tex
Backup 22/4/16

@@
 
+\section{Camera Image Simulation}
+The first requirement for reconstruction using the LPD method is to identify the DC pixel in a shower image, and consequently determine the number of DC photons present.
+A full simulation of air showers was performed using the CORSIKA package, and the simtelarray package was used to simulate HESS camera images generated from the shower.
+The hesioxxx package was used to extract camera image pixel positions and signals.
+
+\subsection{CORSIKA}
+A full simulation of air showers was performed using the CORSIKA package \cite{Heck98}, assuming a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
+The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{2.7}$.
+Four random seed numbers were passed to the program, generated using the overall job number and the run number corresponding to the parallel computing task index.
+Thus, for each set of simulations, 4 unique random number seeds were used.
+An altitude of 1800m was assumed, again corresponding to the HESS site.
+The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$.
+
+In order to identify the DC pixel, each simulation run with an energy cut of 10 PeV on all muons and electrons.
+The consequence of this was to ensure that only the Cherenkov Light from the primary particle, as well as its fragments, was simulated.
+A second identical simulation was run with the same random seeds but without the energy cut on muons and electrons, giving a complete air shower including the DC light.
+
+\subsection{Sim\textunderscore telarray}
+Using the sim\textunderscore telarray package, the expected hardware response to the air shower can be simulated. Again, the response of the HESS telescope was selected for simulation, accounting for
+
 \section{Cosmic Ray Event Simulation}
@@
 \subsection{Atmospheric Absorption}
-Cosmic Rays get absorbed and stuff.
+The Cherenkov Light, mostly emitted in the visible blue part of the EM spectrum, experiences relatively little atmospheric absorption.
+The major of Rayleigh scattering-based atmospheric absorption occurs in the lower part of the troposphere, and thus the atmospheric absorption is almost independent of emission up to first interaction height.
 

### 2016-04-26 report/draft1.tex
Backup 26/4/16

@@
 \usepackage{gensymb}
+\usepackage{booktabs}
 \begin{document}
@@
 \newpage
+
+\section{Preface}
+I basically just did everything. It was great.
+\newpage
+
 \section{Introduction}
@@
 
-\section{Camera Image Simulation}
+\section{DC Pixel Identification}
 The first requirement for reconstruction using the LPD method is to identify the DC pixel in a shower image, and consequently determine the number of DC photons present.
 A full simulation of air showers was performed using the CORSIKA package, and the simtelarray package was used to simulate HESS camera images generated from the shower.
-The hesioxxx package was used to extract camera image pixel positions and signals.
+A Boosted Decision Tree (BDT) was trained using image parameters to identify DC pixels, and its performance was tested.
 
@@
 \subsection{Sim\textunderscore telarray}
-Using the sim\textunderscore telarray package, the expected hardware response to the air shower can be simulated. Again, the response of the HESS telescope was selected for simulation, accounting for
+Using the sim\textunderscore telarray package, the expected hardware response to the air shower can be simulated.
+Again, the built-in response of the HESS telescope was selected for simulation.
+The program accounts for atmospheric transmission and density, mirror positions, sizes and reflectivities, camera shadowing and triggering, quantum efficiency and pulse responses.
+The resultant images can be considered representative of true camera images to a good approximation.
+
+A script was written to extract the location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated NUMBER OF PHOTOELECTRONS.
+In addition, the Sim\textunderscore telarray derives various Hillas image parameters, which the script also extracted.
+These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated.
+Further the reconstructed shower direction and the shower center of gravity were calculated as positions in azimuth and zenith.
+Additionally the calculated energy and distance to core $r_{core}$ were recorded.
+
+A entry was constructed for every pixel, containing its count and position.
+The variables $ \Delta_{C.o.G}$, $\Delta_{Direction}$ and $\Delta_{Line}$ were defined as the distance from the pixel to the shower center of gravity, shower direction, and the line joining those two points.
+Furthermore, the nearest neigbouring pixel IDs were calculated for every pixel position, enabling the count in each neighbouring pixel to be found.
+From this, two further pixel variables were defined.
+The largest neighbouring count $Count_{N.N.max}$ was found, and the ratio $ Q_{DC} = \frac{Count}{Count_{N.N.max}} $ was recorded.
+In addition the Nearest Neighbour Mean Count was recorded.
+This pixel dataset was created for each camera image, and stored for further analysis.
+
+\subsection{Classic DC Identification}
+The initial method used by the HESS collaboration \cite{hess07} was replicated for this analysis, in which a number of cuts were applied to each image dataset.
+
+\begin{table}[h!]
+  \centering
+  \caption{Cuts applied to image pixel sets}
+  \label{tab:table1}
+  \begin{tabular}{ccc}
+    \toprule
+    Variable & Cut\\
+    \midrule
+     $r_{core}$ & \textgreater 0.4 \\
+     $Q_{DC}$ & \textgreater 1.3 \\
+     $ \Delta_{C.o.G}$ & \textgreater 0.17 \\
+     $ \Delta_{C.o.G}$ & \textless 0.91 \\
+     $\Delta_{Direction}$ & \textless 0.45 \\
+     $\Delta_{Line}$ & \textless 0.23 \\
+     Aspect Ratio & \textless 0.75 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+From the subset of pixels satisfying these conditions, the DC pixel was selected as the remaining pixel with $Q_{DC}$.
+The result was compared with the true DC pixel, identified from the hadron-only image, to test the accuracy of this cut.
+Out of 400 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Count_{DC} > 5500$ in the hadron-only image.
+SOMETHING!
+Of this subset of 'DC events', 17\% events passed all of the required cuts.
+The QDC was found to be 100\% accurate in identifying the DC pixel in those passing events.
+
+\subsection{Boosted Decision Tree DC Identification}  As an alternative to  new method of DC pixel identification was developed as part of this analysis, using a BDT trained with the Scikit Learn Python package.
+A set of 2000 simulated events was selected, and randomly split through use of the python random.random() function into two subsets for training and testing.
+The variable $DC_{Count} = Count-Mean_{N.N}$ was defined as the reconstructed \textquoteleft DC signal', assuming the pixel was the DC candidate.
+For every pixel in the 2000 simulated events HESS 1 images, an entry was formed of $Q_{DC}$, $ \Delta_{C.o.G}$, $\Delta_{Direction}$, $\Delta_{Line}$, Channel1, Channel0, $DC_{Count}$ and $Mean_{N.N}$.
+A score of 0 was assigned to every pixel to indicate background, with the exception of those that were identified as the DC pixel through the Shower-Free simulation.
+If the DC count was larger than 300, the pixel was included with a score of 1, identifying it as a signal pixel.
+Pure DC pixels below the threshold cut of 300 were deemed to be too faint to reconstruct, so these entries were omitted from the training set.
+
+Having created a dataset, the BDT was then trained with a maximum depth of 5, and 100 trees generated.
+It was found that the BDT was 100 \% accurate for the entire training dataset, with a breakdown of 100 \% for the training background and 99 \% accurate with the training signal.
+When the trained BDT was applied to the testing pixels, it was found to be 99.99 \%  accurate for the entire training dataset, with a breakdown of 100 \% for the testing background and 99 \% accurate with the testing signal.
+This indicates that the BDT was not significantly overtrained, which would otherwise be manifested by a large divergence in accuracy between testing and training data.
+
+\subsection{Composite Event Selection}
+Having trained the BDT successfully, it was then applied to the same dataset as for the classic QDC identification.
+In each camera image, the event with the largest BDT score was deemed to be \textquoteleft most signal-like', and thus selected as the DC pixel candidate.
+A cut was applied, requiring $Probability_{signal} > 0.5$ for the DC candidate to be accepted.
+
+With this cut applied, out of 1896 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Count_{DC} > 5500$ in the hadron-only image.
+Of this subset of 'DC events', 46\% events passed all of the required cuts.
+The BDT was found to be 75 \% accurate in identifying the DC pixel in those passing events.
+
+In FIG, a plot of true vs.
+reconstructed DC count is shown, obtained by comparing the BDT selected pixel to the hadron-only DC pixel.
+The black line indicates the optimal 1:1 ratio that we are aiming for.
+It is seen that there the vast majority of misidentified events have a small $candidate_{DC count}$, forming a red line in the region $candidate_{DC count} \approx 0$.
+To remove these misidentified events, we can apply a second cut requiring $candidate_{DC count} > 300$.
+
+Application of this combined cut greatly increases the successful identification rate.
+Of the 2000 events, 84\% of events passed all of the required cuts.
+The BDT was found to be 90 \% accurate in identifying the DC pixel in those passing events.
+This represents a very significant improvement in DC pixel identification over the previous QDC method, and corresponds to a fivefold increase in the number of HESS data events that can be studied using the LPD method.
+
+\subsection{Error in calculated $Count_{DC}$}
+Having successfully identified the DC pixel in many events, we can calculate the difference between the derived $candidate_{DC count}$ and the hadron-only $True_{DC}$ to determine the error we will find for the LPD.
+Binning the difference $\Delta = candidate_{DC count} - True_{DC count}$ as shown in FIG, we find that the mean difference is 65 and the median difference is -75.
+We thus see that the distribution is not significantly skewed.
+However, the Standard deviation is approximately 600 when measured both by half of the difference from the 16th to 84th centile, and by 68th centile of an absolute difference.
+This again suggests that, although skewed, the fraction error in intensity is rather large.
 
@@
 The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...
+
+NOW I KNOW!
 

### 2016-04-26 CORSIKA/combineforBDT.py

@@ -16,21 +16,32 @@ j = 2000
 
 targetfolder = filepath + cfg.jobID +"/"
 
+sys.path.append('/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/misc')
+from progressbar import ProgressBar
+custom_options = {
+	'end': 100,
+	'width': 100,
+	'format': '%(progress)s%% [%(fill)s%(blank)s]'
+}
+
+p = ProgressBar(**custom_options)
+print p
+
 with open(targetfolder + "BDTpixels.csv", 'wb') as csvout:
 	writer = csv.writer(csvout, delimiter=',')
-	writer.writerow(["Count", "QDC", "Delta_direction", "Delta_Centre_of_Gravity", "Delta_line", "Energy", "Nearest_Neighbour_Mean", "score"])
+	writer.writerow(["Channel1", "QDC", "Delta_direction", "Delta_Centre_of_Gravity", "Delta_line", "Energy", "Nearest_Neighbour_Mean", "score", "Channel0"])
 	while (i < j) or (os.path.isfile(targetfolder + "run" + str(i) + "/fullpixels1.csv")):
 		if (os.path.isfile(targetfolder + "run" + str(i) + "/fullpixels1.csv")):
 			for k in range(1,5):
 			
 				path = targetfolder + "run" + str(i) + "/fullpixels" + str(k) + ".csv"
-				print path
 				
 				with open(path, 'rb') as csvfile:
 					reader = csv.reader(csvfile, delimiter=',', quotechar='|')
 					for row in reader:
 						if (row[11] == str(0)) or (row[11] == str(1)):
-							count = row[1]
+							channel1 = row[1]
+							channel0 = row[2]
 							QDC = row[7]
 							Dd = row[8]
 							Dcg = row[9]
@@ -39,9 +50,11 @@ with open(targetfolder + "BDTpixels.csv", 'wb') as csvout:
 							energy = row[12]
 							nnmean = row[13]
 							
-							entry = [count, QDC, Dd, Dcg, Dline, energy, nnmean, score]
+							entry = [channel1, QDC, Dd, Dcg, Dline, energy, nnmean, score, channel0]
 							
 							writer.writerow(entry)
 						else:
 							pass
+		if (int(float(i)*100/float(j)) - float(i)*100/float(j)) ==0:
+			print p+1
 		i+=1

### 2016-04-26 CORSIKA/extractpixels.py

@@ -3,6 +3,7 @@ import os.path
 import numpy as np
 from sklearn.externals import joblib
 from sklearn import ensemble
+import initialisecuts as ic
 
 offset="0"
 
@@ -49,11 +50,21 @@ with open(base_file_name, 'rb') as csvfile:
 
 		if len(row) > 8:
 			if row[8] == "Pixel":
-				if str(row[11]) == "1:":
+				if str(row[11]) == "0:":
 					pixno = float(row[9][:-1])
 					channel = float(row[11][:-1])
 					count = float(row[12])
-					current.append([pixno, count, channel])
+					current.append([pixno, count])
+					new=False
+					test=True
+				elif str(row[11]) == "1:":
+					pixno = int(row[9][:-1])
+					channel = float(row[11][:-1])
+					count = float(row[12])
+					entry = current[pixno]
+					oldpixno = entry[0]
+					oldcount = entry[1]
+					current[pixno] = [pixno, count, oldcount]
 					new=False
 					test=True
 		
@@ -124,14 +135,8 @@ mpl.use('Agg')
 import matplotlib.pyplot as plt
 from matplotlib.patches import Circle
 
-arcut = 0.75
-ddireccut = 0.45
-dcogl = 0.17
-dcogu = 0.91
-dlinecut = 0.23
-radiuscut = 40
-QDCcut = 1
-
+arcut, ddireccut, dcogl, dcogu, dlinecut, radiuscut = ic.run()
+cut, ucut, QDCcut, DCcut, signalcut = ic.runforstats()
 
 picklepath = '/nfs/astrop/d6/rstein/BDTpickle/DCpixelclassifier.pkl'
 if os.path.isfile(picklepath):
@@ -231,10 +236,13 @@ with open(run_dir + "/hillasparameters.csv", 'rb') as csvfile:
 						
 					
 					entry = current[ID]
-					value = entry[1]
+					channel1 = entry[1]
+					channel0 = entry[2]
 					
-					QDC = float(value)/max(nncounts)
+					QDC = float(channel1)/max(nncounts)
 					nnmean = np.mean(nncounts)
+					
+					signal = channel1-nnmean
 
 					ddirec = math.sqrt((xpos-showerx)**2 + (ypos-showery)**2)
 					dcog = math.sqrt((xpos-cogx)**2 + (ypos-cogy)**2)
[…]

### 2016-04-27 report/draft1.tex
Backup 27/4/16

@@
 
-From the subset of pixels satisfying these conditions, the DC pixel was selected as the remaining pixel with $Q_{DC}$.
+From the subset of pixels satisfying these conditions, the remaining pixel with the largest $Q_{DC}$ was selected as the DC pixel.
 The result was compared with the true DC pixel, identified from the hadron-only image, to test the accuracy of this cut.
@@
 Of this subset of 'DC events', 17\% events passed all of the required cuts.
-The QDC was found to be 100\% accurate in identifying the DC pixel in those passing events.
+The QDC was found to be 100\% accurate in identifying the DC pixel in those passing events \ref{fig:cutdistribution}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{cutdistribution}
+\caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000.
+Events below this are unlikely to be identified correctly because the DEC light is too faint.
+In the top right- the distribution of the dataset is shown, once all the non-QDC cuts have been applied.
+In the bottom left, the BDT score distribution is shown before any cuts.
+On the bottom right, we see the same distribution after both signal and BDT score cuts are applied.
+All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.}
+\label{fig:cutdistribution}
+\end{center}
+\end{figure}
 
@@
 
-With this cut applied, out of 1896 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Count_{DC} > 5500$ in the hadron-only image.
-Of this subset of 'DC events', 46\% events passed all of the required cuts.
-The BDT was found to be 75 \% accurate in identifying the DC pixel in those passing events.
+With this cut applied, out of 1200 events, 46\% events passed all of the required cuts. The BDT was found to be 75 \% accurate in identifying the DC pixel in those passing events.
 
-In FIG, a plot of true vs.
+In \ref{fig:cutdistribution}, a plot of true vs.
 reconstructed DC count is shown, obtained by comparing the BDT selected pixel to the hadron-only DC pixel.
@@
 This represents a very significant improvement in DC pixel identification over the previous QDC method, and corresponds to a fivefold increase in the number of HESS data events that can be studied using the LPD method.
+Use of this BDT method is thus assumed throughout the rest of this analysis.
 
@@
 This again suggests that, although skewed, the fraction error in intensity is rather large.
+However, the fractional error found purely on the basis of QDC calculations is EQUALLY LARGE??LARGER?.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{DCcounterror}
+\caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left.
+In the top right the same is shown for events which were rejected.
+The true DC signals for events which passed the cuts is plotted against the reconstructed signals in the lower left, and for rejected events in the lower right.
+As in \ref{fig:cutdistribution}, in all plots a green event is one in which the DC pixel has been correctly identified, while a red event is one that has been incorrectly identified.}
+\label{fig:dcdiff}
+\end{center}
+\end{figure}
 
@@
 These restrictions confine us to Cosmic Rays with specific characteristics.
+
+\subsection{Cherenkov Emission}
+Cosmic Rays follow a well-defined power law where $ \frac{dN(E)}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ?
+$.
+Consequently higher energy Cosmic Rays are heavily suppressed.
+The Energy Threshold for Cherenkov Light Emission as a function of height is illustrated in \ref{fig:generalenergy}.
+Once the Energy of a Cosmic Ray exceeds the local Cherenkov Energy Threshold of the atmosphere, the Nucleus will begin emitting a ring of Cherenkov Light.
+
+Above threshold, Cherenkov Emission is determined by the Frank Tamm formula!!!!!
+A full simulation of the LPD was undertaken.
+Under the assumption of constant magnetic permittivity and a zenith angle of $90\degree$ we can use the approximate form \[ N_{photons} \approx (37000 \times Z^{2} \times \Delta_{h} \times \Delta_{E})\] where $\Delta_{h}$ is the vertical distance travelled in meters and $\Delta_{E}$ is the emission energy range in eV.
+
+If we divide the number of emitted photons by the area of the annulus between the ring radii at $h$ and $h - \Delta_{h}$, we retrieve the LDF shown in \ref{fig:lpd}, which varies with $ \rho_{DC}  = f(r) \times Z^{2}$ .
+Thus the amplitude of the LDF is proportional to the charge of the Cosmic Ray, enabling the Charge to be determined from the DC emission.
+This is the basis for charge reconstruction in the LDF method.
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=0.9\textheight]{logenergyradius}
+\caption{The Threshold Energy for Cherenkov Emission is marked in blue.
+With the assumption of $\beta=1$, the maximum emission radius is marked in black.
+The red and green and magenta line show the emission radius at 3.57 and 0.75 and 0.23 TeV per Nucleon respectively.
+The Green line is sufficiently close to the background to be saturated at 24km, while the magenta line is not.}
+\label{fig:generalenergy}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=0.9\textheight]{simulatedlpd}
+\caption{The LPD obtained from simulation of an Iron Nucleus up to a first interaction height of 25km for a range of Core Energies.
+An altitude of 1.8km for the experimental array is assumed.
+Atmospheric absorption, although neglected, is broadly constant across the emission range leading to uniform amplitude scaling.}
+\label{fig:lpd}
+\end{center}
+\end{figure}
+
+The Refractive Index of the atmosphere, and thus the Cherenkov angle $\theta_{C}$, increases as the altitude decreases.
+The refractive index at a series of heights, based on data from the HESS site, is shown \ref{fig:lpd}.
+Exponentials are fitted between points to provide interpolation, and a comparison can be made to a linear interpolation that is also plotted.
+Despite the exponential interpolation, discontinuities in the second derivative of the refractive index prevent the LPD from being smooth in the simulation.
+This is unimportant, because in reality the variation due to atmospheric conditions and random noise will smear out any discontinuities in the LDF.
+
+Emission continues until the first interaction with the atmosphere, occurring at a randomly distributed height we call $h$.
+Then for a given Telescope Array altitude above sea level, simple trigonometry yields the radius of the LDF on the ground:
+\[ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})\]
+
+Thus the upper atmosphere emission contributes to the inner LDF, while the lower atmosphere emission contributes to the outer LDF.
+We can also see ground emission radius as a function of height in \ref{fig:generalenergy}.
+We find that the high-radius emission (occurring near the first interaction region) varies little between different high energies.
+We deem this to be \textquoteleft Saturated Emission\textquoteright.
+
+To accurately quantify Saturated Emission, we can compare the photon density to the theoretical maximum photon density, corresponding to an infinite-energy particle with $\beta =1$.
+The illustrated maximum is useful as a reference, although because the atmosphere is not modelled beyond an altitude of 120km, the small-radius emission is not accurately simulated entirely correctly.
+However, real cosmic rays in the considered energy regime will all cross the emission threshold and begin emission at an altitude much lower than 120km, so can be considered accurately modelled.
+Absorption WAS/WAS NOT modelled.
+
+However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon as shown in \ref{fig:lpd}!
+The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...
 
@@
 \end{figure}
-
-\subsection{Energy Considerations}
-Cosmic Rays follow a well-defined power law where $ \frac{dN(E)}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ?
-$.
-Consequently higher energy Cosmic Rays are heavily suppressed.
-The Energy Threshold for Cherenkov Light Emission as a function of height is illustrated in \ref{fig:generalenergy}.
-Once the Energy of a Cosmic Ray exceeds the local Cherenkov Energy Threshold of the atmosphere, the Nucleus will begin emitting a ring of Cherenkov Light.
-Emission continues until the first interaction with the atmosphere, occurring at a randomly distributed height we call $h$.
-Then for a given Telescope Array altitude above sea level, simple trigonometry yields the radius of the LDF on the ground:
-\[ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})\]
-
-The Refractive Index of the atmosphere, and thus the Cherenkov angle $\theta_{C}$, increases as the altitude decreases.
-Thus the upper atmosphere emission contributes to the inner LDF, while the lower atmosphere emission contributes to the outer LDF.
-We can also see ground emission radius as a function of height in \ref{fig:generalenergy}.
-We find that the high-radius emission (occurring near the first interaction region) varies little between different high energies.
-We deem this to be \textquoteleft Saturated Emission\textquoteright.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=0.9\textheight]{logenergyradius}
-\caption{The Threshold Energy for Cherenkov Emission is marked in blue.
-With the assumption of $\beta=1$, the maximum emission radius is marked in black.
-The red and green and magenta line show the emission radius at 3.57 and 0.75 and 0.23 TeV per Nucleon respectively.
-The Green line is sufficiently close to the background to be saturated at 24km, while the magenta line is not.}
-\label{fig:generalenergy}
-\end{center}
-\end{figure}
-
-\subsection{Nuclear Charge}
-Cherenkov Emission is determined by the Frank Tamm formula!!!!!
-
-Under the assumption of constant magnetic permittivity and a zenith angle of $90\degree$ we can use the approximate form \[ N_{photons} \approx (37000 \times Z^{2} \times \Delta_{h} \times \Delta_{E})\] where $\Delta_{h}$ is the vertical distance travelled in meters and $\Delta_{E}$ is the emission energy range in eV.
-
-If we divide the number of emitted photons by the area of the annulus between the ring radii at $h$ and $h - \Delta_{h}$, we retrieve the LDF shown in \ref{fig:lpd}, which varies with $ \rho_{DC}  = f(r) \times Z^{2}$ .
-Thus the amplitude of the LDF is proportional to the charge of the Cosmic Ray, enabling the Charge to be determined from the DC emission.
-This is the basis for charge reconstruction in the LDF method.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=0.9\textheight]{simulatedlpd}
-\caption{The LPD obtained from simulation of an Iron Nucleus up to a first interaction height of 25km for a range of Core Energies.
-An altitude of 1.8km for the experimental array is assumed.
-Atmospheric absorption, although neglected, is broadly constant across the emission range leading to uniform amplitude scaling.}
-\label{fig:lpd}
-\end{center}
-\end{figure}
-
-\subsection{Energy saturation region}
-However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon as shown in \ref{fig:lpd}!
-The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...
-
-NOW I KNOW!
 

### 2016-04-27 CORSIKA/counterrorstats.py

@@ -1,0 +1,189 @@
+import sys
+import os.path
+import argparse, math, random, time
+import csv
+import numpy as np
+import os.path
+import initialisecuts as ic
+import matplotlib as mpl
+mpl.use('Agg')
+import matplotlib.pyplot as plt
+
+sys.path.append('/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/misc')
+from progressbar import ProgressBar
+
+parser = argparse.ArgumentParser()
+parser.add_argument("-jid", "--jobID", default="1957737")
+
+cfg = parser.parse_args()
+
+filepath = "/nfs/astrop/d6/rstein/data/"
+
+i = 1
+j = 500
+
+passed = [[], []]
+rejected = [[], []]
+passeddiff=[]
+rejecteddiff=[]
+
+passedcsignals= [[], [], [], []]
+passedDCsignals = [[], [], [], []]
+rejectedcsignals = [[], [], [], []]
+rejectedDCsignals =[[], [], [], []]
+
+targetfolder = filepath + cfg.jobID +"/"
+
+cut, ucut, QDCcut, DCcut, signalcut = ic.runforstats()
+
+custom_options = {
+	'end': 100,
+	'width': 100,
+	'format': '%(progress)s%% [%(fill)s%(blank)s]'
+}
+
+p = ProgressBar(**custom_options)
+print p
+
+while (i < j):
+	for k in range(1,5):
+		path = targetfolder + "run" + str(i) + "/candidate" + str(k) + ".txt"
+		if (os.path.isfile(path)):
+			
+			DCpath =  targetfolder + "run" + str(i) + "/DCpixel" + str(k) + ".text"
+			
+			with open(path, 'rb') as f:
+				result = str(f.readline()).rstrip()
+				candidateentry = eval(str(f.readline()))
+				candidatecount = candidateentry[1]
+				candidatennmean = candidateentry[13]
+				candidatesignal = candidatecount-candidatennmean
+				score = candidateentry[14]
+				
+				candidatenn = candidateentry[6]
+				nnmax = np.max(candidatenn)
+				nnmin = np.min(candidatenn)
+				bkg = 0.5* (nnmax + nnmin)
+				newsig = candidatecount - bkg
+				
+				passcut = False
+				
+				if (str(result) == str(True)):
+					markerindex = 2
+					passcut = True
+				else:
+					markerindex = 0
[…]

### 2016-04-27 misc/progressbar.py

@@ -1,0 +1,80 @@
+import sys
+import time
+
+class ProgressBar(object):
+    """ProgressBar class holds the options of the progress bar.
+    The options are:
+        start   State from which start the progress. For example, if start is
+                5 and the end is 10, the progress of this state is 50%
+        end     State in which the progress has terminated.
+        width   --
+        fill    String to use for "filled" used to represent the progress
+        blank   String to use for "filled" used to represent remaining space.
+        format  Format
+        incremental
+    """
+    def __init__(self, start=0, end=10, width=12, fill='=', blank='.', format='[%(fill)s>%(blank)s] %(progress)s%%', incremental=True):
+        super(ProgressBar, self).__init__()
+
+        self.start = start
+        self.end = end
+        self.width = width
+        self.fill = fill
+        self.blank = blank
+        self.format = format
+        self.incremental = incremental
+        self.step = 100 / float(width) #fix
+        self.reset()
+
+    def __add__(self, increment):
+        increment = self._get_progress(increment)
+        if 100 > self.progress + increment:
+            self.progress += increment
+        else:
+            self.progress = 100
+        return self
+
+    def __str__(self):
+        progressed = int(self.progress / self.step) #fix
+        fill = progressed * self.fill
+        blank = (self.width - progressed) * self.blank
+        return self.format % {'fill': fill, 'blank': blank, 'progress': int(self.progress)}
+
+    __repr__ = __str__
+
+    def _get_progress(self, increment):
+        return float(increment * 100) / self.end
+
+    def reset(self):
+        """Resets the current progress to the start point"""
+        self.progress = self._get_progress(self.start)
+        return self
+
+class AnimatedProgressBar(ProgressBar):
+    """Extends ProgressBar to allow you to use it straighforward on a script.
+    Accepts an extra keyword argument named `stdout` (by default use sys.stdout)
+    and may be any file-object to which send the progress status.
+    """
+    def __init__(self, *args, **kwargs):
+        super(AnimatedProgressBar, self).__init__(*args, **kwargs)
+        self.stdout = kwargs.get('stdout', sys.stdout)
+
+    def show_progress(self):
+        if hasattr(self.stdout, 'isatty') and self.stdout.isatty():
+            self.stdout.write('\r')
+        else:
+            self.stdout.write('\n')
+        self.stdout.write(str(self))
+        self.stdout.flush()
+
+if __name__ == '__main__':
[…]

### 2016-04-27 report/draft1.tex
Backup 27/4/16

@@
 \section{Introduction}
-There are numerous Telescope Arrays which image the Cherenkov Light emitted by Cosmic Rays in the atmosphere, including the HESS, Magic and Veritas Experiments.
+There are numerous Telescope Arrays which image the Cherenkov Light emitted by Cosmic Rays in the atmosphere, including the HESS, MAGIC and VERITAS Experiments.
 All rely on Hillas Analysis with extracted parameters from each of the camera images being used to reconstruct the events, but heavy atmospheric blurring means that charge resolution is very poor.
@@
 Cosmic Rays that are imaged by these telescopes have energies between $13 $TeV and $200 $TeV.
-At present, no study of the relative abundance of different cosmic ray elemental abundances exists at these energies.It could provide important clues regarding the mechanism of CR formation and propagation in the galaxy but current charge resolution from Hillas Analysis is not small enough to undertake such a study.
+At present, no study of the relative abundance of different cosmic ray elemental abundances exists at these energies.
+It could provide important clues regarding the mechanism of Cosmic Ray formation and propagation in the galaxy, but current charge resolution from Hillas Analysis is not small enough to undertake such a study.
 
@@
 \section{DC Pixel Identification}
-The first requirement for reconstruction using the LPD method is to identify the DC pixel in a shower image, and consequently determine the number of DC photons present.
-A full simulation of air showers was performed using the CORSIKA package, and the simtelarray package was used to simulate HESS camera images generated from the shower.
+The first requirement for reconstruction using the LPD method is to identify the DC pixel in a shower image, and consequently determine the number of DC photoelectrons present.
+A full simulation of air showers was performed using the CORSIKA package, and the sim\textunderscore telarray package was used to simulate HESS camera images generated from the shower.
 A Boosted Decision Tree (BDT) was trained using image parameters to identify DC pixels, and its performance was tested.
@@
 \subsection{CORSIKA}
-A full simulation of air showers was performed using the CORSIKA package \cite{Heck98}, assuming a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
+A full simulation of Cosmic Ray air showers was performed using the CORSIKA package \cite{Heck98}, assuming a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
 The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{2.7}$.
@@
 The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$.
+The four smaller HESS-phase-1 telescopes were arranged in a cross along the x/y axis with the larger HESS-phase-2 \textquoteleft CT5' telescope placed at the center.
+The length of each cross arm was $85m$.
+The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis.
 
@@
 \subsection{Sim\textunderscore telarray}
-Using the sim\textunderscore telarray package, the expected hardware response to the air shower can be simulated.
+Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected hardware response to the air shower can be simulated.
 Again, the built-in response of the HESS telescope was selected for simulation.
@@
 The resultant images can be considered representative of true camera images to a good approximation.
+For the second, full, simulation, the night sky background was also simulated.
 
-A script was written to extract the location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated NUMBER OF PHOTOELECTRONS.
-In addition, the Sim\textunderscore telarray derives various Hillas image parameters, which the script also extracted.
+A script was written to extract the location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated Intensity.
+THe HESS telescope has both a low gain Channel 0 and a high gain Channel 1.
+In the case of many iron core events, Channel 0 will reach its maximum value and become saturated.
+Thus Channel 0 ceases to be useful for discriminating between high energy DC and non-DC pixels, so was not used in this analysis.
+Instead, only the Channel 1 ADC was extracted by the script, and will be referred to throughout this analysis as $Count$.
+For use in later calculation, the pedestal and calibration of each pixel was recorded.
+
+In addition to the $Count$ of each pixel, the Sim\textunderscore telarray derives various Hillas whole-image parameters, which the script also extracted.
 These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated.
@@
 
-A entry was constructed for every pixel, containing its count and position.
+An entry was constructed for every pixel, containing its count and position.
 The variables $ \Delta_{C.o.G}$, $\Delta_{Direction}$ and $\Delta_{Line}$ were defined as the distance from the pixel to the shower center of gravity, shower direction, and the line joining those two points.
@@
 Use of this BDT method is thus assumed throughout the rest of this analysis.
+
+\subsection{Determining Photoelectrons}
+The number of photoelectrons was ultimately calculated using the formula \[N_{Photoelectrons} = (Intensity-Pedestal)\times calibration\].
 
@@
 
-In order to improve the count rate of high-multiplicity events, we can consider a 3x3 array of Cherenkov Telescopes, which we want to use for identifying CR Elements accurately.
+In order to improve the count rate of high-multiplicity events, we can consider a 3x3 array of Cherenkov Telescopes, which we want to use for identifying Cosmic Ray Elements accurately.
 In \ref{fig:optmiselayout} we see that the \textquoteleft High Multiplicity Count Rate' of events observed by 4 or more telescopes falls with increasing grid separation.

### 2016-04-27 CORSIKA/tester.sh

@@ -1,0 +1,53 @@
+#!/bin/zsh
+# 
+
+#        This is how to submit a job to the cluster:
+#          login to a submit node, e.g. astro-wgs01.desy.de
+#          Initialize by sourcing init script: . /usr/sge/default/common/settings.sh
+#          Start using "qsub empty.sh".
+#          Als Arrawy-Job mit "qsub -t 10-100:2 empty.sh" (10 bis 100 mit Schrittweite 2)
+#          Mit "qstat" wird der Status der Jobs ausgegeben.
+#          Mit "qdel job-id" kann ein Job gekillt werden.
+
+# Name of the job
+#$ -N CorsikaSIM
+
+# runtime/ Maximale Laufzeit, hat einfluss auf die Priorität. Die Schwellen sind 2:59:59, 23:59:59, 2:59:59, 167:59:59
+#~ #$ -l h_rt=167:59:59
+#$ -l h_rt=2:59:59 
+
+# Hosts/  host die benutzt werden sollen
+#$ -l hostname="!bird001.desy.de&!bird002.desy.de&!bird003.desy.de&!bird004.desy.de&!bird009.desy.de"
+
+# 32 oder 64 Bit (x86 oder amd6[[:Troubleshooting|Troubleshooting]]4) ? Es gibt mehr Hosts mit 64 Bit.
+#$ -l arch="amd64"
+
+# Stacksize/  Größe des Stacks
+#$ -l h_stack=10M 
+
+# needed memory/  Benötigter Speicher. Vorsicht: bei mehr als 2G kommt der Job in die long queue.
+#$ -l h_vmem=2G
+
+# Disk space/  Benötigter temporärer Festplattenspeicher auf dem Host .
+#$ -l h_fsize=20G
+
+# group resource for astroparticle group/ unsere Gruppe, damit haben wir Priorität auf den ASTRO-WGS-Hosts.
+#$ -P astrop
+
+# cluster sends email when:/Festlegen, wann eine E-Mail gesendet werden soll:( b bei Beginn, e bei Ende, a bei Abbruch, s bei Suspend)
+#$ -m s
+
+# E-Mail
+#$ -M robert.stein@desy.de
+
+
+# Path for/ Pfade für stdout und stderr
+#$ -o /nfs/astrop/d6/rstein/cluster_output
+#$ -e /nfs/astrop/d6/rstein/cluster_error
+#
+
+# Ab hier beginnt das Script
+
+echo "Temporary directory: " $TMPDIR
+
+

### 2016-04-27 report/draft1.tex
Backup 27/4/16

@@
 All rely on Hillas Analysis with extracted parameters from each of the camera images being used to reconstruct the events, but heavy atmospheric blurring means that charge resolution is very poor.
-For Iron Nucleus events, we would expect to reconstruct \[Z \approx 26 \pm 5 \] with a core position resolution of the core position resolution is roughly $d \approx 20 m $ \cite{hess07}.
+For Iron Nucleus events, we would expect to reconstruct \[Z \approx 26 \pm 5 \] with a core position resolution of roughly $d \approx 20 m $ \cite{hess07}.
 
@@
 From this, two further pixel variables were defined.
-The largest neighbouring count $Count_{N.N.max}$ was found, and the ratio $ Q_{DC} = \frac{Count}{Count_{N.N.max}} $ was recorded.
+The largest neighbouring count $Count_{N.N.max}$ was found, and the ratio $ Q_{DC} = \frac{Count}{Count_{N.N.max}} $ was derived.
 In addition the Nearest Neighbour Mean Count was recorded.
-This pixel dataset was created for each camera image, and stored for further analysis.
+These variables were recorded in every pixel entry, and together the pixel entries formed a complete dataset for each camera image.
 
 \subsection{Classic DC Identification}
-The initial method used by the HESS collaboration \cite{hess07} was replicated for this analysis, in which a number of cuts were applied to each image dataset.
+The original method used by the HESS collaboration \cite{hess07} was initially replicated, for which a number of cuts were applied to each image dataset.
 
@@
 Of this subset of 'DC events', 17\% events passed all of the required cuts.
-The QDC was found to be 100\% accurate in identifying the DC pixel in those passing events \ref{fig:cutdistribution}.
+The $Q_{DC}$ was found to be 100\% accurate in identifying the DC pixel in those passing events, as shown in \ref{fig:cutdistribution}.
 
@@
 Events below this are unlikely to be identified correctly because the DEC light is too faint.
-In the top right- the distribution of the dataset is shown, once all the non-QDC cuts have been applied.
+In the top right- the distribution of the dataset is shown, once all the non-$Q_{DC}$ cuts have been applied.
 In the bottom left, the BDT score distribution is shown before any cuts.
@@
 
-\subsection{Boosted Decision Tree DC Identification}  As an alternative to  new method of DC pixel identification was developed as part of this analysis, using a BDT trained with the Scikit Learn Python package.
+\subsection{Boosted Decision Tree DC Identification}  As an alternative to use of $Q_{DC}$, a new method of DC pixel identification was developed as part of this analysis by using a BDT trained with the Scikit Learn Python package.
 A set of 2000 simulated events was selected, and randomly split through use of the python random.random() function into two subsets for training and testing.
-The variable $DC_{Count} = Count-Mean_{N.N}$ was defined as the reconstructed \textquoteleft DC signal', assuming the pixel was the DC candidate.
+The variable $DC_{Count} = Count-Mean_{N.N}$ was defined as an approximate \textquoteleft DC signal', if the pixel were to be selected as the DC candidate.
 For every pixel in the 2000 simulated events HESS 1 images, an entry was formed of $Q_{DC}$, $ \Delta_{C.o.G}$, $\Delta_{Direction}$, $\Delta_{Line}$, Channel1, Channel0, $DC_{Count}$ and $Mean_{N.N}$.
 A score of 0 was assigned to every pixel to indicate background, with the exception of those that were identified as the DC pixel through the Shower-Free simulation.
-If the DC count was larger than 300, the pixel was included with a score of 1, identifying it as a signal pixel.
+If the DC count in the shower-free simulation was larger than 300, the pixel was included with a score of 1, identifying it as a signal pixel.
 Pure DC pixels below the threshold cut of 300 were deemed to be too faint to reconstruct, so these entries were omitted from the training set.

### 2016-05-10 report/bdtarticle.tex
Backup 10/5/16

--- 2016-04-27 report/draft1.tex
@@
-\documentclass{article}
+\documentclass[]{article}
 \usepackage{graphicx}
@@
 \usepackage{geometry}
-\geometry{a4paper, portrait, margin=1.0in}
 \usepackage{gensymb}
 \usepackage{booktabs}
+
+%opening
+\title{Identification of DC Pixels using Boosted Decision Trees}
+\author{Robert Stein}
 \begin{document}
-\begin{titlepage}
-    \begin{center}
-        \vspace*{1cm}
 
-        \Huge
-        \textbf{Reconstruction of Charge Number of Heavy Cosmic Rays using Cherenkov Light}
+\maketitle
 
-        \LARGE
-
-        \vspace{1cm}
-
-        \textbf{Robert Stein}\\
-        \textbf{CID 00819615}
-
-        \vspace{1cm}
-        \includegraphics[width=0.4\textwidth]{Imperial_College_London_logo} 
-        \hspace{0.5cm}
-        \includegraphics[width=0.4\textwidth]{hamburglogo}
-
-        \vspace{1cm}
-
-        Supervisor: Professor Dieter Horns
-
-        \large
-        \vspace{1.0cm}
-
-        A thesis presented for the degree of\\
-        \textbf{Master in Science}
-
-        \vspace{0.5cm}
-
-        Physics Department\\
-        Imperial College London
-
-        \vspace{0.5cm}
-
-        \today
-
-    \end{center}
-\end{titlepage}
-\section*{Abstract}
-Between impact with the upper atmosphere and decay into a charged particle shower, heavy cosmic ray elements such as Iron emit Cherenkov Light at an angle determined by the Refractive Index of the air and the energy per nucleon.
-This direct Cherenkov Light forms a characteristic circular light distribution on the Earth's surface with an intensity proportional to the square of the cosmic ray charge.
-A new method has been developed to reconstruct this charge number, by fitting the received Cherenkov Photons to the characteristic Lateral Photon Distribution.
-The expected performance for various existing and planned installations will be discussed.
-
-\section*{Zusammenfassung}
-Between impact with the upper atmosphere and decay into a charged particle shower, heavy cosmic ray elements such as Iron emit Cherenkov Light at an angle determined by the Refractive Index of the air and the energy per nucleon.
-This direct Cherenkov Light forms a characteristic circular light distribution on the Earth's surface with an intensity proportional to the square of the cosmic ray charge.
-A new method has been developed to reconstruct this charge number, by fitting the received Cherenkov Photons to the characteristic Lateral Photon Distribution.
-The expected performance for various existing and planned installations will be discussed.
-\newpage
-\tableofcontents
-\newpage
-
-\section{Preface}
-I basically just did everything. It was great.
-\newpage
+\begin{abstract}
+A new method of Direct Cherenkov (DC) pixel identification, relying on machine learning, was developed.
+A set of Cosmic Ray telescope images for training were each simulated twice, both with and without the Extended Air Shower (EAS) background, enabling the DC pixel in every realistic telescope images to be reliably identified using the corresponding background-free image.
+Using all pixels from these realistic training images, a Boosted Decision Tree (BDT) was trained to identify DC pixels.
+The BDT performance was tested on a second set of test realistic telescope images, and compared to existing methods of DC pixel identification.
+\end{abstract}
 
 \section{Introduction}
-There are numerous Telescope Arrays which image the Cherenkov Light emitted by Cosmic Rays in the atmosphere, including the HESS, MAGIC and VERITAS Experiments.
-All rely on Hillas Analysis with extracted parameters from each of the camera images being used to reconstruct the events, but heavy atmospheric blurring means that charge resolution is very poor.
-For Iron Nucleus events, we would expect to reconstruct \[Z \approx 26 \pm 5 \] with a core position resolution of roughly $d \approx 20 m $ \cite{hess07}.
+In Cosmic Ray air showers, the primary particle will often emit DC light in the upper atmosphere, before generating an EAS in interaction with the lower atmosphere.
+In telescope images, this DC light is usually concentrated in a single  \textquoteleft DC pixel'.
+Identifying this pixel is challenging, because the DC light is much fainter than that from the EAS, which will be recorded in the DC pixel and many of surrounding pixels.
+As a result, most telescope images will have many bright pixels adjacent to one another, among which one will be the DC pixel.
+However, if found, the DC pixel can indicate the primary particle energy and charge.
 
-Cosmic Rays that are imaged by these telescopes have energies between $13 $TeV and $200 $TeV.
-At present, no study of the relative abundance of different cosmic ray elemental abundances exists at these energies.
-It could provide important clues regarding the mechanism of Cosmic Ray formation and propagation in the galaxy, but current charge resolution from Hillas Analysis is not small enough to undertake such a study.
+Currently, the DC pixel is identified after applying a number of cuts first, used a method developed by the HESS collaboration \cite{hess07}.
+From the subset of events passing these cuts, the variable \[Q_{DC} = \frac{Intensity}{Intensity_{N.N.max}}\] is defined as the ratio of the intensity of a pixel to the largest neighbouring pixel intensity.
+The DC pixel candidate is simply that with the largest $Q_{DC}$ among those passing the cuts.
+However, this method is neither reliable nor efficient.
+An improved method would aim to increase the number of correctly identified events, and enable cuts which better discriminate between correctly and incorrectly identified events.
 
-Instead of Hillas Analysis, we consider a new method for event reconstruction, in which we fit the known Direct Cherenkovn (DC) Light observed by each telescope to a characteristic Lateral Photon Distribution (LPD) function.
-This new technique is valid both for currently running experiments, as well as planned experiments such as the Cherenkov Telescope Array (CTA).
-It uses only the information from the DC Pixel identified in the shower images.
+Using the CORSIKA package, Cosmic Ray events were simulated both with and without an EAS component.
+The sim\textunderscore telarray package was used to simulate the resultant telescope image, assuming the events were observed by the HESS telescope array.
+Using the EAS-free image to reliably identify the DC pixel, a Boosted Decision Tree (BDT) was trained on each pixel from a training set of telescope images.
+The pixel information was provided in the form of individual pixel entries, rather than as discrete sets for images or events.
 
-A theoretical study by Kieda in 2001 \cite{kieda01} suggested that for a core position resolution of $d \approx 5 $ m, we could expect to see a charge resolution of $ \sigma_{Z} \approx 1 $ for elements of $Z = 20$ or higher.
-In this case the core position resolution would be the limiting value.
-Thus, if the LPD method can achieve this core position resolution, the precision will be sufficient to extract the abundances of the different Cosmic Ray Elements.
-This the prime motivation for the new LPD technique.
+Thus, once trained, the BDT was applied to every pixel entry in a 'testing' set of simulated telescope images.
+For each pixel, the BDT assigned a 'Signal Probability', $P_{signal}$, indicating the likelihood of the pixel being the DC pixel.
+From an entire image, the pixel with the largest $P_{signal}$ was identified as the DC pixel candidate.
+Repeating the double simulation technique for the test data, the true DC pixels in the test telescope images were reliably identified from EAS-free images.
+Thus, we can calculate the accuracy of BDT identification for test telescope images.
 
-\section{DC Pixel Identification}
-The first requirement for reconstruction using the LPD method is to identify the DC pixel in a shower image, and consequently determine the number of DC photoelectrons present.
-A full simulation of air showers was performed using the CORSIKA package, and the sim\textunderscore telarray package was used to simulate HESS camera images generated from the shower.
-A Boosted Decision Tree (BDT) was trained using image parameters to identify DC pixels, and its performance was tested.
-
-\subsection{CORSIKA}
+\section{Image Simulation}
 A full simulation of Cosmic Ray air showers was performed using the CORSIKA package \cite{Heck98}, assuming a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
-The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{2.7}$.
-Four random seed numbers were passed to the program, generated using the overall job number and the run number corresponding to the parallel computing task index.
-Thus, for each set of simulations, 4 unique random number seeds were used.
+The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{-2.7}$.
+For each set of simulated event, 4 unique random number seeds were used to generate the shower.
 An altitude of 1800m was assumed, again corresponding to the HESS site.
@@
 
-In order to identify the DC pixel, each simulation run with an energy cut of 10 PeV on all muons and electrons.
+In order to identify the DC pixel, a \textquoteleft DC Simulation' was initially run with an energy cut of 10 PeV on all muons and electrons.
 The consequence of this was to ensure that only the Cherenkov Light from the primary particle, as well as its fragments, was simulated.
-A second identical simulation was run with the same random seeds but without the energy cut on muons and electrons, giving a complete air shower including the DC light.
+A second identical \textquoteleft Full Simulation' was run including the same random seeds, but without the energy cut on muons and electrons.
+This gave a complete air shower including the DC light, representative of those imaged in telescope arrays.
+Comparisons of the Full and DC simulations enabled us to identify background light in the Full shower.
 
-\subsection{Sim\textunderscore telarray}
-Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected hardware response to the air shower can be simulated.
+Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected hardware response to an air shower can be simulated.
 Again, the built-in response of the HESS telescope was selected for simulation.
 The program accounts for atmospheric transmission and density, mirror positions, sizes and reflectivities, camera shadowing and triggering, quantum efficiency and pulse responses.
-The resultant images can be considered representative of true camera images to a good approximation.
-For the second, full, simulation, the night sky background was also simulated.
+Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered representative of true camera images.
+For the Full Simulation, the night sky background was also simulated by sim\textunderscore telarray.
 
-A script was written to extract the location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated Intensity.
-THe HESS telescope has both a low gain Channel 0 and a high gain Channel 1.
+The HESS telescope has both a high gain Channel 0 and a low gain Channel 1.
+The location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated value of SOMETHING?
+in each value was extracted.
+The pedestal and gain for each channel was also recorded, and from this, Intensity can be found.
+
+\[ Intensity = (Count - Pedestal)\times Gain \]
+
 In the case of many iron core events, Channel 0 will reach its maximum value and become saturated.
 Thus Channel 0 ceases to be useful for discriminating between high energy DC and non-DC pixels, so was not used in this analysis.
-Instead, only the Channel 1 ADC was extracted by the script, and will be referred to throughout this analysis as $Count$.
-For use in later calculation, the pedestal and calibration of each pixel was recorded.
+Instead, only the Channel 1 was used in later analysis.
+Thus the Channel 1 Intensity will simply be referred to throughout this analysis as $Intensity$.
 
-In addition to the $Count$ of each pixel, the Sim\textunderscore telarray derives various Hillas whole-image parameters, which the script also extracted.
+In addition to the $Intensity$ of each pixel, the Sim\textunderscore telarray derives various Hillas whole-image parameters, which the script also extracted.
 These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated.
@@
 From this, two further pixel variables were defined.
-The largest neighbouring count $Count_{N.N.max}$ was found, and the ratio $ Q_{DC} = \frac{Count}{Count_{N.N.max}} $ was derived.
+The largest neighbouring intensity $Intensity_{N.N.max}$ was found, and the ratio $ Q_{DC} = \frac{Intensity}{Intensity_{N.N.max}} $ was derived.
 In addition the Nearest Neighbour Mean Count was recorded.
@@
 The result was compared with the true DC pixel, identified from the hadron-only image, to test the accuracy of this cut.
-Out of 400 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Count_{DC} > 5500$ in the hadron-only image.
+Out of 400 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Intensity_{DC} > 150$ in the hadron-only image.
 SOMETHING!
@@
 \begin{center}
-\includegraphics[width=\textwidth]{cutdistribution}
+\includegraphics[width=\textwidth]{cutdistributionhess1None}
 \caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000.
@@
 
-With this cut applied, out of 1200 events, 46\% events passed all of the required cuts. The BDT was found to be 75 \% accurate in identifying the DC pixel in those passing events.
+With this cut applied, out of 1200 events, 46\% events passed all of the required cuts. The BDT was found to be 85 \% accurate in identifying the DC pixel in those passing events.
 
@@
 
-\subsection{Determining Photoelectrons}
-The number of photoelectrons was ultimately calculated using the formula \[N_{Photoelectrons} = (Intensity-Pedestal)\times calibration\].
-
 \subsection{Error in calculated $Count_{DC}$}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{DCcounterror}
+\includegraphics[width=\textwidth]{DCcounterrorhess1}
 \caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left.
@@
 
-\section{Cosmic Ray Event Simulation}
-In order to reconstruct events using the LPD method, we require saturation of the Cosmic Ray Energy, and that the event can be seen by at least 4 telescopes.
-These restrictions confine us to Cosmic Rays with specific characteristics.
-
-\subsection{Cherenkov Emission}
-Cosmic Rays follow a well-defined power law where $ \frac{dN(E)}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ?
-$.
-Consequently higher energy Cosmic Rays are heavily suppressed.
-The Energy Threshold for Cherenkov Light Emission as a function of height is illustrated in \ref{fig:generalenergy}.
-Once the Energy of a Cosmic Ray exceeds the local Cherenkov Energy Threshold of the atmosphere, the Nucleus will begin emitting a ring of Cherenkov Light.
-
-Above threshold, Cherenkov Emission is determined by the Frank Tamm formula!!!!!
-A full simulation of the LPD was undertaken.
-Under the assumption of constant magnetic permittivity and a zenith angle of $90\degree$ we can use the approximate form \[ N_{photons} \approx (37000 \times Z^{2} \times \Delta_{h} \times \Delta_{E})\] where $\Delta_{h}$ is the vertical distance travelled in meters and $\Delta_{E}$ is the emission energy range in eV.
-
-If we divide the number of emitted photons by the area of the annulus between the ring radii at $h$ and $h - \Delta_{h}$, we retrieve the LDF shown in \ref{fig:lpd}, which varies with $ \rho_{DC}  = f(r) \times Z^{2}$ .
-Thus the amplitude of the LDF is proportional to the charge of the Cosmic Ray, enabling the Charge to be determined from the DC emission.
-This is the basis for charge reconstruction in the LDF method.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=0.9\textheight]{logenergyradius}
-\caption{The Threshold Energy for Cherenkov Emission is marked in blue.
-With the assumption of $\beta=1$, the maximum emission radius is marked in black.
-The red and green and magenta line show the emission radius at 3.57 and 0.75 and 0.23 TeV per Nucleon respectively.
-The Green line is sufficiently close to the background to be saturated at 24km, while the magenta line is not.}
-\label{fig:generalenergy}
-\end{center}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=0.9\textheight]{simulatedlpd}
-\caption{The LPD obtained from simulation of an Iron Nucleus up to a first interaction height of 25km for a range of Core Energies.
-An altitude of 1.8km for the experimental array is assumed.
-Atmospheric absorption, although neglected, is broadly constant across the emission range leading to uniform amplitude scaling.}
-\label{fig:lpd}
-\end{center}
-\end{figure}
-
-The Refractive Index of the atmosphere, and thus the Cherenkov angle $\theta_{C}$, increases as the altitude decreases.
-The refractive index at a series of heights, based on data from the HESS site, is shown \ref{fig:lpd}.
-Exponentials are fitted between points to provide interpolation, and a comparison can be made to a linear interpolation that is also plotted.
-Despite the exponential interpolation, discontinuities in the second derivative of the refractive index prevent the LPD from being smooth in the simulation.
-This is unimportant, because in reality the variation due to atmospheric conditions and random noise will smear out any discontinuities in the LDF.
-
-Emission continues until the first interaction with the atmosphere, occurring at a randomly distributed height we call $h$.
-Then for a given Telescope Array altitude above sea level, simple trigonometry yields the radius of the LDF on the ground:
-\[ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})\]
-
-Thus the upper atmosphere emission contributes to the inner LDF, while the lower atmosphere emission contributes to the outer LDF.
-We can also see ground emission radius as a function of height in \ref{fig:generalenergy}.
-We find that the high-radius emission (occurring near the first interaction region) varies little between different high energies.
-We deem this to be \textquoteleft Saturated Emission\textquoteright.
-
-To accurately quantify Saturated Emission, we can compare the photon density to the theoretical maximum photon density, corresponding to an infinite-energy particle with $\beta =1$.
-The illustrated maximum is useful as a reference, although because the atmosphere is not modelled beyond an altitude of 120km, the small-radius emission is not accurately simulated entirely correctly.
-However, real cosmic rays in the considered energy regime will all cross the emission threshold and begin emission at an altitude much lower than 120km, so can be considered accurately modelled.
-Absorption WAS/WAS NOT modelled.
-
-However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon as shown in \ref{fig:lpd}!
-The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...
-
-\subsection{First Interaction Height}
-Cosmic Rays survival in from the top of the atmosphere follows an exponential decay with the number of 'interaction lengths' passed.
-The interaction length is dependent on the interaction cross section, which increases with density.
-Thus the number of interaction lengths increases exponentially as height decreases.
-The resultant decays occur most often at a height of $h \approx 40 \pm 10$ km , as seen in \ref{fig:generalheight}.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=0.9\textheight]{generalheight}
-\caption{The integrated interaction lengths increases as height decreases.
-Thus the decay probability follows a exponentially increasing distribution.
-The mean first interaction height for all events is roughly 40km above sea level.}
-\label{fig:generalheight}
-\end{center}
-\end{figure}
-
-\subsection{Atmospheric Absorption}
-The Cherenkov Light, mostly emitted in the visible blue part of the EM spectrum, experiences relatively little atmospheric absorption.
-The major of Rayleigh scattering-based atmospheric absorption occurs in the lower part of the troposphere, and thus the atmospheric absorption is almost independent of emission up to first interaction height.
-
-\section{LPD Event Reconstruction}
-
-\subsection{Log Likelihood Minimisation}
-In order to fully reconstruct an event, we need to find the x/y core position, the Energy per Nucleon, the first interaction height and the charge.
-However, if one telescope in a five-telescope array does not observe DC light, this data point can be used to constrain the core position.
-Thus, for the LDF method to be applied, we require a minimum of five telescopes, four or more of which must image the DC light.
-We consider the amount of DC light that each telescope receives to be Poissonian \[  P_{i} ( N_{i, Received} \mid X, Y, Z, height, Epn )  =  \frac{ e^{- \lambda_{i} } \times \lambda_{i} ^{N_{i}} }{N_{i}!} \]
-
-In order to reduce computing time, we can use Stirling's Approximation $\ln( N!
-)  \approx  N \ln(N) - N + \frac{1}{2} \ln(2 \pi N)$.
-Pure night sky background requires that there be more that X photons in a DC pixel, and for this Stirling's Approximation has an error of just Y?.
-We then minimise the Log Likelihood function \[ - \ln(L) = - \sum_{i=1}^{n} \ln(P_{i}) \approx  \sum_{i=1}^{n} [\lambda _{i} - N_{i} \ln(\lambda _{i}) + N_{i} \ln(N_{i}) - N_{i} + \frac{1}{2} \ln(2 \pi N_{i})]  \] where n is the total number of telescopes in the array.
-
-\subsection{Extracting Charge Resolution}
-Having reconstructed many events, we can then derive the $\sigma_{Z}$ of the dataset, giving us a number to directly compare the quality of event reconstruction.
-However, a simple Gaussian 68\% method will yield only half integer values of $\sigma_{Z}$ and very frequently 0.
-This will be unhelpful for comparisons of minor modifications of reconstruction methods.
-
-Instead, we can assume a Gaussian with tails at the highest and lowest reconstructed charge values in the dataset.
-The size of the dataset can be used to calculate the fraction of events that the extreme values represent, and this probability can be converted into a \textquoteleft number of standard deviations from mean'.
-Dividing the Gaussian total width by the number of standard deviations gives us a value for $\sigma$.
-Although this will in most cases tend to overestimate the spread of the data, it will also be sensitive to all increases in the proportion of correctly reconstructed events.
-
-\subsection{Iterative Scanning Minimisation}
-Through $\sigma_{Z}$ calculation, we find that the LDF method initially provides very poor charge reconstruction.
-This is as a result of varying Threshold Energies and the sharp drop in the LDF above the maximum radius, which means the Log Likelihood is frequently discontinuous within the parameter space.
-Consequently, a Minuit-type minimisation algorithm will only be able to find a local minimum near the starting values for the fit parameters.
-
-To overcome this problem, we can iterate over a series of starting values for the parameters, with the aim of scanning the true minimum among the many minima found.
-To simplify matters, we can scan only the integer Z values over the range $ 20 \leq Z \leq 32 $, rather than considering the charge to be a free floating parameter.
-
-In order to reduce the number of calculations needed, we can consider the core position region derived from camera images, as in Hillas Analysis.
-Each telescope will have a Gaussian smeared central axis indicating the direction of the core.
-We overlay the simulated telescope array with a grid of points with grid width 1m.
-Then we select all points satisfy the condition of lying within the shower axis direction confidence interval for every telescope.
-The angular width of the confidence interval from the shower axis will be determined by the precision of the telescopes.
-
-Having determined the relevant Height and Energy ranges, we can then consider combinations of Energy and Height for which the Energy is above the Cherenkov Emission Threshold (and is saturated!).
-This gives us a second set of starting \textquoteleft Coordinates \textquoteright.
-
-The Z value is fixed and the LL function is then minimised with the assigned starting values, with the other four variables allowed to float freely.
-Minimisation typically scans 13 Z values, 10 core position coordinates, and 50 Height/Energy coordinates, yielding $ 13 \times 10 \times 50 = 6500$ minimisations in total.
-Such a technique is resource intensive but reduces $\sigma_{Z}$ by a factor of 5 or more.
-(CHECK this quantitatively and get a graph yo.
-Want to see some plateauing of sigma Z!).
-
-\subsection{Boosted Decision Trees}
-Using one quarter of a large sample of Monte Carlo data, we can train a Boosted Decision Tree (BDT) for a given telescope multiplicity, using the reconstructed x/y core position, height and energy, as well as the Log Likelihood.
-The BDT is told whether each event is \textquoteleft signal' (correctly reconstructed) or \textquoteleft background' (incorrectly reconstructed).
-
-For every simulated event, this trained BDT can then be used to assign a \textquoteleft Signal Probability'.
-On a second quarter of the dataset we can optimise a cut on the minimum signal probability, in order to maximise the ratio of signal to background.
-We find that the $\sigma_{Z}$ of the remaining \textquoteleft Test' Monte Carlo data is reduced when the same BDT cut is applied.
-
-\section{HESS-type Event Reconstruction}
-With a simulation of the HESS Cherenkov 5-Telescope Array we can verify the effectiveness of the technique. 
-\subsection{First Interaction and Energy Saturation}
-The mean first interaction height for all Cherenkov Emitting Cosmic Rays in the atmosphere is 40km, and neglecting variations in atmospheric density profiles around the Earth, this can be considered independent of experimental array.
-However, the multiplicity of event is determined by equipment efficiencies, altitude and telescope layout.
-When the HESS layout is simulated, we find that the 4 telescope events have a mean height of $h \approx 23 \pm 5$ km, as shown in \ref{fig:Hessheight}.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=0.9\textheight]{hessheight}
-\caption{The mean first interaction height for all Cherenkov Events is 40km???. The mean first interaction height for 4 telescope events in the HESS array is 23km}
-\label{fig:Hessheight}
-\end{center}
-\end{figure}
-
-\subsection{Extended Air Shower Background}
-A typical HESS image is shown in \ref{fig:hess}, with the DC pixel visible.
-For HESS cameras, the Extended Air Shower (EAS) produced after the first interaction of the Cosmic Ray overlaps the DC pixel and thus provides background in the LDF.
-As the Energy of the Cosmic Ray increases, the EAS speads over a larger angular area, and at smaller radii, the EAS-DC-shower direction axis contracts, leading to more overlap.
-Thus the background in the DC pixel increases with decreasing radius and increasing Energy.
-In addition, we have a fixed night sky background with 7 photons $m^{-2}$.
-We thus parameterise the background with \[ \rho_{bkg}  = 7 + 5E\].
-The modeled background LPD is shown as part of REF.
-It begins to dominate above roughly 1 TeV per Nucleon, particularly in the case of smaller radii.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{hess}
-\caption{A 4-camera HESS event.
-The shower direction is marked with a white cross, and the DC pixel is indicated with a white arrow.
-The shower axis passes through the shower direction, the DC pixel, and the center of the Extensive Air Shower region lying beyond the DC pixel.}
-\label{fig:hess}
-\end{center}
-\end{figure}
-
-\subsection{Reconstructed Charge Resolution}
-In the preliminary HESS simulation, it was found that the 4 telescope event reconstruction had a charge resolution of $\sigma_{Z} = 1.4$.
-However, requiring that the BDT signal probability satisfied $P > 0.81$ removed $75 \%$ of events, while reducing the Charge resolution to $\sigma_{Z} = 0.9$ .
-With this cut, core position resolution was $d \approx 1.4 m $.
-For 5 telescope events, it was found that the charge resolution was also $\sigma_{Z} = 1.4$.
-However, requiring that the signal probability satisfied $P > 0.05$ removed $53 \%$ of events, including all wrongly reconstructed ones.
-This placed an upper limit on the charge resolution of $\sigma_{Z} < 0.35$ .
-With this cut, core position resolution was $d \approx 0.8 m $.
-
-However, the simulated number of hours for the data was 1200?
-hours, and comparisons with HESS data show just 12 4-telescope events rather than 600.
-Thus, although the technique is valid and effective for HESS, the count rate will limit the potential to conduct any statistical analysis from this experiment.
-
-\section{Optimised Telescope Array}
-NO Background!!!!!
-\subsection{Count Rates}
-
-In order to improve the count rate of high-multiplicity events, we can consider a 3x3 array of Cherenkov Telescopes, which we want to use for identifying Cosmic Ray Elements accurately.
-In \ref{fig:optmiselayout} we see that the \textquoteleft High Multiplicity Count Rate' of events observed by 4 or more telescopes falls with increasing grid separation.
-We can clearly see that the optimum grid spacing will likely lie in the 20-50m region to provide a reasonable count rate.
-Competing with this effect is the reliance of LDF reconstruction on sampling the entire lateral distribution.
-Thus the reconstruction quality will decrease as Grid Width decreases.
-Further study of $\sigma_{Z}$ in this region is required to determine the optimum layout (not necessarily be a grid) for event reconstruction.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{optimiselayout}
-\caption{A simulation of 50 hours of run time for various grid spacing for a 3x3 telescope array.
-Although raw count rate increases with increasing grid width, the \textquoteleft good count' rate of events observed by sufficient telescopes falls rapidly with increasing grid width}
-\label{fig:optmiselayout}
-\end{center}
-\end{figure}
-
-\subsection{Saturation Region Energies}
-
-\subsection{High Speed Telescopes}
-By definition, the EAS shower will arrive on the ground shortly before the DC light.
-There are currently several high-speed Cherenkov telescopes capable of distinguishing between these, allowing a background-free LDF to be fitted.
-Additional study of alternative energy regimes and layouts will also be considered for the case of a high-speed imaging telescope array.
-
-\section{Conclusion}
-Preliminary results suggest that the LDF reconstruction technique will significantly improve charge reconstruction, to a level sufficient for cosmic ray abundance studies.
-However, reliance on high-multiplicity events means that although applicable to current experiments such as HESS, a new optimised telescope array would be required for a statistical analysis.
-Such an array may have a grid spacing of 20-50m, although further study is needed to determine the ideal layout.
 \bibliographystyle{plain}
 \bibliography{report}
+
 \end{document}

### 2016-05-10 report/draft1.tex
Backup 10/5/16

@@
 A full simulation of Cosmic Ray air showers was performed using the CORSIKA package \cite{Heck98}, assuming a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
-The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{2.7}$.
-Four random seed numbers were passed to the program, generated using the overall job number and the run number corresponding to the parallel computing task index.
-Thus, for each set of simulations, 4 unique random number seeds were used.
+The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{-2.7}$.
+For each set of simulated event, 4 unique random number seeds were used to generate the shower.
 An altitude of 1800m was assumed, again corresponding to the HESS site.
@@
 
-In order to identify the DC pixel, each simulation run with an energy cut of 10 PeV on all muons and electrons.
+In order to identify the DC pixel, a \textquoteleft DC Simulation' was initially run with an energy cut of 10 PeV on all muons and electrons.
 The consequence of this was to ensure that only the Cherenkov Light from the primary particle, as well as its fragments, was simulated.
-A second identical simulation was run with the same random seeds but without the energy cut on muons and electrons, giving a complete air shower including the DC light.
+A second identical \textquoteleft Full Simulation' was run including the same random seeds, but without the energy cut on muons and electrons.
+This gave a complete air shower including the DC light, representative of those imaged in telescope arrays.
+Comparisons of the Full and DC simulations enabled us to identify background light in the Full shower.
 
 \subsection{Sim\textunderscore telarray}
-Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected hardware response to the air shower can be simulated.
+Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected hardware response to an air shower can be simulated.
 Again, the built-in response of the HESS telescope was selected for simulation.
 The program accounts for atmospheric transmission and density, mirror positions, sizes and reflectivities, camera shadowing and triggering, quantum efficiency and pulse responses.
-The resultant images can be considered representative of true camera images to a good approximation.
-For the second, full, simulation, the night sky background was also simulated.
+Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered representative of true camera images.
+For the Full Simulation, the night sky background was also simulated by sim\textunderscore telarray.
 
-A script was written to extract the location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated Intensity.
-THe HESS telescope has both a low gain Channel 0 and a high gain Channel 1.
+The HESS telescope has both a high gain Channel 0 and a low gain Channel 1.
+The location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated value of SOMETHING?
+in each value was extracted.
+The pedestal and gain for each channel was also recorded, and from this, Intensity can be found.
+
+\[ Intensity = (Count - Pedestal)\times Gain \]
+
 In the case of many iron core events, Channel 0 will reach its maximum value and become saturated.
 Thus Channel 0 ceases to be useful for discriminating between high energy DC and non-DC pixels, so was not used in this analysis.
-Instead, only the Channel 1 ADC was extracted by the script, and will be referred to throughout this analysis as $Count$.
-For use in later calculation, the pedestal and calibration of each pixel was recorded.
+Instead, only the Channel 1 was used in later analysis.
+Thus the Channel 1 Intensity will simply be referred to throughout this analysis as $Intensity$.
 
-In addition to the $Count$ of each pixel, the Sim\textunderscore telarray derives various Hillas whole-image parameters, which the script also extracted.
+In addition to the $Intensity$ of each pixel, the Sim\textunderscore telarray derives various Hillas whole-image parameters, which the script also extracted.
 These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated.
@@
 \begin{center}
-\includegraphics[width=\textwidth]{cutdistribution}
+\includegraphics[width=\textwidth]{cutdistributionhess1}
 \caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000.

### 2016-05-10 CORSIKA/combineforstatistics.py

@@ -11,355 +11,434 @@ parser.add_argument("-jid", "--jobID", default="2567181")
 
 cfg = parser.parse_args()
 
-filepath = "/nfs/astrop/d6/rstein/data/"
-i = 1
-j = 2000
-totalimages = [0, 0]
-DCpasstotal = [0, 0]
-correctimages =[0, 0]
-totalcut=[0, 0]
-correctcut = [0, 0]
+hess1rgrpath = '/nfs/astrop/d6/rstein/BDTpickle/hess1signalregressor.p'
+hess2rgrpath = '/nfs/astrop/d6/rstein/BDTpickle/hess2signalregressor.p'
+if os.path.isfile(hess1rgrpath):
+	hess1rgr = pickle.load(open(hess1rgrpath, "r"))
+else:
+	print "No hess1 pickle!"
+if os.path.isfile(hess2rgrpath):
+	hess2rgr = pickle.load(open(hess2rgrpath, "r"))
+else:
+	print "No hess2 pickle!"
+	
+signalbdtvariables = []
+with open('/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/CORSIKA/signalBDTvariables.csv', 'rb') as csvfile:
+	reader = csv.reader(csvfile, delimiter=',', quotechar='|')
+	for row in reader:
+		signalbdtvariables.append(row[0])
+print signalbdtvariables
 
-oldtotalimages =[0, 0]
-oldDCpasstotal = [0, 0]
-oldcorrectimages =[0, 0]
-oldtotalcut=[0, 0]
-oldcorrectcut = [0, 0]
+def makeBDTentry(pixelentry):
+	bdtentry =[]
+	for variable in signalbdtvariables:
+		varsplit = variable.split('.')
+		suffix = pixelentry
+		if len(varsplit) > 1:
+			for name in varsplit[:-1]:
+				 suffix = getattr(suffix, name)
+			varname = varsplit[-1]
+		else:
+			varname = variable
+		if hasattr(suffix, varname):
+			newval = getattr(suffix, varname)
+			bdtentry.append(newval)
+		else:
+			return None
+	return bdtentry
 
-altcorrectimages =[0, 0]
-alttotalcut=[0, 0]
-altcorrectcut = [0, 0]
-
-combinedtotal = [0, 0]
-combinedcorrect = [0, 0]
-
-cut, ucut, QDCcut, DCcut, signalcut = ic.runforstats()
-
[…]

### 2016-05-10 CORSIKA/initialisecuts.py

@@ -9,7 +9,7 @@ cut = 0.50
 ucut = 1.01
 QDCcut = 1.3
 DCcut = 150
-signalcut = DCcut
+signalcut = 200
 
 def run(): 
 	return arcut, ddireccut, dcogl, dcogu, dlinecut, radiuscut

### 2016-05-11 report/bdtarticle.tex
Backup 11/5/16

@@
 
-Thus, once trained, the BDT was applied to every pixel entry in a 'testing' set of simulated telescope images.
-For each pixel, the BDT assigned a 'Signal Probability', $P_{signal}$, indicating the likelihood of the pixel being the DC pixel.
+Once trained, the BDT was applied to every pixel entry in a separate 'testing' set of simulated telescope images.
+For each pixel, the BDT assigned a \textquoteleft Signal Probability', $P_{signal}$, indicating the likelihood of the pixel being the DC pixel.
 From an entire image, the pixel with the largest $P_{signal}$ was identified as the DC pixel candidate.
 Repeating the double simulation technique for the test data, the true DC pixels in the test telescope images were reliably identified from EAS-free images.
-Thus, we can calculate the accuracy of BDT identification for test telescope images.
+Thus, the accuracy of BDT identification for test telescope images was calculated.
 
@@
 
-In order to identify the DC pixel, a \textquoteleft DC Simulation' was initially run with an energy cut of 10 PeV on all muons and electrons.
-The consequence of this was to ensure that only the Cherenkov Light from the primary particle, as well as its fragments, was simulated.
-A second identical \textquoteleft Full Simulation' was run including the same random seeds, but without the energy cut on muons and electrons.
-This gave a complete air shower including the DC light, representative of those imaged in telescope arrays.
-Comparisons of the Full and DC simulations enabled us to identify background light in the Full shower.
+In order to identify the DC pixel, a simulation was initially run with an energy cut of 10 PeV on all muons and electrons.
+As the primary particle energy did not exceed this value, neither daughter muons and electrons, nor the photons they would have emitted, were simulated.
+Thus the hadronic Cherenkov Light from the primary particle and daughter fragments, but not the EAS light, was present in the camera image.
+A second identical \textquoteleft EAS Simulation' was run including the same random seeds, but without the energy cut on muons and electrons.
+This gave a complete EAS image including the DC light.
 
-Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected hardware response to an air shower can be simulated.
-Again, the built-in response of the HESS telescope was selected for simulation.
-The program accounts for atmospheric transmission and density, mirror positions, sizes and reflectivities, camera shadowing and triggering, quantum efficiency and pulse responses.
-Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered representative of true camera images.
-For the Full Simulation, the night sky background was also simulated by sim\textunderscore telarray.
+Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected HESS hardware response to each air shower was simulated.
+Among other things, the program accounts for atmospheric transmission and density, mirror positions, sizes and reflectivities, camera shadowing and triggering, quantum efficiency and pulse responses.
+Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered \textquoteleft realistic camera images'.
+For the EAS Simulation, the night sky background was also included by sim\textunderscore telarray, further obscuring the DC pixel.
 
 The HESS telescope has both a high gain Channel 0 and a low gain Channel 1.
-The location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated value of SOMETHING?
-in each value was extracted.
-The pedestal and gain for each channel was also recorded, and from this, Intensity can be found.
+The Sim\textunderscore telarray simulated value of SOMETHING?
+for each channel were recorded.
+The pedestal and gain for each channel were also recorded, and from this, Intensity in the pixel channel was found.
 
@@
 In the case of many iron core events, Channel 0 will reach its maximum value and become saturated.
-Thus Channel 0 ceases to be useful for discriminating between high energy DC and non-DC pixels, so was not used in this analysis.
-Instead, only the Channel 1 was used in later analysis.
-Thus the Channel 1 Intensity will simply be referred to throughout this analysis as $Intensity$.
+Thus Channel 0 ceases to be useful for discriminating between high energy DC and non-DC pixels.
+Consequently, Channel 0 Intensities neglected while Channel 1 Intensities were used in all later analysis.
+This variable will henceforth be referred to simply as $Intensity$.
 
-In addition to the $Intensity$ of each pixel, the Sim\textunderscore telarray derives various Hillas whole-image parameters, which the script also extracted.
+In addition to the $Intensity$ of each pixel, the Sim\textunderscore telarray package derives various Hillas whole-image parameters.
 These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated.
-Further the reconstructed shower direction and the shower center of gravity were calculated as positions in azimuth and zenith.
+Further, the reconstructed shower direction and the shower center of gravity were calculated as positions in azimuth and zenith.
 Additionally the calculated energy and distance to core $r_{core}$ were recorded.
 
-An entry was constructed for every pixel, containing its count and position.
+For every pixel, the location within the image was determined from a standard HESS layout.
 The variables $ \Delta_{C.o.G}$, $\Delta_{Direction}$ and $\Delta_{Line}$ were defined as the distance from the pixel to the shower center of gravity, shower direction, and the line joining those two points.
@@
 
-\subsection{Classic DC Identification}
+\section{DC Pixel Identification}  
 The original method used by the HESS collaboration \cite{hess07} was initially replicated, for which a number of cuts were applied to each image dataset.
@@
     \midrule
-     $r_{core}$ & \textgreater 0.4 \\
      $Q_{DC}$ & \textgreater 1.3 \\
@@
 From the subset of pixels satisfying these conditions, the remaining pixel with the largest $Q_{DC}$ was selected as the DC pixel.
+In the original analysis, an additional cut $r_{core} \textgreater 0.4$ was applied.
+However, the uncertainty in determining the core position through Hillas Analysis is typically of the order of $\pm 30m$.
+Consequently, this particular cut was omitted, along with the Impact Parameter cuts.
+For every image, the total image amplitude $I_{tot}$ was found.
+A cut was also placed requiring $Q_{DC} < 0.14 \times \log(\dfrac{I_{tot}}{(161 \times \cos \theta)})$ where $\theta$ was the zenith angle.
 The result was compared with the true DC pixel, identified from the hadron-only image, to test the accuracy of this cut.
@@
 \begin{center}
-\includegraphics[width=\textwidth]{cutdistributionhess1None}
+\includegraphics[width=\textwidth]{cutdistribution1None}
 \caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000.
@@
 
-\subsection{Boosted Decision Tree DC Identification}  As an alternative to use of $Q_{DC}$, a new method of DC pixel identification was developed as part of this analysis by using a BDT trained with the Scikit Learn Python package.
+As an alternative to use of $Q_{DC}$, a new method of DC pixel identification was developed as part of this analysis by using a BDT trained with the Scikit Learn Python package.
 A set of 2000 simulated events was selected, and randomly split through use of the python random.random() function into two subsets for training and testing.
@@
 
-\subsection{Composite Event Selection}
 Having trained the BDT successfully, it was then applied to the same dataset as for the classic QDC identification.
@@
 
-\subsection{Error in calculated $Count_{DC}$}
-Having successfully identified the DC pixel in many events, we can calculate the difference between the derived $candidate_{DC count}$ and the hadron-only $True_{DC}$ to determine the error we will find for the LPD.
-Binning the difference $\Delta = candidate_{DC count} - True_{DC count}$ as shown in FIG, we find that the mean difference is 65 and the median difference is -75.
-We thus see that the distribution is not significantly skewed.
-However, the Standard deviation is approximately 600 when measured both by half of the difference from the 16th to 84th centile, and by 68th centile of an absolute difference.
-This again suggests that, although skewed, the fraction error in intensity is rather large.
-However, the fractional error found purely on the basis of QDC calculations is EQUALLY LARGE??LARGER?.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{DCcounterrorhess1}
-\caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left.
-In the top right the same is shown for events which were rejected.
-The true DC signals for events which passed the cuts is plotted against the reconstructed signals in the lower left, and for rejected events in the lower right.
-As in \ref{fig:cutdistribution}, in all plots a green event is one in which the DC pixel has been correctly identified, while a red event is one that has been incorrectly identified.}
-\label{fig:dcdiff}
-\end{center}
-\end{figure}
+\section{Conclusion}
+Basically it just worked really well.
 

### 2016-05-11 CORSIKA/extractpixels.py

@@ -13,7 +13,7 @@ mpl.use('Agg')
 import matplotlib.pyplot as plt
 from matplotlib.patches import Circle
 
-arcut, ddireccut, dcogl, dcogu, dlinecut, radiuscut = ic.run()
+arcut, ddireccut, dcogl, dcogu, dlinecut, radiuscut, c1cut = ic.run()
 cut, ucut, QDCcut, DCcut, signalcut = ic.runforstats()
 
 offset="0"
@@ -148,6 +148,7 @@ for category in ["DC", "full"]:
 			for telID in currentsimulation.triggerIDs:
 				tel = currentsimulation.images[telID]
 				tel.findintensities()
+				print tel.hillas.image_size_amplitude_
 			
 			currentsimulation.extractpixelhillas()
 	

### 2016-05-11 CORSIKA/initialisecuts.py

@@ -4,6 +4,7 @@ dcogl = 0.17
 dcogu = 0.91
 dlinecut = 0.23
 radiuscut = 40
+c1cut = 2500
 
 cut = 0.50
 ucut = 1.01
@@ -12,7 +13,7 @@ DCcut = 150
 signalcut = 200
 
 def run(): 
-	return arcut, ddireccut, dcogl, dcogu, dlinecut, radiuscut
+	return arcut, ddireccut, dcogl, dcogu, dlinecut, radiuscut, c1cut
 	
 def runforstats():
 	return cut, ucut, QDCcut, DCcut, signalcut

### 2016-05-11 CORSIKA/runBDT.py

@@ -36,7 +36,7 @@ def wait():
 bdttargetfolder = "/nfs/astrop/d6/rstein/data/" + cfg.BDTID + "/bdtpickle/"
 bdtfilename = bdttargetfolder + "hess2bdtdata.p"
 
-if not cfg.reextract and not cfg.recombine:
+if not cfg.reextract:
 	pass
 else:
 	rextract_for_BDT = "qsub -t 1-200:1 extractpixelsoncluster.sh " + cfg.BDTID

### 2016-05-11 CORSIKA/telescopeclasses.py

@@ -17,7 +17,7 @@ from matplotlib.patches import Circle
 
 #Retrieve the cut values for selecting the candidates, stored in a common file initialisecuts.py
 
-arcut, ddireccut, dcogl, dcogu, dlinecut, radiuscut = ic.run()
+arcut, ddireccut, dcogl, dcogu, dlinecut, radiuscut, c1cut = ic.run()
 cut, ucut, QDCcut, DCcut, signalcut = ic.runforstats()
 
 #Define the total number of channels, here 2 (CHannel0/Channel1)
@@ -433,7 +433,7 @@ class telescopeimage:
 		assigned as the telescope attribute self.QDCID
 		""" 
 		bestID = None
-		bestQDC = None
+		bestQDC = 5.0
 		if hasattr(self.hillas, "aspect_ratio_"):
 			if self.hillas.aspect_ratio_ < arcut:
 				for i in range(len(self.pixels)):
@@ -441,9 +441,11 @@ class telescopeimage:
 					if pixelentry.ddirec < ddireccut:				
 						if dcogl < pixelentry.dcog < dcogu:
 							if pixelentry.dline < dlinecut:
-								if pixelentry.QDC > bestQDC:
-									bestID=i
-									bestQDC=pixelentry.QDC
+								if pixelentry.channel1.intensity < c1cut:
+									if pixelentry.QDC < self.qdccut:
+										if pixelentry.QDC < bestQDC:
+											bestID=i
+											bestQDC=pixelentry.QDC
 		self.QDCID = bestID
 		
 	def getQDCpixel(self):
@@ -577,9 +579,15 @@ class telescopeimage:
 		sm = (cogy-showery)/(cogx - showerx)
 		sc = showery - (sm * showerx)
 		
+		itot = self.hillas.image_size_amplitude_
+		
 		for pixelentry in self.pixels:
 			pixelentry.hillas(cogx, cogy, showerx, showery, sm, sc)
+			pixelentry.image_size_amplitude_=itot
 		
+		arg = itot / (math.sin(math.radians(float(self.altitude)))*161)
+		self.qdccut = 0.14 * math.log(arg)
+				
 		self.findQDCpixel()
 		self.findrawQDCpixel()
 		self.findBDTpixel()
@@ -666,16 +674,17 @@ class pixel:
 		intersectiony = (m * intersectionx) + c
[…]

### 2016-05-17 report/bdtarticle.tex

@@
 In order to identify the DC pixel, a simulation was initially run with an energy cut of 10 PeV on all muons and electrons.
-As the primary particle energy did not exceed this value, neither daughter muons and electrons, nor the photons they would have emitted, were simulated.
+Because this cut exceeded the primary particle energy, neither daughter muons and electrons, nor the photons they would have emitted, were simulated.
 Thus the hadronic Cherenkov Light from the primary particle and daughter fragments, but not the EAS light, was present in the camera image.
@@
 
+\begin{figure}
+\newgeometry{a4paper, portrait, margin=1.0in}
+\centering
+\begin{minipage}{0.45\textwidth}
+\centering
+\includegraphics[trim=80 120 80 150,clip,width=\textwidth]{graphDC}
+\caption{A typical camera image without the EAS shower.
+The DC light is visible in every telescope, indicated by the yellow arrow.
+The shower direction is represented by the white circle.
+The largest telescope is CT5, but the relative image sizes are not done to scale}
+\label{fig:DCtelimage}
+\end{minipage}\hfill
+\begin{minipage}{0.45\textwidth}
+\centering
+\includegraphics[trim=80 120 80 150,clip,width=\textwidth]{graphfull}
+\caption{The same shower as in \ref{fig:DCtelimage} is shown here with the inclusion of the EAS shower.
+The DC light is pixels are again denoted by an orange circle.
+The white star represents the BDT-selected DC pixel, while the white cross represents the shower center of gravity.}
+\label{fig:cutdistribution2}
+\end{minipage}
+\restoregeometry
+\end{figure}
+
 The HESS telescope has both a high gain Channel 0 and a low gain Channel 1.
-The Sim\textunderscore telarray simulated value of SOMETHING?
+The Sim\textunderscore telarray value of SOMETHING?
 for each channel were recorded.
@@
 Thus Channel 0 ceases to be useful for discriminating between high energy DC and non-DC pixels.
-Consequently, Channel 0 Intensities neglected while Channel 1 Intensities were used in all later analysis.
-This variable will henceforth be referred to simply as $Intensity$.
+Consequently, Channel 0 Intensities were neglected while Channel 1 Intensities were used in all later analysis.
+This variable $Intensity$ will henceforth be used referred to Channel 1 Intensity.
 
-In addition to the $Intensity$ of each pixel, the Sim\textunderscore telarray package derives various Hillas whole-image parameters.
+The Sim\textunderscore telarray package derives various Hillas whole-image parameters.
 These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated.
-Further, the reconstructed shower direction and the shower center of gravity were calculated as positions in azimuth and zenith.
-Additionally the calculated energy and distance to core $r_{core}$ were recorded.
+The reconstructed shower direction and the shower center of gravity were also calculated, as positions in azimuth and zenith.
+Additionally the estimated energy and distance from each telescope to core, $r_{core}$,  were recorded.
 
-For every pixel, the location within the image was determined from a standard HESS layout.
+For every pixel, in addition to the $Intensity$, its location within the telescope image was determined from a standard HESS layout.
 The variables $ \Delta_{C.o.G}$, $\Delta_{Direction}$ and $\Delta_{Line}$ were defined as the distance from the pixel to the shower center of gravity, shower direction, and the line joining those two points.
-Furthermore, the nearest neigbouring pixel IDs were calculated for every pixel position, enabling the count in each neighbouring pixel to be found.
-From this, two further pixel variables were defined.
-The largest neighbouring intensity $Intensity_{N.N.max}$ was found, and the ratio $ Q_{DC} = \frac{Intensity}{Intensity_{N.N.max}} $ was derived.
-In addition the Nearest Neighbour Mean Count was recorded.
-These variables were recorded in every pixel entry, and together the pixel entries formed a complete dataset for each camera image.
+Furthermore, the nearest neigbouring pixel IDs were calculated for every pixel position, enabling the $Intensity$ in each neighbouring pixel to be found.
+The largest neighbouring intensity $Intensity_{N.N.max}$ was identified, and the ratio $ Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity} $ was derived.
+In addition, the Nearest Neighbour Mean Intensity was recorded.
 
@@
     \midrule
-     $Q_{DC}$ & \textgreater 1.3 \\
      $ \Delta_{C.o.G}$ & \textgreater 0.17 \\
@@
      Aspect Ratio & \textless 0.75 \\
+     $Q_{DC}$ & \textless 0.14$ \times \log(\frac{I_{tot}}{161 \times \cos \theta})$ \\
     \bottomrule
@@
 
-From the subset of pixels satisfying these conditions, the remaining pixel with the largest $Q_{DC}$ was selected as the DC pixel.
+From the subset of pixels satisfying these conditions, the remaining pixel with the smallest $Q_{DC}$ was selected as the DC pixel candidate.
 In the original analysis, an additional cut $r_{core} \textgreater 0.4$ was applied.
@@
 Consequently, this particular cut was omitted, along with the Impact Parameter cuts.
-For every image, the total image amplitude $I_{tot}$ was found.
-A cut was also placed requiring $Q_{DC} < 0.14 \times \log(\dfrac{I_{tot}}{(161 \times \cos \theta)})$ where $\theta$ was the zenith angle.
-The result was compared with the true DC pixel, identified from the hadron-only image, to test the accuracy of this cut.
-Out of 400 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Intensity_{DC} > 150$ in the hadron-only image.
+For every image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a unique $Q_{DC}$ cut.
+
+The candidates were checked against the true DC pixels from the hadron-only image.
+Out of 400 events, it was fount that only 55\% of the hadron-free events contained a clear DC signal, as defined by requiring the DC pixel to have $Intensity_{DC} > 150$.
+This represents a reasonable target number for DC identification.
 SOMETHING!
-Of this subset of 'DC events', 17\% events passed all of the required cuts.
-The $Q_{DC}$ was found to be 100\% accurate in identifying the DC pixel in those passing events, as shown in \ref{fig:cutdistribution}.
+Of all events, 17\% passed the required cuts.
+The $Q_{DC}$ was found to be 68\% accurate in identifying the DC pixel in those passing events, as shown in \ref{fig:cutdistribution}.
+These values served as a benchmark for BDT performance.
 
@@
 \includegraphics[width=\textwidth]{cutdistribution1None}
-\caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000.
-Events below this are unlikely to be identified correctly because the DEC light is too faint.
-In the top right- the distribution of the dataset is shown, once all the non-$Q_{DC}$ cuts have been applied.
-In the bottom left, the BDT score distribution is shown before any cuts.
-On the bottom right, we see the same distribution after both signal and BDT score cuts are applied.
-All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.}
+\caption{The true $Intensity_{DC}$ in the EAS-free image is shown in the top left, with a broad exponential decay in count as DC intensity increases.
+Sim\textunderscore telarray requires a minimum of 20 photoelectrons in order for a telescope to be triggered, meaning that only events with a true $Intensity_{DC}>20$ photoelectrons can be studied.
+In the top right- the distribution of the dataset is shown, once all $Q_{DC}$ cuts have been applied.
+In the bottom left, the $P_{signal}$ (BDT score) distribution is shown before any cuts.
+On the bottom right, we see the same distribution after both $DC_{Count}$ and $P_{signal}$ cuts are applied.
+All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.
+We desire both a large number of green events, and a good degree separability of red and green events.}
 \label{fig:cutdistribution}
@@
 
-As an alternative to use of $Q_{DC}$, a new method of DC pixel identification was developed as part of this analysis by using a BDT trained with the Scikit Learn Python package.
+For this analysis, a BDT was trained with the Scikit Learn Python package.
 A set of 2000 simulated events was selected, and randomly split through use of the python random.random() function into two subsets for training and testing.
-The variable $DC_{Count} = Count-Mean_{N.N}$ was defined as an approximate \textquoteleft DC signal', if the pixel were to be selected as the DC candidate.
-For every pixel in the 2000 simulated events HESS 1 images, an entry was formed of $Q_{DC}$, $ \Delta_{C.o.G}$, $\Delta_{Direction}$, $\Delta_{Line}$, Channel1, Channel0, $DC_{Count}$ and $Mean_{N.N}$.
-A score of 0 was assigned to every pixel to indicate background, with the exception of those that were identified as the DC pixel through the Shower-Free simulation.
-If the DC count in the shower-free simulation was larger than 300, the pixel was included with a score of 1, identifying it as a signal pixel.
-Pure DC pixels below the threshold cut of 300 were deemed to be too faint to reconstruct, so these entries were omitted from the training set.
+The variable $DC_{Count} = Count-Mean_{N.N}$ was defined as an rough guess of the \textquoteleft DC signal' component in the pixel.
+Within the subset of training events, every triggered HESS 1 image was used.
+For each of the 3.6 million triggered image pixels, an entry was formed of the variables listed in table \ref{tab:table2}.
+A score of 0 was assigned to every pixel to indicate background, with the exception of those that were identified as the true DC pixel through the Shower-Free simulation.
+These pixels were included with a score of 1, identifying it as a signal pixel.
+Having created a dataset, the BDT was then trained with a maximum depth of 5, and 100 trees generated.
 
-Having created a dataset, the BDT was then trained with a maximum depth of 5, and 100 trees generated.
-It was found that the BDT was 100 \% accurate for the entire training dataset, with a breakdown of 100 \% for the training background and 99 \% accurate with the training signal.
-When the trained BDT was applied to the testing pixels, it was found to be 99.99 \%  accurate for the entire training dataset, with a breakdown of 100 \% for the testing background and 99 \% accurate with the testing signal.
+\begin{table}[h!]
+  \centering
+  \caption{Relative Feature Importance in BDT training}
+  \label{tab:table2}
+  \begin{tabular}{ccc}
+    \toprule
+    Variable & Relative Importance\\
+    \midrule
+    $DC_{Count}$ & 0.38\\
+    $Mean_{N.N}$ & 0.22\\
+    $\Delta_{Direction}$ & 0.15\\
+    $Q_{DC}$ & 0.11\\
+    $raw_{Q}$ & 0.06\\
+    $\Delta_{Line}$ & 0.04\\
+    $Intensity$ & 0.04\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+The relative importance of each \textquoteleft feature' is automatically calculated by the Scikit Learn package, and is also recorded in table \ref{tab:table2}.
+The variable $DC_{Count}$ was consistently the most importance variable across many combinations of included variables and BDT training parameters.
+It was found that, under the conditions listed above, the BDT was 99.94 \% accurate for the entire training dataset, and 99.93 \%  accurate for the testing dataset.
 This indicates that the BDT was not significantly overtrained, which would otherwise be manifested by a large divergence in accuracy between testing and training data.
 
-Having trained the BDT successfully, it was then applied to the same dataset as for the classic QDC identification.
+Having trained the BDT successfully, it was then applied to the same separate dataset as for the classic QDC identification.
 In each camera image, the event with the largest BDT score was deemed to be \textquoteleft most signal-like', and thus selected as the DC pixel candidate.
-A cut was applied, requiring $Probability_{signal} > 0.5$ for the DC candidate to be accepted.
-
-With this cut applied, out of 1200 events, 46\% events passed all of the required cuts. The BDT was found to be 85 \% accurate in identifying the DC pixel in those passing events.
-
-In \ref{fig:cutdistribution}, a plot of true vs.
-reconstructed DC count is shown, obtained by comparing the BDT selected pixel to the hadron-only DC pixel.
-The black line indicates the optimal 1:1 ratio that we are aiming for.
-It is seen that there the vast majority of misidentified events have a small $candidate_{DC count}$, forming a red line in the region $candidate_{DC count} \approx 0$.
-To remove these misidentified events, we can apply a second cut requiring $candidate_{DC count} > 300$.
+A cut was applied, requiring $P_{signal} > 0.5$ for the DC candidate to be accepted.
+A second cut requiring $DC_{Count} > 200$ removed many incorrectly identified events.
 
@@
 This represents a very significant improvement in DC pixel identification over the previous QDC method, and corresponds to a fivefold increase in the number of HESS data events that can be studied using the LPD method.
-Use of this BDT method is thus assumed throughout the rest of this analysis.
+
+HESS2!
 
 \section{Conclusion}
-Basically it just worked really well.
+The use of BDT identification has been shown to be superior to the traditional $Q_{DC}$ method, by providing five times as many correctly identified events, once cuts have been applied.
+Furthermore, the resultant sample has only half the contamination of the $Q_{DC}$ method, with 15\% of the sample being incorrectly identified events rather than 30\% for $Q_{DC}$.
 

### 2016-05-17 report/bdtarticle.tex
Backup 17/05/16

@@
 \usepackage{geometry}
+\geometry{a4paper, portrait, margin=1.0in}
 \usepackage{gensymb}
@@
 %opening
-\title{Identification of DC Pixels using Boosted Decision Trees}
+\title{Identification of Direct Cherenkov Pixels using Boosted Decision Trees}
 \author{Robert Stein}
@@
 \begin{abstract}
-A new method of Direct Cherenkov (DC) pixel identification, relying on machine learning, was developed.
-A set of Cosmic Ray telescope images for training were each simulated twice, both with and without the Extended Air Shower (EAS) background, enabling the DC pixel in every realistic telescope images to be reliably identified using the corresponding background-free image.
-Using all pixels from these realistic training images, a Boosted Decision Tree (BDT) was trained to identify DC pixels.
-The BDT performance was tested on a second set of test realistic telescope images, and compared to existing methods of DC pixel identification.
+When Cosmic Rays travel through the atmosphere, the primary particle will often emit some Cherenkov light before the much brighter Extended Air Shower is generated.
+Unlike the broader shower component of telescope images, all of the Direct Cherenkov light will usually be concentrated in a single pixel.
+A new method for identifying these Direct Cherenkov pixels was developed, relying on machine learning.
+A set of Cosmic Ray telescope images were simulated, both with and without the Extended Air Shower background, for use in classifier training.
+With reference to the background-free telescope images, the Direct Cherenkov pixel in each corresponding full-shower telescope image could be reliably identified.
+A Boosted Decision Tree to identify these Direct Cherenkov pixels was trained, using data from the full-shower training images.
+The Boosted Decision Tree performance was then tested on a second set of full-shower telescope images, and compared to existing methods of Direct Cherenkov pixel identification.
 \end{abstract}
@@
 \section{Introduction}
-In Cosmic Ray air showers, the primary particle will often emit DC light in the upper atmosphere, before generating an EAS in interaction with the lower atmosphere.
-In telescope images, this DC light is usually concentrated in a single  \textquoteleft DC pixel'.
-Identifying this pixel is challenging, because the DC light is much fainter than that from the EAS, which will be recorded in the DC pixel and many of surrounding pixels.
-As a result, most telescope images will have many bright pixels adjacent to one another, among which one will be the DC pixel.
-However, if found, the DC pixel can indicate the primary particle energy and charge.
+A Cosmic Ray will often emit Direct Cherenkov (DC) light in the upper atmosphere, before generating an Extended Air Shower (EAS) through interaction with the lower atmosphere.
+Analysis of the DC light from a shower can indicate primary particle energy, charge and position.
+It is consequently very useful to identify and measure the quantity and direction of DC light emission, for use in event reconstruction.
+There are numerous Telescope Arrays which currently image Cherenkov Light emission from Cosmic Rays in the atmosphere, including the HESS, MAGIC and VERITAS Experiments.
+In these telescope images, the DC light is usually concentrated in a single  \textquoteleft DC pixel'.
+Identifying this pixel is challenging, because the brighter EAS Cherenkov light background often overlaps with the DC pixel.
 
-Currently, the DC pixel is identified after applying a number of cuts first, used a method developed by the HESS collaboration \cite{hess07}.
-From the subset of events passing these cuts, the variable \[Q_{DC} = \frac{Intensity}{Intensity_{N.N.max}}\] is defined as the ratio of the intensity of a pixel to the largest neighbouring pixel intensity.
-The DC pixel candidate is simply that with the largest $Q_{DC}$ among those passing the cuts.
+At present, the DC pixel candidate can be identified by applying a number of cuts to pixels in an image, such as those used by the HESS collaboration \cite{hess07}.
+The variable $Q_{DC}$ is defined as the ratio of the largest neighbouring pixel intensity to the intensity of a given pixel, and from the subset of pixels passing these cuts, the DC candidate is simply the pixel with the smallest $Q_{DC}$.
 However, this method is neither reliable nor efficient.
-An improved method would aim to increase the number of correctly identified events, and enable cuts which better discriminate between correctly and incorrectly identified events.
+An better method would aim to increase the number of correctly identified events, and enable cuts which better discriminate between correctly and incorrectly identified events.
 
-Using the CORSIKA package, Cosmic Ray events were simulated both with and without an EAS component.
-The sim\textunderscore telarray package was used to simulate the resultant telescope image, assuming the events were observed by the HESS telescope array.
-Using the EAS-free image to reliably identify the DC pixel, a Boosted Decision Tree (BDT) was trained on each pixel from a training set of telescope images.
-The pixel information was provided in the form of individual pixel entries, rather than as discrete sets for images or events.
+Classifiers provides an alternative method of identification, making use of supervised machine learning to find structure in datasets.
+To train a classifier, we require a set of training data entries containing several variables, as well as the correct class for each of the entries in the dataset.
+Once trained, a classifier can be used to predict the class for any such data entry.
+In this case, the classifier must learn to distinguish between non-DC and DC pixels.
 
-Once trained, the BDT was applied to every pixel entry in a separate 'testing' set of simulated telescope images.
-For each pixel, the BDT assigned a \textquoteleft Signal Probability', $P_{signal}$, indicating the likelihood of the pixel being the DC pixel.
-From an entire image, the pixel with the largest $P_{signal}$ was identified as the DC pixel candidate.
-Repeating the double simulation technique for the test data, the true DC pixels in the test telescope images were reliably identified from EAS-free images.
+The CORSIKA package \cite{Heck98} was used to generate Cosmic Ray events, while the sim\textunderscore telarray package  \cite{Bernlohr08} was used to generate corresponding HESS array telescope images.
+Simulation with EAS background was used to produce training pixel sets, while corresponding simulation without EAS background was used to determine the true class of each pixel in the training sets.
+The data was used to train a Boosted Decision Tree (BDT) classifier to identify DC pixels.
+The data was provided in the form of individual pixel entries, rather than as discrete sets for images or events.
+
+Once trained, the BDT was applied to all pixel entries in a separate \textquoteleft testing' set of simulated telescope images.
+For each pixel, the BDT assigned a \textquoteleft Signal Probability', $P_{signal}$, indicating the likelihood of the pixel being a DC pixel.
+For each image, the pixel with the largest $P_{signal}$ was identified as the sole DC pixel candidate.
+As before, the true class of each pixel was determined from a second EAS-free simulation.
 Thus, the accuracy of BDT identification for test telescope images was calculated.
@@
 \section{Image Simulation}
-A full simulation of Cosmic Ray air showers was performed using the CORSIKA package \cite{Heck98}, assuming a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
+The full simulation of air showers was performed using the CORSIKA package atmospheric profile derived from measurements conducted at the HESS site in Namibia.
 The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{-2.7}$.
@@
 
-In order to identify the DC pixel, a simulation was initially run with an energy cut of 10 PeV on all muons and electrons.
+To determine the true class of each pixel, a simulation was initially run with an energy cut of 10 PeV on all muons and electrons.
 Because this cut exceeded the primary particle energy, neither daughter muons and electrons, nor the photons they would have emitted, were simulated.
@@
 A second identical \textquoteleft EAS Simulation' was run including the same random seeds, but without the energy cut on muons and electrons.
-This gave a complete EAS image including the DC light.
+This gave a complete EAS image including identical DC light.
 
-Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected HESS hardware response to each air shower was simulated.
+With the sim\textunderscore telarray package, the expected HESS hardware response to each air shower was simulated.
 Among other things, the program accounts for atmospheric transmission and density, mirror positions, sizes and reflectivities, camera shadowing and triggering, quantum efficiency and pulse responses.
-Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered \textquoteleft realistic camera images'.
-For the EAS Simulation, the night sky background was also included by sim\textunderscore telarray, further obscuring the DC pixel.
+For the full-shower image, the night sky background was also simulated by sim\textunderscore telarray.
+Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered \textquoteleft realistic' camera images.
+However, sim\textunderscore telarray introduces various sources of random noise to the simulation, leading to some divergence between the EAS-free and full-shower images.
 
@@
 
-The HESS telescope has both a high gain Channel 0 and a low gain Channel 1.
-The Sim\textunderscore telarray value of SOMETHING?
-for each channel were recorded.
-The pedestal and gain for each channel were also recorded, and from this, Intensity in the pixel channel was found.
+The various pixel entry variables were then found from the sim\textunderscore telarray output.
+The HESS telescope pixels have a high gain Channel 0 and a low gain Channel 1, with both voltages undergoing a Flash Analogue-to-Digital Conversion (FADC).
+The simulated value of the FADC Voltage for each channel was found.
+Alongside the pedestal and gain, the quantity $Intensity = (FADC - Pedestal)\times Gain $ was calculated.
+Due to possible saturation of the high gain FADC, only the low gain $Intensity$ was used.
 
-\[ Intensity = (Count - Pedestal)\times Gain \]
-
-In the case of many iron core events, Channel 0 will reach its maximum value and become saturated.
-Thus Channel 0 ceases to be useful for discriminating between high energy DC and non-DC pixels.
-Consequently, Channel 0 Intensities were neglected while Channel 1 Intensities were used in all later analysis.
-This variable $Intensity$ will henceforth be used referred to Channel 1 Intensity.
-
-The Sim\textunderscore telarray package derives various Hillas whole-image parameters.
+Sim\textunderscore telarray also derives various Hillas whole-image parameters.
 These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated.
 The reconstructed shower direction and the shower center of gravity were also calculated, as positions in azimuth and zenith.
-Additionally the estimated energy and distance from each telescope to core, $r_{core}$,  were recorded.
+Additionally the estimated energy and distance from each telescope to core, $r_{core}$,  were found.
 
-For every pixel, in addition to the $Intensity$, its location within the telescope image was determined from a standard HESS layout.
+For every pixel, in addition to the $Intensity$, its location within the telescope image was determined using the standard HESS layout.
 The variables $ \Delta_{C.o.G}$, $\Delta_{Direction}$ and $\Delta_{Line}$ were defined as the distance from the pixel to the shower center of gravity, shower direction, and the line joining those two points.
 Furthermore, the nearest neigbouring pixel IDs were calculated for every pixel position, enabling the $Intensity$ in each neighbouring pixel to be found.
-The largest neighbouring intensity $Intensity_{N.N.max}$ was identified, and the ratio $ Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity} $ was derived.
-In addition, the Nearest Neighbour Mean Intensity was recorded.
+The largest neighbouring intensity was identified, and the ratio $Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity}$ was derived.
+Similarly the largest neighbouring FADC was found, and the ratio $raw_{Q} = \frac{FADC_{N.N.max}}{FADC}$ was calculated.
+In addition, the Nearest Neighbour Mean Intensity $Mean_{N.N}$ was recorded.
+The variable $DC_{Signal} = Intensity-Mean_{N.N}$ was defined as an rough guess of the \textquoteleft DC signal' component in the pixel.
 
 \section{DC Pixel Identification}  
-The original method used by the HESS collaboration \cite{hess07} was initially replicated, for which a number of cuts were applied to each image dataset.
+As a basis for comparison, the original HESS cuts listed in \ref{tab:table1} were replicated for a set of test data.
+For every image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a unique $Q_{DC}$ cut, reducing the number of accepted DC candidates.
+For each image, the smallest $Q_{DC}$ among any remaining pixels was used to identify as the DC pixel candidate.
+Because many images had no pixel that passed all cuts, the $Q_{DC}$ method was frequently unable to identify a DC pixel.
+In the original analysis, an additional cut $r_{core} \textgreater 40m$ was applied.
+However, the uncertainty in determining the core position through Hillas Analysis is typically of the order of $\pm 30m$.
+Consequently, this particular cut was omitted, along with the Impact Parameter cuts.
 
@@
   \centering
-  \caption{Cuts applied to image pixel sets}
+  \caption{Cuts applied to image pixel sets, used by HESS collaboration \cite{hess07}}
   \label{tab:table1}
@@
 
-From the subset of pixels satisfying these conditions, the remaining pixel with the smallest $Q_{DC}$ was selected as the DC pixel candidate.
-In the original analysis, an additional cut $r_{core} \textgreater 0.4$ was applied.
-However, the uncertainty in determining the core position through Hillas Analysis is typically of the order of $\pm 30m$.
-Consequently, this particular cut was omitted, along with the Impact Parameter cuts.
-For every image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a unique $Q_{DC}$ cut.
-
-The candidates were checked against the true DC pixels from the hadron-only image.
-Out of 400 events, it was fount that only 55\% of the hadron-free events contained a clear DC signal, as defined by requiring the DC pixel to have $Intensity_{DC} > 150$.
-This represents a reasonable target number for DC identification.
-SOMETHING!
-Of all events, 17\% passed the required cuts.
-The $Q_{DC}$ was found to be 68\% accurate in identifying the DC pixel in those passing events, as shown in \ref{fig:cutdistribution}.
+The candidates were checked against the true DC pixels identified in the EAS-free images.
+Of 2000 events it was found that there were 6000 triggered images.
+Of these images, 17\% passed the required cuts.
+The $Q_{DC}$ was found to be 68\% accurate in identifying the DC pixel in those passing images, as shown in \ref{fig:cutdistribution}.
 These values served as a benchmark for BDT performance.
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{cutdistribution1None}
-\caption{The true $Intensity_{DC}$ in the EAS-free image is shown in the top left, with a broad exponential decay in count as DC intensity increases.
-Sim\textunderscore telarray requires a minimum of 20 photoelectrons in order for a telescope to be triggered, meaning that only events with a true $Intensity_{DC}>20$ photoelectrons can be studied.
-In the top right- the distribution of the dataset is shown, once all $Q_{DC}$ cuts have been applied.
-In the bottom left, the $P_{signal}$ (BDT score) distribution is shown before any cuts.
-On the bottom right, we see the same distribution after both $DC_{Count}$ and $P_{signal}$ cuts are applied.
-All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.
-We desire both a large number of green events, and a good degree separability of red and green events.}
-\label{fig:cutdistribution}
-\end{center}
-\end{figure}
-
-For this analysis, a BDT was trained with the Scikit Learn Python package.
-A set of 2000 simulated events was selected, and randomly split through use of the python random.random() function into two subsets for training and testing.
-The variable $DC_{Count} = Count-Mean_{N.N}$ was defined as an rough guess of the \textquoteleft DC signal' component in the pixel.
+The BDT was trained with the Scikit Learn Python package \cite{scikit-learn}.
+A set of 2000 CORSIKA events was selected, and randomly split through use of the Python random.random() function into the two subsets for training and testing.
 Within the subset of training events, every triggered HESS 1 image was used.
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{cutdistribution1None}
+\caption{The true $Intensity_{DC}$ in the EAS-free image is shown in the top left, with a broad exponential decay in count as DC intensity increases.
+Sim\textunderscore telarray requires a minimum of 20 photoelectrons in order for a telescope to be triggered, leading to a discontinuity at low intensities in the graph.
+In the top right- the distribution of the dataset is shown, once all $Q_{DC}$ cuts have been applied.
+In the bottom left, the $P_{signal}$ (BDT score) distribution is shown before any cuts.
+On the bottom right, we see the same distribution after both $DC_{Count}$ and $P_{signal}$ cuts are applied.
+All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.
+We desire both a large number of green events, and a good degree separability of red and green events.}
+\label{fig:cutdistribution}
+\end{center}
+\end{figure}
+
 HESS2!

### 2016-05-18 report/bdtarticle.tex
Backup 18/05/16

@@
 \section{Image Simulation}
-The full simulation of air showers was performed using the CORSIKA package atmospheric profile derived from measurements conducted at the HESS site in Namibia.
-The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{-2.7}$.
+The full simulation of air showers was performed using the CORSIKA package, with a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
+In total, 2000 training events and a further 2000 testing events were simulated.
+The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi(E) \propto E^{-2.7}$.
 For each set of simulated event, 4 unique random number seeds were used to generate the shower.
@@
 \section{DC Pixel Identification}  
-As a basis for comparison, the original HESS cuts listed in \ref{tab:table1} were replicated for a set of test data.
+As a basis for comparison, the original HESS cuts listed in \ref{tab:table1} were replicated for the set of test data.
 For every image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a unique $Q_{DC}$ cut, reducing the number of accepted DC candidates.
@@
 The candidates were checked against the true DC pixels identified in the EAS-free images.
-Of 2000 events it was found that there were 6000 triggered images.
-Of these images, 17\% passed the required cuts.
+Of 2000 testing events it was found that there were 6000 triggered images.
+Of these images, 5.7\% passed the required cuts.
 The $Q_{DC}$ was found to be 68\% accurate in identifying the DC pixel in those passing images, as shown in \ref{fig:cutdistribution}.
@@
 Application of this combined cut greatly increases the successful identification rate.
-Of the 2000 events, 84\% of events passed all of the required cuts.
-The BDT was found to be 90 \% accurate in identifying the DC pixel in those passing events.
-This represents a very significant improvement in DC pixel identification over the previous QDC method, and corresponds to a fivefold increase in the number of HESS data events that can be studied using the LPD method.
+Of the 2000 events, 57\% of events passed all of the required cuts.
+The BDT was found to be 85 \% accurate in identifying the DC pixel in those passing events.
+This represents a very significant improvement in identification accuracy over the previous QDC method, and corresponds to a fivefold increase in the number of HESS telescope images with corresponding identified DC pixels.
 

### 2016-05-18 report/bdtarticle.tex
Backup 18/05/16

@@
 The variable $Q_{DC}$ is defined as the ratio of the largest neighbouring pixel intensity to the intensity of a given pixel, and from the subset of pixels passing these cuts, the DC candidate is simply the pixel with the smallest $Q_{DC}$.
-However, this method is neither reliable nor efficient.
-An better method would aim to increase the number of correctly identified events, and enable cuts which better discriminate between correctly and incorrectly identified events.
+Despite a good degree of accuracy, this method is very inefficient, leaving the majority of events having no DC candidate from the $Q_{DC}$ method.
+A better method would aim to increase the number of correctly identified events, while still enabling cuts which discriminate well between correctly and incorrectly identified events.
 
@@
 Of 2000 testing events it was found that there were 6000 triggered images.
-Of these images, 5.7\% passed the required cuts.
-The $Q_{DC}$ was found to be 68\% accurate in identifying the DC pixel in those passing images, as shown in \ref{fig:cutdistribution}.
+Of these images, 5.2\% passed the required cuts.
+The $Q_{DC}$ was found to be 86.2\% accurate in identifying the DC pixel in those passing images, as shown in \ref{fig:cutdistribution}.
 These values served as a benchmark for BDT performance.
@@
 The BDT was trained with the Scikit Learn Python package \cite{scikit-learn}.
-A set of 2000 CORSIKA events was selected, and randomly split through use of the Python random.random() function into the two subsets for training and testing.
-Within the subset of training events, every triggered HESS 1 image was used.
-For each of the 3.6 million triggered image pixels, an entry was formed of the variables listed in table \ref{tab:table2}.
-A score of 0 was assigned to every pixel to indicate background, with the exception of those that were identified as the true DC pixel through the Shower-Free simulation.
-These pixels were included with a score of 1, identifying it as a signal pixel.
-Having created a dataset, the BDT was then trained with a maximum depth of 5, and 100 trees generated.
+Using the training set of 2000 CORSIKA events, and randomly split through use of the Python random.random() function into two further subsets, one for learning and one to check overtraining.
+Within the subset of learning events, every HESS 1 image was used, provided it was triggered in both EAS-free and full-shower simulations.
+For each of the 1.7 million triggered image pixels, an entry was formed of the variables listed in table \ref{tab:table2}.
+A class of 0 was assigned to every non-DC pixel, and a class of 1 was assigned to every DC pixel.
+Having created a dataset, the BDT was then trained with a maximum depth of 8, and 100 trees generated.
 
@@
 The variable $DC_{Count}$ was consistently the most importance variable across many combinations of included variables and BDT training parameters.
-It was found that, under the conditions listed above, the BDT was 99.94 \% accurate for the entire training dataset, and 99.93 \%  accurate for the testing dataset.
-This indicates that the BDT was not significantly overtrained, which would otherwise be manifested by a large divergence in accuracy between testing and training data.
+It was found that, under the conditions listed above, the BDT was 99.94 \% accurate for the entire learning pixel set, and 99.93 \%  accurate for the overtraining-check pixel set.
+This indicates that the BDT was not significantly overtrained, which would otherwise be manifested by a large divergence in accuracy between learning and overtraining-check data.
 
-Having trained the BDT successfully, it was then applied to the same separate dataset as for the classic QDC identification.
+Having trained the BDT successfully, it was then applied to the same test dataset as for the classic QDC identification.
 In each camera image, the event with the largest BDT score was deemed to be \textquoteleft most signal-like', and thus selected as the DC pixel candidate.
 A cut was applied, requiring $P_{signal} > 0.5$ for the DC candidate to be accepted.
-A second cut requiring $DC_{Count} > 200$ removed many incorrectly identified events.
+A second cut requiring $DC_{Count} > 150$ removed many incorrectly identified events.
 
 Application of this combined cut greatly increases the successful identification rate.
-Of the 2000 events, 57\% of events passed all of the required cuts.
-The BDT was found to be 85 \% accurate in identifying the DC pixel in those passing events.
-This represents a very significant improvement in identification accuracy over the previous QDC method, and corresponds to a fivefold increase in the number of HESS telescope images with corresponding identified DC pixels.
+Of the 2000 events, 37.8\% of images passed all of the required cuts.
+The BDT was found to be 86.0\% accurate in identifying the DC pixel in those passing events.
+This represents a very significant improvement in pixel identification efficiency, at the cost of a negligible increase in the fraction of incorrectly identified pixels.
 

### 2016-05-23 report/bdtarticle.tex
Backup 23/05/16

@@
 \begin{abstract}
-When Cosmic Rays travel through the atmosphere, the primary particle will often emit some Cherenkov light before the much brighter Extended Air Shower is generated.
-Unlike the broader shower component of telescope images, all of the Direct Cherenkov light will usually be concentrated in a single pixel.
-A new method for identifying these Direct Cherenkov pixels was developed, relying on machine learning.
+When Cosmic Rays travel through the atmosphere, the primary particle will often emit some Direct Cherenkov light before the much brighter Extended Air Shower is generated.
+Unlike the broader air shower component of telescope images, all of the Direct Cherenkov light will usually be concentrated in a single pixel.
+A new method for identifying these Direct Cherenkov pixels was developed, relying on supervised machine learning.
 A set of Cosmic Ray telescope images were simulated, both with and without the Extended Air Shower background, for use in classifier training.
@@
 Analysis of the DC light from a shower can indicate primary particle energy, charge and position.
-It is consequently very useful to identify and measure the quantity and direction of DC light emission, for use in event reconstruction.
+It is consequently very useful to measure the quantity and direction of DC light emission, for use in event reconstruction.
 There are numerous Telescope Arrays which currently image Cherenkov Light emission from Cosmic Rays in the atmosphere, including the HESS, MAGIC and VERITAS Experiments.
@@
 At present, the DC pixel candidate can be identified by applying a number of cuts to pixels in an image, such as those used by the HESS collaboration \cite{hess07}.
-The variable $Q_{DC}$ is defined as the ratio of the largest neighbouring pixel intensity to the intensity of a given pixel, and from the subset of pixels passing these cuts, the DC candidate is simply the pixel with the smallest $Q_{DC}$.
-Despite a good degree of accuracy, this method is very inefficient, leaving the majority of events having no DC candidate from the $Q_{DC}$ method.
-A better method would aim to increase the number of correctly identified events, while still enabling cuts which discriminate well between correctly and incorrectly identified events.
+The variable $Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity}$ is defined as the ratio of the largest neighbouring pixel intensity to the intensity of a given pixel, and from the subset of pixels passing these cuts, the DC candidate is simply the pixel with the smallest $Q_{DC}$.
+Despite a good degree of accuracy, this method is very inefficient, leaving the majority of events with no DC candidate.
+An improved method would aim to increase the number of correctly identified events, while still enabling cuts which discriminate well between correctly and incorrectly identified events.
 
@@
 The candidates were checked against the true DC pixels identified in the EAS-free images.
-Of 2000 testing events it was found that there were 6000 triggered images.
-Of these images, 5.2\% passed the required cuts.
-The $Q_{DC}$ was found to be 86.2\% accurate in identifying the DC pixel in those passing images, as shown in \ref{fig:cutdistribution}.
+From the testing sample, 5.2\% of all images were correctly identified and passed the cuts.
+The $Q_{DC}$ accurate in identifying DC pixels which passed the cuts, as shown in \ref{fig:cutdistribution}.
 These values served as a benchmark for BDT performance.
@@
   \centering
-  \caption{Relative Feature Importance in BDT training}
+  \caption{Relative Feature Importance in HESS-1 BDT training}
   \label{tab:table2}
@@
 Application of this combined cut greatly increases the successful identification rate.
-Of the 2000 events, 37.8\% of images passed all of the required cuts.
-The BDT was found to be 86.0\% accurate in identifying the DC pixel in those passing events.
-This represents a very significant improvement in pixel identification efficiency, at the cost of a negligible increase in the fraction of incorrectly identified pixels.
+From the testing sample, 37.8\% of all images were correctly identified and passed the cuts.
+The BDT was found to be 86.0\% accurate in identifying DC pixels which passed the cuts.
+This represents a very significant improvement in pixel identification efficiency, at the cost of a negligible decrease in accuracy after cuts.
 
@@
 
-HESS2!
+\section{HESS-2 BDT}
+The original HESS study predated the construction of the larger CT5 telescope, and thus focused exclusively in the four HESS-1 telescopes.
+Although the cuts in \ref{tab:table1} were not optimised for the differing pixel size and angular viewing region of CT5, they were replicated to provide a basis for comparison.
+Based on CT5 images from the training sample, an increased 5.7\% of DC pixels were correctly identified and passed the cut.
+However, this represented only 34.8\% of DC pixels passing the cuts, a much worsened efficiency.
+Although we can assume that better optimised CT5 cuts could remove many of the misidentified events, it is unlikely that any significant improvement in the fraction of correctly identified DC pixels would be possible.
+Thus, this is still a valid benchmark for comparative BDT performance.
+
+Due to the distinct nature of the CT5 telescope, direct application of the HESS1 BDT results in a worsening of performance, leading to just X \% of correctly identified events passing the cut with a resultant accuracy of Y \%.
+To improve pixel identification, a separate HESS-2 BDT was instead trained with the same variables as above.
+The relative features are listed in \ref{tab:table3}.
+Ultimately just 23.2 \% of pixels were correctly identified and accepted, forming only 73.2 \% of the total accepted events.
+Part of this performance discrepancy can be explained by the HESS2 learning dataset, which has just one DC pixel per event rather than the four HESS1 DC pixels.
+Additionally, HESS 2 images will have roughly 2600 non-DC pixels per event, versus 3600 DC pixels per event for HESS 1 images.
+
+\begin{table}[h!]
+  \centering
+  \caption{Relative Feature Importance in HESS-2 BDT training}
+  \label{tab:table3}
+  \begin{tabular}{ccc}
+    \toprule
+    Variable & Relative Importance\\
+    \midrule
+    $DC_{Count}$ & 0.38\\
+    $Mean_{N.N}$ & 0.22\\
+    $\Delta_{Direction}$ & 0.15\\
+    $Q_{DC}$ & 0.11\\
+    $raw_{Q}$ & 0.06\\
+    $\Delta_{Line}$ & 0.04\\
+    $Intensity$ & 0.04\\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
 \section{Conclusion}
-The use of BDT identification has been shown to be superior to the traditional $Q_{DC}$ method, by providing five times as many correctly identified events, once cuts have been applied.
-Furthermore, the resultant sample has only half the contamination of the $Q_{DC}$ method, with 15\% of the sample being incorrectly identified events rather than 30\% for $Q_{DC}$.
+The use of BDT identification has been shown to be superior to the traditional $Q_{DC}$ method, by providing many more correctly identified DC pixels withoput a corresponding loss of accuracy.
+In the case of HESS 1, this represented a sevenfold increase in the expected number of DC pixels.
+BDT performance improves with increasing training data size, so there is no reason not to think that the successful ID rate for pixels could continue to be increased further.
+Adoption of BDT identification for DC pixel could prove invaluable to future event reconstruction for large Cherenkov Telescopes, both currently operating, and those planned for the future.
 

### 2016-05-23 report/draft1.tex
Backup 17/05/16
Backup 23/05/16

@@
 This the prime motivation for the new LPD technique.
-
-\section{DC Pixel Identification}
-The first requirement for reconstruction using the LPD method is to identify the DC pixel in a shower image, and consequently determine the number of DC photoelectrons present.
-A full simulation of air showers was performed using the CORSIKA package, and the sim\textunderscore telarray package was used to simulate HESS camera images generated from the shower.
-A Boosted Decision Tree (BDT) was trained using image parameters to identify DC pixels, and its performance was tested.
-
-\subsection{CORSIKA}
-A full simulation of Cosmic Ray air showers was performed using the CORSIKA package \cite{Heck98}, assuming a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
-The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{-2.7}$.
-For each set of simulated event, 4 unique random number seeds were used to generate the shower.
-An altitude of 1800m was assumed, again corresponding to the HESS site.
-The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$.
-The four smaller HESS-phase-1 telescopes were arranged in a cross along the x/y axis with the larger HESS-phase-2 \textquoteleft CT5' telescope placed at the center.
-The length of each cross arm was $85m$.
-The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis.
-
-In order to identify the DC pixel, a \textquoteleft DC Simulation' was initially run with an energy cut of 10 PeV on all muons and electrons.
-The consequence of this was to ensure that only the Cherenkov Light from the primary particle, as well as its fragments, was simulated.
-A second identical \textquoteleft Full Simulation' was run including the same random seeds, but without the energy cut on muons and electrons.
-This gave a complete air shower including the DC light, representative of those imaged in telescope arrays.
-Comparisons of the Full and DC simulations enabled us to identify background light in the Full shower.
-
-\subsection{Sim\textunderscore telarray}
-Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected hardware response to an air shower can be simulated.
-Again, the built-in response of the HESS telescope was selected for simulation.
-The program accounts for atmospheric transmission and density, mirror positions, sizes and reflectivities, camera shadowing and triggering, quantum efficiency and pulse responses.
-Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered representative of true camera images.
-For the Full Simulation, the night sky background was also simulated by sim\textunderscore telarray.
-
-The HESS telescope has both a high gain Channel 0 and a low gain Channel 1.
-The location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated value of SOMETHING?
-in each value was extracted.
-The pedestal and gain for each channel was also recorded, and from this, Intensity can be found.
-
-\[ Intensity = (Count - Pedestal)\times Gain \]
-
-In the case of many iron core events, Channel 0 will reach its maximum value and become saturated.
-Thus Channel 0 ceases to be useful for discriminating between high energy DC and non-DC pixels, so was not used in this analysis.
-Instead, only the Channel 1 was used in later analysis.
-Thus the Channel 1 Intensity will simply be referred to throughout this analysis as $Intensity$.
-
-In addition to the $Intensity$ of each pixel, the Sim\textunderscore telarray derives various Hillas whole-image parameters, which the script also extracted.
-These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated.
-Further the reconstructed shower direction and the shower center of gravity were calculated as positions in azimuth and zenith.
-Additionally the calculated energy and distance to core $r_{core}$ were recorded.
-
-An entry was constructed for every pixel, containing its count and position.
-The variables $ \Delta_{C.o.G}$, $\Delta_{Direction}$ and $\Delta_{Line}$ were defined as the distance from the pixel to the shower center of gravity, shower direction, and the line joining those two points.
-Furthermore, the nearest neigbouring pixel IDs were calculated for every pixel position, enabling the count in each neighbouring pixel to be found.
-From this, two further pixel variables were defined.
-The largest neighbouring intensity $Intensity_{N.N.max}$ was found, and the ratio $ Q_{DC} = \frac{Intensity}{Intensity_{N.N.max}} $ was derived.
-In addition the Nearest Neighbour Mean Count was recorded.
-These variables were recorded in every pixel entry, and together the pixel entries formed a complete dataset for each camera image.
-
-\subsection{Classic DC Identification}
-The original method used by the HESS collaboration \cite{hess07} was initially replicated, for which a number of cuts were applied to each image dataset.
-
-\begin{table}[h!]
-  \centering
-  \caption{Cuts applied to image pixel sets}
-  \label{tab:table1}
-  \begin{tabular}{ccc}
-    \toprule
-    Variable & Cut\\
-    \midrule
-     $r_{core}$ & \textgreater 0.4 \\
-     $Q_{DC}$ & \textgreater 1.3 \\
-     $ \Delta_{C.o.G}$ & \textgreater 0.17 \\
-     $ \Delta_{C.o.G}$ & \textless 0.91 \\
-     $\Delta_{Direction}$ & \textless 0.45 \\
-     $\Delta_{Line}$ & \textless 0.23 \\
-     Aspect Ratio & \textless 0.75 \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-From the subset of pixels satisfying these conditions, the remaining pixel with the largest $Q_{DC}$ was selected as the DC pixel.
-The result was compared with the true DC pixel, identified from the hadron-only image, to test the accuracy of this cut.
-Out of 400 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Intensity_{DC} > 150$ in the hadron-only image.
-SOMETHING!
-Of this subset of 'DC events', 17\% events passed all of the required cuts.
-The $Q_{DC}$ was found to be 100\% accurate in identifying the DC pixel in those passing events, as shown in \ref{fig:cutdistribution}.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{cutdistributionhess1}
-\caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000.
-Events below this are unlikely to be identified correctly because the DEC light is too faint.
-In the top right- the distribution of the dataset is shown, once all the non-$Q_{DC}$ cuts have been applied.
-In the bottom left, the BDT score distribution is shown before any cuts.
-On the bottom right, we see the same distribution after both signal and BDT score cuts are applied.
-All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.}
-\label{fig:cutdistribution}
-\end{center}
-\end{figure}
-
-\subsection{Boosted Decision Tree DC Identification}  As an alternative to use of $Q_{DC}$, a new method of DC pixel identification was developed as part of this analysis by using a BDT trained with the Scikit Learn Python package.
-A set of 2000 simulated events was selected, and randomly split through use of the python random.random() function into two subsets for training and testing.
-The variable $DC_{Count} = Count-Mean_{N.N}$ was defined as an approximate \textquoteleft DC signal', if the pixel were to be selected as the DC candidate.
-For every pixel in the 2000 simulated events HESS 1 images, an entry was formed of $Q_{DC}$, $ \Delta_{C.o.G}$, $\Delta_{Direction}$, $\Delta_{Line}$, Channel1, Channel0, $DC_{Count}$ and $Mean_{N.N}$.
-A score of 0 was assigned to every pixel to indicate background, with the exception of those that were identified as the DC pixel through the Shower-Free simulation.
-If the DC count in the shower-free simulation was larger than 300, the pixel was included with a score of 1, identifying it as a signal pixel.
-Pure DC pixels below the threshold cut of 300 were deemed to be too faint to reconstruct, so these entries were omitted from the training set.
-
-Having created a dataset, the BDT was then trained with a maximum depth of 5, and 100 trees generated.
-It was found that the BDT was 100 \% accurate for the entire training dataset, with a breakdown of 100 \% for the training background and 99 \% accurate with the training signal.
-When the trained BDT was applied to the testing pixels, it was found to be 99.99 \%  accurate for the entire training dataset, with a breakdown of 100 \% for the testing background and 99 \% accurate with the testing signal.
-This indicates that the BDT was not significantly overtrained, which would otherwise be manifested by a large divergence in accuracy between testing and training data.
-
-\subsection{Composite Event Selection}
-Having trained the BDT successfully, it was then applied to the same dataset as for the classic QDC identification.
-In each camera image, the event with the largest BDT score was deemed to be \textquoteleft most signal-like', and thus selected as the DC pixel candidate.
-A cut was applied, requiring $Probability_{signal} > 0.5$ for the DC candidate to be accepted.
-
-With this cut applied, out of 1200 events, 46\% events passed all of the required cuts. The BDT was found to be 75 \% accurate in identifying the DC pixel in those passing events.
-
-In \ref{fig:cutdistribution}, a plot of true vs.
-reconstructed DC count is shown, obtained by comparing the BDT selected pixel to the hadron-only DC pixel.
-The black line indicates the optimal 1:1 ratio that we are aiming for.
-It is seen that there the vast majority of misidentified events have a small $candidate_{DC count}$, forming a red line in the region $candidate_{DC count} \approx 0$.
-To remove these misidentified events, we can apply a second cut requiring $candidate_{DC count} > 300$.
-
-Application of this combined cut greatly increases the successful identification rate.
-Of the 2000 events, 84\% of events passed all of the required cuts.
-The BDT was found to be 90 \% accurate in identifying the DC pixel in those passing events.
-This represents a very significant improvement in DC pixel identification over the previous QDC method, and corresponds to a fivefold increase in the number of HESS data events that can be studied using the LPD method.
-Use of this BDT method is thus assumed throughout the rest of this analysis.
-
-\subsection{Error in calculated $Count_{DC}$}
-Having successfully identified the DC pixel in many events, we can calculate the difference between the derived $candidate_{DC count}$ and the hadron-only $True_{DC}$ to determine the error we will find for the LPD.
-Binning the difference $\Delta = candidate_{DC count} - True_{DC count}$ as shown in FIG, we find that the mean difference is 65 and the median difference is -75.
-We thus see that the distribution is not significantly skewed.
-However, the Standard deviation is approximately 600 when measured both by half of the difference from the 16th to 84th centile, and by 68th centile of an absolute difference.
-This again suggests that, although skewed, the fraction error in intensity is rather large.
-However, the fractional error found purely on the basis of QDC calculations is EQUALLY LARGE??LARGER?.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{DCcounterrorhess1}
-\caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left.
-In the top right the same is shown for events which were rejected.
-The true DC signals for events which passed the cuts is plotted against the reconstructed signals in the lower left, and for rejected events in the lower right.
-As in \ref{fig:cutdistribution}, in all plots a green event is one in which the DC pixel has been correctly identified, while a red event is one that has been incorrectly identified.}
-\label{fig:dcdiff}
-\end{center}
-\end{figure}
 
@@
 
+\section{DC Pixel Identification}
+In order to apply the LPD method to data, we must first identify the DC pixel in a shower image, and determine the number of DC photoelectrons present.
+A full simulation of air showers was performed using the CORSIKA package, and the sim\textunderscore telarray package was used to simulate HESS camera images generated from the shower.
+As part of a new method developed for this analysis, a Boosted Decision Tree (BDT) was trained using image parameters to identify DC pixels, and its performance was tested.
+
+\subsection{CORSIKA}
+A full simulation of Cosmic Ray air showers was performed using the CORSIKA package \cite{Heck98}, assuming a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
+The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{-2.7}$.
+For each set of simulated event, 4 unique random number seeds were used to generate the shower.
+An altitude of 1800m was assumed, again corresponding to the HESS site.
+The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$.
+The four smaller HESS-phase-1 telescopes were arranged in a cross along the x/y axis with the larger HESS-phase-2 \textquoteleft CT5' telescope placed at the center.
+The length of each cross arm was $85m$.
+The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis.
+
+In order to identify the DC pixel, a \textquoteleft DC Simulation' was initially run with an energy cut of 10 PeV on all muons and electrons.
+The consequence of this was to ensure that only the Cherenkov Light from the primary particle, as well as its fragments, was simulated.
+A second identical \textquoteleft Full Simulation' was run including the same random seeds, but without the energy cut on muons and electrons.
+This gave a complete air shower including the DC light, representative of those imaged in telescope arrays.
+Comparisons of the Full and DC simulations enabled us to identify background light in the Full shower.
+
+\subsection{Sim\textunderscore telarray}
+Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected hardware response to an air shower can be simulated.
+Again, the built-in response of the HESS telescope was selected for simulation.
+The program accounts for atmospheric transmission and density, mirror positions, sizes and reflectivities, camera shadowing and triggering, quantum efficiency and pulse responses.
+Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered representative of true camera images.
+For the Full Simulation, the night sky background was also simulated by sim\textunderscore telarray.
+
+The HESS telescope has both a high gain Channel 0 and a low gain Channel 1.
+The location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated value of SOMETHING?
+in each value was extracted.
+The pedestal and gain for each channel was also recorded, and from this, Intensity can be found.
+
+\[ Intensity = (Count - Pedestal)\times Gain \]
+
+In the case of many iron core events, Channel 0 will reach its maximum value and become saturated.
+Thus Channel 0 ceases to be useful for discriminating between high energy DC and non-DC pixels, so was not used in this analysis.
+Instead, only the Channel 1 was used in later analysis.
+Thus the Channel 1 Intensity will simply be referred to throughout this analysis as $Intensity$.
+
+In addition to the $Intensity$ of each pixel, the Sim\textunderscore telarray derives various Hillas whole-image parameters, which the script also extracted.
+These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated.
+Further the reconstructed shower direction and the shower center of gravity were calculated as positions in azimuth and zenith.
+Additionally the calculated energy and distance to core $r_{core}$ were recorded.
+
+An entry was constructed for every pixel, containing its count and position.
+The variables $ \Delta_{C.o.G}$, $\Delta_{Direction}$ and $\Delta_{Line}$ were defined as the distance from the pixel to the shower center of gravity, shower direction, and the line joining those two points.
+Furthermore, the nearest neigbouring pixel IDs were calculated for every pixel position, enabling the count in each neighbouring pixel to be found.
+From this, two further pixel variables were defined.
+The largest neighbouring intensity $Intensity_{N.N.max}$ was found, and the ratio $ Q_{DC} = \frac{Intensity}{Intensity_{N.N.max}} $ was derived.
+In addition the Nearest Neighbour Mean Count was recorded.
+These variables were recorded in every pixel entry, and together the pixel entries formed a complete dataset for each camera image.
+
+\subsection{Classic DC Identification}
+The original method used by the HESS collaboration \cite{hess07} was initially replicated, for which a number of cuts were applied to each image dataset.
+
+\begin{table}[h!]
+  \centering
+  \caption{Cuts applied to image pixel sets}
+  \label{tab:table1}
+  \begin{tabular}{ccc}
+    \toprule
+    Variable & Cut\\
+    \midrule
+     $r_{core}$ & \textgreater 0.4 \\
+     $Q_{DC}$ & \textgreater 1.3 \\
+     $ \Delta_{C.o.G}$ & \textgreater 0.17 \\
+     $ \Delta_{C.o.G}$ & \textless 0.91 \\
+     $\Delta_{Direction}$ & \textless 0.45 \\
+     $\Delta_{Line}$ & \textless 0.23 \\
+     Aspect Ratio & \textless 0.75 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+From the subset of pixels satisfying these conditions, the remaining pixel with the largest $Q_{DC}$ was selected as the DC pixel.
+The result was compared with the true DC pixel, identified from the hadron-only image, to test the accuracy of this cut.
+Out of 400 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Intensity_{DC} > 150$ in the hadron-only image.
+SOMETHING!
+Of this subset of 'DC events', 17\% events passed all of the required cuts.
+The $Q_{DC}$ was found to be 100\% accurate in identifying the DC pixel in those passing events, as shown in \ref{fig:cutdistribution}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{cutdistribution1None}
+\caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000.
+Events below this are unlikely to be identified correctly because the DEC light is too faint.
+In the top right- the distribution of the dataset is shown, once all the non-$Q_{DC}$ cuts have been applied.
+In the bottom left, the BDT score distribution is shown before any cuts.
+On the bottom right, we see the same distribution after both signal and BDT score cuts are applied.
+All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.}
+\label{fig:cutdistribution}
+\end{center}
+\end{figure}
+
+\subsection{Boosted Decision Tree DC Identification}  As an alternative to use of $Q_{DC}$, a new method of DC pixel identification was developed as part of this analysis by using a BDT trained with the Scikit Learn Python package.
+A set of 2000 simulated events was selected, and randomly split through use of the python random.random() function into two subsets for training and testing.
+The variable $DC_{Count} = Count-Mean_{N.N}$ was defined as an approximate \textquoteleft DC signal', if the pixel were to be selected as the DC candidate.
+For every pixel in the 2000 simulated events HESS 1 images, an entry was formed of $Q_{DC}$, $ \Delta_{C.o.G}$, $\Delta_{Direction}$, $\Delta_{Line}$, Channel1, Channel0, $DC_{Count}$ and $Mean_{N.N}$.
+A score of 0 was assigned to every pixel to indicate background, with the exception of those that were identified as the DC pixel through the Shower-Free simulation.
+If the DC count in the shower-free simulation was larger than 300, the pixel was included with a score of 1, identifying it as a signal pixel.
+Pure DC pixels below the threshold cut of 300 were deemed to be too faint to reconstruct, so these entries were omitted from the training set.
+
+Having created a dataset, the BDT was then trained with a maximum depth of 5, and 100 trees generated.
+It was found that the BDT was 100 \% accurate for the entire training dataset, with a breakdown of 100 \% for the training background and 99 \% accurate with the training signal.
+When the trained BDT was applied to the testing pixels, it was found to be 99.99 \%  accurate for the entire training dataset, with a breakdown of 100 \% for the testing background and 99 \% accurate with the testing signal.
+This indicates that the BDT was not significantly overtrained, which would otherwise be manifested by a large divergence in accuracy between testing and training data.
+
+\subsection{Composite Event Selection}
+Having trained the BDT successfully, it was then applied to the same dataset as for the classic QDC identification.
+In each camera image, the event with the largest BDT score was deemed to be \textquoteleft most signal-like', and thus selected as the DC pixel candidate.
+A cut was applied, requiring $Probability_{signal} > 0.5$ for the DC candidate to be accepted.
+
+With this cut applied, out of 1200 events, 46\% events passed all of the required cuts. The BDT was found to be 75 \% accurate in identifying the DC pixel in those passing events.
+
+In \ref{fig:cutdistribution}, a plot of true vs.
+reconstructed DC count is shown, obtained by comparing the BDT selected pixel to the hadron-only DC pixel.
+The black line indicates the optimal 1:1 ratio that we are aiming for.
+It is seen that there the vast majority of misidentified events have a small $candidate_{DC count}$, forming a red line in the region $candidate_{DC count} \approx 0$.
+To remove these misidentified events, we can apply a second cut requiring $candidate_{DC count} > 300$.
+
+Application of this combined cut greatly increases the successful identification rate.
+Of the 2000 events, 84\% of events passed all of the required cuts.
+The BDT was found to be 90 \% accurate in identifying the DC pixel in those passing events.
+This represents a very significant improvement in DC pixel identification over the previous QDC method, and corresponds to a fivefold increase in the number of HESS data events that can be studied using the LPD method.
+Use of this BDT method is thus assumed throughout the rest of this analysis.
+
+\subsection{Error in calculated $Count_{DC}$}
+Having successfully identified the DC pixel in many events, we can calculate the difference between the derived $candidate_{DC count}$ and the hadron-only $True_{DC}$ to determine the error we will find for the LPD.
+Binning the difference $\Delta = candidate_{DC count} - True_{DC count}$ as shown in FIG, we find that the mean difference is -17 and the median difference is -47.
+We thus see that the distribution is not significantly skewed.
+However, the Standard deviation is 158 when measured both by half of the difference from the 16th to 84th centile, and by 68th centile of an absolute difference.
+This again suggests that, although skewed, the fraction error in intensity is fairly large.
+However, the fractional error found purely on the basis of QDC calculations is EQUALLY LARGE??LARGER?.
+
+Due to the inherent sim\textunderscore telarray random error, there will be an inherent discrepancy due to uncertainty in measurement of the \textquoteleft True Count' as well as in the $DC_{Count}$.
+Thus, any recorded errror is likely to be an overestimate.
+In order to account for this, 2000 events were simulated with CORSIKA as before.
+This time, each event simply contained one simulated image with only hadronic cherenkov light, and another including the hadronic Cherenkov Light as well as the night sky background.
+The distribution was found to have a mean fractional sigma value of roughly 20 \%, due to inconsistencies with sim\textunderscore telarray.
+Thus, we conclude that the resultant
+
+We can parameterise the error by considering the energy and distance to the core for a selection of DC pixels. We find that, for a fixed energy...
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{DCcounterrorhess1}
+\caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left.
+In the top right the same is shown for events which were rejected.
+The true DC signals for events which passed the cuts is plotted against the reconstructed signals in the lower left, and for rejected events in the lower right.
+As in \ref{fig:cutdistribution}, in all plots a green event is one in which the DC pixel has been correctly identified, while a red event is one that has been incorrectly identified.}
+\label{fig:dcdiff}
+\end{center}
+\end{figure}
+
 \section{HESS-type Event Reconstruction}

### 2016-05-23 CORSIKA/lpdforfixedenergy.py

@@ -1,0 +1,131 @@
+import sys
+import os.path
+import argparse, math, random, time
+import csv
+import numpy as np
+import cPickle as pickle
+from telescopeclasses import *
+from matplotlib import rc
+
+parser = argparse.ArgumentParser()
+parser.add_argument("-jid", "--jobID", default="4894324")
+
+cfg = parser.parse_args()
+
+
+filepath = "/nfs/astrop/d6/rstein/data/"
+
+j=500
+i=0
+
+distances=[[],[]]
+signals=[[],[]]
+truesignals=[[],[]]
+
+cut, ucut, QDCcut, DCcut, signalcut = ic.runforstats()
+
+targetfolder = filepath + cfg.jobID +"/"
+
+sys.path.append('/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/misc')
+from progressbar import ProgressBar
+custom_options = {
+	'end': 100,
+	'width': 100,
+	'format': '%(progress)s%% [%(fill)s%(blank)s]'
+}
+
+p = ProgressBar(**custom_options)
+print p
+
+hessstatus=[False, False]
+if os.path.isfile(hess1picklepath):
+	hessstatus[0] = True
+if os.path.isfile(hess2picklepath):
+	hessstatus[1] = True
+if not os.path.isfile(hess1picklepath) and not os.path.isfile(hess2picklepath):
+	raise Exception("No BDT saved, so no results to plot!")
+
+while (i < j):
+	targetpath = targetfolder +  "run" + str(i) + "/pickle/eventdata.p"
+	if (os.path.isfile(targetpath)):
+		event = pickle.load(open(targetpath, 'rb'))
+		if hasattr(event.simulations, "DC") and hasattr(event.simulations, "full"):
+			DCsim =event.simulations.DC
+			fullsim = event.simulations.full
+			
+
+			for index in DCsim.triggerIDs:
+				DCtel = DCsim.images[index]
+				fulltel =  fullsim.images[index]
+				trueID = DCtel.trueDC
+				DCtrue = DCtel.getpixel(trueID)
+				DCcount = DCtrue.channel1.intensity
+				
+				if fulltel.BDTID != None:
+					fullBDT = fulltel.getBDTpixel()
+					
+					if (fullBDT.bdtscore != None):				
+						candidatesignal = fullBDT.channel1.intensity - fullBDT.nnmean
+							
[…]

### 2016-05-27 report/bdtarticle.tex
Backup 27/05/16

@@
 \title{Identification of Direct Cherenkov Pixels using Boosted Decision Trees}
-\author{Robert Stein}
+\author{Robert Stein, Atilla Abramowski, Dieter Horns}
 \begin{document}
@@
 The Boosted Decision Tree performance was then tested on a second set of full-shower telescope images, and compared to existing methods of Direct Cherenkov pixel identification.
+After applying cuts to the test sample, 37.3\% of all Direct Cherenkov pixels were accepted and correctly identified, representing a sevenfold increase in acceptance rates when compared to existing methods.
+The corresponding sample purity after cuts was 87.7\%, a slight increase on existing methods.
 \end{abstract}
-
 \section{Introduction}
-A Cosmic Ray will often emit Direct Cherenkov (DC) light in the upper atmosphere, before generating an Extended Air Shower (EAS) through interaction with the lower atmosphere.
+Cosmic Rays will often emit Direct Cherenkov (DC) light in the upper atmosphere, before generating an Extended Air Shower (EAS) through interaction with the lower atmosphere.
 Analysis of the DC light from a shower can indicate primary particle energy, charge and position.
-It is consequently very useful to measure the quantity and direction of DC light emission, for use in event reconstruction.
-There are numerous Telescope Arrays which currently image Cherenkov Light emission from Cosmic Rays in the atmosphere, including the HESS, MAGIC and VERITAS Experiments.
+It is consequently very useful for event reconstruction to measure the quantity and direction of DC light emission.
+There are numerous Telescope Arrays which currently image Cherenkov Light emission from Cosmic Rays in the atmosphere, such as the HESS, MAGIC and VERITAS experiments.
 In these telescope images, the DC light is usually concentrated in a single  \textquoteleft DC pixel'.
@@
 
-At present, the DC pixel candidate can be identified by applying a number of cuts to pixels in an image, such as those used by the HESS collaboration \cite{hess07}.
-The variable $Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity}$ is defined as the ratio of the largest neighbouring pixel intensity to the intensity of a given pixel, and from the subset of pixels passing these cuts, the DC candidate is simply the pixel with the smallest $Q_{DC}$.
-Despite a good degree of accuracy, this method is very inefficient, leaving the majority of events with no DC candidate.
-An improved method would aim to increase the number of correctly identified events, while still enabling cuts which discriminate well between correctly and incorrectly identified events.
+We define the variable $Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity}$ as the ratio of the largest neighbouring pixel intensity to the intensity of a given pixel.
+At present, the DC pixel candidate can be identified by applying a number of cuts to pixels in an image \cite{hess07}, and from the subset of pixels passing the specified cuts, selecting the pixel with the smallest $Q_{DC}$ as the \textquoteleft DC candidate'.
+Due to the low pass rate for cuts, we obtain a small low-contamination dataset, while the majority of telescope images are left without a DC pixel candidate.
+An improved method would aim to increase the number of correctly identified DC pixels, while still enabling cuts which discriminate well between correctly and incorrectly identified DC pixels.
 
-Classifiers provides an alternative method of identification, making use of supervised machine learning to find structure in datasets.
-To train a classifier, we require a set of training data entries containing several variables, as well as the correct class for each of the entries in the dataset.
-Once trained, a classifier can be used to predict the class for any such data entry.
+Classifiers provides an alternative method of identification, making use of supervised machine learning to find rules for categorising pixels.
+To train a classifier, we require a set of training pixels, as well as the correct class for each pixel.
+Once trained, a classifier can then be used to predict the class of a pixel.
 In this case, the classifier must learn to distinguish between non-DC and DC pixels.
 
-The CORSIKA package \cite{Heck98} was used to generate Cosmic Ray events, while the sim\textunderscore telarray package  \cite{Bernlohr08} was used to generate corresponding HESS array telescope images.
-Simulation with EAS background was used to produce training pixel sets, while corresponding simulation without EAS background was used to determine the true class of each pixel in the training sets.
-The data was used to train a Boosted Decision Tree (BDT) classifier to identify DC pixels.
-The data was provided in the form of individual pixel entries, rather than as discrete sets for images or events.
-
-Once trained, the BDT was applied to all pixel entries in a separate \textquoteleft testing' set of simulated telescope images.
-For each pixel, the BDT assigned a \textquoteleft Signal Probability', $P_{signal}$, indicating the likelihood of the pixel being a DC pixel.
-For each image, the pixel with the largest $P_{signal}$ was identified as the sole DC pixel candidate.
-As before, the true class of each pixel was determined from a second EAS-free simulation.
+The CORSIKA package \cite{Heck98} was used to generate Cosmic Ray events, and the Sim\textunderscore telarray package  \cite{Bernlohr08} was used to generate corresponding HESS array telescope images.
+Simulation with EAS background was used to produce training pixel sets, while corresponding simulation without EAS background was used to find the true DC pixel in each training image.
+A Boosted Decision Tree (BDT) classifier was trained with the data to identify DC pixels.
+Once trained, the BDT was applied to a separate \textquoteleft testing' set of simulated telescope images.
+As before, the true DC pixel was determined from a second EAS-free simulation.
 Thus, the accuracy of BDT identification for test telescope images was calculated.
@@
 The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis.
+Due to hardware differences between CT5 and the original HESS 1 telescopes, only images from HESS-phase-1 were considered.
 
@@
 For the full-shower image, the night sky background was also simulated by sim\textunderscore telarray.
-Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered \textquoteleft realistic' camera images.
-However, sim\textunderscore telarray introduces various sources of random noise to the simulation, leading to some divergence between the EAS-free and full-shower images.
+Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered \textquoteleft realistic'.
+However, sim\textunderscore telarray introduces various sources of random noise to the simulation, leading to some divergence in the DC light between the EAS-free and full-shower images.
 
@@
 
-The various pixel entry variables were then found from the sim\textunderscore telarray output.
+The various pixel entry variables were found from the sim\textunderscore telarray output.
 The HESS telescope pixels have a high gain Channel 0 and a low gain Channel 1, with both voltages undergoing a Flash Analogue-to-Digital Conversion (FADC).
 The simulated value of the FADC Voltage for each channel was found.
-Alongside the pedestal and gain, the quantity $Intensity = (FADC - Pedestal)\times Gain $ was calculated.
+Using the pedestal and gain, the quantity $Intensity = (FADC - Pedestal)\times Gain $ was calculated for each channel.
 Due to possible saturation of the high gain FADC, only the low gain $Intensity$ was used.
-
 Sim\textunderscore telarray also derives various Hillas whole-image parameters.
@@
 The variable $DC_{Signal} = Intensity-Mean_{N.N}$ was defined as an rough guess of the \textquoteleft DC signal' component in the pixel.
+Lastly the Image Amplitude $I_{tot}$, defined as the total image intensity after the default tail cuts have been applied to the image.
 
@@
 As a basis for comparison, the original HESS cuts listed in \ref{tab:table1} were replicated for the set of test data.
-For every image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a unique $Q_{DC}$ cut, reducing the number of accepted DC candidates.
-For each image, the smallest $Q_{DC}$ among any remaining pixels was used to identify as the DC pixel candidate.
+For every image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a dynamic cut, $Q_{DC} < 0.14 \times \log(\frac{I_{tot}}{161 \times \cos \theta})$.
+Among pixels passing all cuts, the one with the smallest $Q_{DC}$ among those remaining was selected as the DC pixel candidate for the image.
 Because many images had no pixel that passed all cuts, the $Q_{DC}$ method was frequently unable to identify a DC pixel.
@@
 However, the uncertainty in determining the core position through Hillas Analysis is typically of the order of $\pm 30m$.
-Consequently, this particular cut was omitted, along with the Impact Parameter cuts.
+Consequently, this particular cut was omitted.
+
+The candidates were checked against the true DC pixels identified in the EAS-free images.
+From the testing sample, 5.2\% of all images were correctly identified and passed the cuts.
+Once misidentified events were considered, the post-cuts sample was 86.2\% accurate, as shown in \ref{fig:cutdistribution}.
+These values served as a benchmark for BDT performance.
 
@@
 
-The candidates were checked against the true DC pixels identified in the EAS-free images.
-From the testing sample, 5.2\% of all images were correctly identified and passed the cuts.
-The $Q_{DC}$ accurate in identifying DC pixels which passed the cuts, as shown in \ref{fig:cutdistribution}.
-These values served as a benchmark for BDT performance.
-
 The BDT was trained with the Scikit Learn Python package \cite{scikit-learn}.
-Using the training set of 2000 CORSIKA events, and randomly split through use of the Python random.random() function into two further subsets, one for learning and one to check overtraining.
-Within the subset of learning events, every HESS 1 image was used, provided it was triggered in both EAS-free and full-shower simulations.
-For each of the 1.7 million triggered image pixels, an entry was formed of the variables listed in table \ref{tab:table2}.
+Using the training set of 2000 CORSIKA events, and randomly split further, with 90\% in a learning subset and 10\% in a subset to check for overtraining.
+Within the learning subset, every HESS 1 image was used, provided it was triggered in both EAS-free and full-shower simulations.
+For each of the 1.7 million triggered image pixels, an entry was formed with the variables listed in table \ref{tab:table2}.
 A class of 0 was assigned to every non-DC pixel, and a class of 1 was assigned to every DC pixel.
-Having created a dataset, the BDT was then trained with a maximum depth of 8, and 100 trees generated.
+Having created a dataset, the BDT was then trained with a maximum depth of 8, and with 100 trees generated.
+The data was provided in the form of individual pixel entries, rather than as discrete sets for images or events.
 
@@
     \midrule
-    $DC_{Count}$ & 0.38\\
-    $Mean_{N.N}$ & 0.22\\
-    $\Delta_{Direction}$ & 0.15\\
-    $Q_{DC}$ & 0.11\\
-    $raw_{Q}$ & 0.06\\
-    $\Delta_{Line}$ & 0.04\\
-    $Intensity$ & 0.04\\
+    $DC_{Count}$ & 0.34\\
+    $Mean_{N.N}$ & 0.26\\
+    $\Delta_{Direction}$ & 0.11\\
+    Image Amplitude & 0.10\\
+    $Q_{DC}$ & 0.10\\
+    $raw_{Q}$ & 0.05\\
+    $\Delta_{Line}$ & 0.02\\
+    $Intensity$ & 0.02\\
     \bottomrule
@@
 The variable $DC_{Count}$ was consistently the most importance variable across many combinations of included variables and BDT training parameters.
-It was found that, under the conditions listed above, the BDT was 99.94 \% accurate for the entire learning pixel set, and 99.93 \%  accurate for the overtraining-check pixel set.
+It was found that, under the conditions listed above, the BDT was 99.94 \% accurate for the learning pixel subset, and 99.93 \%  accurate for the overtraining-check pixel subset.
 This indicates that the BDT was not significantly overtrained, which would otherwise be manifested by a large divergence in accuracy between learning and overtraining-check data.
 
-Having trained the BDT successfully, it was then applied to the same test dataset as for the classic QDC identification.
+Having trained the BDT successfully, it was then applied to the same test dataset as for the classic $Q_{DC}$ identification.
 In each camera image, the event with the largest BDT score was deemed to be \textquoteleft most signal-like', and thus selected as the DC pixel candidate.
@@
 A second cut requiring $DC_{Count} > 150$ removed many incorrectly identified events.
+Application of this combined cut greatly increases the successful identification rate.
+From the testing sample, 37.3\% of all images were correctly identified and passed the cuts.
+The BDT was found to be 87.7\% accurate in identifying DC pixels which passed the cuts.
+This represents a very significant improvement in pixel identification efficiency, as well as a minor increase in accuracy after cuts.
+The results are summarised in \ref{tab:table3}.
 
-Application of this combined cut greatly increases the successful identification rate.
-From the testing sample, 37.8\% of all images were correctly identified and passed the cuts.
-The BDT was found to be 86.0\% accurate in identifying DC pixels which passed the cuts.
-This represents a very significant improvement in pixel identification efficiency, at the cost of a negligible decrease in accuracy after cuts.
+\begin{table}[h!]
+  \centering
+  \caption{Comparison of $Q_{DC}$ and BDT Performance}
+  \label{tab:table3}
+  \begin{tabular}{ccc}
+    \toprule
+    & $Q_{DC}$ & BDT\\
+    \midrule
+    Pixels Accepted and Correctly Identified (\%) & 5.2 & 37.2\\
+   Pixels Accepted and Incorrectly Identified (\%) & 0.8 & 5.2\\
+    Sample Purity (\%) & 86.2 & 87.7\\
+  \end{tabular}
+\end{table}
 
@@
 
-\section{HESS-2 BDT}
-The original HESS study predated the construction of the larger CT5 telescope, and thus focused exclusively in the four HESS-1 telescopes.
-Although the cuts in \ref{tab:table1} were not optimised for the differing pixel size and angular viewing region of CT5, they were replicated to provide a basis for comparison.
-Based on CT5 images from the training sample, an increased 5.7\% of DC pixels were correctly identified and passed the cut.
-However, this represented only 34.8\% of DC pixels passing the cuts, a much worsened efficiency.
-Although we can assume that better optimised CT5 cuts could remove many of the misidentified events, it is unlikely that any significant improvement in the fraction of correctly identified DC pixels would be possible.
-Thus, this is still a valid benchmark for comparative BDT performance.
-
-Due to the distinct nature of the CT5 telescope, direct application of the HESS1 BDT results in a worsening of performance, leading to just X \% of correctly identified events passing the cut with a resultant accuracy of Y \%.
-To improve pixel identification, a separate HESS-2 BDT was instead trained with the same variables as above.
-The relative features are listed in \ref{tab:table3}.
-Ultimately just 23.2 \% of pixels were correctly identified and accepted, forming only 73.2 \% of the total accepted events.
-Part of this performance discrepancy can be explained by the HESS2 learning dataset, which has just one DC pixel per event rather than the four HESS1 DC pixels.
-Additionally, HESS 2 images will have roughly 2600 non-DC pixels per event, versus 3600 DC pixels per event for HESS 1 images.
-
-\begin{table}[h!]
-  \centering
-  \caption{Relative Feature Importance in HESS-2 BDT training}
-  \label{tab:table3}
-  \begin{tabular}{ccc}
-    \toprule
-    Variable & Relative Importance\\
-    \midrule
-    $DC_{Count}$ & 0.38\\
-    $Mean_{N.N}$ & 0.22\\
-    $\Delta_{Direction}$ & 0.15\\
-    $Q_{DC}$ & 0.11\\
-    $raw_{Q}$ & 0.06\\
-    $\Delta_{Line}$ & 0.04\\
-    $Intensity$ & 0.04\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
 \section{Conclusion}
-The use of BDT identification has been shown to be superior to the traditional $Q_{DC}$ method, by providing many more correctly identified DC pixels withoput a corresponding loss of accuracy.
+The use of BDT identification has been shown to be superior to the traditional $Q_{DC}$ method, by providing many more correctly identified DC pixels without a corresponding loss of accuracy.
 In the case of HESS 1, this represented a sevenfold increase in the expected number of DC pixels.
 BDT performance improves with increasing training data size, so there is no reason not to think that the successful ID rate for pixels could continue to be increased further.
+Due to the good degree ofr separability of the BDT signal probability, a further increase in sample purity would certainly be possible at the expense of harsher
+$P_{signal}$ cuts reducing the size of the datasets.
+In short, the BDT method produces not just superior performance but increased flexibility for balancing sample purity and size.
 Adoption of BDT identification for DC pixel could prove invaluable to future event reconstruction for large Cherenkov Telescopes, both currently operating, and those planned for the future.
-
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{report}

### 2016-05-27 report/draft1.tex
Backup 27/05/16

@@
   \caption{Cuts applied to image pixel sets}
-  \label{tab:table1}
+  \label{tab:qdccuts}
   \begin{tabular}{ccc}
@@
 
+\subsection{HESS-2 BDT}
+The original HESS study predated the construction of the larger CT5 telescope, and thus focused exclusively in the four HESS-1 telescopes.
+Although the cuts in \ref{tab:qdccuts} were not optimised for the differing pixel size and angular viewing region of CT5, they were replicated to provide a basis for comparison.
+Based on CT5 images from the training sample, an increased 5.7\% of DC pixels were correctly identified and passed the required cut.
+A further 10 \% of all pixels passed the cuts, despite being misidentified.
+This represented a very heavy decrease in sample purity to just 38\%.
+We can assume that better optimised CT5 cuts could remove many of these misidentified events, though it is unlikely that any significant improvement in the number of correctly identified DC pixels would be possible.
+Thus, the number of DC pixels successfully identified using the $Q_{DC}$ method is still a valid benchmark for comparative BDT performance.
+A true accuracy rate closer to the HESS 1 rate of 86\% could be expected.
+
+Due to the distinctiveness of the CT5 telescope, direct application of the HESS1 classifier to the CT5 telescope yields poorer BDT performance, with just 14.8 \% of correctly identified events passing the cut and an accuracy of 71.7\%.
+To improve CT5 pixel identification, a separate HESS2 BDT was instead trained with the same variables as above.
+The relative feature importance is listed in \ref{tab:hess2classifier}.
+The CT5 performance was improved for the new classifier, with 24.0 \% of pixels being correctly identified and accepted, and an accuracy of 80.2 \%.
+Despite this improvement, a clear gap emerged between the between the performance of HESS1 classifier on old telescopes, and the performance of the HESS2 classifier on CT5.
+Part of this discrepancy can be explained by the HESS2 learning dataset, which has just one DC pixel per event rather than the four HESS1 DC pixels.
+Additionally, HESS 2 images will have roughly 2600 non-DC pixels per event, versus 3600 DC pixels per event for HESS 1 images.
+The HESS2 classifier was thus trained on significantly fewer DC pixels, so we would expect to see the clear performance gap in comparison to the HESS1 classifier.
+
+\begin{table}[h!]
+  \centering
+  \caption{Relative Feature Importance in HESS-2 Classifier BDT training}
+  \label{tab:hess2classifier}
+  \begin{tabular}{ccc}
+    \toprule
+    Variable & Relative Importance\\
+    \midrule
+    $DC_{Count}$ & 0.27\\
+    $Mean_{N.N}$ & 0.14\\
+    $Q_{DC}$ & 0.12\\
+    $\Delta_{Direction}$ & 0.12\\
+    $\Delta_{Line}$ & 0.10\\
+    Image Amplitude & 0.09\\
+    $raw_{Q}$ & 0.07\\
+    $Intensity$ & 0.06\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
 \subsection{Error in calculated $Count_{DC}$}
-Having successfully identified the DC pixel in many events, we can calculate the difference between the derived $candidate_{DC count}$ and the hadron-only $True_{DC}$ to determine the error we will find for the LPD.
-Binning the difference $\Delta = candidate_{DC count} - True_{DC count}$ as shown in FIG, we find that the mean difference is -17 and the median difference is -47.
+Having successfully identified the DC pixel in many events, we can find the error $\sigma_{LPD}$ in our calculated $candidate_{DC count}$, through comparison with the correct value $True_{DC}$.
+However, $True_{DC}$ also has an associated error $\sigma_{STA}$, originating in the use of internal random numbers for Sim\textunderscore telarray simulations.
+If we neglect to account for this $\sigma_{STA}$, our final $\sigma_{calculated}$ will be an overestimate that also includes the random fluctuation of $True_{DC}$ around the actual DC intensity.
+As we cannot directly measure the actual DC intensity, we must instead measure $\sigma_{TrueDC}$.
+
+A study of 2000 events was conducted, in which each cosmic ray was simulation without night sky background or EAS background.
+Each telescope image simulation was conducted twice, and difference between $I_{1}$ and $I_{2}$ was plotted in \ref{fig:simtelerror}.
+The fractional difference from the mean Intensity of an image was defined as $\Delta = 2 \times \frac{I_{2} - I_{1}}{{I_{2} + I_{1}}}$ .
+It was found that the standard deviation in fractional difference was $\sigma_{STA}=0.09$, meaning that there is an inherent error of 9 \% in measurements of $True_{DC}$.
+In later calculations of the error in Intensity, this fractional error can be subtracted in quadrature.
+
+\[ \sigma_{LPD}^{2} = \sigma_{calculated}^{2} - \sigma_{STA}^{2}  \]
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{simtelerror1}
+\caption{The fractional difference in total Image Intensity between the two simulations is shown in the graph above.
+A clear symmetric Gaussian is observed, with a mean of 0.00, and a standard deviation of 0.06.
+Below, the two intensities are plotted against one another.
+The distribution does not deviate significantly from the ideal 1:1 correspondence illustrated with the black line.}
+\label{fig:simtelerror}
+\end{center}
+\end{figure}
+
+To assess the error in the LPD, a simulation of 2000 events was conducted with a fixed energy of 56TeV, and both Zenith and azimuth fixed to 0 degrees.
+The true distance to core was recorded from Sim\textunderscore telarray, and a graph was plotted of DC pixel intensity against core distance.
+As expected, a characteristic LPD is observed.
+Due to the application of a signal cut to the BDT candidates, we are only able to see the LPD at around $r_{core} \textgreater 35m$, at which point the LPD intensity crosses the threshold of 150 p.e.
+From here, there is a clear LPD continuing up to around 100m.
+Above roughly 100m, the LPD becomes dominated by highly random hadron fragmentation, and thus ceases to be coherent.
+The region 35-90m is considered, and if an exponential if fitted to the LPD, then the fractional deviation $\Delta_{TrueDC} = \frac{signal_{fit} - True_{DC count}}{signal_{fit}}$ can be found.
+Using the 68th centile of all absolute fractional deviations $\Delta_{TrueDC}$, we find that the LPD for $True_{DC}$ has an error of $\sigma_{TrueDC}=0.22$.
+Taking account of $\sigma_{STA}$, we deduce that the true assosiated error in the LPD is $\sigma_{TrueLPD} = \sqrt{(\sigma_{TrueDC}^{2} - \sigma_{STA}^{2})} = 0.20$.
+Thus we conclude that, in an ideal case, any LPD calculated from full shower images would always have a minimum error of 20\%.
+This is reasonably high, and can be partially explained by the random nature of atmospheric conditions, among other things.
+
+The same exercise was repeated using the value of $DC_{Count}$ for the BDT candidate pixels in a full shower image, if the pixel had passed both the $DC_{Count}$ and $P_{signal}$ cuts.
+This provides a more reasonable etimate of the expected LPD error likely to be obtained experimentally, and includes the additional complication of having incorrectly identified pixels in the dataset.
+As before, the absolute fractional deviation of each pixel from the fit of the $True_DC$ LPD was found.
+In this case, the error was much larger, with $\sigma_{DCcount}=0.55$, with the $\sigma_{STA}$ being negligible in comparison.
+This representative error is extremely large, and will pose significant problems for event reconstruction.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{corsikalpd1}
+\caption{The fractional difference in total Image Intensity between the two simulations is shown in the graph above.
+A clear symmetric Gaussian is observed, with a mean of 0.00, and a standard deviation of 0.06.
+Below, the two intensities are plotted against one another.
+The distribution does not deviate significantly from the ideal 1:1 correspondence illustrated with the black line.}
+\label{fig:corsikalpd}
+\end{center}
+\end{figure}
+
+\subsection{Regression BDT for $DC_{Count}$}
+In order to reduce the LPD error, an alternative method of calculating the DC signal was developed.
+A regressor BDT was trained to extrapolate the DC signal, using the variables listed in \ref{tab:hess1regressor}.
+Let's define $Intensity_{N.N.max}$!
+
+\begin{table}[h!]
+  \centering
+  \caption{Relative Feature Importance in HESS-1 Regressor BDT training}
+  \label{tab:hess1regressor}
+  \begin{tabular}{ccc}
+    \toprule
+    Variable & Relative Importance\\
+    \midrule
+    $DC_{Count}$ & 0.45\\
+    $Intensity_{N.N.max}$ & 0.32\\
+    Image Amplitude & 0.14\\
+    $Q_{DC}$ & 0.09\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+Repeating the comparison for the regressor, we find $\sigma_{rgr} = 0.52$, a slight improvement over $\sigma_{DCcount}$.
+
+Binning the fractional difference $\Delta = \frac{ candidate_{DC count} - True_{DC count}}{True_{DC count}}$ as shown in \ref{fig:dcdiff}, we find that the mean difference is -17 and the median difference is -47.
 We thus see that the distribution is not significantly skewed.
@@
 
-Due to the inherent sim\textunderscore telarray random error, there will be an inherent discrepancy due to uncertainty in measurement of the \textquoteleft True Count' as well as in the $DC_{Count}$.
-Thus, any recorded errror is likely to be an overestimate.
-In order to account for this, 2000 events were simulated with CORSIKA as before.
-This time, each event simply contained one simulated image with only hadronic cherenkov light, and another including the hadronic Cherenkov Light as well as the night sky background.
-The distribution was found to have a mean fractional sigma value of roughly 20 \%, due to inconsistencies with sim\textunderscore telarray.
-Thus, we conclude that the resultant
-
 We can parameterise the error by considering the energy and distance to the core for a selection of DC pixels. We find that, for a fixed energy...
@@
 \begin{center}
-\includegraphics[width=\textwidth]{DCcounterrorhess1}
+\includegraphics[width=\textwidth]{DCcounterrorhess1None}
 \caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left.
@@
 Such an array may have a grid spacing of 20-50m, although further study is needed to determine the ideal layout.
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{report}

### 2016-05-27 CORSIKA/lpdforfixedenergy.py

@@ -8,18 +8,61 @@ from telescopeclasses import *
 from matplotlib import rc
 
 parser = argparse.ArgumentParser()
-parser.add_argument("-jid", "--jobID", default="4894324")
+parser.add_argument("-jid", "--jobID", default="56tev-lpd")
 
 cfg = parser.parse_args()
+
+hess1rgrpath = '/nfs/astrop/d6/rstein/BDTpickle/hess1signalregressor.p'
+hess2rgrpath = '/nfs/astrop/d6/rstein/BDTpickle/hess2signalregressor.p'
+if os.path.isfile(hess1rgrpath):
+	hess1rgr = pickle.load(open(hess1rgrpath, "r"))
+else:
+	print "No hess1 pickle!"
+if os.path.isfile(hess2rgrpath):
+	hess2rgr = pickle.load(open(hess1rgrpath, "r"))
+else:
+	print "No hess2 pickle!"
+	
+signalbdtvariables = []
+with open('/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/CORSIKA/signalBDTvariables.csv', 'rb') as csvfile:
+	reader = csv.reader(csvfile, delimiter=',', quotechar='|')
+	for row in reader:
+		signalbdtvariables.append(row[0])
+print signalbdtvariables
+
+minmultiplicity=3
+
+def makeBDTentry(pixelentry):
+	bdtentry =[]
+	for variable in signalbdtvariables:
+		varsplit = variable.split('.')
+		suffix = pixelentry
+		if len(varsplit) > 1:
+			for name in varsplit[:-1]:
+				 suffix = getattr(suffix, name)
+			varname = varsplit[-1]
+		else:
+			varname = variable
+		if hasattr(suffix, varname):
+			newval = getattr(suffix, varname)
+			bdtentry.append(newval)
+		else:
+			return None
+	return bdtentry
 
 
 filepath = "/nfs/astrop/d6/rstein/data/"
 
-j=500
+
+
+j=100
 i=0
 
 distances=[[],[]]
 signals=[[],[]]
+rgrsignals=[[],[]]
+rgrdiffs=[[],[]]
+simplediffs=[[],[]]
 truesignals=[[],[]]
 
 cut, ucut, QDCcut, DCcut, signalcut = ic.runforstats()
@@ -52,7 +95,6 @@ while (i < j):
 		if hasattr(event.simulations, "DC") and hasattr(event.simulations, "full"):
[…]

### 2016-05-27 CORSIKA/runBDT.py

@@ -78,6 +78,8 @@ else:
 	rgrcommand = "python trainextrapolation.py -jid " + cfg.BDTID
 	print time.asctime(time.localtime()), rgrcommand, "\n"
 	os.system(rgrcommand)
+	lpdcommand = "python lpdforfixedenergy.py"
+	os.system(lpdcommand)
 	
 stats_combine_command = "python combineforstatistics.py -jid " + cfg.testID
 print time.asctime(time.localtime()), stats_combine_command, "\n"

### 2016-05-27 CORSIKA/telescopeclasses.py

@@ -412,8 +412,8 @@ class telescopeimage:
 			plt.annotate("Not \n Triggered", xy=(0.2, 0.5), xycoords="axes fraction", zorder=2, color='w', fontsize=(0.3*self.plotscale))
 		
 		if simcategory == "full":
-			if hasattr(self.hillas, "showery"):
-				plt.scatter(self.hillas.showery, self.hillas.showerx, c='w', s=100, marker="o")			
+			#~ if hasattr(self.hillas, "showery"):
+				#~ plt.scatter(self.hillas.showery, self.hillas.showerx, c='w', s=100, marker="o")			
 			if hasattr(self.hillas, "image_cog_y_"):
 				plt.scatter(self.hillas.image_cog_y_, self.hillas.image_cog_x_, c='w', s=100, marker="x")
 			#~ if self.QDCID != None:
@@ -426,16 +426,14 @@ class telescopeimage:
 		if self.trueDC != None:
 			truepixel = self.gettruepixel()
 			print truepixel.ID
-			if simcategory == "full":	
-				plt.scatter(truepixel.y, truepixel.x, facecolors='none', edgecolors="orange", s=(self.plotscale*1.2), marker="o", linewidth=2, zorder=3)
-			elif simcategory == "DC":
-				plt.annotate("",
-				            xy=(truepixel.y+0.05, truepixel.x+0.05), xycoords='data',
-				            xytext=(0.0, 0.0), textcoords='data',
-				            size=20, va="center", ha="center",
-				            arrowprops=dict(arrowstyle="simple",
-				                            connectionstyle="arc3,rad=-0.2", color="yellow"), 
-				            )
+			plt.scatter(truepixel.y, truepixel.x, facecolors='none', edgecolors="white", s=(self.plotscale*1.2), marker="o", linewidth=2, zorder=3)
+			plt.annotate("",
+			            xy=(truepixel.y+0.05, truepixel.x+0.05), xycoords='data',
+			            xytext=(-0.5, 0.0), textcoords='data',
+			            size=20, va="center", ha="center",
+			            arrowprops=dict(arrowstyle="simple",
+			                            connectionstyle="arc3,rad=-0.2", color="white"), 
+			            )
 		plt.xlim(-self.angularwidth, self.angularwidth)
 		plt.ylim(-self.angularwidth, self.angularwidth)
 		plt.axis('off')

### 2016-05-27 CORSIKA/trainextrapolation.py

@@ -42,7 +42,7 @@ def makeBDTentry(pixelentry):
 	return bdtentry
 
 categories = ["hess2","hess1"]
-learningrates = [0.003, 0.005]
+learningrates = [0.002, 0.007]
 
 for i in range(len(categories)):
 	

### 2016-05-30 report/bdtarticle.tex
Backup 30/05/16

@@
 A new method for identifying these Direct Cherenkov pixels was developed, relying on supervised machine learning.
-A set of Cosmic Ray telescope images were simulated, both with and without the Extended Air Shower background, for use in classifier training.
+A set of Cosmic Ray telescope images was simulated, both with and without the Extended Air Shower background, for use in classifier training.
 With reference to the background-free telescope images, the Direct Cherenkov pixel in each corresponding full-shower telescope image could be reliably identified.
@@
 The corresponding sample purity after cuts was 87.7\%, a slight increase on existing methods.
+When only high multiplicity Boosted Decision Tree events were considered, 11.8\% of all Direct Cherenkov pixels were identified, with a sample purity of 90.9\%, while the existing method was not able to find a single comparable high-multiplicity event.
 \end{abstract}
@@
 
-Classifiers provides an alternative method of identification, making use of supervised machine learning to find rules for categorising pixels.
+Classifiers provide an alternative method of identification, making use of supervised machine learning to find rules for categorising pixels.
 To train a classifier, we require a set of training pixels, as well as the correct class for each pixel.
@@
 \caption{A typical camera image without the EAS shower.
-The DC light is visible in every telescope, indicated by the yellow arrow.
-The shower direction is represented by the white circle.
-The largest telescope is CT5, but the relative image sizes are not done to scale}
+The DC light is visible in every telescope, indicated by the white arrow.
+The DC pixel is circled in white.
+The largest telescope image is from CT5, but was not used in analysis.}
 \label{fig:DCtelimage}
@@
 \includegraphics[trim=80 120 80 150,clip,width=\textwidth]{graphfull}
-\caption{The same shower as in \ref{fig:DCtelimage} is shown here with the inclusion of the EAS shower.
-The DC light is pixels are again denoted by an orange circle.
-The white star represents the BDT-selected DC pixel, while the white cross represents the shower center of gravity.}
+\caption{The same shower as in Figure \ref{fig:DCtelimage} is shown here with the inclusion of the EAS shower.
+The DC light is pixels indicated with a white arrow and circle.
+The shower center of gravity is marked by a white cross.}
 \label{fig:cutdistribution2}
@@
 \section{DC Pixel Identification}  
-As a basis for comparison, the original HESS cuts listed in \ref{tab:table1} were replicated for the set of test data.
+As a basis for comparison, the original HESS cuts listed in Table \ref{tab:qdccuts} were replicated for the set of test data.
 For every image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a dynamic cut, $Q_{DC} < 0.14 \times \log(\frac{I_{tot}}{161 \times \cos \theta})$.
-Among pixels passing all cuts, the one with the smallest $Q_{DC}$ among those remaining was selected as the DC pixel candidate for the image.
+Among those pixels passing all cuts, the one with the smallest $Q_{DC}$ was selected as the DC pixel candidate for the image.
 Because many images had no pixel that passed all cuts, the $Q_{DC}$ method was frequently unable to identify a DC pixel.
@@
 
-The candidates were checked against the true DC pixels identified in the EAS-free images.
-From the testing sample, 5.2\% of all images were correctly identified and passed the cuts.
-Once misidentified events were considered, the post-cuts sample was 86.2\% accurate, as shown in \ref{fig:cutdistribution}.
-These values served as a benchmark for BDT performance.
-
 \begin{table}[h!]
@@
   \caption{Cuts applied to image pixel sets, used by HESS collaboration \cite{hess07}}
-  \label{tab:table1}
+  \label{tab:qdccuts}
   \begin{tabular}{ccc}
@@
 
+The candidates were checked against the true DC pixels identified in the EAS-free images.
+From the testing sample, 5.2\% of all images were correctly identified and passed the cuts.
+Once misidentified events were considered, the post-cuts sample was 86.2\% accurate, as shown in Figure \ref{fig:cutdistribution}.
+These values served as a benchmark for BDT performance.
+
 The BDT was trained with the Scikit Learn Python package \cite{scikit-learn}.
-Using the training set of 2000 CORSIKA events, and randomly split further, with 90\% in a learning subset and 10\% in a subset to check for overtraining.
+The training set of 2000 CORSIKA events was randomly split further, with 90\% in a learning subset and 10\% in a subset to check for overtraining.
 Within the learning subset, every HESS 1 image was used, provided it was triggered in both EAS-free and full-shower simulations.
-For each of the 1.7 million triggered image pixels, an entry was formed with the variables listed in table \ref{tab:table2}.
+For each of the 4.7 million triggered image pixels, an entry was formed with the variables listed in Table \ref{tab:hess1classifier}.
 A class of 0 was assigned to every non-DC pixel, and a class of 1 was assigned to every DC pixel.
@@
   \caption{Relative Feature Importance in HESS-1 BDT training}
-  \label{tab:table2}
+  \label{tab:hess1classifier}
   \begin{tabular}{ccc}
@@
 
-The relative importance of each \textquoteleft feature' is automatically calculated by the Scikit Learn package, and is also recorded in table \ref{tab:table2}.
+The relative importance of each \textquoteleft feature' is automatically calculated by the Scikit Learn package, and is also recorded in Table \ref{tab:hess1classifier}.
 The variable $DC_{Count}$ was consistently the most importance variable across many combinations of included variables and BDT training parameters.
@@
 This represents a very significant improvement in pixel identification efficiency, as well as a minor increase in accuracy after cuts.
-The results are summarised in \ref{tab:table3}.
+
+For event reconstruction, we often require events to have a high telescope multiplicity.
+If we only consider events in which all four DC pixels were identified, we can determine the high-multiplicity BDT performance.
+In this case, the fraction of correctly identified DC pixels falls to 11.8\%, while the fraction of incorrectly identified pixels passing the cuts falls to 1.2\%.
+The sample purity increases slightly to 90.9\%.
+The relatively high fraction of passing events, in excess of the random expectation of $0.372^{4}=1.9 \%$, suggests that DC pixel identification between different telescope images is strongly correlated.
+
+However, out of 1245 triggered events, there were none in which the $Q_{DC}$ method identified four DC pixels.
+Using poissonian statistics, we can place an upper limit of $<0.24 \%$ on the rate of accepted, high-multiplicity $Q_{DC}$ events.
+Thus, as well as BDT accuracy slightly improving, the performance gap over the $Q_{DC}$ method is vastly increased for high-multiplicity events.
+The results are summarised in Table \ref{tab:table3}.
 
@@
    Pixels Accepted and Incorrectly Identified (\%) & 0.8 & 5.2\\
-    Sample Purity (\%) & 86.2 & 87.7\\
+    Sample Purity (\%) & 86.2 & 87.7 \\
+    \midrule
+    High Multiplicity Pixels Accepted and Correctly Identified (\%) & $<0.24$ & 11.8\\
+    High Multiplicity Pixels Accepted and Incorrectly Identified (\%) & $<0.24$ & 1.2\\
+    Sample Purity (\%) & / & 90.9\\
+    \bottomrule
   \end{tabular}
@@
 \includegraphics[width=\textwidth]{cutdistribution1None}
-\caption{The true $Intensity_{DC}$ in the EAS-free image is shown in the top left, with a broad exponential decay in count as DC intensity increases.
-Sim\textunderscore telarray requires a minimum of 20 photoelectrons in order for a telescope to be triggered, leading to a discontinuity at low intensities in the graph.
-In the top right- the distribution of the dataset is shown, once all $Q_{DC}$ cuts have been applied.
-In the bottom left, the $P_{signal}$ (BDT score) distribution is shown before any cuts.
-On the bottom right, we see the same distribution after both $DC_{Count}$ and $P_{signal}$ cuts are applied.
-All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.
-We desire both a large number of green events, and a good degree separability of red and green events.}
+\caption{A study of 2000 simulated events is displayed above.
+For all graphs, the green represents correctly identified pixels, while the grey indicates incorrectly identified pixels.
+We desire many green pixels, few grey pixels, and a good degree of separability between the two groups.
+In the top left, the $P_{signal}$ (BDT score) distribution is shown before any cuts.
+A low score indicates a non-DC pixel, and a high score indicates a DC pixel.
+Most incorrectly identified events are found at lower $P_{signal}$ values.
+In the top right, the true intensity $True_{DC}$ in the EAS-free image is shown, with a broad exponential decay in count as DC intensity increases.
+As might be expected, events with a larger $True_{DC}$ are more likely to be correctly identified, as they have clearer signal.
+A cut is applied to the calculated value $DC_{Count}$, which is strongly correlated to $True_{DC}$.
+In the bottom left, we see the same BDT score distribution after both $DC_{Count}$ and $P_{signal}$ cuts are applied.
+The proportion of incorrectly identified events is visibly decreased.
+In the bottom right, a comparative distribution of $Q_{DC}$ values for pixels that have passed all the $Q_{DC}$-related cuts is shown.
+The sample purity is similar to the BDT-reconstructed distribution, but the raw number of correctly identified events is significantly smaller.}
 \label{fig:cutdistribution}
@@
 The use of BDT identification has been shown to be superior to the traditional $Q_{DC}$ method, by providing many more correctly identified DC pixels without a corresponding loss of accuracy.
-In the case of HESS 1, this represented a sevenfold increase in the expected number of DC pixels.
-BDT performance improves with increasing training data size, so there is no reason not to think that the successful ID rate for pixels could continue to be increased further.
-Due to the good degree ofr separability of the BDT signal probability, a further increase in sample purity would certainly be possible at the expense of harsher
-$P_{signal}$ cuts reducing the size of the datasets.
+For all simulated HESS 1 images, the BDT yielded a sevenfold increase in the expected number of DC pixels.
+In the case of high-multiplicity events, the relative performance improves dramatically, representing at least a fifty-fold increase in the rate of correctly identified pixels passing all cuts.
+BDT performance improves with increasing training data size, so we can assume that the successful ID rate for pixels could continue to be increased further.
+Due to the good degree of separability of the BDT signal probability, a further increase in sample purity would certainly be possible at the expense of harsher $P_{signal}$ cuts reducing the size of the datasets.
 In short, the BDT method produces not just superior performance but increased flexibility for balancing sample purity and size.

### 2016-05-30 report/draft1.tex
Backup 30/05/16

@@
 \section{DC Pixel Identification}
+\textbf{Cosmic Rays will emit Direct Cherenkov (DC) light in the upper atmosphere, before generating an Extended Air Shower (EAS) through interaction with the lower atmosphere. }
+
+In telescope images, the DC light is usually concentrated in a single  \textquoteleft DC pixel'.
+Identifying this pixel is challenging, because the brighter EAS Cherenkov light background often overlaps with the DC pixel.
 In order to apply the LPD method to data, we must first identify the DC pixel in a shower image, and determine the number of DC photoelectrons present.
-A full simulation of air showers was performed using the CORSIKA package, and the sim\textunderscore telarray package was used to simulate HESS camera images generated from the shower.
-As part of a new method developed for this analysis, a Boosted Decision Tree (BDT) was trained using image parameters to identify DC pixels, and its performance was tested.
 
-\subsection{CORSIKA}
-A full simulation of Cosmic Ray air showers was performed using the CORSIKA package \cite{Heck98}, assuming a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
-The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{-2.7}$.
+We define the variable $Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity}$ as the ratio of the largest neighbouring pixel intensity to the intensity of a given pixel.
+In previous experiments, the DC pixel candidate was identified by applying a number of cuts to pixels in an image \cite{hess07}, and from the subset of pixels passing the specified cuts, selecting the pixel with the smallest $Q_{DC}$ as the \textquoteleft DC candidate'.
+Due to the low pass rate for cuts, we obtain a small low-contamination dataset, while the majority of telescope images are left without a DC pixel candidate.
+An improved method would aim to increase the number of correctly identified DC pixels, while still enabling cuts which discriminate well between correctly and incorrectly identified DC pixels.
+
+Classifiers provide an alternative method of identification, making use of supervised machine learning to find rules for categorising pixels.
+To train a classifier, we require a set of training pixels, as well as the correct class for each pixel.
+Once trained, a classifier can then be used to predict the class of a pixel.
+
+The CORSIKA package \cite{Heck98} was used to generate Cosmic Ray events, and the Sim\textunderscore telarray package  \cite{Bernlohr08} was used to generate corresponding HESS array telescope images.
+Simulation with EAS background was used to produce training pixel sets, while corresponding simulation without EAS background was used to find the true DC pixel in each training image.
+As part of a new method developed for this analysis, a Boosted Decision Tree (BDT) classifier was trained with the data to identify DC pixels.
+Once trained, the BDT was applied to a separate \textquoteleft testing' set of simulated telescope images.
+As before, the true DC pixel was determined from a second EAS-free simulation.
+Thus, the accuracy of BDT identification for test telescope images was calculated.
+
+\subsection{Image Simulation}
+The full simulation of air showers was performed using the CORSIKA package, with a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
+In total, 2000 training events and a further 2000 testing events were simulated.
+The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi(E) \propto E^{-2.7}$.
 For each set of simulated event, 4 unique random number seeds were used to generate the shower.
@@
 
-In order to identify the DC pixel, a \textquoteleft DC Simulation' was initially run with an energy cut of 10 PeV on all muons and electrons.
-The consequence of this was to ensure that only the Cherenkov Light from the primary particle, as well as its fragments, was simulated.
-A second identical \textquoteleft Full Simulation' was run including the same random seeds, but without the energy cut on muons and electrons.
-This gave a complete air shower including the DC light, representative of those imaged in telescope arrays.
-Comparisons of the Full and DC simulations enabled us to identify background light in the Full shower.
+\textbf{Due to hardware differences between CT5 and the original HESS 1 telescopes, only images from HESS-phase-1 were considered.}
 
-\subsection{Sim\textunderscore telarray}
-Using the sim\textunderscore telarray package \cite{Bernlohr08}, the expected hardware response to an air shower can be simulated.
-Again, the built-in response of the HESS telescope was selected for simulation.
-The program accounts for atmospheric transmission and density, mirror positions, sizes and reflectivities, camera shadowing and triggering, quantum efficiency and pulse responses.
-Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered representative of true camera images.
-For the Full Simulation, the night sky background was also simulated by sim\textunderscore telarray.
+To determine the true class of each pixel, a simulation was initially run with an energy cut of 10 PeV on all muons and electrons.
+Because this cut exceeded the primary particle energy, neither daughter muons and electrons, nor the photons they would have emitted, were simulated.
+Thus the hadronic Cherenkov Light from the primary particle and daughter fragments, but not the EAS light, was present in the camera image.
+A second identical \textquoteleft EAS Simulation' was run including the same random seeds, but without the energy cut on muons and electrons.
+This gave a complete EAS image including identical DC light.
 
-The HESS telescope has both a high gain Channel 0 and a low gain Channel 1.
-The location of each pixel (dependent on camera size), alongside the Sim\textunderscore telarray simulated value of SOMETHING?
-in each value was extracted.
-The pedestal and gain for each channel was also recorded, and from this, Intensity can be found.
+With the sim\textunderscore telarray package, the expected HESS hardware response to each air shower was simulated.
+Among other things, the program accounts for atmospheric transmission and density, mirror positions, sizes and reflectivities, camera shadowing and triggering, quantum efficiency and pulse responses.
+For the full-shower image, the night sky background was also simulated by sim\textunderscore telarray.
+Due to the comprehensive and detailed nature of these hardware simulations, the resultant images can be considered \textquoteleft realistic'.
+However, sim\textunderscore telarray introduces various sources of random noise to the simulation, leading to some divergence in the DC light between the EAS-free and full-shower images.
 
-\[ Intensity = (Count - Pedestal)\times Gain \]
+\begin{figure}
+\newgeometry{a4paper, portrait, margin=1.0in}
+\centering
+\begin{minipage}{0.45\textwidth}
+\centering
+\includegraphics[trim=80 120 80 150,clip,width=\textwidth]{graphDC}
+\caption{A typical camera image without the EAS shower.
+The DC light is visible in every telescope, indicated by the white arrow.
+The DC pixel is circled in white.
+The largest telescope image is from CT5, but was not used in analysis.}
+\label{fig:DCtelimage}
+\end{minipage}\hfill
+\begin{minipage}{0.45\textwidth}
+\centering
+\includegraphics[trim=80 120 80 150,clip,width=\textwidth]{graphfull}
+\caption{The same shower as in \ref{fig:DCtelimage} is shown here with the inclusion of the EAS shower.
+The DC light is pixels indicated with a white arrow and circle.
+The shower center of gravity is marked by a white cross.}
+\label{fig:cutdistribution2}
+\end{minipage}
+\restoregeometry
+\end{figure}
 
-In the case of many iron core events, Channel 0 will reach its maximum value and become saturated.
-Thus Channel 0 ceases to be useful for discriminating between high energy DC and non-DC pixels, so was not used in this analysis.
-Instead, only the Channel 1 was used in later analysis.
-Thus the Channel 1 Intensity will simply be referred to throughout this analysis as $Intensity$.
+The various pixel entry variables were found from the sim\textunderscore telarray output.
+The HESS telescope pixels have a high gain Channel 0 and a low gain Channel 1, with both voltages undergoing a Flash Analogue-to-Digital Conversion (FADC).
+The simulated value of the FADC Voltage for each channel was found.
+Using the pedestal and gain, the quantity $Intensity = (FADC - Pedestal)\times Gain $ was calculated for each channel.
+Due to possible saturation of the high gain FADC, only the low gain $Intensity$ was used.
+Sim\textunderscore telarray also derives various Hillas whole-image parameters.
+These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated.
+The reconstructed shower direction and the shower center of gravity were also calculated, as positions in azimuth and zenith.
+Additionally the estimated energy and distance from each telescope to core, $r_{core}$,  were found.
 
-In addition to the $Intensity$ of each pixel, the Sim\textunderscore telarray derives various Hillas whole-image parameters, which the script also extracted.
-These include the image width and length measured in degrees, from which the aspect ratio $A.R = \frac{width}{length}$ was calculated.
-Further the reconstructed shower direction and the shower center of gravity were calculated as positions in azimuth and zenith.
-Additionally the calculated energy and distance to core $r_{core}$ were recorded.
+For every pixel, in addition to the $Intensity$, its location within the telescope image was determined using the standard HESS layout.
+The variables $ \Delta_{C.o.G}$, $\Delta_{Direction}$ and $\Delta_{Line}$ were defined as the distance from the pixel to the shower center of gravity, shower direction, and the line joining those two points.
+Furthermore, the nearest neigbouring pixel IDs were calculated for every pixel position, enabling the $Intensity$ in each neighbouring pixel to be found.
+The largest neighbouring intensity was identified, and the ratio $Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity}$ was derived.
+Similarly the largest neighbouring FADC was found, and the ratio $raw_{Q} = \frac{FADC_{N.N.max}}{FADC}$ was calculated.
+In addition, the Nearest Neighbour Mean Intensity $Mean_{N.N}$ was recorded.
+The variable $DC_{Signal} = Intensity-Mean_{N.N}$ was defined as an rough guess of the \textquoteleft DC signal' component in the pixel.
+Lastly the Image Amplitude $I_{tot}$, defined as the total image intensity after the default tail cuts have been applied to the image.
 
-An entry was constructed for every pixel, containing its count and position.
-The variables $ \Delta_{C.o.G}$, $\Delta_{Direction}$ and $\Delta_{Line}$ were defined as the distance from the pixel to the shower center of gravity, shower direction, and the line joining those two points.
-Furthermore, the nearest neigbouring pixel IDs were calculated for every pixel position, enabling the count in each neighbouring pixel to be found.
-From this, two further pixel variables were defined.
-The largest neighbouring intensity $Intensity_{N.N.max}$ was found, and the ratio $ Q_{DC} = \frac{Intensity}{Intensity_{N.N.max}} $ was derived.
-In addition the Nearest Neighbour Mean Count was recorded.
-These variables were recorded in every pixel entry, and together the pixel entries formed a complete dataset for each camera image.
-
-\subsection{Classic DC Identification}
-The original method used by the HESS collaboration \cite{hess07} was initially replicated, for which a number of cuts were applied to each image dataset.
+\subsection{Classic DC Pixel Identification}
+As a basis for comparison, the original HESS cuts listed in \ref{tab:table1} were replicated for the set of test data.
+For every image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a dynamic cut, $Q_{DC} < 0.14 \times \log(\frac{I_{tot}}{161 \times \cos \theta})$.
+Among those pixels passing all cuts, the one with the smallest $Q_{DC}$ was selected as the DC pixel candidate for the image.
+Because many images had no pixel that passed all cuts, the $Q_{DC}$ method was frequently unable to identify a DC pixel.
+In the original analysis, an additional cut $r_{core} \textgreater 40m$ was applied.
+However, the uncertainty in determining the core position through Hillas Analysis is typically of the order of $\pm 30m$.
+Consequently, this particular cut was omitted.
 
@@
   \centering
-  \caption{Cuts applied to image pixel sets}
-  \label{tab:qdccuts}
+  \caption{Cuts applied to image pixel sets, used by HESS collaboration \cite{hess07}}
+  \label{tab:table1}
   \begin{tabular}{ccc}
@@
     \midrule
-     $r_{core}$ & \textgreater 0.4 \\
-     $Q_{DC}$ & \textgreater 1.3 \\
      $ \Delta_{C.o.G}$ & \textgreater 0.17 \\
@@
 
-From the subset of pixels satisfying these conditions, the remaining pixel with the largest $Q_{DC}$ was selected as the DC pixel.
-The result was compared with the true DC pixel, identified from the hadron-only image, to test the accuracy of this cut.
-Out of 400 events, it was fount that only 55\% of these events contained a clear DC signal, as defined by requiring the DC pixel to have $Intensity_{DC} > 150$ in the hadron-only image.
-SOMETHING!
-Of this subset of 'DC events', 17\% events passed all of the required cuts.
-The $Q_{DC}$ was found to be 100\% accurate in identifying the DC pixel in those passing events, as shown in \ref{fig:cutdistribution}.
+The candidates were checked against the true DC pixels identified in the EAS-free images.
+From the testing sample, 5.2\% of all images were correctly identified and passed the cuts.
+Once misidentified events were considered, the post-cuts sample was 86.2\% accurate, as shown in \ref{fig:cutdistribution}.
+These values served as a benchmark for BDT performance.
 
@@
 
-\subsection{Boosted Decision Tree DC Identification}  As an alternative to use of $Q_{DC}$, a new method of DC pixel identification was developed as part of this analysis by using a BDT trained with the Scikit Learn Python package.
-A set of 2000 simulated events was selected, and randomly split through use of the python random.random() function into two subsets for training and testing.
-The variable $DC_{Count} = Count-Mean_{N.N}$ was defined as an approximate \textquoteleft DC signal', if the pixel were to be selected as the DC candidate.
-For every pixel in the 2000 simulated events HESS 1 images, an entry was formed of $Q_{DC}$, $ \Delta_{C.o.G}$, $\Delta_{Direction}$, $\Delta_{Line}$, Channel1, Channel0, $DC_{Count}$ and $Mean_{N.N}$.
-A score of 0 was assigned to every pixel to indicate background, with the exception of those that were identified as the DC pixel through the Shower-Free simulation.
-If the DC count in the shower-free simulation was larger than 300, the pixel was included with a score of 1, identifying it as a signal pixel.
-Pure DC pixels below the threshold cut of 300 were deemed to be too faint to reconstruct, so these entries were omitted from the training set.
+\subsection{Boosted Decision Tree DC Identification}
+As an alternative to use of $Q_{DC}$, a new method of DC pixel identification was developed as part of this analysis by using a BDT trained with the Scikit Learn Python package \cite{scikit-learn}.
+Using the training set of 2000 CORSIKA events, and randomly split further, with 90\% in a learning subset and 10\% in a subset to check for overtraining.
+Within the learning subset, every HESS 1 image was used, provided it was triggered in both EAS-free and full-shower simulations.
+For each of the 4.7 million triggered image pixels, an entry was formed with the variables listed in table \ref{tab:hess1classifier}.
+A class of 0 was assigned to every non-DC pixel, and a class of 1 was assigned to every DC pixel.
+Having created a dataset, the BDT was then trained with a maximum depth of 8, and with 100 trees generated.
+The data was provided in the form of individual pixel entries, rather than as discrete sets for images or events.
 
-Having created a dataset, the BDT was then trained with a maximum depth of 5, and 100 trees generated.
-It was found that the BDT was 100 \% accurate for the entire training dataset, with a breakdown of 100 \% for the training background and 99 \% accurate with the training signal.
-When the trained BDT was applied to the testing pixels, it was found to be 99.99 \%  accurate for the entire training dataset, with a breakdown of 100 \% for the testing background and 99 \% accurate with the testing signal.
-This indicates that the BDT was not significantly overtrained, which would otherwise be manifested by a large divergence in accuracy between testing and training data.
+\begin{table}[h!]
+  \centering
+  \caption{Relative Feature Importance in HESS-1 BDT training}
+  \label{tab:hess1classifier}
+  \begin{tabular}{ccc}
+    \toprule
+    Variable & Relative Importance\\
+    \midrule
+    $DC_{Count}$ & 0.34\\
+    $Mean_{N.N}$ & 0.26\\
+    $\Delta_{Direction}$ & 0.11\\
+    Image Amplitude & 0.10\\
+    $Q_{DC}$ & 0.10\\
+    $raw_{Q}$ & 0.05\\
+    $\Delta_{Line}$ & 0.02\\
+    $Intensity$ & 0.02\\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
-\subsection{Composite Event Selection}
-Having trained the BDT successfully, it was then applied to the same dataset as for the classic QDC identification.
+The relative importance of each \textquoteleft feature' is automatically calculated by the Scikit Learn package, and is also recorded in table \ref{tab:hess1classifier}.
+The variable $DC_{Count}$ was consistently the most importance variable across many combinations of included variables and BDT training parameters.
+It was found that, under the conditions listed above, the BDT was 99.94 \% accurate for the learning pixel subset, and 99.93 \%  accurate for the overtraining-check pixel subset.
+This indicates that the BDT was not significantly overtrained, which would otherwise be manifested by a large divergence in accuracy between learning and overtraining-check data.
+
+Having trained the BDT successfully, it was then applied to the same test dataset as for the classic $Q_{DC}$ identification.
 In each camera image, the event with the largest BDT score was deemed to be \textquoteleft most signal-like', and thus selected as the DC pixel candidate.
-A cut was applied, requiring $Probability_{signal} > 0.5$ for the DC candidate to be accepted.
+A cut was applied, requiring $P_{signal} > 0.5$ for the DC candidate to be accepted.
+A second cut requiring $DC_{Count} > 150$ removed many incorrectly identified events.
+Application of this combined cut greatly increases the successful identification rate.
+From the testing sample, 37.3\% of all images were correctly identified and passed the cuts.
+The BDT was found to be 87.7\% accurate in identifying DC pixels which passed the cuts.
+This represents a very significant improvement in pixel identification efficiency, as well as a minor increase in accuracy after cuts.
 
-With this cut applied, out of 1200 events, 46\% events passed all of the required cuts. The BDT was found to be 75 \% accurate in identifying the DC pixel in those passing events.
+For LPD event reconstruction, we require events to have a telescope multiplicity $>3$.
+If we only consider events in which at least four DC pixels were identified, we can determine the high-multiplicity BDT performance.
+In this case, the fraction of correctly identified DC pixels falls to 16.8\%, while the fraction of incorrectly identified pixels passing the cuts falls to 1.8\%.
+The sample purity increases slightly to 90.3\%.
+The relatively high fraction of passing events, in excess of the random expectation of $0.372^{4}=1.9 \%$, suggests that DC pixel identification between different telescope images is strongly correlated.
 
-In \ref{fig:cutdistribution}, a plot of true vs.
-reconstructed DC count is shown, obtained by comparing the BDT selected pixel to the hadron-only DC pixel.
-The black line indicates the optimal 1:1 ratio that we are aiming for.
-It is seen that there the vast majority of misidentified events have a small $candidate_{DC count}$, forming a red line in the region $candidate_{DC count} \approx 0$.
-To remove these misidentified events, we can apply a second cut requiring $candidate_{DC count} > 300$.
+However, out of 1245 triggered events, there were none in which the $Q_{DC}$ method identified four DC pixels.
+Using poissonian statistics, we can place an upper limit of $<0.24 \%$ on the rate of accepted, high-multiplicity $Q_{DC}$ events.
+Thus, as well as BDT accuracy slightly improving, the performance gap over the $Q_{DC}$ method is vastly increased for high-multiplicity events.
+The results are summarised in Table \ref{tab:qdcbdtcomparison1}.
+The BDT method represents a very significant improvement in DC pixel identification over the previous $Q_{DC}$ method, and corresponds to at least a fifty-fold increase in the number of HESS data events that can be studied using the LPD method.
+Use of this BDT method is thus assumed throughout the rest of this analysis.
 
-Application of this combined cut greatly increases the successful identification rate.
-Of the 2000 events, 84\% of events passed all of the required cuts.
-The BDT was found to be 90 \% accurate in identifying the DC pixel in those passing events.
-This represents a very significant improvement in DC pixel identification over the previous QDC method, and corresponds to a fivefold increase in the number of HESS data events that can be studied using the LPD method.
-Use of this BDT method is thus assumed throughout the rest of this analysis.
+\begin{table}[h!]
+  \centering
+  \caption{Comparison of $Q_{DC}$ and HESS 1 BDT Performance}
+  \label{tab:qdcbdtcomparison1}
+  \begin{tabular}{ccc}
+    \toprule
+    & $Q_{DC}$ & BDT\\
+    \midrule
+    Pixels Accepted and Correctly Identified (\%) & 5.2 & 37.2\\
+   Pixels Accepted and Incorrectly Identified (\%) & 0.8 & 5.2\\
+    Sample Purity (\%) & 86.2 & 87.7 \\
+    \midrule
+    High Multiplicity Pixels Accepted and Correctly Identified (\%) & $<0.24$ & 16.8\\
+    High Multiplicity Pixels Accepted and Incorrectly Identified (\%) & $<0.24$ & 1.8\\
+    Sample Purity (\%) & / & 90.3\\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
@@
 To improve CT5 pixel identification, a separate HESS2 BDT was instead trained with the same variables as above.
-The relative feature importance is listed in \ref{tab:hess2classifier}.
-The CT5 performance was improved for the new classifier, with 24.0 \% of pixels being correctly identified and accepted, and an accuracy of 80.2 \%.
-Despite this improvement, a clear gap emerged between the between the performance of HESS1 classifier on old telescopes, and the performance of the HESS2 classifier on CT5.
-Part of this discrepancy can be explained by the HESS2 learning dataset, which has just one DC pixel per event rather than the four HESS1 DC pixels.
-Additionally, HESS 2 images will have roughly 2600 non-DC pixels per event, versus 3600 DC pixels per event for HESS 1 images.
-The HESS2 classifier was thus trained on significantly fewer DC pixels, so we would expect to see the clear performance gap in comparison to the HESS1 classifier.
+The relative feature importance is listed in Table \ref{tab:hess2classifier}.
 
@@
 
-\subsection{Error in calculated $Count_{DC}$}
+The CT5 performance was improved for the new classifier, with 24.0 \% of pixels being correctly identified and accepted, and an accuracy of 79.4\%.
+Despite this improvement, a clear gap emerged between the between the performance of HESS1 classifier on old telescopes, and the performance of the HESS2 classifier on CT5.
+Part of this discrepancy can be explained by the HESS2 learning dataset, which has just one DC pixel per event rather than the four HESS1 DC pixels.
+Additionally, HESS 2 images will have roughly 2600 non-DC pixels per event, versus 3600 DC pixels per event for HESS 1 images.
+The HESS2 classifier was thus trained on significantly fewer DC pixels, so we would expect to see the clear performance gap in comparison to the HESS1 classifier.
+In the case of the high-multiplicity events, the gap narrows somewhat.
+In total 9.4\% of pixels are correctly identified and accepted, although the accuracy rate is only increased to 81.0\%.
+As stated before, no $Q_{DC}$ event had four or more DC pixels identified, and thus the only conclusion to be drawn on the $Q_{DC} method$ is to place an upper limit of the event rate.
+
+\begin{table}[h!]
+  \centering
+  \caption{Comparison of $Q_{DC}$ and HESS 2 BDT Performance}
+  \label{tab:qdcbdtcomparison2}
+  \begin{tabular}{ccc}
+    \toprule
+    & $Q_{DC}$ & BDT\\
+    \midrule
+    Pixels Accepted and Correctly Identified (\%) & 5.7 & 24.8\\
+   Pixels Accepted and Incorrectly Identified (\%) & 10.6 & 6.4\\
+    Sample Purity (\%) & 34.8 & 79.4 \\
+    \midrule
+    High Multiplicity Pixels Accepted and Correctly Identified (\%) & $<0.24$ & 9.4\\
+    High Multiplicity Pixels Accepted and Incorrectly Identified (\%) & $<0.24$ & 2.2\\
+    Sample Purity (\%) & / & 81.0\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\subsection{Determining $True_{DC}$}
+yeah stuff and such....
+
+\textbf{Let's define $Intensity_{N.N.max}$!}
+
+\subsection{Error in calculated $DC_{count}$}
 Having successfully identified the DC pixel in many events, we can find the error $\sigma_{LPD}$ in our calculated $candidate_{DC count}$, through comparison with the correct value $True_{DC}$.
@@
 The fractional difference from the mean Intensity of an image was defined as $\Delta = 2 \times \frac{I_{2} - I_{1}}{{I_{2} + I_{1}}}$ .
-It was found that the standard deviation in fractional difference was $\sigma_{STA}=0.09$, meaning that there is an inherent error of 9 \% in measurements of $True_{DC}$.
+It was found that the standard deviation in fractional difference was $\sigma_{STA}=0.06$, meaning that there is an inherent error of 6 \% in measurements of $True_{DC}$.
 In later calculations of the error in Intensity, this fractional error can be subtracted in quadrature.
@@
 \begin{center}
-\includegraphics[width=\textwidth]{simtelerror1}
+\includegraphics[height=0.9\textheight]{simtelerror1}
 \caption{The fractional difference in total Image Intensity between the two simulations is shown in the graph above.
@@
 The region 35-90m is considered, and if an exponential if fitted to the LPD, then the fractional deviation $\Delta_{TrueDC} = \frac{signal_{fit} - True_{DC count}}{signal_{fit}}$ can be found.
-Using the 68th centile of all absolute fractional deviations $\Delta_{TrueDC}$, we find that the LPD for $True_{DC}$ has an error of $\sigma_{TrueDC}=0.22$.
-Taking account of $\sigma_{STA}$, we deduce that the true assosiated error in the LPD is $\sigma_{TrueLPD} = \sqrt{(\sigma_{TrueDC}^{2} - \sigma_{STA}^{2})} = 0.20$.
-Thus we conclude that, in an ideal case, any LPD calculated from full shower images would always have a minimum error of 20\%.
+Using the 68th centile of all absolute fractional deviations $\Delta_{TrueDC}$, we find that the LPD for $True_{DC}$ has an error of $\sigma_{TrueDC}=0.12$.
+Taking account of $\sigma_{STA}$, we deduce that the true associated error in the LPD is $\sigma_{TrueLPD} = \sqrt{(\sigma_{TrueDC}^{2} - \sigma_{STA}^{2})} = 0.11$.
+Thus we conclude that, in an ideal case, any LPD calculated from full shower images would always have a minimum error of 11\%.
 This is reasonably high, and can be partially explained by the random nature of atmospheric conditions, among other things.
@@
 The same exercise was repeated using the value of $DC_{Count}$ for the BDT candidate pixels in a full shower image, if the pixel had passed both the $DC_{Count}$ and $P_{signal}$ cuts.
-This provides a more reasonable etimate of the expected LPD error likely to be obtained experimentally, and includes the additional complication of having incorrectly identified pixels in the dataset.
-As before, the absolute fractional deviation of each pixel from the fit of the $True_DC$ LPD was found.
-In this case, the error was much larger, with $\sigma_{DCcount}=0.55$, with the $\sigma_{STA}$ being negligible in comparison.
+This provides a more reasonable estimate of the expected LPD error likely to be obtained experimentally, and includes the additional complication of having incorrectly identified pixels in the dataset.
+As before, the absolute fractional deviation of each pixel from the fit of the $True_{DC}$ LPD was found.
+Due to consistent underestimate of the $True_{DC}$ value using the simple $DC_{Count}$ method, the error was much larger, with $\sigma_{DCcount}=0.57$ and the $\sigma_{STA}$ being negligible in comparison.
 This representative error is extremely large, and will pose significant problems for event reconstruction.
@@
 \includegraphics[width=\textwidth]{corsikalpd1}
-\caption{The fractional difference in total Image Intensity between the two simulations is shown in the graph above.
-A clear symmetric Gaussian is observed, with a mean of 0.00, and a standard deviation of 0.06.
-Below, the two intensities are plotted against one another.
-The distribution does not deviate significantly from the ideal 1:1 correspondence illustrated with the black line.}
+\caption{The LPDs are shown above for $True_{DC}$, the simple guess $DC_{Count}$, and the regressor calculated $DC_{rgr}$.
+An exponential is fit to the $True_{DC}$ distribution, and the 68\% fractional deviation is shown in green.
+The same curve is shown on the two derived DC values, with the new fractional deviation being much greater.}
 \label{fig:corsikalpd}
@@
 In order to reduce the LPD error, an alternative method of calculating the DC signal was developed.
-A regressor BDT was trained to extrapolate the DC signal, using the variables listed in \ref{tab:hess1regressor}.
-Let's define $Intensity_{N.N.max}$!
+Supervised machine learning was again used to solve the problem, by training a BDT Regressor.
+As with Classifiers, Regressors are initially trained using individual data entries.
+Instead of the true classes for the entries, regressors require the true value of a continuous variable.
+Once trained, the regressor can be used to predict a value of the variable for a given data entry.
+In this case, the Regressor is trained to estimate the quantity of DC light $True_{DC}$ for a given pixel.
+Once a DC pixel has been identified, the regressor is applied to it.
+The regressor returns the calculated value of $DC_{rgr}$, an alternative estimate of the DC signal.
+
+Accurate measurement of the value of $True_{DC}$ is hindered because the DC light can be split into multiple pixels.
+Instead of the brightest pixel intensity the total Image Amplitude in the EAS free image was used.
+However, for high altitude/zenith angles, the DC light may lie partially outside the telescope image.
+To account for this, a new training sample was simulated in CORSIKA with both zenith and azimuth angle fixed at 0.
+Despite intuitive expectation that regressor performance should worsen significantly when it was tested on the use 2000-event testing sample, the more accurate $True_{DC}$ values for the training more than compensated for this.
+
+The training set of data consisted of the true DC pixel in each full shower image.
+A regressor BDT was trained to extrapolate the DC signal, using the variables listed in Table \ref{tab:hess1regressor}.
+To account for the differing hardware, a separate regressor was trained, as before, for the CT5 camera.
+However, initial performance was poor, due to the size of the training dataset.
+Only one pixel per image was usable, leading to a small training dataset.
+Initial performance, as measured by deviation in \ref{fig:corsikalpd}, was initially poor.
+However, an expanded dataset of 5000 events greatly reduced the deviation from $True_{DC}$ values.
+The final BDT was trained with 1000 estimators and a max depth of 3.
+The Feature Importances for the HESS1 and HESS2 regressor are listed in Table \ref{tab:hess1regressor} and Table \ref{tab:hess2regressor} respectively.
+There is again a discrepancy in variable importance between the two BDTs.
 
@@
     \midrule
-    $DC_{Count}$ & 0.45\\
-    $Intensity_{N.N.max}$ & 0.32\\
-    Image Amplitude & 0.14\\
-    $Q_{DC}$ & 0.09\\
+    $Q_{DC}$ & 0.17\\
+    $DC_{Count}$ & 0.16\\
+    Image Amplitude & 0.15\\
+    $Intensity_{N.N.min}$ & 0.14\\
+    $Intensity_{N.N.max}$ & 0.14\\
+    $Intensity$ & 0.13\\
+    $Mean_{N.N}$ & 0.11\\
     \bottomrule
@@
 
-Repeating the comparison for the regressor, we find $\sigma_{rgr} = 0.52$, a slight improvement over $\sigma_{DCcount}$.
+\begin{table}[h!]
+  \centering
+  \caption{Relative Feature Importance in HESS-2 Regressor BDT training}
+  \label{tab:hess2regressor}
+  \begin{tabular}{ccc}
+    \toprule
+    Variable & Relative Importance\\
+    \midrule
+    Image Amplitude & 0.20\\
+    $Intensity_{N.N.min}$ & 0.15\\
+    $Q_{DC}$ & 0.15\\
+    $Mean_{N.N}$ & 0.14\\
+    $DC_{Count}$ & 0.13\\
+    $Intensity_{N.N.max}$ & 0.13\\
+    $Intensity$ & 0.13\\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
-Binning the fractional difference $\Delta = \frac{ candidate_{DC count} - True_{DC count}}{True_{DC count}}$ as shown in \ref{fig:dcdiff}, we find that the mean difference is -17 and the median difference is -47.
-We thus see that the distribution is not significantly skewed.
-However, the Standard deviation is 158 when measured both by half of the difference from the 16th to 84th centile, and by 68th centile of an absolute difference.
-This again suggests that, although skewed, the fraction error in intensity is fairly large.
-However, the fractional error found purely on the basis of QDC calculations is EQUALLY LARGE??LARGER?.
+Repeating the comparison for the HESS1 regressor, we find for $\sigma_{rgrfit} = 0.35$, a significant improvement over $\sigma_{DCcount}$.
+Taking into account $\sigma_{STA}$, we find that ultimately $\sigma_{rgr}=0.34$, a fairly large value that nonetheless should be acceptable in 4-telescope events.
+The comparative performance is recorded in Table \ref{tab:lpderror}.
+
+\begin{table}[h!]
+  \centering
+  \caption{Fractional error from fitted 56-TeV LPD distribution, accounting for $\sigma_{STA}$}
+  \label{tab:lpderror}
+  \begin{tabular}{ccc}
+    \toprule
+    & HESS1 & HESS2\\
+    \midrule
+    $\sigma_{TrueDC}$ & 0.13 & 0.18\\
+    $\sigma_{DCcount}$ & 0.70 & 0.88\\
+    $\sigma_{rgr}$ & 0.36 & 0.50\\ 
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+To get a more accurate estimate of the error, the testing set of 2000 events with varying azimuth/zenith was again considered.
+The fractional difference $\Delta = \frac{ candidate_{DC count} - True_{DC count}}{True_{DC count}}$ was binned in a histogram format, as shown in \ref{fig:dcdiff}.
+It was observed that the mean was 0.09 and the median was -0.08, meaning the distribution was partially skewed.
+If the absolute deviation from the $True_{DC}$ value is considered, then 68\% of pixels have a fractional deviation less than 0.33.
+Accounting for $\sigma_{STA}$, we find that the $sigma_{LPD}=\sigma_{rgr1}=0.32$, an improvement over the fixed 56Tev directly incident simulation.
+
+For HESS2, the mean was 0.22 while the median was -0.09, leading to an even more skewed distribution.
+However the 68\% absolute fractional deviation was 0.29, and with $sigma_{STA}$, we find that $sigma_{LPD}=\sigma_{rgr2}=0.29$, slightly better than for HESS1.
+The improved performance can be explained by the matching energy distribution for the training and testing datasets.
+Higher-energy events have more background EAS light without consequently increased DC light, meaning the signal becomes harder to extract.
+The testing dataset has predominantly low-energy events, with reduced background.
 
@@
 
+56 and 26 teV comparison. Sigma is a function of E???
+
 \begin{figure}
 \begin{center}
-\includegraphics[width=\textwidth]{DCcounterrorhess1None}
+\includegraphics[width=\textwidth]{DCcounterrorhess1rgr}
 \caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left.

### 2016-05-30 CORSIKA/lpdforfixedenergy.py

@@ -55,7 +55,7 @@ filepath = "/nfs/astrop/d6/rstein/data/"
 
 
 
-j=100
+j=2000
 i=0
 
 distances=[[],[]]
@@ -100,9 +100,7 @@ while (i < j):
 				DCtel = DCsim.images[index]
 				fulltel =  fullsim.images[index]
 				trueID = DCtel.trueDC
-				DCtrue = DCtel.getpixel(trueID)
-				DCcount = DCtrue.channel1.intensity
-				
+
 				if fulltel.BDTID != None:
 					fullBDT = fulltel.getBDTpixel()
 								
@@ -134,7 +132,7 @@ while (i < j):
 								raise Exception("Telescope.size error, size is " +fulltel.size)
 							
 							distances[plotindex].append(fulltel.hillas.core_distance_to_telescope)
-							truesignals[plotindex].append(DCcount)
+							truesignals[plotindex].append(DCtel.hillas.image_size_amplitude_)
 							signals[plotindex].append(simplecandidatesignal)
 							rgrsignals[plotindex].append(candidatesignal)
 
@@ -148,7 +146,7 @@ mpl.use('Agg')
 import matplotlib.pyplot as plt
 
 for i in [0, 1]:
-	print "HESS"+str(i)
+	print "HESS"+str(i+1)
 	figure = plt.gcf() # get current figure
 	figure.set_size_inches(20, 20)
 	

### 2016-05-31 report/draft1.tex
Backup 31/05/16

@@
 \subsection{Determining $True_{DC}$}
-yeah stuff and such....
+Determining the value off $True_{DC}$ is important for
 
@@
 \includegraphics[width=\textwidth]{corsikalpd1}
-\caption{The LPDs are shown above for $True_{DC}$, the simple guess $DC_{Count}$, and the regressor calculated $DC_{rgr}$.
+\caption{The two LPDs shown above are estimates of HESS1 $True_{DC}$ calculated via $I_{tot}$, as well as for the maximum pixel $Intensity$.
+The two full-shower calculated LPDSs are shown underneath, with the simple guess $DC_{Count}$, and the regressor calculated $DC_{rgr}$.
 An exponential is fit to the $True_{DC}$ distribution, and the 68\% fractional deviation is shown in green.
 The same curve is shown on the two derived DC values, with the new fractional deviation being much greater.}
-\label{fig:corsikalpd}
+\label{fig:corsikalpd1}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{corsikalpd2}
+\caption{The two LPDs shown above are estimates of HESS2 $True_{DC}$ calculated via $I_{tot}$, as well as for the maximum pixel $Intensity$.
+The two full-shower calculated LPDSs are shown underneath, with the simple guess $DC_{Count}$, and the regressor calculated $DC_{rgr}$.
+An exponential is fit to the $True_{DC}$ distribution, and the 68\% fractional deviation is shown in green.
+The same curve is shown on the two derived DC values, with the new fractional deviation being much greater.}
+\label{fig:corsikalpd2}
 \end{center}

### 2016-05-31 CORSIKA/combineforregressor.py

@@ -9,7 +9,7 @@ import cPickle as pickle
 from telescopeclasses import *
 
 parser = argparse.ArgumentParser()
-parser.add_argument("-jid", "--jobID", default="6051560")
+parser.add_argument("-jid", "--jobID", default="regressorset")
 
 cfg = parser.parse_args()
 

### 2016-05-31 CORSIKA/fifthtelescopelpd.py

@@ -8,7 +8,7 @@ from telescopeclasses import *
 from matplotlib import rc
 
 parser = argparse.ArgumentParser()
-parser.add_argument("-jid", "--jobID", default="56tev-lpd")
+parser.add_argument("-jid", "--jobID", default="26tev-lpd")
 
 cfg = parser.parse_args()
 
@@ -63,8 +63,7 @@ signals=[[],[]]
 rgrsignals=[[],[]]
 rgrdiffs=[[],[]]
 simplediffs=[[],[]]
-truesignals1=[[],[]]
-truesignals2=[[],[]]
+truesignals=[[],[]]
 
 cut, ucut, QDCcut, DCcut, signalcut = ic.runforstats()
 
@@ -96,18 +95,33 @@ while (i < j):
 		if hasattr(event.simulations, "DC") and hasattr(event.simulations, "full"):
 			DCsim =event.simulations.DC
 			fullsim = event.simulations.full
-
+			
+			IDs=[0,1,2,3,4]
+			
 			for index in DCsim.triggerIDs:
-				DCtel = DCsim.images[index]
 				fulltel =  fullsim.images[index]
-				trueID = DCtel.trueDC
-				DCpixel = DCtel.gettruepixel()
 
 				if fulltel.BDTID != None:
 					fullBDT = fulltel.getBDTpixel()
 								
 					simplecandidatesignal = fullBDT.channel1.intensity -fullBDT.nnmean
-
+					
+					if float(ucut) > float(fullBDT.bdtscore) > float(cut):
+						if float(simplecandidatesignal) > float(signalcut):
+							IDs.remove(index)
+			
+			if len(IDs) == 1:
+				print IDs
+				fulltel =  fullsim.images[IDs[0]]
+				DCtel = DCsim.images[IDs[0]]
+				trueID = DCtel.trueDC
+				
+				if fulltel.BDTID != None:
+			
+					fullBDT = fulltel.getBDTpixel()
+									
+					simplecandidatesignal = fullBDT.channel1.intensity -fullBDT.nnmean
+				
 					bdtentry = makeBDTentry(fullBDT)
 					if (fulltel.size=="HESS1") and (bdtentry != None):
 						candidatesignal = hess1rgr.predict([bdtentry])[0]
@@ -115,29 +129,25 @@ while (i < j):
 						candidatesignal = hess2rgr.predict([bdtentry])[0]
 					elif bdtentry == None:
[…]

### 2016-06-07 report/bdtarticle.tex
Backup 07/06/16

@@
 The corresponding sample purity after cuts was 87.7\%, a slight increase on existing methods.
-When only high multiplicity Boosted Decision Tree events were considered, 11.8\% of all Direct Cherenkov pixels were identified, with a sample purity of 90.9\%, while the existing method was not able to find a single comparable high-multiplicity event.
+When only high multiplicity Boosted Decision Tree events were considered, 11.8\% of all Direct Cherenkov pixels were identified, with a sample purity of 90.9\%.
+The existing method was not able to find a single comparable high-multiplicity event.
 \end{abstract}

### 2016-06-07 report/draft1.tex
Backup 07/06/16

@@
 \begin{figure}
-\newgeometry{a4paper, portrait, margin=1.0in}
+\newgeometry{a4paper, portrait, margin=1.5in}
 \centering
@@
 Similarly the largest neighbouring FADC was found, and the ratio $raw_{Q} = \frac{FADC_{N.N.max}}{FADC}$ was calculated.
-In addition, the Nearest Neighbour Mean Intensity $Mean_{N.N}$ was recorded.
+In addition, the Nearest Neighbour Mean Intensity $Mean_{N.N}$ was recorded, as well as the smallest neighbouring pixel intensity $Intensity_{N.N.min}$.
 The variable $DC_{Signal} = Intensity-Mean_{N.N}$ was defined as an rough guess of the \textquoteleft DC signal' component in the pixel.
@@
 The candidates were checked against the true DC pixels identified in the EAS-free images.
-From the testing sample, 5.2\% of all images were correctly identified and passed the cuts.
-Once misidentified events were considered, the post-cuts sample was 86.2\% accurate, as shown in \ref{fig:cutdistribution}.
+From the testing sample, 1.8\% of all images were correctly identified and passed the cuts.
+Once misidentified events were considered, the post-cuts sample was 89.9\% accurate, as shown in Figure \ref{fig:cutdistribution}.
 These values served as a benchmark for BDT performance.
@@
 Application of this combined cut greatly increases the successful identification rate.
-From the testing sample, 37.3\% of all images were correctly identified and passed the cuts.
-The BDT was found to be 87.7\% accurate in identifying DC pixels which passed the cuts.
+From the testing sample, 15.2\% of all images were correctly identified and passed the cuts.
+The BDT was found to be 90.2\% accurate in identifying DC pixels which passed the cuts.
 This represents a very significant improvement in pixel identification efficiency, as well as a minor increase in accuracy after cuts.
@@
 If we only consider events in which at least four DC pixels were identified, we can determine the high-multiplicity BDT performance.
-In this case, the fraction of correctly identified DC pixels falls to 16.8\%, while the fraction of incorrectly identified pixels passing the cuts falls to 1.8\%.
-The sample purity increases slightly to 90.3\%.
-The relatively high fraction of passing events, in excess of the random expectation of $0.372^{4}=1.9 \%$, suggests that DC pixel identification between different telescope images is strongly correlated.
+In this case, the fraction of correctly identified DC pixels falls to 2.2\%, while the fraction of incorrectly identified pixels passing the cuts falls to 0.2\%.
+The sample purity increases slightly to 91.2\%.
+The relatively high fraction of passing events, in excess of the random expectation of $0.152^{4}=0.05\%$, suggests that DC pixel identification between different telescope images is strongly correlated.
 
-However, out of 1245 triggered events, there were none in which the $Q_{DC}$ method identified four DC pixels.
-Using poissonian statistics, we can place an upper limit of $<0.24 \%$ on the rate of accepted, high-multiplicity $Q_{DC}$ events.
+However, out of 18652 total images, there were none belonging to events in which the $Q_{DC}$ method identified four DC pixels.
+Using poissonian statistics, we can place an upper limit of $<0.02 \%$ on the rate of accepted, high-multiplicity $Q_{DC}$ events.
 Thus, as well as BDT accuracy slightly improving, the performance gap over the $Q_{DC}$ method is vastly increased for high-multiplicity events.
@@
     \midrule
-    Pixels Accepted and Correctly Identified (\%) & 5.2 & 37.2\\
-   Pixels Accepted and Incorrectly Identified (\%) & 0.8 & 5.2\\
-    Sample Purity (\%) & 86.2 & 87.7 \\
+    Pixels Accepted and Correctly Identified (\%)  & 1.8 & 15.2\\
+   Pixels Accepted and Incorrectly Identified (\%)  & 0.2& 1.7\\
+    Sample Purity (\%)  & 89.9& 90.2 \\
     \midrule
-    High Multiplicity Pixels Accepted and Correctly Identified (\%) & $<0.24$ & 16.8\\
-    High Multiplicity Pixels Accepted and Incorrectly Identified (\%) & $<0.24$ & 1.8\\
-    Sample Purity (\%) & / & 90.3\\
+    High Multiplicity Pixels Accepted and Correctly Identified (\%) & $<0.02$ & 2.2\\
+    High Multiplicity Pixels Accepted and Incorrectly Identified (\%) & $<0.02$ & 0.2\\
+    Sample Purity (\%) & / & 91.2\\
     \bottomrule
@@
 Although the cuts in \ref{tab:qdccuts} were not optimised for the differing pixel size and angular viewing region of CT5, they were replicated to provide a basis for comparison.
-Based on CT5 images from the training sample, an increased 5.7\% of DC pixels were correctly identified and passed the required cut.
-A further 10 \% of all pixels passed the cuts, despite being misidentified.
-This represented a very heavy decrease in sample purity to just 38\%.
+Based on CT5 images from the training sample, an increased 5.6\% of DC pixels were correctly identified and passed the required cut.
+A further 11.3 \% of all pixels passed the cuts, despite being misidentified.
+This represented a very heavy decrease in sample purity to just 33.0\%.
 We can assume that better optimised CT5 cuts could remove many of these misidentified events, though it is unlikely that any significant improvement in the number of correctly identified DC pixels would be possible.
 Thus, the number of DC pixels successfully identified using the $Q_{DC}$ method is still a valid benchmark for comparative BDT performance.
-A true accuracy rate closer to the HESS 1 rate of 86\% could be expected.
+A true accuracy rate closer to the HESS 1 rate of 90\% could be expected.
 
-Due to the distinctiveness of the CT5 telescope, direct application of the HESS1 classifier to the CT5 telescope yields poorer BDT performance, with just 14.8 \% of correctly identified events passing the cut and an accuracy of 71.7\%.
+Due to the distinctiveness of the CT5 telescope, direct application of the HESS1 classifier to the CT5 telescope yields poorer BDT performance, \textbf{with just 14.8 \% of correctly identified events passing the cut and an accuracy of 71.7\%}.
 To improve CT5 pixel identification, a separate HESS2 BDT was instead trained with the same variables as above.
@@
 
-The CT5 performance was improved for the new classifier, with 24.0 \% of pixels being correctly identified and accepted, and an accuracy of 79.4\%.
+The CT5 performance was improved for the new classifier, with 17.9 \% of pixels being correctly identified and accepted, and an accuracy of 66.1\%.
 Despite this improvement, a clear gap emerged between the between the performance of HESS1 classifier on old telescopes, and the performance of the HESS2 classifier on CT5.
@@
 In the case of the high-multiplicity events, the gap narrows somewhat.
-In total 9.4\% of pixels are correctly identified and accepted, although the accuracy rate is only increased to 81.0\%.
-As stated before, no $Q_{DC}$ event had four or more DC pixels identified, and thus the only conclusion to be drawn on the $Q_{DC} method$ is to place an upper limit of the event rate.
+In total 1.9\% of pixels are correctly identified and accepted, although the accuracy rate is only increased to 80.7\%.
+As before, non-observation of a qualifying high-multiplicity $Q_{DC}$ event allows us to calculate a Poissonian upper limit.
+Out of 4663 HESS2 images, there were none belonging to events in which the $Q_{DC}$ method identified four DC pixels, limiting the rate to $<0.06\%$.
 
@@
     \midrule
-    Pixels Accepted and Correctly Identified (\%) & 5.7 & 24.8\\
-   Pixels Accepted and Incorrectly Identified (\%) & 10.6 & 6.4\\
-    Sample Purity (\%) & 34.8 & 79.4 \\
+    Pixels Accepted and Correctly Identified (\%) & 5.6 & 17.9 \\
+   Pixels Accepted and Incorrectly Identified (\%) & 11.3 & 9.2 \\
+    Sample Purity (\%) & 33.0 & 66.1 \\
     \midrule
-    High Multiplicity Pixels Accepted and Correctly Identified (\%) & $<0.24$ & 9.4\\
-    High Multiplicity Pixels Accepted and Incorrectly Identified (\%) & $<0.24$ & 2.2\\
-    Sample Purity (\%) & / & 81.0\\
+    High Multiplicity Pixels Accepted and Correctly Identified (\%) & $<0.06$ & 1.9\\
+    High Multiplicity Pixels Accepted and Incorrectly Identified (\%) & $<0.06$ & 0.5\\
+    Sample Purity (\%) & / & 80.7\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\subsection{Proton Background}
+It is important to discriminate between the heavy cosmic ray elements, such as iron, and the much more abundant proton events.
+Protons tend to emit negligible DC light, so will contaminate any data sample with events that cannot be reconstructed using the LPD method.
+To determine the acceptance rate for proton events, a simulation was conducted with 2000 proton events in CORSIKA.
+For HESS1, the raw acceptance rate was 15.1\% while the sample purity of 32.2\%.
+For HESS2, the raw acceptance rate was 58.6\% while the sample purity of 6.8\%.
+Although the HESS1 acceptance rate is relatively small, the proton flux is approximately ten times greater than iron flux.
+A mixed sample would have many more proton images than iron images.
+Once multiplicity cuts are applied, the acceptance rate falls steeply to just 2.9\%.
+With the factor 10 discrepancy in flux, the number of proton and iron images will be comparable.
+Of those passing the cuts, 24.5\% are correctly identified.
+For HESS2, the comparable number is 21.7\% with multiplicity cuts.
+The sample purities are just 24.4\% and 7.7\% respectively.
+This poor performance motivates our desire to remove protons from our sample for analysis.
+
+We require an additional cut to remove the majority of these proton events.
+If we can eliminate one or two accepted proton images per event, then the remaining proton pixels will all be rejected by the multiplicity cuts.
+Hence, loose cuts can sharply reduce the acceptance rate of protons.
+In this case, as shown in Figure \ref{fig:aspectratio}, there is a fair degree of separation between proton and Iron Aspect Ratio for pixels which pass all cuts.
+We aim to remove proton pixels but not iron pixels.
+Applying a cut requiring Aspect Ratio $> 0.35$ eliminated all accepted proton events for HESS1 and HESS2.
+With 17792 total HESS1 images, just 6195 images were triggered by DC light.
+Of all 17792 images, there were none passing all of the required cuts.
+We can place a poissonian upper limit on the acceptance rate of $< 0.02 \%$.
+Of the for 4448 HESS2 images, just 2169 contained DC light.
+As no image passed all cuts, we place an upper limit of $< 0.07\%$.
+For HESS1 iron events, the total acceptance rate falls slightly from 2.4\% to 2.3\%, while the sample purity decreases slightly to 89.0\%.
+For HESS2, the total acceptance rate falls slightly from 2.4\% to 2.3 \%, while the sample purity decreases slightly to 79.8\%.
+Iron images form at least 90\% of a sample, because most proton images are at least one hundred times less likely to be accepted.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{aspectratio}
+\caption{The aspect ratio of images in events which pass the multiplicity cut are shown.
+It is clear that the proton events have a strong tendency towards lower Aspect Ratios.
+We must remove the white proton pixels passing all other cuts, without removing dark green iron pixels passing all other cuts.
+A cut requiring Aspect Ratio $> 0.35$ should remove a large proportion of proton images without reducing the pass rate for iron nucleii.}
+\label{fig:aspectratio}
+\end{center}
+\end{figure}
+
+\begin{table}[h!]
+  \centering
+  \caption{Comparison of Proton and Iron Acceptance}
+  \label{tab:protonacceptance}
+  \begin{tabular}{ccc}
+    \toprule
+    & HESS1  & HESS2 \\
+    \midrule
+    Proton Pixels Accepted (\%) & 15.1 & 58.6\\
+    Sample Purity (\%) & 32.2 & 6.8 \\
+    \midrule
+    High Multiplicity Proton Pixels Accepted (\%) & 2.9 & 21.7\\
+    Sample Purity (\%) & 24.5 & 7.7 \\
+    \midrule
+    Proton Pixels Accepted after All Cuts(\%) & $< 0.02$ & $< 0.07$\\
+    Sample Purity (\%) & / & / \\
+    \midrule
+    Iron Pixels Accepted after All Cuts(\%) & 2.3 & 2.3\\
+    Sample Purity (\%) & 89.0 & 79.8 \\
     \bottomrule
@@
 \subsection{Determining $True_{DC}$}
-Determining the value off $True_{DC}$ is important for
+Determining the value off $True_{DC}$ is important for determining the error in our LPD measurements.
+However, there are two natural ways of quantifying $True_{DC}$.
+In the basic case, we can simply consider the EAS-free intensity $Intensity_{max}$ in the DC pixel.
+An alternative is to take the entire EAS-free image amplitude $I_{tot}$ as our $True_{DC}$ value.
+The use of Image Amplitude accounts for the fact that the DC light is almost always split between two or more pixels.
+Although in most cases, one pixel has the majority of the light, in extreme cases the light can be evenly split between two.
+As a result of the smaller angular region covered by each CT5 pixel, this happens much more frequently for HESS2 than for HESS1.
+A countervailing argument is the susceptibility of the Image Amplitude measurement to edge effects.
+A DC pixel lying near the image edge will be unaffected by this fact, but the total image amplitude may decline because dimmer pixels move over the image edge.
 
-\textbf{Let's define $Intensity_{N.N.max}$!}
+To quantitatively compare the two methods, we can measure the error associated with both values of $True_{DC}$.
+A study of 2000 events was conducted, in which each cosmic ray was simulation without night sky background or EAS background.
+Each telescope image simulation was conducted twice, and difference between $I_{1}$ and $I_{2}$ was plotted as in \ref{fig:simtelerror}.
+The fractional difference from the mean Intensity of an image was defined as $\Delta = 2 \times \frac{I_{2} - I_{1}}{{I_{2} + I_{1}}}$.
+
+For $I_{tot}$, it was found that the standard deviation in fractional difference was $\sigma_{Itot}=0.06$, meaning that there is an inherent error of 6 \% in measurements of $True_{DC}$.
+In later calculations of the error in Intensity, this fractional error can be subtracted in quadrature.
+The distribution did not vary between HESS1 and HESS2 telescopes.
+For the alternative $Intensity_{max}$ measurement, the standard deviation was $\sigma_{Imax}=0.09$ for HESS1 and $\sigma_{Imax}=0.12$, a clear increase.
+This implies that the $I_{tot}$ measurements are more reliable.
+
+For an alternative measurement of error in the LPD, a simulation of 2000 events was conducted with a fixed energy of 56TeV, and both Zenith and azimuth fixed to 0 degrees.
+The interaction height was fixed at 23km above sea level.
+The true distance to core was recorded from Sim\textunderscore telarray, and a graph was plotted of DC pixel intensity against core distance.
+As expected, a characteristic LPD is observed, as seen in Figure \ref{fig:corsikalpd1}.
+Due to the application of a signal cut to the BDT candidates, we are only able to see the LPD at around $r_{core} \textgreater 35m$, at which point the LPD intensity crosses the threshold of 150 p.e.
+From here, there is a clear LPD continuing up to around 100m.
+Above roughly 100m, the LPD becomes dominated by highly random hadron fragmentation, and thus ceases to be coherent.
+
+The region 35-90m is considered, and if an exponential if fitted to the LPD, then the fractional deviation $\Delta_{TrueDC} = \frac{signal_{fit} - True_{DC count}}{signal_{fit}}$ can be found.
+Using the 68th centile of all absolute fractional deviations $\Delta_{TrueDC}$, we find that the HESS LPD for $I_{tot}$ has an error of $\sigma_{Itot}=0.12$.
+Repeating for $Intensity_{max}$ calculated values, the resultant LPD had an error of $\sigma_{Imax} = 0.24$.
+Again, it is clear that the $I_{tot}$ value has a smaller associated error than $Intensity_{max}$.
+
+It is interesting to note that the values of $I_{max}$ and $DC_{count}$ are strongly correlated with one another.
+The mean fractional deviation between $I_{max}$ and $DC_{count}$ is relatively small, at 0.34.
+In the LPD plot, it becomes clear that the $I_{max}$ value, and thus the $DC_{count}$ value, consistently underestimates the quantity of DC light in an image.
+This is not surprising, and indicates the degree to which DC light is often split between multiple pixels.
+As this effect is clearly not negligible, we choose to define $True_{DC}=I_{tot}$ for the rest of this analysis.
 
@@
 
-To assess the error in the LPD, a simulation of 2000 events was conducted with a fixed energy of 56TeV, and both Zenith and azimuth fixed to 0 degrees.
-The true distance to core was recorded from Sim\textunderscore telarray, and a graph was plotted of DC pixel intensity against core distance.
-As expected, a characteristic LPD is observed.
-Due to the application of a signal cut to the BDT candidates, we are only able to see the LPD at around $r_{core} \textgreater 35m$, at which point the LPD intensity crosses the threshold of 150 p.e.
-From here, there is a clear LPD continuing up to around 100m.
-Above roughly 100m, the LPD becomes dominated by highly random hadron fragmentation, and thus ceases to be coherent.
-The region 35-90m is considered, and if an exponential if fitted to the LPD, then the fractional deviation $\Delta_{TrueDC} = \frac{signal_{fit} - True_{DC count}}{signal_{fit}}$ can be found.
-Using the 68th centile of all absolute fractional deviations $\Delta_{TrueDC}$, we find that the LPD for $True_{DC}$ has an error of $\sigma_{TrueDC}=0.12$.
+STUFF!
+
 Taking account of $\sigma_{STA}$, we deduce that the true associated error in the LPD is $\sigma_{TrueLPD} = \sqrt{(\sigma_{TrueDC}^{2} - \sigma_{STA}^{2})} = 0.11$.
@@
 \includegraphics[width=\textwidth]{corsikalpd2}
-\caption{The two LPDs shown above are estimates of HESS2 $True_{DC}$ calculated via $I_{tot}$, as well as for the maximum pixel $Intensity$.
-The two full-shower calculated LPDSs are shown underneath, with the simple guess $DC_{Count}$, and the regressor calculated $DC_{rgr}$.
-An exponential is fit to the $True_{DC}$ distribution, and the 68\% fractional deviation is shown in green.
-The same curve is shown on the two derived DC values, with the new fractional deviation being much greater.}
+\caption{The same curves in Figure \ref{fig:corsikalpd1} are shown here for HESS2.
+Because the CT5 telescope has an area approximately six times larger than the HESS1 telescopes, the LPD is linearly scaled here by a factor of six compared to the HESS1 LPD.
+It is clear that all other methods of calculating the LPD underestimate the value of $True_{DC}$, as seen in the top plot.}
 \label{fig:corsikalpd2}
@@
 In order to reduce the LPD error, an alternative method of calculating the DC signal was developed.
-Supervised machine learning was again used to solve the problem, by training a BDT Regressor.
+Supervised machine learning was again used to solve the problem, through training of a BDT Regressor.
 As with Classifiers, Regressors are initially trained using individual data entries.
 Instead of the true classes for the entries, regressors require the true value of a continuous variable.
-Once trained, the regressor can be used to predict a value of the variable for a given data entry.
+Once trained, the Regressor can be used to predict a value of the variable for a given data entry.
 In this case, the Regressor is trained to estimate the quantity of DC light $True_{DC}$ for a given pixel.
-Once a DC pixel has been identified, the regressor is applied to it.
-The regressor returns the calculated value of $DC_{rgr}$, an alternative estimate of the DC signal.
+Once a DC pixel has been identified, the Regressor is applied to it.
+The Regressor returns the calculated value of $DC_{rgr}$, an alternative estimate of the DC signal.
 
@@
 Repeating the comparison for the HESS1 regressor, we find for $\sigma_{rgrfit} = 0.35$, a significant improvement over $\sigma_{DCcount}$.
-Taking into account $\sigma_{STA}$, we find that ultimately $\sigma_{rgr}=0.34$, a fairly large value that nonetheless should be acceptable in 4-telescope events.
+Taking into account $\sigma_{STA}$, we find that ultimately $\sigma_{rgr1}=0.34$, a fairly large value that nonetheless should be acceptable in 4-telescope events.
 The comparative performance is recorded in Table \ref{tab:lpderror}.
+Instead of rejecting DC pixels which do not meet out $DC_{count}$ and $P_{signal}$ cuts, we can separately measure their deviation from the LPD.
+In this way, we can include the information from these DC pixels in later analysis, while accounting for the larger uncertainty in their LPD measurements.
+For images which do pass only the multiplicity cuts, but not the $P_{signal}$ or $DC_{count}$ cuts, we find that the regressor error is $\sigma_{rejected1}=0.32$.
 
@@
   \centering
-  \caption{Fractional error from fitted 56-TeV LPD distribution, accounting for $\sigma_{STA}$}
+  \caption{Fractional error from fitted 56-TeV LPD distribution up to $r_{core}=90$, accounting for $\sigma_{STA}$}
   \label{tab:lpderror}
@@
     \midrule
-    $\sigma_{TrueDC}$ & 0.13 & 0.18\\
-    $\sigma_{DCcount}$ & 0.70 & 0.88\\
-    $\sigma_{rgr}$ & 0.36 & 0.50\\ 
+    $\sigma_{TrueDC}$ & 0.13 & 0.29\\
+    $\sigma_{DCcount}$ & 0.69 & 0.91\\
+    $\sigma_{rgr}$ & 0.27 & 0.53\\ 
+    $\sigma_{rejected}$ & 0.32 & 0.43\\ 
     \bottomrule
@@
 To get a more accurate estimate of the error, the testing set of 2000 events with varying azimuth/zenith was again considered.
-The fractional difference $\Delta = \frac{ candidate_{DC count} - True_{DC count}}{True_{DC count}}$ was binned in a histogram format, as shown in \ref{fig:dcdiff}.
+The fractional difference \[  \Delta = \frac{ candidate_{DC count} - True_{DC count}}{True_{DC count}} \] was binned in a histogram format, as shown in Figure \ref{fig:dcdiff}.
 It was observed that the mean was 0.09 and the median was -0.08, meaning the distribution was partially skewed.
@@
 Accounting for $\sigma_{STA}$, we find that the $sigma_{LPD}=\sigma_{rgr1}=0.32$, an improvement over the fixed 56Tev directly incident simulation.
+For the high-multiplicity rejected events, we find the regressor has an error of $\sigma_{rejected1}=0.41$.
 
@@
 The testing dataset has predominantly low-energy events, with reduced background.
+For the rejected events, we find that $\sigma_{rejected2}=0.63$, with $\sigma_{STA}$ being negligible.
+
+\begin{table}[h!]
+  \centering
+  \caption{Fractional error from $True_{DC}$ for all high-multiplicity test pixels}
+  \label{tab:altlpderror}
+  \begin{tabular}{ccc}
+    \toprule
+    & HESS1 & HESS2\\
+    \midrule
+    $\sigma_{rgr}$ & 0.32 & 0.29\\ 
+    $\sigma_{rejected}$ & 0.41 & 0.63\\ 
+    \bottomrule
+  \end{tabular}
+\end{table}
 

### 2016-06-07 CORSIKA/combineforBDT.py

@@ -18,14 +18,14 @@ def isfloat(value):
 		return False
 
 parser = argparse.ArgumentParser()
-parser.add_argument("-jid", "--jobID", default="2842781")
+parser.add_argument("-jid", "--jobID", default="traindata")
 
 cfg = parser.parse_args()
 
 filepath = "/nfs/astrop/d6/rstein/data/"
 
 i = 1
-j = 2000
+j = 5000
 
 targetfolder = filepath + cfg.jobID +"/"
 

### 2016-06-07 CORSIKA/combineforstatistics.py

@@ -8,7 +8,7 @@ from telescopeclasses import *
 from matplotlib import rc
 
 parser = argparse.ArgumentParser()
-parser.add_argument("-jid", "--jobID", default="2567181")
+parser.add_argument("-jid", "--jobID", default="testdata")
 
 cfg = parser.parse_args()
 
@@ -53,8 +53,9 @@ def makeBDTentry(pixelentry):
 for sigfit in ["rgr", None]:
 	filepath = "/nfs/astrop/d6/rstein/data/"
 	i = 1
-	j = 2000
+	j = 5000
 	totalimages = [0, 0]
+	triggeredimages = [0, 0]
 	DCpasstotal = [0, 0]
 	correctimages =[0, 0]
 	totalcut=[0, 0]
@@ -76,11 +77,15 @@ for sigfit in ["rgr", None]:
 	fulltotal = [0, 0]
 	fullcorrect = [0, 0]
 	
+	finaltotal = [0, 0]
+	finalcorrect = [0, 0]
+		
 	oldcombinedtotal = [0, 0]
 	oldcombinedcorrect = [0, 0]
 	
 	
 	cut, ucut, QDCcut, DCcut, signalcut = ic.runforstats()
+	arcut = ic.runar()
 	
 	right = [[], []]
 	wrong = [[], []]
@@ -107,8 +112,6 @@ for sigfit in ["rgr", None]:
 	rejectedcsignals = [[[], []], [[], []]]
 	rejectedDCsignals =[[[], []], [[], []]]
 	
-	mpass=0
-	lpass=0
 	mtotal=0
 	
 	
@@ -142,147 +145,150 @@ for sigfit in ["rgr", None]:
 				fullsim = event.simulations.full
 				
 				k=0
+				kar=0
 				l=0
 				
-				for index in DCsim.triggerIDs:
-					fulltel =  fullsim.images[index]
-					
+				for fulltel in fullsim.images:
 					if fulltel.BDTID != None:
 						fullBDT = fulltel.getBDTpixel()
 						candidatesignal = fullBDT.channel1.intensity - fullBDT.nnmean
 						if float(ucut) > float(fullBDT.bdtscore) > float(cut):
 								if float(candidatesignal) > float(signalcut):
 									k+=1
+									if float(fulltel.hillas.aspect_ratio_) > arcut:
+										kar +=1
 					
 					if fulltel.QDCID != None:
 						l+=1
-						
-				if l > minmultiplicity:
-					lpass += 1
[…]

### 2016-06-07 CORSIKA/corsikatocluster.sh

@@ -94,7 +94,7 @@ echo "MAX_PRINT_ARRAY set to 2100"
 
 mkdir -p /nfs/astrop/d6/rstein/data/$JOB_ID
 
-for (( i=0; i <= 3; i++ ))
+for (( i=0; i <= 9; i++ ))
 do 
  python /nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/CORSIKA/runcorsika.py -rn $((($i*500) + $SGE_TASK_ID)) -td $TMPDIR -jid $JOB_ID
 

### 2016-06-07 CORSIKA/lpdforfixedenergy.py

@@ -6,9 +6,13 @@ import numpy as np
 import cPickle as pickle
 from telescopeclasses import *
 from matplotlib import rc
+from scipy.optimize import curve_fit
 
 parser = argparse.ArgumentParser()
 parser.add_argument("-jid", "--jobID", default="56tev-lpd")
+
+sys.path.append('/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/positioning/')
+import cherenkovradius as cr
 
 cfg = parser.parse_args()
 
@@ -53,20 +57,22 @@ def makeBDTentry(pixelentry):
 
 filepath = "/nfs/astrop/d6/rstein/data/"
 
-
-
-j=200
+j=100
 i=0
 
-distances=[[],[]]
+accepteddistances=[[],[]]
 signals=[[],[]]
 rgrsignals=[[],[]]
 rgrdiffs=[[],[]]
 simplediffs=[[],[]]
 truesignals1=[[],[]]
 truesignals2=[[],[]]
+truedistances=[[],[]]
+rejecteddistances=[[],[]]
+rejectedrgrsignals=[[],[]]
 
 cut, ucut, QDCcut, DCcut, signalcut = ic.runforstats()
+arcut = ic.runar()
 
 targetfolder = filepath + cfg.jobID +"/"
 
@@ -96,48 +102,62 @@ while (i < j):
 		if hasattr(event.simulations, "DC") and hasattr(event.simulations, "full"):
 			DCsim =event.simulations.DC
 			fullsim = event.simulations.full
-
+			
+			IDs=[]
+			
 			for index in DCsim.triggerIDs:
-				DCtel = DCsim.images[index]
 				fulltel =  fullsim.images[index]
-				trueID = DCtel.trueDC
-				DCpixel = DCtel.gettruepixel()
 
 				if fulltel.BDTID != None:
 					fullBDT = fulltel.getBDTpixel()
 								
 					simplecandidatesignal = fullBDT.channel1.intensity -fullBDT.nnmean
-
-					bdtentry = makeBDTentry(fullBDT)
-					if (fulltel.size=="HESS1") and (bdtentry != None):
-						candidatesignal = hess1rgr.predict([bdtentry])[0]
-					elif (fulltel.size=="HESS2") and (bdtentry != None):
-						candidatesignal = hess2rgr.predict([bdtentry])[0]
-					elif bdtentry == None:
-						candidatesignal = 0
-						
+					
[…]

### 2016-06-07 CORSIKA/runBDT.py

@@ -2,8 +2,8 @@ import os, argparse, subprocess, time
 import os.path
 
 parser = argparse.ArgumentParser()
-parser.add_argument("-bid", "--BDTID", default="2842781")
-parser.add_argument("-tid", "--testID", default="2567181")
+parser.add_argument("-bid", "--BDTID", default="traindata")
+parser.add_argument("-tid", "--testID", default="testdata")
 parser.add_argument("-t", "--train", action="store_true")
 parser.add_argument("-tr", "--trainregressor", action="store_true")
 parser.add_argument("-re", "--reextract", action="store_true")

### 2016-06-07 CORSIKA/runcorsika.py

@@ -66,7 +66,7 @@ for cardname in cards:
 	f_out.write("TELFIL " + iact_name + ":100:100:1              Telescope photon bunch output (eventio format)  \n")
 
 	if cardname == "DC":
-		f_out.write("ECUTS 0.3 1E7 1E7 0.003 \n")
+		f_out.write("ECUTS 400 1E7 1E7 0.003 \n")
 		
 	elif cardname == "full":
 		f_out.write("ECUTS 0.3 0.3 0.003 0.003 \n")

### 2016-06-07 CORSIKA/simtelerror.py

@@ -55,6 +55,8 @@ while (i < j):
 					if hasattr(DCtel.hillas, "image_size_amplitude_") and hasattr(fulltel.hillas, "image_size_amplitude_"):
 						DCcount = DCtel.hillas.image_size_amplitude_
 						candidatesignal = fulltel.hillas.image_size_amplitude_
+						DCcount = DCtel.hillas.image_size_amplitude_
+						candidatesignal = fulltel.hillas.image_size_amplitude_
 						
 						if fulltel.size == "HESS1":
 							plotindex = 0

### 2016-06-07 CORSIKA/telescopeclasses.py

@@ -269,11 +269,13 @@ class telescopeimage:
 			self.angularwidth=1.675
 			self.imagewidth=105
 			self.plotscale =180
+			self.mirrorarea=614
 		elif self.size == "HESS1":
 			self.pixelfile = "hess1pixels.csv"
 			self.angularwidth=2.85
 			self.imagewidth=70
 			self.plotscale =100
+			self.mirrorarea=108
 		else:
 			raise NameError(self.size)
 		
@@ -562,7 +564,28 @@ class telescopeimage:
 		This is the 'BDT candidate pixel'.
 		"""
 		if self.BDTID != None:
-			return self.getpixel(self.BDTID)
+			pixelentry = self.getpixel(self.BDTID)
+			#~ bdtentry=[]
+			#~ for variable in bdtvariables:
+				#~ varsplit = variable.split('.')
+				#~ suffix = pixelentry
+				#~ if len(varsplit) > 1:
+					#~ for name in varsplit[:-1]:
+						 #~ suffix = getattr(suffix, name)
+					#~ varname = varsplit[-1]
+				#~ else:
+					#~ varname = variable
+				#~ if hasattr(suffix, varname):
+					#~ newval = getattr(suffix, varname)
+					#~ if newval != None:
+						#~ bdtentry.append(newval)
+					#~ else:
+						#~ include=False
+				#~ else:
+					#~ raise Exception("No variable named " +variable)
+			#~ print bdtvariables
+			#~ print bdtentry
+			return pixelentry
 		else:
 			raise Exception("No BDT pixel!")
 		

### 2016-06-10 report/draft1.tex
Backup 10/06/16

@@
 The full simulation of air showers was performed using the CORSIKA package, with a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
-In total, 2000 training events and a further 2000 testing events were simulated.
+In total, 5000 training events and a further 10000 testing events were simulated.
 The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi(E) \propto E^{-2.7}$.
@@
 The length of each cross arm was $85m$.
-The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis.
-
-\textbf{Due to hardware differences between CT5 and the original HESS 1 telescopes, only images from HESS-phase-1 were considered.}
-
+The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis.Due to hardware differences between CT5 and the original HESS 1 telescopes, we analyse HESS1 and HESS2 images separately.
 To determine the true class of each pixel, a simulation was initially run with an energy cut of 10 PeV on all muons and electrons.
@@
 
-\subsection{Classic DC Pixel Identification}
-As a basis for comparison, the original HESS cuts listed in \ref{tab:table1} were replicated for the set of test data.
-For every image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a dynamic cut, $Q_{DC} < 0.14 \times \log(\frac{I_{tot}}{161 \times \cos \theta})$.
+\subsection{Classic HESS1 DC Pixel Identification}
+As a basis for comparison, the original HESS cuts listed in Table \ref{tab:table1} were replicated for the set of test data.
+For every HESS1 image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a dynamic cut, $Q_{DC} < 0.14 \times \log(\frac{I_{tot}}{161 \times \cos \theta})$.
 Among those pixels passing all cuts, the one with the smallest $Q_{DC}$ was selected as the DC pixel candidate for the image.
@@
 The candidates were checked against the true DC pixels identified in the EAS-free images.
-From the testing sample, 1.8\% of all images were correctly identified and passed the cuts.
-Once misidentified events were considered, the post-cuts sample was 89.9\% accurate, as shown in Figure \ref{fig:cutdistribution}.
-These values served as a benchmark for BDT performance.
+From the testing sample, 1.81\% of all HESS1 images were correctly identified and passed the cuts.
+Once misidentified events were considered, the post-cuts sample was 77.8\% accurate, as shown in Figure \ref{fig:cutdistribution}.
+These values will serve as a useful benchmark for BDT performance.
+Increasing the acceptance rate will be essential for enabling spectroscopic analysis of cosmic rays, by providing more events to analyse.
 
@@
 Within the learning subset, every HESS 1 image was used, provided it was triggered in both EAS-free and full-shower simulations.
-For each of the 4.7 million triggered image pixels, an entry was formed with the variables listed in table \ref{tab:hess1classifier}.
+For each of the triggered image pixels, an entry was formed with the variables listed in table \ref{tab:hess1classifier}.
 A class of 0 was assigned to every non-DC pixel, and a class of 1 was assigned to every DC pixel.
@@
     \midrule
-    $DC_{Count}$ & 0.34\\
-    $Mean_{N.N}$ & 0.26\\
-    $\Delta_{Direction}$ & 0.11\\
-    Image Amplitude & 0.10\\
-    $Q_{DC}$ & 0.10\\
+    $DC_{Count}$ & 0.33\\
+    $Mean_{N.N}$ & 0.24\\
+    $Q_{DC}$ & 0.14\\
+    $\Delta_{Direction}$ & 0.12\\
+    Image Amplitude & 0.07\\
     $raw_{Q}$ & 0.05\\
@@
 The variable $DC_{Count}$ was consistently the most importance variable across many combinations of included variables and BDT training parameters.
-It was found that, under the conditions listed above, the BDT was 99.94 \% accurate for the learning pixel subset, and 99.93 \%  accurate for the overtraining-check pixel subset.
+It was found that, under the conditions listed above, the BDT was 99.94 \% accurate for the learning pixel subset, and 99.94 \%  accurate for the overtraining-check pixel subset.
 This indicates that the BDT was not significantly overtrained, which would otherwise be manifested by a large divergence in accuracy between learning and overtraining-check data.
@@
 Application of this combined cut greatly increases the successful identification rate.
-From the testing sample, 15.2\% of all images were correctly identified and passed the cuts.
-The BDT was found to be 90.2\% accurate in identifying DC pixels which passed the cuts.
+From the testing sample, 16.01\% of all images were correctly identified and passed the cuts.
+The BDT was found to be 79.2\% accurate in identifying DC pixels which passed the cuts.
 This represents a very significant improvement in pixel identification efficiency, as well as a minor increase in accuracy after cuts.
 
-For LPD event reconstruction, we require events to have a telescope multiplicity $>3$.
-If we only consider events in which at least four DC pixels were identified, we can determine the high-multiplicity BDT performance.
-In this case, the fraction of correctly identified DC pixels falls to 2.2\%, while the fraction of incorrectly identified pixels passing the cuts falls to 0.2\%.
-The sample purity increases slightly to 91.2\%.
-The relatively high fraction of passing events, in excess of the random expectation of $0.152^{4}=0.05\%$, suggests that DC pixel identification between different telescope images is strongly correlated.
-
-However, out of 18652 total images, there were none belonging to events in which the $Q_{DC}$ method identified four DC pixels.
-Using poissonian statistics, we can place an upper limit of $<0.02 \%$ on the rate of accepted, high-multiplicity $Q_{DC}$ events.
-Thus, as well as BDT accuracy slightly improving, the performance gap over the $Q_{DC}$ method is vastly increased for high-multiplicity events.
 The results are summarised in Table \ref{tab:qdcbdtcomparison1}.
-The BDT method represents a very significant improvement in DC pixel identification over the previous $Q_{DC}$ method, and corresponds to at least a fifty-fold increase in the number of HESS data events that can be studied using the LPD method.
-Use of this BDT method is thus assumed throughout the rest of this analysis.
+The BDT method represents a clear improvement in DC pixel identification over the previous $Q_{DC}$ method, and corresponds to a fifteen-fold increase in identified pixels.
 
@@
     \midrule
-    Pixels Accepted and Correctly Identified (\%)  & 1.8 & 15.2\\
-   Pixels Accepted and Incorrectly Identified (\%)  & 0.2& 1.7\\
-    Sample Purity (\%)  & 89.9& 90.2 \\
-    \midrule
-    High Multiplicity Pixels Accepted and Correctly Identified (\%) & $<0.02$ & 2.2\\
-    High Multiplicity Pixels Accepted and Incorrectly Identified (\%) & $<0.02$ & 0.2\\
-    Sample Purity (\%) & / & 91.2\\
+    Pixels Accepted and Correctly Identified (\%)  & 1.81 & 16.01\\
+   Pixels Accepted and Incorrectly Identified (\%)  & 0.52& 4.22\\
+    Sample Purity (\%)  & 77.8 & 79.2 \\
     \bottomrule
@@
 A true accuracy rate closer to the HESS 1 rate of 90\% could be expected.
-
-Due to the distinctiveness of the CT5 telescope, direct application of the HESS1 classifier to the CT5 telescope yields poorer BDT performance, \textbf{with just 14.8 \% of correctly identified events passing the cut and an accuracy of 71.7\%}.
+Due to the distinctiveness of the CT5 telescope, direct application of the HESS1 classifier to the CT5 telescope yields poorer BDT performance.
 To improve CT5 pixel identification, a separate HESS2 BDT was instead trained with the same variables as above.
@@
     \midrule
-    $DC_{Count}$ & 0.27\\
-    $Mean_{N.N}$ & 0.14\\
-    $Q_{DC}$ & 0.12\\
-    $\Delta_{Direction}$ & 0.12\\
-    $\Delta_{Line}$ & 0.10\\
-    Image Amplitude & 0.09\\
-    $raw_{Q}$ & 0.07\\
+    $DC_{Count}$ & 0.32\\
+    $Mean_{N.N}$ & 0.24\\
+    $raw_{Q}$ & 0.09\\
+    $Q_{DC}$ & 0.08\\
+    $\Delta_{Direction}$ & 0.8\\
+    Image Amplitude & 0.07\\
     $Intensity$ & 0.06\\
+    $\Delta_{Line}$ & 0.04\\
     \bottomrule
@@
 
-The CT5 performance was improved for the new classifier, with 17.9 \% of pixels being correctly identified and accepted, and an accuracy of 66.1\%.
+For the training events, the classifier was 99.97\% accurate, while for the overtraining check data, it was 99.96\% accurate.
+The classifier was thus not significantly overtrained.
+Applying the new classifier lede to an improvement in CT5 classification, with 17.9 \% of pixels being correctly identified and accepted, and an accuracy of 66.1\%.
 Despite this improvement, a clear gap emerged between the between the performance of HESS1 classifier on old telescopes, and the performance of the HESS2 classifier on CT5.
@@
 The HESS2 classifier was thus trained on significantly fewer DC pixels, so we would expect to see the clear performance gap in comparison to the HESS1 classifier.
-In the case of the high-multiplicity events, the gap narrows somewhat.
-In total 1.9\% of pixels are correctly identified and accepted, although the accuracy rate is only increased to 80.7\%.
-As before, non-observation of a qualifying high-multiplicity $Q_{DC}$ event allows us to calculate a Poissonian upper limit.
-Out of 4663 HESS2 images, there were none belonging to events in which the $Q_{DC}$ method identified four DC pixels, limiting the rate to $<0.06\%$.
 
@@
     \midrule
-    Pixels Accepted and Correctly Identified (\%) & 5.6 & 17.9 \\
-   Pixels Accepted and Incorrectly Identified (\%) & 11.3 & 9.2 \\
-    Sample Purity (\%) & 33.0 & 66.1 \\
+    Pixels Accepted and Correctly Identified (\%) & 5.59 & 18.52 \\
+   Pixels Accepted and Incorrectly Identified (\%) & 14.75 & 4.44 \\
+    Sample Purity (\%) & 27.5 & 80.6 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\subsection{High Multiplicity Events}
+For LPD event reconstruction, we require at least four measurements of the DC light.
+We define the telescope multiplicity of an event as the number of DC pixels which are identified and pass all cuts.
+Telescope multiplicity measures both HESS1 and HESS2 pixels.
+A \textquoteleft high-multiplicity event' is one in which we have telescope multiplicity $>3$.
+If we only consider high-multiplicity events, we can determine the $Q_{DC}$ performance for use in LPD reconstruction.
+After applying this cut, there were was just one single high-multiplicity event found using the $Q_{DC}$ method.
+This meant that just 0.01\% of all pixels were accepted, although with a sample purity of 100\%.
+Because the final sample consisted of just three HESS1 pixels, and one HESS2 pixel, the associated Poissonian error in acceptance rates and accuracy rates will be extremely large.
+
+Through we application of the two HESS classifiers, we can find the comparative high-multiplicity BDT performance.
+If we only consider high-multiplicity BDT events, the fraction of correctly identified HESS1 DC pixels falls to 2.2\%, while the fraction of incorrectly identified pixels passing the cuts falls to 0.2\%.
+The sample purity increases slightly to 91.2\%.
+In the case of the high-multiplicity HESS2 images, the BDT performance gap narrows somewhat.
+In total 1.9\% of pixels are correctly identified and accepted, although the accuracy rate is only increased to 80.7\%.
+The relatively high fraction of passing events is in excess of the random expectation of $0.16^{4}=0.07\%$ and $0.19^{4}=0.13\%$ for HESS1 and HESS2.
+This suggests that DC pixel identification between different telescope images is strongly correlated.
+The same is true for the $Q_{DC}$ high multiplicity rates.
+As well as general BDT accuracy improving after high-multiplicity cuts, the performance gap over the $Q_{DC}$ method is vastly increased for high-multiplicity events.
+As a result of the two-hundred-fold increase in acceptance rate for high multiplicity events, the expected data sample size will increase dramatically.
+This should enable spectroscopic analysis of Cosmic Ray Elements to be conducted after a much shorter experimental run time that for the $Q_{DC}$ method.
+
+\begin{table}[h!]
+  \centering
+  \caption{Comparison of high-multiplicity performance Performance}
+  \label{tab:highmultiplicitycomparison}
+  \begin{tabular}{c|cc|cc}
+    \toprule
+    & \multicolumn{2}{c|}{HESS 1} & \multicolumn{2}{c}{HESS 2} \\
+    & $Q_{DC}$ & BDT & $Q_{DC}$ & BDT\\
     \midrule
-    High Multiplicity Pixels Accepted and Correctly Identified (\%) & $<0.06$ & 1.9\\
-    High Multiplicity Pixels Accepted and Incorrectly Identified (\%) & $<0.06$ & 0.5\\
-    Sample Purity (\%) & / & 80.7\\
+    High Multiplicity Pixels Accepted and Correctly Identified (\%)& 0.01 & 2.20 & 0.01 & 1.61\\
+    High Multiplicity Pixels Accepted and Incorrectly Identified (\%)  & 0.00 & 0.43 & 0.01 & 0.22\\
+    Sample Purity (\%)& 100.0 & 83.8 & 100.0 & 88.0\\
     \bottomrule
@@
 Protons tend to emit negligible DC light, so will contaminate any data sample with events that cannot be reconstructed using the LPD method.
-To determine the acceptance rate for proton events, a simulation was conducted with 2000 proton events in CORSIKA.
+To determine the acceptance rate for proton events, a simulation was conducted with 5000 proton events in CORSIKA.
 For HESS1, the raw acceptance rate was 15.1\% while the sample purity of 32.2\%.
@@
 As no image passed all cuts, we place an upper limit of $< 0.07\%$.
+
+Using poissonian statistics, we can place a 95\% confidence upper limit on the rate of accepted, high-multiplicity $Q_{DC}$ events.
+By virtue of passing a multiplicity cut, the number of accepted pixels must be at least 4, or none.
+It is thus more appropriate to instead consider the total number of events for calculations of an upper limit.
+There were 4711 fully triggered events, of which none were \textquoteleft High multiplicity Events'.
+We find a value for the mean $\lambda$ such that the probability of not observing a high multiplicity event is less than 5\%.
+\[ P(n|\lambda)=\frac{e^{-\lambda}\lambda^{n}}{n!} \Longrightarrow P(0|\lambda)=\frac{e^{-\lambda}\lambda^{0}}{0!}=e^{-\lambda}=0.05
+\Longrightarrow
+\lambda = -\ln(0.05)=3.00\]
+
+Thus, we can conclude that if the mean was greater that if the mean $\lambda>3$, we would have expected to observe at least one event with a 95\% probability.
+As we did not observe an event, we conclude that the mean high multiplicity event rate is less than $\frac{3}{4711}=0.06\%$.
+
 For HESS1 iron events, the total acceptance rate falls slightly from 2.4\% to 2.3\%, while the sample purity decreases slightly to 89.0\%.
 For HESS2, the total acceptance rate falls slightly from 2.4\% to 2.3 \%, while the sample purity decreases slightly to 79.8\%.
-Iron images form at least 90\% of a sample, because most proton images are at least one hundred times less likely to be accepted.
+Iron images form at least 75\% of a sample, because most proton images are at least one hundred times less likely to be accepted.
+Use of this BDT method is thus assumed throughout the rest of this analysis.
 
@@
     \midrule
-    Proton Pixels Accepted (\%) & 15.1 & 58.6\\
-    Sample Purity (\%) & 32.2 & 6.8 \\
+    Proton Pixels Accepted (\%) & 15.10 & 32.68\\
+    Sample Purity (\%) & 10.1 & 5.1 \\
     \midrule
-    High Multiplicity Proton Pixels Accepted (\%) & 2.9 & 21.7\\
-    Sample Purity (\%) & 24.5 & 7.7 \\
+    High Multiplicity Proton Pixels Accepted (\%) & 0.83 & 1.03\\
+    Sample Purity (\%) & 6.8 & 4.3 \\
     \midrule
-    Proton Pixels Accepted after All Cuts(\%) & $< 0.02$ & $< 0.07$\\
+    Proton Pixels Accepted after All Cuts(\%) & $< 0.06$ & $< 0.06$\\
     Sample Purity (\%) & / & / \\
     \midrule
-    Iron Pixels Accepted after All Cuts(\%) & 2.3 & 2.3\\
-    Sample Purity (\%) & 89.0 & 79.8 \\
+    Iron Pixels Accepted after All Cuts(\%) & 2.44 & 1.66\\
+    Sample Purity (\%) & 84.3 & 88.2 \\
     \bottomrule
@@
 \includegraphics[height=0.9\textheight]{hessheight}
-\caption{The mean first interaction height for all Cherenkov Events is 40km???. The mean first interaction height for 4 telescope events in the HESS array is 23km}
+\caption{The mean first interaction height for all Cherenkov Events is 40km???.
+Events in blue met the multiplicity threshold, with DC light in four telescopes.
+The mean first interaction height for four telescope events in the HESS array is 23km}
 \label{fig:Hessheight}

### 2016-06-10 CORSIKA/fulllpd.py

@@ -1,0 +1,199 @@
+import sys
+import os.path
+import argparse, math, random, time
+import csv
+import numpy as np
+import cPickle as pickle
+from telescopeclasses import *
+from matplotlib import rc
+from scipy.optimize import curve_fit
+
+import matplotlib as mpl
+mpl.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.patches as mpatches
+
+data=["36tev-lpdfull", "56tev-lpdfull"]
+
+
+
+areas = [108., 614.]
+
+mindensity = 0.1
+height = 25000
+
+filepath = "/nfs/astrop/d6/rstein/data/"
+
+
+
+cut, ucut, QDCcut, DCcut, signalcut = ic.runforstats()
+arcut = ic.runar()
+
+
+
+sys.path.append('/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/misc')
+from progressbar import ProgressBar
+custom_options = {
+	'end': 100,
+	'width': 100,
+	'format': '%(progress)s%% [%(fill)s%(blank)s]'
+}
+
+for k in range(len(data)):
+	jobID=data[k]
+	targetfolder = filepath + jobID +"/"
+	truesignals1=[[],[]]
+	truedistances=[[],[]]
+	p = ProgressBar(**custom_options)
+	print p
+	j=500
+	i=0
+	while (i < j):
+		targetpath = targetfolder +  "run" + str(i) + "/pickle/eventdata.p"
+		if (os.path.isfile(targetpath)):
+			event = pickle.load(open(targetpath, 'rb'))
+			if hasattr(event.simulations, "DC") and hasattr(event.simulations, "full"):
+				DCsim =event.simulations.DC
+				fullsim = event.simulations.full
+				
+				IDs=0
+			
+				for fulltel in fullsim.images:	
+					if fulltel.BDTID != None:
+						fullBDT = fulltel.getBDTpixel()
+									
+						simplecandidatesignal = fullBDT.channel1.intensity -fullBDT.nnmean
+						
+						if float(ucut) > float(fullBDT.bdtscore) > float(cut):
+							if float(simplecandidatesignal) > float(signalcut):
+								if float(fulltel.hillas.aspect_ratio_) > arcut:
+									IDs+=1
+			
+				if IDs > 3:
+	
+					for fulltel in fullsim.images:
+							
[…]

### 2016-06-10 CORSIKA/old.py

@@ -57,7 +57,7 @@ def makeBDTentry(pixelentry):
 
 filepath = "/nfs/astrop/d6/rstein/data/"
 
-j=50
+j=200
 i=0
 
 accepteddistances=[[],[]]
@@ -145,11 +145,12 @@ while (i < j):
 							candidatesignal = hess2rgr.predict([bdtentry])[0]/fulltel.mirrorarea
 						elif bdtentry == None:
 							candidatesignal = 0
-													
-						if (float(ucut) > float(fullBDT.bdtscore) > float(cut)) and (float(simplecandidatesignal) > float(signalcut)) and (float(fulltel.hillas.aspect_ratio_) > arcut):
-							truedistances[plotindex].append(fulltel.hillas.core_distance_to_telescope)
-							truesignals1[plotindex].append(DCtel.hillas.image_size_amplitude_/fulltel.mirrorarea)
-							truesignals2[plotindex].append(DCpixel.channel1.intensity/fulltel.mirrorarea)						
+							
+						truedistances[plotindex].append(fulltel.hillas.core_distance_to_telescope)
+						truesignals1[plotindex].append(DCtel.hillas.image_size_amplitude_/fulltel.mirrorarea)
+						truesignals2[plotindex].append(DCpixel.channel1.intensity/fulltel.mirrorarea)
+							
+						if (float(ucut) > float(fullBDT.bdtscore) > float(cut)) and (float(simplecandidatesignal) > float(signalcut)) and (float(fulltel.hillas.aspect_ratio_) > arcut):						
 							accepteddistances[plotindex].append(fulltel.hillas.core_distance_to_telescope)
 							signals[plotindex].append(simplecandidatesignal/fulltel.mirrorarea)
 							rgrsignals[plotindex].append(candidatesignal)
@@ -214,11 +215,7 @@ for i in [0, 1]:
 		elif value > rmax:
 			extrad.append(value)
 			extras.append(math.log(expval))
-			
-	extraA, extralogC = np.polyfit(extrad, extras, 1)
-	extraC = math.exp(extralogC)
-	print extraA, extralogC, extraC
-			
+				
 	def f1(x, p1, p2, p3, p4):
 		if x < rmax:
[…]

### 2016-06-10 CORSIKA/powerlawlpd.py

@@ -1,0 +1,268 @@
+import sys
+import os.path
+import argparse, math, random, time
+import csv
+import numpy as np
+import cPickle as pickle
+from telescopeclasses import *
+from matplotlib import rc
+from scipy.optimize import curve_fit
+
+import matplotlib as mpl
+mpl.use('Agg')
+import matplotlib.pyplot as plt
+import matplotlib.patches as mpatches
+
+data=np.arange(36, 97, 10)
+print data
+
+
+
+areas = [108., 614.]
+
+mindensity = 0.1
+height = 25000
+
+filepath = "/nfs/astrop/d6/rstein/data/"
+
+
+cut, ucut, QDCcut, DCcut, signalcut = ic.runforstats()
+arcut = ic.runar()
+
+
+
+sys.path.append('/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/misc')
+from progressbar import ProgressBar
+custom_options = {
+	'end': 100,
+	'width': 100,
+	'format': '%(progress)s%% [%(fill)s%(blank)s]'
+}
+
+for k in range(2):
+	
+	Cvalues=[]
+	sigmas=[]
+
+	Avalues=[]
+
+	for energy in data:
+		jobID= str(energy) + "tev-lpdfull"
+		targetfolder = filepath + jobID +"/"
+		truesignals1=[[],[]]
+		truedistances=[[],[]]
+		p = ProgressBar(**custom_options)
+		print p
+		j=500
+		i=0
+		
+		if k == 0:
+			gradient = -0.0095
+		else:
+			gradient = Afit(energy)
+		
+		while (i < j):
+			targetpath = targetfolder +  "run" + str(i) + "/pickle/eventdata.p"
+			if (os.path.isfile(targetpath)):
+				event = pickle.load(open(targetpath, 'rb'))
+				if hasattr(event.simulations, "DC") and hasattr(event.simulations, "full"):
+					DCsim =event.simulations.DC
+					fullsim = event.simulations.full
+					
+					IDs=0
+				
+					for fulltel in fullsim.images:	
+						if fulltel.BDTID != None:
+							fullBDT = fulltel.getBDTpixel()
+										
+							simplecandidatesignal = fullBDT.channel1.intensity -fullBDT.nnmean
+							
[…]

### 2016-06-14 report/draft1.tex
Backup 14/06/16

@@
 \usepackage{geometry}
-\geometry{a4paper, portrait, margin=1.0in}
+\geometry{a4paper, portrait, margin=1.5in}
 \usepackage{gensymb}
@@
 Thus, for the LDF method to be applied, we require a minimum of five telescopes, four or more of which must image the DC light.
-We consider the amount of DC light that each telescope receives to be Poissonian \[  P_{i} ( N_{i, Received} \mid X, Y, Z, height, Epn )  =  \frac{ e^{- \lambda_{i} } \times \lambda_{i} ^{N_{i}} }{N_{i}!} \]
+We consider the amount of DC light that each telescope receives to be Gaussian, with an expectation of $\mu(X, Y, Z, height, Epn)$ and a standard deviation of $\sigma(\mu)$.
 
-In order to reduce computing time, we can use Stirling's Approximation $\ln( N!
-)  \approx  N \ln(N) - N + \frac{1}{2} \ln(2 \pi N)$.
-Pure night sky background requires that there be more that X photons in a DC pixel, and for this Stirling's Approximation has an error of just Y?.
-We then minimise the Log Likelihood function \[ - \ln(L) = - \sum_{i=1}^{n} \ln(P_{i}) \approx  \sum_{i=1}^{n} [\lambda _{i} - N_{i} \ln(\lambda _{i}) + N_{i} \ln(N_{i}) - N_{i} + \frac{1}{2} \ln(2 \pi N_{i})]  \] where n is the total number of telescopes in the array.
+\[  P_{i} ( N_{i, Received} \mid X, Y, Z, height, Epn )  =  \frac{1}{\sqrt{2 \sigma^{2} \pi}} \exp(-\frac{(N_{i, Received} - \mu)^{2}}{2 \sigma^{2}}) \].
+
+We then minimise the Log Likelihood function, assuming n is the total number of telescopes in the array.
+\[ - \ln(L) = - \sum_{i=1}^{n} \ln(P_{i}) =  \sum_{i=1}^{n} [ \frac{1}{2}\ln(2 \pi) + \ln(\sigma) + \frac{(N_{i, Received} - \mu)^{2}}{2 \sigma^{2}}]\]
 
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{corsikalpd2}
-\caption{The same curves in Figure \ref{fig:corsikalpd1} are shown here for HESS2.
-Because the CT5 telescope has an area approximately six times larger than the HESS1 telescopes, the LPD is linearly scaled here by a factor of six compared to the HESS1 LPD.
-It is clear that all other methods of calculating the LPD underestimate the value of $True_{DC}$, as seen in the top plot.}
-\label{fig:corsikalpd2}
-\end{center}
-\end{figure}
-
 \subsection{Regression BDT for $DC_{Count}$}
@@
 
-56 and 26 teV comparison. Sigma is a function of E???
-
 \begin{figure}
 \begin{center}
-\includegraphics[width=\textwidth]{DCcounterrorhess1rgr}
+\includegraphics[width=\textwidth]{DCcounterrorhess1rgrbigtestdata}
 \caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left.
@@
 \label{fig:dcdiff}
+\end{center}
+\end{figure}
+
+\subsection{Full-Shower LPD}
+Having restricted ourselves to high-multiplicity events, we reduce our data sample to mostly images in which air shower lies relatively close to the center of the telescope field of view.
+We can conclude that in many of our images, the air shower will lie mostly within the telescope image.
+In the same way as for DC light, we can look for the existence of a Characteristic LPD describing the Total Shower Intensity, where we define $I_{tot}$=Image Amplitude.
+The results for high-multiplicity events at various energies is shown in Figure \ref{fig:fullshowerlpd}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{corsikafullshowerlpd}
+\caption{The distribution of HESS 1 Image Amplitude is shown for various energies in the range 36-96 TeV.
+In each case, the exponential fit is indicated, along with the fractional deviation band in green.}
+\label{fig:fullshowerlpd}
+\end{center}
+\end{figure}
+
+For each energy, a clear exponential decay in Image Amplitude is observed.
+The data is fitted with a line of the form $y_{i} (x) =A_{i} \exp (K_{i} x)$.
+The fractional deviation from the fit is found in an analogous way to the DC LPD found in Figure \ref{fig:corsikalpd1}.
+Across all Energies, the mean fractional deviation from the fitted exponential was roughly 0.15.
+For the purposes of reconstruction, an exponential decay with a varying exponent and amplitude will not be particularly useful, because there are two degrees of freedom.
+
+In order to overcome this, we can instead parameterise the exponential fits.
+Across all energies, a fit is made and the exponent coefficients are recorded.
+A plot of the $K_{i}$ exponent values is then made, as shown in Figure  \ref{fig:powerlawlpd}.
+The K coefficients follow a clear linear distribution, to which a line is fitted.
+We obtain an equation to determine the exponent of each power law.
+
+\[ K_{i} = K(E_{i}) = -0.00004 E_{i} + -0.00692 \]
+
+Having retrieved a law for K, each dataset is then fitted a second time.
+The exponent is determined by the Energy, leaving only one degree of freedom for the fit.
+The fitted Amplitudes $A_{i}$ are then recorded, and are also plotted in Figure \ref{fig:powerlawlpd}.
+A clear linear relationship is again observed.
+A straight line is fitted to the data, and we retrieve a second relationship describing the amplitude as a function of the Energy.
+
+\[ A_{i} = A(E_{i}) = 9.4 E_{i} + -204.1 \]
+
+Through combined use of the two equations, we can parameterise the entire Full-Shower LPD using only the Energy.
+These fitted LPDs are also plotted in Figure \ref{fig:fullshowerlpd}.
+The fractional deviation bands are also shown in green, with a mean fractional deviation of roughly 0.15 across the energies.
+The Full Shower LPDs continue to be large enough to trigger telescopes for several hundred meters.
+It is thus likely that, for high-multiplicity events, we will obtain an additional four or five data points from the Full Shower LPD.
+Although the Full Shower LPDs do not depend upon the charge of the primary particle, they will still enable the core position and energy to be effectively constrained.
+This in turn should reduce the uncertainty when determining the charge of the primary particle.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{lpdpowerlaw}
+\caption{The fitted exponents $K_{i}$ are shown above, along with the equation of the Fitted Exponent Line K(E).
+Once the fitted exponents are used, the resultant amplitudes $A_{i}$ are shown below, along with the fitted Amplitude Line A(E).}
+\label{fig:powerlawlpd}
 \end{center}
@@
 It begins to dominate above roughly 1 TeV per Nucleon, particularly in the case of smaller radii.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{hess}
-\caption{A 4-camera HESS event.
-The shower direction is marked with a white cross, and the DC pixel is indicated with a white arrow.
-The shower axis passes through the shower direction, the DC pixel, and the center of the Extensive Air Shower region lying beyond the DC pixel.}
-\label{fig:hess}
-\end{center}
-\end{figure}
 

### 2016-06-14 cluster_input/cleardatasets.py

@@ -11,7 +11,7 @@ import argparse, math, random, time
 import csv
 import numpy as np
 
-nparrallel = 50
+nparrallel = 500
 
 targetfolder = "reconstructeddata/"
 
@@ -33,12 +33,12 @@ with open(afspath + targetfolder + batchname + "_saved.csv", 'wb') as csvout:
 				writer2 = csv.writer(csvfile, delimiter=',', quotechar='|')
 				writer2.writerow(["Detections","X","Y","Energy Per Nucleon","Z","Height","True X","True Y","True Energy per nucleon","True Z","True Height", "Phi", "Epsilon", "Guess Log Likelihood", "True Log Likelihood"])
 			
-	filename= batchname + "_combined"
-	path = afspath + targetfolder + filename + ".csv"
+	#~ filename= batchname + "_combined"
+	#~ path = afspath + targetfolder + filename + ".csv"
 		
-	print "Adding", path
-	with open(path, 'rb') as csvfile:
-		reader = csv.reader(csvfile, delimiter=',', quotechar='|')
-		j = 0
-		for row in reader:
-			writer1.writerow(row)
+	#~ print "Adding", path
+	#~ with open(path, 'rb') as csvfile:
+		#~ reader = csv.reader(csvfile, delimiter=',', quotechar='|')
+		#~ j = 0
+		#~ for row in reader:
+			#~ writer1.writerow(row)

### 2016-06-14 cluster_input/combinedatasets.py

@@ -11,50 +11,60 @@ import argparse, math, random, time
 import csv
 import numpy as np
 
-nparrallel = 50
+nparrallel = 5000
 
 targetfolder = "reconstructeddata/"
 
 batchname= "executereconstructed"
 
+combinedstatspath = afspath + targetfolder + batchname + "_combined.csv"
+combinedbdtpath = afspath + targetfolder + batchname + "_trainingset.csv"
 
-with open(afspath + targetfolder + batchname + "_combined.csv", 'wb') as csvout:
-	writer = csv.writer(csvout, delimiter=',', quotechar='|')
+with open(combinedstatspath, 'wb') as csvout1:
+	writer1 = csv.writer(csvout1, delimiter=',', quotechar='|')
 	
-	j=-1
+	with open(combinedbdtpath, 'wb') as csvout2:
+		writer2 = csv.writer(csvout2, delimiter=',', quotechar='|')
 	
-	for i in range (1, int(nparrallel)+1):
-		filename= batchname + str(i)
-		path = afspath + targetfolder + filename + ".csv"
+		j=-1
 		
-		if os.path.isfile(path):
-		
-			print "Adding", path
-	
-			with open(path, 'rb') as csvfile:
-				reader = csv.reader(csvfile, delimiter=',', quotechar='|')
-				
-				for row in reader:
-					if j == -1:
-						writer.writerow(row)
-						j = 1
-					elif j == 1:
-						writer.writerow(row)
-					elif j == 0:
-						j = 1
-						pass
-				
-			j = 0
+		for i in range (1, int(nparrallel)+1):
+			filename= batchname + str(i)
+			path = afspath + targetfolder + filename + ".csv"
 			
-	filename= batchname + "_saved"
-	path = afspath + targetfolder + filename + ".csv"
+			if os.path.isfile(path):
+			
+				print "Adding", path
+				
+				if random.random() > 0.5:
+					writer = writer1
+				else:
+					writer = writer2
 		
-	print "Adding", path
-	with open(path, 'rb') as csvfile:
-		reader = csv.reader(csvfile, delimiter=',', quotechar='|')
-		j = 0
-		for row in reader:
-			if j == 1:
-				writer.writerow(row)
-			elif j == 0:
-				j = 1
+				with open(path, 'rb') as csvfile:
+					reader = csv.reader(csvfile, delimiter=',', quotechar='|')
+					
+					for row in reader:
[…]

### 2016-06-14 cluster_input/corsikatocluster.sh

@@ -1,53 +1,0 @@
-#!/bin/zsh
-# 
-
-#        This is how to submit a job to the cluster:
-#          login to a submit node, e.g. astro-wgs01.desy.de
-#          Initialize by sourcing init script: . /usr/sge/default/common/settings.sh
-#          Start using "qsub empty.sh".
-#          Als Arrawy-Job mit "qsub -t 10-100:2 empty.sh" (10 bis 100 mit Schrittweite 2)
-#          Mit "qstat" wird der Status der Jobs ausgegeben.
-#          Mit "qdel job-id" kann ein Job gekillt werden.
-
-# Name of the job
-#$ -N CorsikaSIM
-
-# runtime/ Maximale Laufzeit, hat einfluss auf die Priorität. Die Schwellen sind 2:59:59, 23:59:59, 2:59:59, 167:59:59
-#$ -l h_rt=167:59:59 
-
-# Hosts/  host die benutzt werden sollen
-#$ -l hostname="!bird001.desy.de&!bird002.desy.de&!bird003.desy.de&!bird004.desy.de&!bird009.desy.de"
-
-# 32 oder 64 Bit (x86 oder amd6[[:Troubleshooting|Troubleshooting]]4) ? Es gibt mehr Hosts mit 64 Bit.
-#$ -l arch="amd64"
-
-# Stacksize/  Größe des Stacks
-#$ -l h_stack=10M 
-
-# needed memory/  Benötigter Speicher. Vorsicht: bei mehr als 2G kommt der Job in die long queue.
-#$ -l h_vmem=2G
-
-# Disk space/  Benötigter temporärer Festplattenspeicher auf dem Host .
-#$ -l h_fsize=20G
-
-# group resource for astroparticle group/ unsere Gruppe, damit haben wir Priorität auf den ASTRO-WGS-Hosts.
-#$ -P astrop
-
-# cluster sends email when:/Festlegen, wann eine E-Mail gesendet werden soll:( b bei Beginn, e bei Ende, a bei Abbruch, s bei Suspend)
-#$ -m as
-
-# E-Mail
-#$ -M robert.stein@desy.de
-
-# Path for/ Pfade für   stdout und stderr
-#$ -o /d6/rstein/Hamburg-Cosmic-Rays/cluster_output
-#$ -e /d6/rstein/Hamburg-Cosmic-Rays/cluster_error
-#
-#
-
[…]

### 2016-06-14 cluster_input/plotcombined.py

@@ -36,19 +36,19 @@ with open(afspath + "/orientations/"+ orientation +".csv", 'rb') as csvfile:
 		rowcount +=1
 		
 reconstructdata = batchname + "_combined"
+traindata = batchname + "_trainingset"
 
-allcounts = cc.run(reconstructdata, rowcount, int(mincount))
-print allcounts
+#~ allcounts = cc.run(reconstructdata, rowcount, int(mincount))
+#~ print "All Counts", allcounts
 
-
-BDT.run(reconstructdata, rowcount, int(mincount), allcounts)
-
-llcuts = oz.run(reconstructdata + "_BDT", rowcount, int(mincount), graph=False, allcounts=allcounts)
-print llcuts
-pz.run(reconstructdata + "_BDT", rowcount, int(mincount), graph=False, cuts=None, allcounts=allcounts)	
-
-pl.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
-pz.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
-pp.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
-pe.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
-ph.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts, allcounts=allcounts)
+#~ BDT.run(traindata, reconstructdata, rowcount, int(mincount))
+#~ 
+#~ llcuts = oz.run(reconstructdata + "_BDT", rowcount, int(mincount), graph=False)
+#~ print "Log Likelihood Cuts", llcuts
+#~ pz.run(reconstructdata + "_BDT", rowcount, int(mincount), graph=False, cuts=None)	
+llcuts=[0,0]
+pl.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts)
+pz.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts)
+pp.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts)
+pe.run(reconstructdata+ "_BDT", rowcount, int(mincount), graph=False, cuts=llcuts)
[…]

### 2016-06-14 positioning/batchreconstruction.py

@@ -6,10 +6,10 @@ import loglikelihood as ll
 import calculateellipse as ce
 
 def run(source, outputfile, detectorcount, rgw, eff):
-	with open("/d6/rstein/Hamburg-Cosmic-Rays/positioning/reconstructeddata/" + str(outputfile) + ".csv", 'wb') as csvout:
+	with open("/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/positioning/reconstructeddata/" + str(outputfile) + ".csv", 'wb') as csvout:
 		writer = csv.writer(csvout, delimiter=',', quotechar='|')
 		writer.writerow(["Detections","X","Y","Energy Per Nucleon","Z","Height","True X","True Y","True Energy per nucleon","True Z","True Height", "Phi", "Epsilon", "Guess Log Likelihood", "True Log Likelihood"])
-		with open("/d6/rstein/Hamburg-Cosmic-Rays/positioning/data/"+ str(source) +".csv", 'rb') as csvfile:
+		with open("/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/positioning/data/"+ str(source) +".csv", 'rb') as csvfile:
 			reader = csv.reader(csvfile, delimiter=',', quotechar='|')
 			i = 0
 			for row in reader:
@@ -23,10 +23,10 @@ def run(source, outputfile, detectorcount, rgw, eff):
 						a += [[row[base], row[base+1], row[base+2], row[base+3], row[base+4], row[base+5], row[base+6]]]
 					lim = lena*detectorcount
 					
-					phi = float(row[lim+lena])
+					phi = float(row[lim+lena-1])
 					smearphi = phi + (math.radians(0.5)*(random.random()-0.5))
 
-					epsilon = float(row[lim+lena+1])
+					epsilon = float(row[lim+lena])
 					smearepsilon = epsilon + (math.radians(0.5)*(random.random()-0.5))
 					
 					true = [row[lim], row[lim+1], row[lim+2], row[lim+3], row[lim+4], math.degrees(phi), math.degrees(epsilon)]

### 2016-06-14 positioning/calculateellipse.py

@@ -36,11 +36,10 @@ def coeff(radius, theta, phi, epsilon):
 	major = 0.5*(ra+rp)
 	minor = math.sqrt(ra*rp)
 
-	if major < minor:
-		e = 0
-	
-	else:
+	if major > minor > 0:
 		e = math.sqrt(1-((minor/major)**2))
+	else:
+		e = 0
 	
 	return ra, rp, major, minor, e
 

### 2016-06-14 positioning/loglikelihood.py

@@ -9,6 +9,8 @@ import calculateellipse as ce
 import telescoperadius as tr
 import atmosphere as atm
 
+threshold = ld.trigger()
+
 def expected(x,y,Epn,Z, height, x0,y0, category, raweff, phi, epsilon):
 	
 	rayradius, theta = cr.run(Epn, height, math.sin(phi))
@@ -23,7 +25,7 @@ def expected(x,y,Epn,Z, height, x0,y0, category, raweff, phi, epsilon):
 		
 	r, dangle = ce.run(rayradius, theta, phi, epsilon, x0, y0, x, y)
 	
-	expectedsig, expectedbkg, dcerror, bkgerror= cs.run(tradius, r, x, y, x0, y0, Epn, Z, eff)
+	expectedcount, expectedbkgcount, dcerror, bkgerror= cs.run(tradius, r, x, y, x0, y0, Epn, Z, eff)
 	
 	return expectedcount, expectedbkgcount, dcerror, bkgerror
 	
@@ -34,13 +36,33 @@ def expected(x,y,Epn,Z, height, x0,y0, category, raweff, phi, epsilon):
 def run(x,y,Epn,Z, height, x0,y0, count, bkgcount, category, eff, phi, epsilon):
 	N = int(count)
 	Nbkg = int(bkgcount)
-	expectedcount, expectedbkgcount, dcerror, bkgerror = expected(x,y,Epn,Z, height, x0,y0, category, eff, phi, epsilon)
+	expectedcount, expectedbkgcount, dcerror, bkgerror = expected(x,y,Epn,Z, height, x0,y0, category, eff, phi, epsilon)\
 	
-	if N == 0:
-		pass
-	else:
-		minusll = ((N-expectedcount)/(dcerror*N))**2
+	minusll=0
+	
+	if expectedcount < 0:
+		expectedcount = 0
 		
-	minusll += ((Nbkg-expectedbkgcount)/(bkgerror*Nbkg))**2
+	if expectedbkgcount < 0:
+		expectedbkgcount = 0
+	dcsigma = dcerror*(expectedcount + 0.0001)
+	bkgsigma = bkgerror*(expectedbkgcount+0.0001)
+	
+		
+	#~ print "Likelihood", 
+	
+	if (N > 0):
+		minusll += math.log(dcsigma)
+		#~ print "DC", minusll,
+		minusll += ((N-expectedcount)/(math.sqrt(2)*dcsigma))**2
[…]

### 2016-06-14 positioning/looptelescopes.py

@@ -36,7 +36,7 @@ def run(layout, rayxpos, rayypos, epsilon, rayradius, Epn, Z, height, phi, theta
 		print "Rayradius is", rayradius
 
 	if rayradius > 0:
-		with open("/d6/rstein/Hamburg-Cosmic-Rays/positioning/orientations/"+ layout +".csv", 'rb') as csvfile:
+		with open("/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/positioning/orientations/"+ layout +".csv", 'rb') as csvfile:
 			reader = csv.reader(csvfile, delimiter=',', quotechar='|')
 
 			for row in reader:
@@ -48,11 +48,11 @@ def run(layout, rayxpos, rayypos, epsilon, rayradius, Epn, Z, height, phi, theta
 				tradius = tr.run(category)
 				r, dangle = ce.run(rayradius, theta, phi, epsilon, xpos, ypos, rayxpos, rayypos)
 				sigcount, bkgcount, sigerror, bkgerror= cs.run(tradius, r, rayxpos, rayypos, xpos, ypos, Epn, Z, eff)
-				print "Height", height, "Rmax", r, "Signal", sigcount,"Background", bkgcount
+				#~ print "Height", height, "Rmax", r, "Distance", math.sqrt((rayxpos - xpos)**2 + (rayypos - ypos)**2),
 				
-				recorded = random.gauss(sigcount, sigerror)
+				recorded = int(random.gauss(sigcount, sigerror*sigcount))
 				
-				bkgrecorded = random.gauss(bkgcount, bkgerror)
+				bkgrecorded = int(random.gauss(bkgcount, bkgerror*bkgcount))
 				
 				recordeddangle = random.gauss(dangle, 0.01)
 				
@@ -65,8 +65,7 @@ def run(layout, rayxpos, rayypos, epsilon, rayradius, Epn, Z, height, phi, theta
 				else:
 					recordedaltitude = "None"
 
-				thresholdfrac = ld.trigger()
-				threshold = float(bkgcount)*thresholdfrac
+				threshold = ld.trigger()
 				
 				if graph:
 					if float(recorded) > 0:
@@ -82,15 +81,21 @@ def run(layout, rayxpos, rayypos, epsilon, rayradius, Epn, Z, height, phi, theta
 						print "Signal accounts for", sigcount, "Background accounts for", bkgcount
 				
 				
-				if float(sigcount) > float(threshold):
+				if float(recorded) > float(threshold):
 					j+=1
 					Trigger=True
[…]

### 2016-06-14 positioning/plotepn.py

@@ -53,7 +53,7 @@ def run(source, detectorcount, mindetections, graph, cuts, allcounts=None):
 						if float(bdtmin) < float(BDT):
 							if float(classifier) < float(1.5):
 								passing += 1
-								difference = (reconEPN-trueEPN)
+								difference = (reconEPN-trueEPN)/trueEPN
 								specificcount.append(difference)
 
 		total = len(specificcount)
@@ -87,9 +87,9 @@ def run(source, detectorcount, mindetections, graph, cuts, allcounts=None):
 		
 		k+=1
 	
-	plt.annotate(info, xy=(0.05, 0.4), xycoords="axes fraction",  fontsize=10)
+	plt.annotate(info, xy=(0.75, 0.4), xycoords="axes fraction",  fontsize=10)
 			
-	n, bins, _ = plt.hist(fullcount, bins=30, label=labels, histtype='bar', stacked=True)
+	n, bins, _ = plt.hist(fullcount, bins=15, label=labels, histtype='bar', stacked=True)
 	
 	mid = (bins[1:] + bins[:-1])*0.5
 	if isinstance(n[0], np.ndarray):
@@ -113,7 +113,7 @@ def run(source, detectorcount, mindetections, graph, cuts, allcounts=None):
 	plt.ylim(0, uplim)
 
 	plt.ylabel("Count")
-	plt.xlabel("Diference from True EPN (GeV)")
+	plt.xlabel("Frasctional Error in Epn")
 	plt.title("Reconstruction of Energy per Nucleon")
 	plt.legend()
 	

### 2016-06-14 positioning/simulate.py

@@ -11,7 +11,7 @@ import looptelescopes as lt
 import atmosphere as atm
 
 def run(raweff, rowcount, mincount=4, text=False, graph=False, output="default", layout="five", number=1):
-	with open("/d6/rstein/Hamburg-Cosmic-Rays/positioning/output/" + output + ".csv", 'wb') as csvout:
+	with open("/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/positioning/output/" + output + ".csv", 'wb') as csvout:
 		writer = csv.writer(csvout, delimiter=',', quotechar='|')
 		writer.writerow(["Event Number", "Category", "Xpos", "Ypos", "Smeared DC Count", "Smeared Background Count", "True X", "True Y", "True Energy per Nucleon", "True Z", "True Height", "Phi", "Epsilon", "Trigger", "Dangle", "Theta", "Background"])
 		

### 2016-06-18 report/draft1.tex
Backup 19/06/16

@@
 \usepackage{geometry}
-\geometry{a4paper, portrait, margin=1.5in}
-\usepackage{gensymb}
+\geometry{a4paper, portrait, margin=1.0in}
 \usepackage{booktabs}
+\usepackage{textcomp}
 \begin{document}
@@
 A full simulation of the LPD was undertaken.
-Under the assumption of constant magnetic permittivity and a zenith angle of $90\degree$ we can use the approximate form \[ N_{photons} \approx (37000 \times Z^{2} \times \Delta_{h} \times \Delta_{E})\] where $\Delta_{h}$ is the vertical distance travelled in meters and $\Delta_{E}$ is the emission energy range in eV.
+Under the assumption of constant magnetic permittivity and a zenith angle of $90\textdegree$ we can use the approximate form \[ N_{photons} \approx (37000 \times Z^{2} \times \Delta_{h} \times \Delta_{E})\] where $\Delta_{h}$ is the vertical distance travelled in meters and $\Delta_{E}$ is the emission energy range in eV.
 
@@
 An altitude of 1800m was assumed, again corresponding to the HESS site.
-The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$.
+The simulated zenith angle ranged from $0\textdegree < \theta < 2 \textdegree$, while the simulated azimuth angle ranges from -2\textdegree $ < \phi < 2 \textdegree$.
 The four smaller HESS-phase-1 telescopes were arranged in a cross along the x/y axis with the larger HESS-phase-2 \textquoteleft CT5' telescope placed at the center.
@@
 \section{HESS-type Event Reconstruction}
-With a simulation of the HESS Cherenkov 5-Telescope Array we can verify the effectiveness of the technique. 
+Having obtained a parameterisation of the LPD, and and assoiated error in the case of a HESS-type array, the Charge reconstruction Technique can be applied to a simpified Monte Carlo simulation of the HESS array, developed as part of this analysis.
+Conducting a Monte Carlo simulation using the Gaussian-smeared LPD, we can measure the effectiveness of the LPD-reconstruction technique.
+
+\subsection{Iron Flux and Energy}
+Iron nucleii, like all Cosmic Rays, follow a well-defined power law where $\phi(E) = \frac{dN(E)}{dt} = \phi_{0} E^{-\gamma} $ for some constant k.
+Using the SIBYLL model for Cosmic Ray Simulation, we assume that $ \gamma = 2.76 \pm 0.11 $ and $\phi_{0}=0.029 \pm 0.01 m^{-2} s^{-1} sr^{-1} TeV ^{-1}$ \cite{hess07}.
+Considering the same Energy Range of 35-135 TeV, we can calculate the integrated Iron Flux.
+
+\[ F(35-135TeV) = \int_{35}^{135} \phi_{0} E^{-2.76} dE = \frac{\phi_{0}}{1.76}[35^{-1.76} - 135^{-1.76}] = 2.86 \times 10^{-5} m^{-2} s^{-1} sr^{-1}\]
+
+Within CORSIKA, a square simulation of 300 x 300m was simulated.
+We can consider an identical $90000 m^{2}$ target region for core position simulation.
+The HESS telescope additionally has a solid and field of view of 5 degrees (0.09 rad),meaning an expected telescope array Iron Flux of $F(35-135TeV) = 0.22 s^{-1}$.
+On the basis of efficiency calculations in DC pixel identification, it is clear that 2.2\% of Iron Ray events will produce high-multiplicity DC pixels accepted by the BDT.
+Thus, we will ultimately obtain an hourly flux of $F(35-135TeV) = 4.4 \times 10^{-4} s^{-1} = 1.58 h^{-1}$ high-multiplicity Iron events.
+
+The full 5-telescope HESS array has been in operation since 2012 \cite{hessCT5}, and has thus had time to collect several years of data.
+Due to the requirement of night operation under favourable weather conditions, the HESS phase 2 experiment has collected approximately 5000 hours of data.
+On the basis of our high-multiplicity flux rate, we can assume that a rough expected event count would be roughly 7900 high-multiplicity iron events.
+The Monte Carlo simulations will be run with approximately this number of events.
+
+To accurately model the Cosmic Rays, the Energy Power Law must be simulated.
+To generate the random Energy value En(R) following the power law, a uniformly distributed random number R is generated.
+The value of R represents a random fraction of the total simulated flux $ F(R) = R \times F(35-135TeV) $, and can thus range from 0-1.
+Having determined the Integrated Flux corresponding to the random number, the Energy corresponding to this flux can be calculated.
+The energy E is defined as the lower bound of the integral which would produce the chosen integrated flux F.
+Thus R=0 corresponds to an Energy of 135TeV yielding no Integrated Flux, while R=1 would correspond to an Energy of 35TeV and the full Integrated Flux.
+
+\[ F(R) = F(En(R)-135TeV) = \int_{En(R)}^{135} \phi_{0} E^{-2.76} dE =\frac{\phi_{0}}{1.76}[En(R)^{-1.76} - 135^{-1.76}]= R \times F(35-135TeV)\] \[\Longrightarrow  En(R) = (\frac{1.76\times R \times F(35-135TeV)}{\phi_{0}} +135^{-1.76})^{\frac{-1}{1.76}} \]
+
 \subsection{First Interaction and Energy Saturation}
+Using the theoretical LPD found from the Frank-Tamm formula, we see that this LPD will have a very abrupt discontinuity.
+However, after the first atmospheric simulation, secondary DC light from daughter nucleii will also be produced.
+it is not possible to effectively distinguish this secondary DC light, so it will contribute to the smearing seen in Figure \ref{fig:corsikalpd1}.
+The first Interaction Height will determine the radius at which the LPD for a given Iron Nucleus will deviate from the ideal case.
+By considering the distribution of first interaction heights, we can consider the variation of the LPD.
+
 The mean first interaction height for all Cherenkov Emitting Cosmic Rays in the atmosphere is 40km, and neglecting variations in atmospheric density profiles around the Earth, this can be considered independent of experimental array.
@@
 When the HESS layout is simulated, we find that the 4 telescope events have a mean height of $h \approx 23 \pm 5$ km, as shown in \ref{fig:Hessheight}.
+
+\subsection{Extended Air Shower Background}
+Having successfully parameterised the LPD using CORSIKA simulations, we can replicate it for out Monte Carlo simulation. We have found that the DC LPD is broadly independent of both height and Energy.
 
@@
 \end{figure}
-
-\subsection{Extended Air Shower Background}
-A typical HESS image is shown in \ref{fig:hess}, with the DC pixel visible.
-For HESS cameras, the Extended Air Shower (EAS) produced after the first interaction of the Cosmic Ray overlaps the DC pixel and thus provides background in the LDF.
-As the Energy of the Cosmic Ray increases, the EAS speads over a larger angular area, and at smaller radii, the EAS-DC-shower direction axis contracts, leading to more overlap.
-Thus the background in the DC pixel increases with decreasing radius and increasing Energy.
-In addition, we have a fixed night sky background with 7 photons $m^{-2}$.
-We thus parameterise the background with \[ \rho_{bkg}  = 7 + 5E\].
-The modeled background LPD is shown as part of REF.
-It begins to dominate above roughly 1 TeV per Nucleon, particularly in the case of smaller radii.
 

### 2016-06-18 cluster_input/combinedatasets.py

@@ -10,61 +10,35 @@ sys.path.append(afspath)
 import argparse, math, random, time
 import csv
 import numpy as np
+import cPickle as pickle
+from classes import *
 
 nparrallel = 5000
 
-targetfolder = "reconstructeddata/"
+pickle_dir = "/nfs/astrop/d6/rstein/chargereconstructionpickle/"
 
-batchname= "executereconstructed"
+targetfolder = pickle_dir + "fullsims/"
+dump_dir = pickle_dir + "/combined/"
 
-combinedstatspath = afspath + targetfolder + batchname + "_combined.csv"
-combinedbdtpath = afspath + targetfolder + batchname + "_trainingset.csv"
-
-with open(combinedstatspath, 'wb') as csvout1:
-	writer1 = csv.writer(csvout1, delimiter=',', quotechar='|')
-	
-	with open(combinedbdtpath, 'wb') as csvout2:
-		writer2 = csv.writer(csvout2, delimiter=',', quotechar='|')
-	
-		j=-1
+stats=[]
+bdt = []
 		
-		for i in range (1, int(nparrallel)+1):
-			filename= batchname + str(i)
-			path = afspath + targetfolder + filename + ".csv"
-			
-			if os.path.isfile(path):
-			
-				print "Adding", path
-				
-				if random.random() > 0.5:
-					writer = writer1
-				else:
-					writer = writer2
+for i in range (1, int(nparrallel)+1):
+	path = targetfolder + "sim" + str(i) +".p"
+	
+	if os.path.isfile(path):
+	
+		print "Adding", path
 		
-				with open(path, 'rb') as csvfile:
-					reader = csv.reader(csvfile, delimiter=',', quotechar='|')
-					
-					for row in reader:
-						if j == -1:
-							writer.writerow(row)
-							j = 1
-						elif j == 1:
-							writer.writerow(row)
-						elif j == 0:
-							j = 1
-							pass
-					
-				j = 0
-			
-	#~ filename= batchname + "_saved"
-	#~ path = afspath + targetfolder + filename + ".csv"
-		#~ 
-	#~ print "Adding", path
-	#~ with open(path, 'rb') as csvfile:
-		#~ reader = csv.reader(csvfile, delimiter=',', quotechar='|')
-		#~ j = 0
-		#~ for row in reader:
-			#~ if j == 1:
-				#~ writer.writerow(row)
-			#~ elif j == 0:
[…]

### 2016-06-18 cluster_input/plotcombined.py

@@ -1,18 +1,13 @@
+import matplotlib
+matplotlib.use('pdf')
+import matplotlib.pyplot as plt
 import sys
-
-afspath = '/d6/rstein/Hamburg-Cosmic-Rays/positioning/'
-
-sys.path.append(afspath)
-
 import argparse, math, random, time
 import csv
 import numpy as np
 
-nparrallel = 10
-
-targetfolder = "reconstructeddata/"
-
-batchname= "executereconstructed"
+afspath = '/d6/rstein/Hamburg-Cosmic-Rays/positioning/'
+sys.path.append(afspath)
 
 import plotz as pz
 import plotposition as pp
@@ -20,35 +15,28 @@ import plotepn as pe
 import plotangle as pa
 import plotheight as ph
 import plotlikelihood as pl
+import plotlpd as plpd
 import optimisez as oz
 import categorycounts as cc
 
 import initialise as i
-numberofhours, mincount, reconstructiongridwidth, orientation, eff, flux, area, solidangle, selectionefficiency = i.run()
-
+numberofhours, mincount, gridwidth, layout, raweff, flux, area, solidangle, selectionefficiency, hmacceptance = i.run()
 sys.path.append('/d6/rstein/Hamburg-Cosmic-Rays/BDT')
 import BDT
 
-with open(afspath + "/orientations/"+ orientation +".csv", 'rb') as csvfile:
-	reader = csv.reader(csvfile, delimiter=',', quotechar='|')
-	rowcount = 0
-	for row in reader:
-		rowcount +=1
-		
-reconstructdata = batchname + "_combined"
-traindata = batchname + "_trainingset"
+pickle_dir = "/nfs/astrop/d6/rstein/chargereconstructionpickle/combined/"		
+statsdata = pickle_dir + "stats.p"
+traindata = pickle_dir + "trainingset.p"
 
-#~ allcounts = cc.run(reconstructdata, rowcount, int(mincount))
-#~ print "All Counts", allcounts
+plpd.run(statsdata)
 
-#~ BDT.run(traindata, reconstructdata, rowcount, int(mincount))
-#~ 
-#~ llcuts = oz.run(reconstructdata + "_BDT", rowcount, int(mincount), graph=False)
-#~ print "Log Likelihood Cuts", llcuts
[…]

### 2016-06-18 positioning/classes.py

@@ -1,42 +1,261 @@
-import math
+import math, csv, time, random
+import generate as g
 import cherenkovradius as cr
+import atmosphere as atm
+import telescoperadius as tr
+import lightdensity as ld
+import calculatearea as ca
+import loglikelihood as ll
+import calculateellipse as ce
+import countsimulation as cs
+import minimise as m
+import cPickle as pickle
 
-class simulation:
+class simulationset:
 	"""A container for many full simulations
 	"""
-	def __init__(self):
+	def __init__(self, raweff, layout, mincount, hmacceptance=1, gridwidth=300):
 		self.simulations = []
+		self.raweff = raweff
+		self.layout = layout
+		self.mincount = mincount
+		self.passcount = 0
+		self.hmcount = 0
+		self.lmcount = 0
+		self.nonDC = 0
+		self.highmultiplicityacceptance = hmacceptance
+		self.gridwidth = gridwidth
+		self.rowcount()
 		
-	def generate(self, n):
-		for i in range (n):
-			
+	def rowcount(self):
+		self.ndetectors = 0
+		with open("/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/positioning/orientations/"+ self.layout +".csv", 'rb') as csvfile:
+			reader = csv.reader(csvfile, delimiter=',', quotechar='|')
+			for row in reader:
+				self.ndetectors +=1
+		print time.asctime(time.localtime()), "Simulated Array contains", self.ndetectors, "Telescopes." 
 
-class fullevent:
-	"""A Full event simulation"""
-	def __init__(self, x, y, Z, N, energy, height, phi, theta):
-		self.true = event(x, y, Z, N, energy, height, phi, theta)
-		self.detected = None
-		self.reconstructed=None
 		
+	def generate(self, n, energy=None, height=None, Z=None):
+		print time.asctime(time.localtime()),"Simulating", n, "Events."
+		for i in range (n):
+			xpos, ypos, epsilon, genergy, gZ, gheight, phi, N = g.run()
+			
+			if energy == None:
+				simenergy = genergy
+			if height == None:
+				simheight = gheight
+			if Z == None:
+				simZ = gZ
+				
+			newsimulation = simulation(xpos, ypos, epsilon, simenergy, simZ, simheight, phi, N, self.layout)
+			newsimulation.simulatedetection(self.raweff)
[…]

### 2016-06-18 positioning/countsimulation.py

@@ -2,61 +2,11 @@ import calculatearea as ca
 import lightdensity as ld
 import math
 
-def run(tradius, r, rayxpos, rayypos, xpos, ypos, Epn, Z, eff):
-	distance = math.sqrt((rayxpos - xpos)**2 + (rayypos - ypos)**2)
-	
-	#~ if tradius > 10:
-		#~ n = 10
-		#~ 
-	#~ else:
-		#~ n=3
-	#~ 
-	#~ if distance > tradius:
-		#~ startr = 0.99*(distance-tradius)
-		#~ deltar = float(2.1*tradius/n)
-	#~ 
-	#~ else:
-		#~ startr=0
-		#~ deltar = float(2.1*r/n)
-	#~ 
-	#~ Trigger = False
-	#~ 
-	#~ rawsigcount = 0
-	#~ rawbkgcount = 0
-	#~ 
-	#~ sigslices = 0
-	#~ bkgslices = 0
-	#~ 
-	#~ for i in range (1, n+2):
-		#~ 
-		#~ currentr = i*deltar + startr
-		#~ previousr = (i-1)*deltar + startr
-		#~ midr = (i-0.5)*deltar + startr
-		#~ 
-		#~ newarea = ca.run(tradius, currentr, distance)
-		#~ 
-		#~ oldarea = ca.run(tradius, previousr, distance)
-		#~ 
-		#~ areaslice = newarea - oldarea
-		#~ 
-		#~ [sigdensity, sigerror], [bkgdensity, bkgerror] = ld.run(midr, Epn, Z, r, eff)
-		#~ print sigdensity, bkgdensity, sigerror, bkgerror
-		#~ 
-		#~ if sigdensity > 0:
-			#~ sigslices += areaslice
-			#~ 
-		#~ if bkgdensity > 0:
-			#~ bkgslices += areaslice
-		#~ 
-		#~ rawsigcount += sigdensity*areaslice
-		#~ rawbkgcount += bkgdensity*areaslice
-		
-	[sigdensity, sigerror], [bkgdensity, bkgerror] = ld.run(distance, Epn, Z, r, eff)
-	
-	rawarea = ca.telarea(tradius)
+def run(tel, simulatedevent):
+	[sigdensity, sigerror], [bkgdensity, bkgerror] = ld.run(tel.coredistance, simulatedevent.epn, simulatedevent.Z, tel.scaledrmax, simulatedevent.efficiency)
 
[…]

### 2016-06-18 positioning/heightstatistics.py

@@ -12,6 +12,7 @@ import looptelescopes as lt
 import atmosphere as atm
 import cherenkovradius as cr
 from matplotlib.patches import Ellipse
+from classes import *
 
 def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", layout="five", number=1, nh=1):
 	
@@ -91,52 +92,29 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 	wmT = []
 	
 	#Iterate over Energies
+	simset = simulationset(eff, layout, mincount=0)
 	
-
-	for i in range (0, int(number)):
-		
-		Rand = random.random()
-		height = atm.runheight(Rand, text)
-		
-		#As in generate.py, randomly generate all variables (expect Epn)
-		
-		xpos = (random.random()*300)-150
-		ypos = (random.random()*300)-150
+	simset.generate(number)
 	
-		Z= 26
-		
-		Re = random.random()*0.0178
-		Epn = ((1.7*Re/321)+(3571**-1.7))**(-1/1.7)
-		
-		weight = Epn ** (-1.7)
+	for sim in simset.simulations:
+		true = sim.true
+		height = true.height
+		multiplicity = int(true.truemultiplicity)
 		
 		hrange.append(height)
-	
-		zenith = random.random()*44
-	
-		phi = math.radians(68+zenith)
-	
-		epsilon = math.pi*random.random()*2
 		
-		radius, theta = cr.run(Epn, height, math.sin(phi), text=text)
-		
-		#Determine what category the event was
-		
-		entry, entrytype = lt.run(layout, xpos, ypos, epsilon, radius, Epn, Z, height, phi, theta, mincount, eff, 1, graph=False, text=False)
-		
-		#append the energy value to the appropriate category
-		
-		if entrytype == "metThreshold":
-			mT.append(height)
-			wmT.append(R)
-		elif entrytype == "belowThreshold":
-			bT.append(height)
-			wbT.append(R)
-		elif entrytype == "nonDC":
+		if multiplicity == int(0):
 			nDC.append(height)
-			wnDC.append(R)
+
+		elif multiplicity < int(mincount):
+			bT.append(height)
+
 		else:
-			print "ERROR OVER HERE!!!!"
+			mT.append(height)
+			
+	print mT
+	print bT
+	print nDC
 
 	#Create labels for each bin
 
[…]

### 2016-06-18 positioning/lightstatistics.py

@@ -156,5 +156,3 @@ def run(eff, rowcount=5, mincount=4, text=False, graph=False, output="default", 
 	if graph:
 		plt.show()
 	plt.close()
-
-run(1)

### 2016-06-18 positioning/minimise.py

@@ -11,36 +11,100 @@ import telescoperadius as tr
 import loglikelihood as ll
 import atmosphere as atm
 import scipy.optimize
+from classes import *
 
-def min(a, gridwidth, eff, phi, epsilon, detections):
-	
-	def f(x,y,Z,Epn, height):
-		sum = 0
-		for detection in a:
-			x0 = float(detection[0])
-			y0 = float(detection[1])
-			count = float(detection[2])
-			bkgcount = float(detection[3])
-			category = detection[4]
-			sum += ll.run(x,y,Epn,Z, height, x0,y0, count, bkgcount, category, eff, phi, epsilon)
-		return sum
+def min(fullsimulation, layout, gridwidth, raweff):
+	measured = fullsimulation.detected
+	true = fullsimulation.true
 
-	
+	def full(x,y, Epn):
+		energy = 56*Epn
+		testevent = event(x, y, measured.epsilon, energy, 26, 25000, measured.phi, N=56, layout=layout, smear=False)
+		testevent.simulatetelescopes(raweff)
+		testevent.calculatefulllikelihood(measured)
+		ll = testevent.minusllfull
+		return ll
+
 	#Runs Minimisation and outputs results
 	
-	startpos=[0, 0, 26.0, 1000, 30000]
+	fullstartpos=[0, 0, 1000]
 	argumentx = "limit_x = (-300, 300), error_x = 100000, "
 	argumenty = "limit_y = (-300, 300), error_y = 100000, "
-	argumentZ = "fix_Z=True, "
-	argumentE = "limit_Epn = (232, 4000), error_Epn=1000, "
+	argumentZ = "limit_Z = (16,36), error_Z = 2, "
 	argumentheight = "limit_height = (17500, 70000), error_height=(100000), "
+	argumentE = "limit_Epn = (232, 4000), error_Epn=1000, "
 	argumenterror = "print_level=0, errordef = 100"
 
-	m = eval("Minuit(f, x="+ str(startpos[0]) + ", " + argumentx + "y="+ str(startpos[1]) + ", " + argumenty+ "Epn = "+ str(startpos[3]) + ", " + argumentE + "Z=" + str(startpos[2]) + "," +argumentZ + "height = " + str(startpos[4]) + ", " + argumentheight + argumenterror + ")")
[…]

### 2016-06-18 positioning/oldminimise.py

@@ -1,0 +1,136 @@
+import array, math
+
+import time
+import numpy as np
+from iminuit import Minuit
+import lightdensity as ld
+import calculatearea as ca
+import cherenkovradius as cr
+import calculateellipse as ce
+import telescoperadius as tr
+import loglikelihood as ll
+import atmosphere as atm
+import scipy.optimize
+
+def min(a, gridwidth, eff, phi, epsilon, detections):
+	
+	def f(x,y,Z,Epn, height):
+		sum = 0
+		for detection in a:
+			x0 = float(detection[0])
+			y0 = float(detection[1])
+			count = float(detection[2])
+			bkgcount = float(detection[3])
+			category = detection[4]
+			sum += ll.run(x,y,Epn,Z, height, x0,y0, count, bkgcount, category, eff, phi, epsilon)
+		return sum
+
+	
+	#Runs Minimisation and outputs results
+	
+	startpos=[0, 0, 26.0, 1000, 30000]
+	argumentx = "limit_x = (-300, 300), error_x = 100000, "
+	argumenty = "limit_y = (-300, 300), error_y = 100000, "
+	argumentZ = "fix_Z=True, "
+	argumentE = "limit_Epn = (232, 4000), error_Epn=1000, "
+	argumentheight = "limit_height = (17500, 70000), error_height=(100000), "
+	argumenterror = "print_level=0, errordef = 100"
+
+	m = eval("Minuit(f, x="+ str(startpos[0]) + ", " + argumentx + "y="+ str(startpos[1]) + ", " + argumenty+ "Epn = "+ str(startpos[3]) + ", " + argumentE + "Z=" + str(startpos[2]) + "," +argumentZ + "height = " + str(startpos[4]) + ", " + argumentheight + argumenterror + ")")
+	m.migrad()
+	params = m.values
+	guess = [params['x'], params['y'], params['Epn'], params['Z'], params['height']]
+	guessfval = m.fval
+
+	xsites = np.linspace(-150, 150, int(gridwidth))
+	ysites = np.linspace(-150, 150, int(gridwidth))
+	
+	eraw = np.linspace(0, 1, num=3)
+	R = eraw*0.0178
+	evals = ((1.7*R/321)+(3571**-1.7))**(-1/1.7)
+	hvals = np.linspace(20000, 30000, num=3)
+	hvals = [25000]
+	
+	zvalues = np.arange(20.,33.)
+	
+	minangle = 0.0
+	j = 0
+	
+	while j < 5:
+		coordinates = []
+		j = 0
[…]

### 2016-06-18 positioning/optimisez.py

@@ -4,12 +4,14 @@ import numpy as np
 import matplotlib.pyplot as plt
 from scipy.optimize import curve_fit
 import scipy.stats
+import cPickle as pickle
 
-def run(source, detectorcount, mindetections, graph=False):
+def run(statsset, mindetections):
+
+	datasimset = pickle.load(open(statsset, 'rb'))
+	detectorcount = datasimset[0].ndetectors
 
 	plt.figure()
-
-	i=1
 
 	Z = 26
 	
@@ -18,10 +20,9 @@ def run(source, detectorcount, mindetections, graph=False):
 	
 	optimumcuts = []
 	
-	for j in range (detectorcount, mindetections -1, -1):
-			
+	for j in range (detectorcount, mindetections -1, -1):	
 		print "Ndetections", j
-		lowestsigma = 5
+		lowestsigma = 10
 		optimumbdt = 0.0
 		optimumpassing = 1.0
 		
@@ -31,101 +32,71 @@ def run(source, detectorcount, mindetections, graph=False):
 		
 		frac=0
 		
-		
 		for i in range(0, len(BDTrange)):
 			BDTcut = BDTrange[i]
-			
 			currentsigma = 5
 			specificcount = []
 			sqvals=[]
 			differences=[]
-			with open("/d6/rstein/Hamburg-Cosmic-Rays/positioning/reconstructeddata/"+ str(source) +".csv", 'rb') as csvfile:
-				reader = csv.reader(csvfile, delimiter=',', quotechar='|')
-				full = 0
-				passing = 0
-				
-				i=-1
-				for row in reader:
-					if i == -1:
-						i=1
-					else:
-						detections = row[0]
-						reconx = row[1]
-						recony = row[2]
-						reconEPN = row[3]
-						reconZ = row[4]
-						reconHeight = row[5]
-						truex = row[6]
-						truey = row[7]
-						trueEPN = row[8]
-						trueZ = row[9]
-						trueHeight = row[10]
-						likelihood = row[13]
-						classifier=row[15]
-						BDT = float(row[16])
-						
-						if float(detections) == float(j):
-							if int(Z) == int(trueZ):
-								full += 1
-								if float(BDTcut) < float(BDT):
-									passing += 1
-									specificcount.append(float(reconZ))
-									diff = math.fabs(float(reconZ)-26)
-									sqvals.append(float(reconZ)**2)
-									differences.append(diff)
-						
-						else:
-							i += 1
[…]

### 2016-06-18 positioning/plotlikelihood.py

@@ -3,8 +3,13 @@ import csv
 import numpy as np
 import matplotlib.pyplot as plt
 from scipy.optimize import curve_fit
+import cPickle as pickle
+from classes import *
 
-def run(source, detectorcount, mindetections, graph=False, cuts=None, allcounts=None):
+def run(statsset, mindetections, cuts=None):
+	
+	datasimset = pickle.load(open(statsset, 'rb'))
+	detectorcount = datasimset[0].ndetectors
 	
 	print detectorcount, mindetections
 	
@@ -18,78 +23,62 @@ def run(source, detectorcount, mindetections, graph=False, cuts=None, allcounts=
 	for j in range (detectorcount, mindetections -1, -1):
 		print "Ndetections", j
 		
-	
-		with open("/d6/rstein/Hamburg-Cosmic-Rays/positioning/reconstructeddata/"+ str(source) +".csv", 'rb') as csvfile:
-			reader = csv.reader(csvfile, delimiter=',', quotechar='|')
-			
-			ax = plt.subplot(nrows, 2, (1+ detectorcount-j))
-			
-			i = -1
-			info = ""
-			correct = []
-			close = []
-			wrong = []
-			full = []
-			plot = []
-			plotcolour = []
-			plotlabel = []
-			
-			bdtmin=cuts[detectorcount-j]
-	
-			for row in reader:
-				if i < 0:
-					i += 1
-				else:
-					detections = row[0]
-					reconx = row[1]
-					recony = row[2]
-					reconEPN = row[3]
-					reconZ = row[4]
-					reconHeight = row[5]
-					truex = row[6]
-					truey = row[7]
-					trueEPN = row[8]
-					trueZ = row[9]
-					trueHeight = row[10]
-					likelihood = row[13]
-					classifier=float(row[15])
-					BDT=row[16]
+		ax = plt.subplot(nrows, 2, (1+ detectorcount-j))
+		
+		i = -1
+		info = ""
+		correct = []
+		close = []
+		wrong = []
+		full = []
+		plot = []
+		plotcolour = []
+		plotlabel = []
+		
+		bdtmin=cuts[detectorcount-j]
+		
+		for simset in datasimset:
+				for sim in simset.simulations:	
+					recon = sim.reconstructed
+					observed = sim.detected
+					true = sim.true
 					
-					if classifier < 1.5:
-						if int(detections) == int(j):
-							deltaz = math.fabs(float(trueZ)-float(reconZ))
-							full.append(float(BDT))
+
[…]

### 2016-06-18 positioning/plotlpd.py

@@ -1,0 +1,67 @@
+import matplotlib
+matplotlib.use('pdf')
+import matplotlib.pyplot as plt
+import matplotlib.patches as mpatches
+import time, math
+from sklearn.tree import DecisionTreeRegressor
+from sklearn import ensemble
+import numpy as np
+from sklearn.metrics import roc_curve, auc
+import pylab as pl
+import argparse
+import csv
+import random
+from classes import *
+import cPickle as pickle
+
+plt.ioff()
+
+def run(statsset):
+	
+	distances=[]
+	truesignals=[]
+	signals=[]
+	fulltrue=[]
+	fullsmear=[]
+	
+	
+	fullsimsets = pickle.load(open(statsset, 'rb'))
+	
+	for simset in fullsimsets:
+		for sim in simset.simulations:
+			recon = sim.reconstructed
+			observed = sim.detected
+			true = sim.true
+			if 36000 > true.energy > 35000:
+				for i in range(len(true.telescopes)):
+					ttel = true.telescopes[i]
+					dtel = observed.telescopes[i]
+					
+					coredistance = ttel.coredistance
+					truesignal = ttel.DCphotons/dtel.area
+					signal = dtel.DCphotons/dtel.area
+					full = ttel.fullphotons/dtel.area
+					smear = dtel.fullphotons/dtel.area
+					distances.append(coredistance)
+					truesignals.append(truesignal)
+					signals.append(signal)
+					fulltrue.append(full)
+					fullsmear.append(smear)
+	
+	data = [truesignals, signals, fulltrue, fullsmear]
+	headings = ["True LPD", "Received LPD", "True Full LPD" "Received Full LPD"]
+	for i in range(len(data)):
+		plt.subplot(4,1, i+1)
+		plotdata = data[i]
+		plt.scatter(distances, plotdata)
+		plt.xlabel("Distance")
+		plt.ylabel("Photoelectron density")
+		
+	figure = plt.gcf() # get current figure
+	figure.set_size_inches(20, 20)
+	
+	plt.savefig("/d6/rstein/Hamburg-Cosmic-Rays/positioning/graphs/stats/lpd.pdf")
+	
+	plt.close()
+
+				

### 2016-06-18 positioning/plotz.py

@@ -3,19 +3,20 @@ import csv
 import numpy as np
 import matplotlib.pyplot as plt
 import scipy.stats
+import cPickle as pickle
+from classes import *
 
-def run(source, detectorcount, mindetections, graph, cuts=None):
+def run(statsset, mindetections, cuts=None):
+
+	datasimset = pickle.load(open(statsset, 'rb'))
+	detectorcount = datasimset[0].ndetectors
 
 	i=1
 
 	zvalues = [26]
 	nplots = len(zvalues)
-	bincount = 13
-	zrange = [19.5, 32.5]
-	reconvalues = np.linspace(zrange[0]+0.5, zrange[1]-0.5, bincount)
-	
+		
 	if cuts == None:
-		cuts = np.zeros(1 + detectorcount-mindetections)
 		classifiermax=8.5
 		path = '/d6/rstein/Hamburg-Cosmic-Rays/positioning/graphs/rawZ.pdf'
 	else:
@@ -39,89 +40,84 @@ def run(source, detectorcount, mindetections, graph, cuts=None):
 		
 		hist_fit = 0
 		k=0
-		
+	
 		for j in range (detectorcount, mindetections -1, -1):
-						
-			with open("/d6/rstein/Hamburg-Cosmic-Rays/positioning/reconstructeddata/"+ str(source) +".csv", 'rb') as csvfile:
-				reader = csv.reader(csvfile, delimiter=',', quotechar='|')
-				specificcount = []
-				differences = []
-				
-				full=0
-				passing=0
-				
-				i = -1
-				
+			print "Ndetections", j
+		
+	
+			specificcount = []
+			differences = []
+			sqvals=[]
+			
+			full=0
+			passing=0
+			plot=True
+			
+			if cuts == None:
+				bdtmin = -0.01
+			else:
 				bdtmin = cuts[k]
-
-				for row in reader:
-					if i < 0:
-						i += 1
-					else:
-						detections = row[0]
-						reconx = row[1]
-						recony = row[2]
-						reconEPN = row[3]
-						reconZ = row[4]
-						reconHeight = row[5]
-						truex = row[6]
-						truey = row[7]
-						trueEPN = row[8]
-						trueZ = row[9]
-						trueHeight = row[10]
-						likelihood = row[13]
-						classifier = float(row[15])
-						BDT=row[16]
-						
-						if int(detections) == int(j):
-							if int(z) == int(trueZ):
+			
+			for simset in datasimset:
+				for sim in simset.simulations:	
+					recon = sim.reconstructed
[…]

### 2016-06-18 positioning/reconstruction.py

@@ -38,8 +38,8 @@ parser.add_argument("-rgw", "--reconstructiongridwidth", default=75)
 
 cfg = parser.parse_args()
 
-eff = 0.06
-selectionefficiency = 0.50
+eff = 1.0
+selectionefficiency = 1.0
 flux = 2.0 * (10**-4)
 area = 300**2
 solidangle = math.radians(5)

### 2016-06-18 positioning/simulate.py

@@ -21,7 +21,7 @@ def run(raweff, rowcount, mincount=4, text=False, graph=False, output="default",
 		
 		for i in range (0, int(number)):
 			
-			rayxpos, rayypos, epsilon, rayradius, Epn, Z, height, phi, theta = g.run(text=text)
+			rayxpos, rayypos, epsilon, rayradius, Epn, Z, height, phi, theta = g.run()
 			
 			frac = atm.runabsorption(height)
 	

### 2016-06-21 report/draft1.tex
Backup 21/06/16

@@
 \usepackage{geometry}
-\geometry{a4paper, portrait, margin=1.0in}
+\geometry{a4paper, portrait, margin=1.5in}
+\usepackage{gensymb}
 \usepackage{booktabs}
-\usepackage{textcomp}
 \begin{document}
@@
 
-Above threshold, Cherenkov Emission is determined by the Frank Tamm formula!!!!!
-A full simulation of the LPD was undertaken.
-Under the assumption of constant magnetic permittivity and a zenith angle of $90\textdegree$ we can use the approximate form \[ N_{photons} \approx (37000 \times Z^{2} \times \Delta_{h} \times \Delta_{E})\] where $\Delta_{h}$ is the vertical distance travelled in meters and $\Delta_{E}$ is the emission energy range in eV.
+Above threshold, Cherenkov Emission is determined by the Frank Tamm formula \cite{ppreview}.
+Under the assumption of constant magnetic permittivity and a zenith angle of $90\degree$, and with  the vertical distance travelled in meters $\Delta_{h}$ and the emission energy range in eV $\Delta_{E}$, we can find an approximate Cherenkov Emission formula.
+\[ \frac{d^{2}N_{photons}}{dEdh} = \frac{\alpha Z^{2}}{\hbar c} \sin^{2} \theta_{c}(E) \approx 370 Z^{2} \sin^{2} \theta_{c}(E)\, cm^{-1}eV^{-1} \]
+
+\[ N_{photons} \approx (37000 \times Z^{2} \times \Delta_{h} \times \Delta_{E}(E))\, m^{-1}eV^{-1}\]
+
+A full simulation of the LPD was undertaken, with the assumption that $\Delta_{E} \approx 0.7$ independent of Energy.
+Although this is certainly an oversimplification of the true picture, it will allow us to understand the variation of the LPD with height.
+A more rigorous LPD parameterisation will be found later to account for the dependence of $\Delta_{E}$ on the Energy.
 
@@
 Thus the upper atmosphere emission contributes to the inner LDF, while the lower atmosphere emission contributes to the outer LDF.
+As the cosmic ray travels down through the atmosphere, Cherenkov Emission continuously illuminates new areas on the ground that were previously unlit, without re-illuminating inner regions.
+This is extremely useful, because it means that for all distances up to the maximum radius, the LPD will be completely independent of the emission height.
+One full parameterisation of the LPD will thus be valid for all heights, provided the maximum radius is known.
+
 We can also see ground emission radius as a function of height in \ref{fig:generalenergy}.
@@
 The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...
-
-\subsection{First Interaction Height}
-Cosmic Rays survival in from the top of the atmosphere follows an exponential decay with the number of 'interaction lengths' passed.
-The interaction length is dependent on the interaction cross section, which increases with density.
-Thus the number of interaction lengths increases exponentially as height decreases.
-The resultant decays occur most often at a height of $h \approx 40 \pm 10$ km , as seen in \ref{fig:generalheight}.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=0.9\textheight]{generalheight}
-\caption{The integrated interaction lengths increases as height decreases.
-Thus the decay probability follows a exponentially increasing distribution.
-The mean first interaction height for all events is roughly 40km above sea level.}
-\label{fig:generalheight}
-\end{center}
-\end{figure}
-
-\subsection{Atmospheric Absorption}
-The Cherenkov Light, mostly emitted in the visible blue part of the EM spectrum, experiences relatively little atmospheric absorption.
-The major of Rayleigh scattering-based atmospheric absorption occurs in the lower part of the troposphere, and thus the atmospheric absorption is almost independent of emission up to first interaction height.
 
@@
 An altitude of 1800m was assumed, again corresponding to the HESS site.
-The simulated zenith angle ranged from $0\textdegree < \theta < 2 \textdegree$, while the simulated azimuth angle ranges from -2\textdegree $ < \phi < 2 \textdegree$.
+The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$.
 The four smaller HESS-phase-1 telescopes were arranged in a cross along the x/y axis with the larger HESS-phase-2 \textquoteleft CT5' telescope placed at the center.
@@
 
+\section{HESS-type Event Reconstruction}
+
 \subsection{Determining $True_{DC}$}
@@
 
-\section{HESS-type Event Reconstruction}
+\subsection{Other Stuff Like}
 Having obtained a parameterisation of the LPD, and and assoiated error in the case of a HESS-type array, the Charge reconstruction Technique can be applied to a simpified Monte Carlo simulation of the HESS array, developed as part of this analysis.
@@
 Thus R=0 corresponds to an Energy of 135TeV yielding no Integrated Flux, while R=1 would correspond to an Energy of 35TeV and the full Integrated Flux.
+THus the simulated Cosmic Rays will obey the power law, with high-energy events being realistically suppressed.
 
@@
 
+\subsection{First Interaction Height}
+Cosmic Rays survival in from the top of the atmosphere follows an exponential decay with the number of 'interaction lengths' passed.
+
+The mean free path $\ell$ of a Cosmic Ray is a function of atmospheric cross section and number density, which are themselves functions of  height, so that $\ell(h) = \frac{1}{\sigma(h) n(h)}$.
+It is instead easier to consider a new variable x, which we name the \textquoteleft Interaction Distance', so that the survival probability of a cosmic ray follows a simple exponential decay with the interaction distance passed.
+We thus define one Interaction Length, $x_{0}$ such that a cosmic ray traveling through one interaction length will have a non-interaction probability of $\frac{1}{e}$, and in general $P_{survival} \propto e^{\frac{-x}{x_{0}}}$ The geometric distance corresponding to one interaction length will vary as a function of height.
+
+The Interaction Length is inversely proportional to the interaction cross section, which is itself proportional to local atmospheric number density, so that $x_{0} \propto \frac{1}{n(h)}$.
+Thus, because the number density of the atmosphere increases with decreasing height, the local interaction length will be geometrically shortened as the height of the cosmic ray decreases.
+If we consider the Integrated Interaction Distance as the total number of interaction lengths passed by a Cosmic Ray from the top of the atmosphere to a given height h, we see in Figure \ref{fig:generalheight} that the total integrated interaction distance increases exponentially with increasing height.
+We use the standard HESS-based data tables also found in the CORSIKA software, containing information regarding the integrated interaction distance and refractive index over a range of heights.
+As a function of x, the corresponding local interaction rate $\Gamma_{interact}(x)$ will be a product of the survival probability and the probability of interacting $P_{interact}(x)= -\frac{dP_{survival}(x)}{dx}$.
+
+\[ \Gamma_{interact}(x) = P_{interact} \times N_{survived} =  - \frac{dP_{survival}(x)}{dx} \times (N \times  P_{survival}) \]
+
+The fraction of surviving and interacting cosmic rays are shown in Figure \ref{fig:generalheight}, alongside the resultant distribution of interactions binned by height h rather than interaction length x.
+The height of each bin can be considered an average local value for $\Gamma_{interact}(h)$, and it is clear that the function $\Gamma_{interact}(h)$ peaks at a height of around 40km.
+This is thus the height region where most of our cosmic rays will interact with the atmosphere.
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=0.9\textheight]{generalheight}
+\caption{The integrated interaction lengths increases as height decreases.
+Thus the decay probability follows a exponentially increasing distribution.
+The mean first interaction height for all events is roughly 40km above sea level.}
+\label{fig:generalheight}
+\end{center}
+\end{figure}
+
+To simulate the First Interaction Height, we assign a uniform random number R to each event, corresponding to the $P_{survival}$ at which the cosmic ray will interact.
+R can be interpreted fraction of events that will have interacted before the simulated cosmic ray does.
+It ranges from R=0 for interaction at the top of the Atmosphere to R=1 for an event reaching the ground.
+Having determined the fraction of events, we assume the survival probability is normalised.
+As with all exponential distributions, we see that the expectation value is equal to one Interaction Length.
+
+\[ P_{survival}(x) = k e^{\frac{-x}{x_{0}}} \Longrightarrow \int_{0}^{\infty} P_{survival}(x) dx = k x_{0} [ e^{0} - e ^ {- \infty}] = 1 \Longrightarrow k = \frac{1}{x_{0}}\]
+\[P_{half}(x) =\int_{0}^{x_{median}} k e^{\frac{-x}{x_{0}}} dx =[1 -e^{\frac{-x_{median}}{x_{0}}} ]= \frac{1}{2} \Longrightarrow {x_{median}} = x_{0} \ln (2)\]
+
+\[ <x> =  \int_{0}^{\infty} P_{survival}(x) dx = x_{0} = \frac{x_{median}}{\ln (2)} \]
+
+Thus, we can simply calculate $x_{0}$ as the expectation value of interaction length.
+This parameter is free-floating, and can only be determined through experimental study of Cosmic Rays.
+Experimental results indicate an approximate cross section of $\sigma_{Fe-air} = 2000mb$ and a corresponding thus $x_{0} \approx 12 g cm^{-2}$ \cite{Montanus2013}.
+
+As with energy, we wish to simulate a realistic spectrum for the first interaction heights.
+We must thus convert the uniform random number R to an interaction distance X.
+Using the standard atmospheric tables, the corresponding height value can be found using exponential interpolation.
+
+\[ R = \int_{0}^{X} k e^{\frac{-x}{x_{0}}} dx = [1 -e^{\frac{-X}{x_{0}}}] \Longrightarrow X = -x_{0} \ln (1 - R) \]
+
+But you lose the tail..
+
+As cited by the HESS study, a typical first interaction height is roughly 30km for a Cherenkov-Emitting event \cite{hess07}.
+With the assumed value of $x_{0}$, a simulation was conducted to determine the expected interaction heights for Cosmic Rays.
+It is found that the mean first interaction height of 36.9km and a median first interaction height of 35.2km for all cosmic rays.
+However, when Cherenkov-Emitting events are considered, we have both a median and mean first interaction height of 30.3km, which clearly agrees with our expectations.
+
+Another parameter exponentially interpolated using the data tables is the optical depth to the surface, $\tau$.
+The Cherenkov Light, mostly emitted in the visible blue part of the EM spectrum, experiences relatively little atmospheric absorption.
+The major of Rayleigh scattering-based atmospheric absorption occurs in the lower part of the troposphere, and thus the atmospheric absorption is almost independent of emission up to first interaction height.
+For a given emitted intensity $I_{0}$ we find that the corresponding I received on the ground decays exponentially with optical depth, so that $\frac{I}{I_{0}}=e^{-\tau}$ with $\tau=\int_{0}^{l}ds$.
+
 \subsection{First Interaction and Energy Saturation}
 Using the theoretical LPD found from the Frank-Tamm formula, we see that this LPD will have a very abrupt discontinuity.
-However, after the first atmospheric simulation, secondary DC light from daughter nucleii will also be produced.
-it is not possible to effectively distinguish this secondary DC light, so it will contribute to the smearing seen in Figure \ref{fig:corsikalpd1}.
-The first Interaction Height will determine the radius at which the LPD for a given Iron Nucleus will deviate from the ideal case.
-By considering the distribution of first interaction heights, we can consider the variation of the LPD.
 

### 2016-06-21 CORSIKA/lpdfit.py

@@ -1,0 +1,36 @@
+import argparse, os, math, random, time, sys, csv, cmath
+import os.path
+import numpy as np
+import cPickle as pickle
+from sklearn import ensemble
+import initialisecuts as ic
+import re
+import cmath
+from telescopeclasses import *
+
+sys.path.append('/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/positioning/')
+
+import lightdensity as ld
+import cherenkovradius as cr
+
+def run(pixel):
+	if hasattr(pixel, "hillasparams") and hasattr(pixel, "dchillasparams"):
+		if hasattr(pixel.hillasparams, "core_distance_to_telescope") and hasattr(pixel.hillasparams, "energy") and hasattr(pixel.dchillasparams, "Hmax_"):
+			coredistance = getattr(pixel.hillasparams, "core_distance_to_telescope")
+			energy = getattr(pixel.hillasparams, "energy")
+			height = getattr(pixel.dchillasparams, "Hmax_")
+		else:
+			#~ print "Doesn't have variables"
+			#~ raw_input("prompt")
+			return None
+		
+		epn = energy/56
+		rmax , theta = cr.run(epn, height, 1, fit="exp")
+		if coredistance > rmax:
+			return ld.f1(coredistance, Z=26)
+		else:
+			return ld.f2(coredistance, Z=26, rmax=rmax)
+	else:
+		#~ print "Doesn't have containers"
+		#~ raw_input("prompt")
+		return None

### 2016-06-21 CORSIKA/powerlawlpd.py

@@ -13,7 +13,7 @@ mpl.use('Agg')
 import matplotlib.pyplot as plt
 import matplotlib.patches as mpatches
 
-data=np.arange(36, 57, 10)
+data=np.arange(36, 97, 10)
 print data
 
 nrows = len(data)-int(len(data)/2)
@@ -64,7 +64,7 @@ for k in range(4):
 		energyindex = int((energy-26)/10)
 		p = ProgressBar(**custom_options)
 		print p
-		j=20
+		j=500
 		i=0
 		
 
@@ -101,7 +101,7 @@ for k in range(4):
 						if hasattr(DCtel.hillas, "Hmax_"):
 							interactionheight = float(DCtel.hillas.Hmax_)
 									
-					if IDs > 0:
+					if IDs > 3:
 		
 						for l in range(len(fullsim.images)):
 							fulltel	= fullsim.images[l]

### 2016-06-21 CORSIKA/telescopeclasses.py

@@ -150,6 +150,21 @@ class fullevent:
 		else:
 			raise Exception("No full simulation exists")
 	
+	def simulationhillasparameters(self, findBDT):
+		"""Get Hillas parameters for both simulations, and
+		pass the DC parameters to the full pixels, to enable
+		regressor training
+		"""
+		if hasattr(self.simulations, "DC"):
+			DCsim = getattr(self.simulations, "DC")
+			DCsim.extractpixelhillas(findBDT)			
+			if hasattr(self.simulations, "full"):
+				fullsim = getattr(self.simulations, "full")
+				fullsim.extractpixelhillas(findBDT, DCsim)
+		elif hasattr(self.simulations, "full"):
+			fullsim.extractpixelhillas(findBDT)
+		
+	
 class simulation:
 	"""One simulation, which can be either full 
 	or DC (hadron only) simulation
@@ -213,14 +228,21 @@ class simulation:
 			value = float(values[i])
 			setattr(self.shower, writename, value)
 			
-	def extractpixelhillas(self, findBDT):
+	def extractpixelhillas(self, findBDT, DCsim=None):
 		"""Using the general shower azimuth and altitude, the hillas parameters
 		for each image are calculated. 
 		""" 
 		if hasattr(self.shower, 'shower_azimuth_') and hasattr(self.shower, 'shower_altitude_'):
 			for index in self.triggerIDs:
 				tel = self.images[index]
-				tel.generatepixelhillasparameters(self.shower.shower_azimuth_, self.shower.shower_altitude_, findBDT)
+				if DCsim != None:
+					if index in DCsim.triggerIDs:
+						DCtel = DCsim.images[index]
+						tel.generatepixelhillasparameters(self.shower.shower_azimuth_, self.shower.shower_altitude_, findBDT, DCtel)
+					else:
+						tel.generatepixelhillasparameters(self.shower.shower_azimuth_, self.shower.shower_altitude_, findBDT, DCtel=None)
+				else:
+					tel.generatepixelhillasparameters(self.shower.shower_azimuth_, self.shower.shower_altitude_, findBDT, DCtel=None)
 		else:
 			print "No Shower Azimuth and Altitude"
 			
@@ -589,7 +611,7 @@ class telescopeimage:
 		else:
 			raise Exception("No BDT pixel!")
 		
-	def generatepixelhillasparameters(self, showerazimuth, showeraltitude, findBDT):
[…]

### 2016-06-21 positioning/heightstatistics.py

@@ -73,7 +73,7 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 	ax3 = plt.subplot(312, sharex=ax2)
 	
 	ax3.plot(survivalheights, Rrange, label="survived")
-	ax3.plot(decayheights, Rrange, label = "decayed")
+	ax3.plot(decayheights, Rrange, label = "interacted")
 	plt.ylabel('Fraction')
 	plt.xlabel('First Interaction Height', labelpad=0)
 	ax3.invert_xaxis()
@@ -90,6 +90,7 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 	wbT = []
 	mT = []
 	wmT = []
+	emith = []
 	
 	#Iterate over Energies
 	simset = simulationset(eff, layout, mincount=0)
@@ -108,13 +109,15 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 
 		elif multiplicity < int(mincount):
 			bT.append(height)
+			emith.append(height)
 
 		else:
 			mT.append(height)
+			emith.append(height)
 			
-	print mT
-	print bT
-	print nDC
+	print "High Multiplicity DC emission is", float(len(mT))/float(number)
+	print "Low Multiplicity DC emission is", float(len(bT))/float(number)
+	print "Non-DC emission is", float(len(nDC))/float(number)
 
 	#Create labels for each bin
 
@@ -162,6 +165,8 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 	fig.tight_layout()
 	fig.subplots_adjust(top=0.95)
 	
+	
+	plt.savefig('/d6/rstein/Hamburg-Cosmic-Rays/positioning/graphs/stats/generalheight.pdf')
 	plt.savefig('/d6/rstein/Hamburg-Cosmic-Rays/report/graphs/generalheight.png')
 	#Plot the unscaled histogram
 	
@@ -170,6 +175,28 @@ def run(eff, rowcount, mincount=4, text=False, graph=False, output="default", la
 	plt.hist([mT, bT, nDC], bins=20, log=True, histtype='bar', range=limits, label=labels)
 	
 	print "Overall mean first interaction height is", np.mean(hrange)
+	hrange.sort()
+	nhrange = len(hrange)
+	halfin = int(nhrange/2.)
+	hmedian = hrange[halfin]
+	print "Overall median first interaction height is", hmedian
+	
[…]

### 2016-06-21 positioning/lightdensity.py

@@ -1,5 +1,17 @@
 import random, math
 
+p1 = 5.23
+p2 = 0.013
+p3 = -6.508
+p4 = -0.06
+
+def f1(distance, Z):
+		#~ print "Distance", distance, "Density", ((Z/26)**2)*(5.23*(math.exp(0.013*distance))-6.508)
+		return ((Z/26)**2)*(p1*(math.exp(p2*distance))+p3)
+		
+def f2(distance, Z, rmax):
+	return f1(rmax, Z)*math.exp(p4*(distance-rmax))
+
 def run(distance, Epn, Z, rmax, eff, N=56):
 	rmax = 95
 	energy=Epn*N/1000
@@ -13,24 +25,20 @@ def run(distance, Epn, Z, rmax, eff, N=56):
 	bkgd = scale * math.e**(distance*exponent)
 	
 	bkgerror = 0.15
-	
-	def f1(distance):
-		#~ print "Distance", distance, "Density", ((Z/26)**2)*(5.23*(math.exp(0.013*distance))-6.508)
-		return ((Z/26)**2)*(5.23*(math.exp(0.013*distance))-6.508)
-		
-	def f2(distance):
-		return f1(rmax)*math.exp(-0.06*(distance-rmax))
-	
+
 	if distance < rmax:
-		density = f1(distance)
+		density = f1(distance, Z)
 		dcerror=0.15
 		if density < 0:
 			density=0
 	else:
-		density = f2(distance)
+		density = f2(distance, Z, rmax)
 		dcerror=1.00
 
    	return [density, dcerror], [bkgd, bkgerror]
+   	
+def pcoeffs():
+	return p2, p3, p4
    	
 def trigger():
 	return 20

### 2016-06-27 report/draft1.tex
Backup 27/06/16

@@
 \usepackage{geometry}
-\geometry{a4paper, portrait, margin=1.5in}
+\geometry{a4paper, portrait, margin=1.0in}
 \usepackage{gensymb}
 \usepackage{booktabs}
+\usepackage{amsfonts}
 \begin{document}
@@
 
-\section{Cosmic Ray Event Simulation}
 In order to reconstruct events using the LPD method, we require saturation of the Cosmic Ray Energy, and that the event can be seen by at least 4 telescopes.
-These restrictions confine us to Cosmic Rays with specific characteristics.
-
-\subsection{Cherenkov Emission}
-Cosmic Rays follow a well-defined power law where $ \frac{dN(E)}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ?
+
+The Cosmic Rays follow a well-defined power law where $ \frac{dN(E)}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ?
 $.
@@
 The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...
-
-\section{LPD Event Reconstruction}
-
-\subsection{Log Likelihood Minimisation}
-In order to fully reconstruct an event, we need to find the x/y core position, the Energy per Nucleon, the first interaction height and the charge.
-However, if one telescope in a five-telescope array does not observe DC light, this data point can be used to constrain the core position.
-Thus, for the LDF method to be applied, we require a minimum of five telescopes, four or more of which must image the DC light.
-We consider the amount of DC light that each telescope receives to be Gaussian, with an expectation of $\mu(X, Y, Z, height, Epn)$ and a standard deviation of $\sigma(\mu)$.
-
-\[  P_{i} ( N_{i, Received} \mid X, Y, Z, height, Epn )  =  \frac{1}{\sqrt{2 \sigma^{2} \pi}} \exp(-\frac{(N_{i, Received} - \mu)^{2}}{2 \sigma^{2}}) \].
-
-We then minimise the Log Likelihood function, assuming n is the total number of telescopes in the array.
-\[ - \ln(L) = - \sum_{i=1}^{n} \ln(P_{i}) =  \sum_{i=1}^{n} [ \frac{1}{2}\ln(2 \pi) + \ln(\sigma) + \frac{(N_{i, Received} - \mu)^{2}}{2 \sigma^{2}}]\]
-
-\subsection{Extracting Charge Resolution}
-Having reconstructed many events, we can then derive the $\sigma_{Z}$ of the dataset, giving us a number to directly compare the quality of event reconstruction.
-However, a simple Gaussian 68\% method will yield only half integer values of $\sigma_{Z}$ and very frequently 0.
-This will be unhelpful for comparisons of minor modifications of reconstruction methods.
-
-Instead, we can assume a Gaussian with tails at the highest and lowest reconstructed charge values in the dataset.
-The size of the dataset can be used to calculate the fraction of events that the extreme values represent, and this probability can be converted into a \textquoteleft number of standard deviations from mean'.
-Dividing the Gaussian total width by the number of standard deviations gives us a value for $\sigma$.
-Although this will in most cases tend to overestimate the spread of the data, it will also be sensitive to all increases in the proportion of correctly reconstructed events.
-
-\subsection{Iterative Scanning Minimisation}
-Through $\sigma_{Z}$ calculation, we find that the LDF method initially provides very poor charge reconstruction.
-This is as a result of varying Threshold Energies and the sharp drop in the LDF above the maximum radius, which means the Log Likelihood is frequently discontinuous within the parameter space.
-Consequently, a Minuit-type minimisation algorithm will only be able to find a local minimum near the starting values for the fit parameters.
-
-To overcome this problem, we can iterate over a series of starting values for the parameters, with the aim of scanning the true minimum among the many minima found.
-To simplify matters, we can scan only the integer Z values over the range $ 20 \leq Z \leq 32 $, rather than considering the charge to be a free floating parameter.
-
-In order to reduce the number of calculations needed, we can consider the core position region derived from camera images, as in Hillas Analysis.
-Each telescope will have a Gaussian smeared central axis indicating the direction of the core.
-We overlay the simulated telescope array with a grid of points with grid width 1m.
-Then we select all points satisfy the condition of lying within the shower axis direction confidence interval for every telescope.
-The angular width of the confidence interval from the shower axis will be determined by the precision of the telescopes.
-
-Having determined the relevant Height and Energy ranges, we can then consider combinations of Energy and Height for which the Energy is above the Cherenkov Emission Threshold (and is saturated!).
-This gives us a second set of starting \textquoteleft Coordinates \textquoteright.
-
-The Z value is fixed and the LL function is then minimised with the assigned starting values, with the other four variables allowed to float freely.
-Minimisation typically scans 13 Z values, 10 core position coordinates, and 50 Height/Energy coordinates, yielding $ 13 \times 10 \times 50 = 6500$ minimisations in total.
-Such a technique is resource intensive but reduces $\sigma_{Z}$ by a factor of 5 or more.
-(CHECK this quantitatively and get a graph yo.
-Want to see some plateauing of sigma Z!).
-
-\subsection{Boosted Decision Trees}
-Using one quarter of a large sample of Monte Carlo data, we can train a Boosted Decision Tree (BDT) for a given telescope multiplicity, using the reconstructed x/y core position, height and energy, as well as the Log Likelihood.
-The BDT is told whether each event is \textquoteleft signal' (correctly reconstructed) or \textquoteleft background' (incorrectly reconstructed).
-
-For every simulated event, this trained BDT can then be used to assign a \textquoteleft Signal Probability'.
-On a second quarter of the dataset we can optimise a cut on the minimum signal probability, in order to maximise the ratio of signal to background.
-We find that the $\sigma_{Z}$ of the remaining \textquoteleft Test' Monte Carlo data is reduced when the same BDT cut is applied.
 
@@
 \begin{center}
-\includegraphics[width=\textwidth]{cutdistribution1None}
+\includegraphics[width=\textwidth]{hess1statsbigtestdata}
 \caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000.
@@
 
+\subsection{Extended Air Shower Background}
+Having successfully parameterised the LPD using CORSIKA simulations, we can replicate it for out Monte Carlo simulation. We have found that the DC LPD is broadly independent of both height and Energy.
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=0.9\textheight]{hessheight}
+\caption{The mean first interaction height for all Cherenkov Events is 40km???.
+Events in blue met the multiplicity threshold, with DC light in four telescopes.
+The mean first interaction height for four telescope events in the HESS array is 23km}
+\label{fig:Hessheight}
+\end{center}
+\end{figure}
+
+\subsection{Full-Shower LPD}
+Having restricted ourselves to high-multiplicity events, we reduce our data sample to mostly images in which air shower lies relatively close to the center of the telescope field of view.
+We can conclude that in many of our images, the air shower will lie mostly within the telescope image.
+In the same way as for DC light, we can look for the existence of a Characteristic LPD describing the Total Shower Intensity, where we define $I_{tot}$=Image Amplitude.
+The results for high-multiplicity events at various energies is shown in Figure \ref{fig:fullshowerlpd}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{corsikafullshowerlpd}
+\caption{The distribution of HESS 1 Image Amplitude is shown for various energies in the range 36-96 TeV.
+In each case, the exponential fit is indicated, along with the fractional deviation band in green.}
+\label{fig:fullshowerlpd}
+\end{center}
+\end{figure}
+
+For each energy, a clear exponential decay in Image Amplitude is observed.
+The data is fitted with a line of the form $y_{i} (x) =A_{i} \exp (K_{i} x)$.
+The fractional deviation from the fit is found in an analogous way to the DC LPD found in Figure \ref{fig:corsikalpd1}.
+Across all Energies, the mean fractional deviation from the fitted exponential was roughly 0.15.
+For the purposes of reconstruction, an exponential decay with a varying exponent and amplitude will not be particularly useful, because there are two degrees of freedom.
+
+In order to overcome this, we can instead parameterise the exponential fits.
+Across all energies, a fit is made and the exponent coefficients are recorded.
+A plot of the $K_{i}$ exponent values is then made, as shown in Figure  \ref{fig:powerlawlpd}.
+The K coefficients follow a clear linear distribution, to which a line is fitted.
+We obtain an equation to determine the exponent of each power law.
+
+\[ K_{i} = K(E_{i}) = -0.00004 E_{i} + -0.00692 \]
+
+Having retrieved a law for K, each dataset is then fitted a second time.
+The exponent is determined by the Energy, leaving only one degree of freedom for the fit.
+The fitted Amplitudes $A_{i}$ are then recorded, and are also plotted in Figure \ref{fig:powerlawlpd}.
+A clear exponential relationship is again observed.
+A straight line is fitted to the logarithm of the data values, and we retrieve a second relationship describing the amplitude as a function of the Energy.
+
+\[ A_{i} = A(E_{i}) =y =73.9 \times \exp (0.025 E_{i}) \]
+
+Through combined use of the two equations, we can parameterise the entire Full-Shower LPD using only the Energy.
+These fitted LPDs are also plotted in Figure \ref{fig:fullshowerlpd}.
+The fractional deviation bands are also shown in green, with a mean fractional deviation of roughly 0.15 across the energies.
+The Full Shower LPDs continue to be large enough to trigger telescopes for several hundred meters.
+It is thus likely that, for high-multiplicity events, we will obtain an additional four or five data points from the Full Shower LPD.
+
+Although the Full Shower LPDs do not depend upon the charge of the primary particle, they will still enable the core position and energy to be effectively constrained.
+We can use the Full Shower LPD to obtain a rough estimate for the core position, and thus a rough estimate of the distance from each telescope to the core.
+similarly the core energy can be estimated.
+Although this reconstruction will be inferior to one accounting for both LPDs, we can make use of the preliminary core position estimate to aid our calculation of $True_{DC}$.
+This in turn should reduce the uncertainty when determining the charge of the primary particle.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{lpdpowerlaw}
+\caption{The fitted exponents $K_{i}$ are shown above, along with the equation of the Fitted Exponent Line K(E).
+Once the fitted exponents are used, the resultant amplitudes $A_{i}$ are shown below, along with the fitted Amplitude Line A(E).}
+\label{fig:powerlawlpd}
+\end{center}
+\end{figure}
+
 \subsection{Determining $True_{DC}$}
-Determining the value off $True_{DC}$ is important for determining the error in our LPD measurements.
+Determining the value of $True_{DC}$ is essential for determining the error in our LPD measurements.
 However, there are two natural ways of quantifying $True_{DC}$.
@@
 A DC pixel lying near the image edge will be unaffected by this fact, but the total image amplitude may decline because dimmer pixels move over the image edge.
+We hope that, as with the full-shower LPD measurements, restricting ourselves to high-multiplicity events will enable us to remove most images that would otherwise suffer from edge effects.
 
@@
 
-For an alternative measurement of error in the LPD, a simulation of 2000 events was conducted with a fixed energy of 56TeV, and both Zenith and azimuth fixed to 0 degrees.
-The interaction height was fixed at 23km above sea level.
+For an alternative measurement of error in the LPD, a simulation of 2000 events was conducted with a fixed energy of 56TeV.
+The interaction height was allowed to vary realistically.
 The true distance to core was recorded from Sim\textunderscore telarray, and a graph was plotted of DC pixel intensity against core distance.
 As expected, a characteristic LPD is observed, as seen in Figure \ref{fig:corsikalpd1}.
-Due to the application of a signal cut to the BDT candidates, we are only able to see the LPD at around $r_{core} \textgreater 35m$, at which point the LPD intensity crosses the threshold of 150 p.e.
-From here, there is a clear LPD continuing up to around 100m.
-Above roughly 100m, the LPD becomes dominated by highly random hadron fragmentation, and thus ceases to be coherent.
-
-The region 35-90m is considered, and if an exponential if fitted to the LPD, then the fractional deviation $\Delta_{TrueDC} = \frac{signal_{fit} - True_{DC count}}{signal_{fit}}$ can be found.
-Using the 68th centile of all absolute fractional deviations $\Delta_{TrueDC}$, we find that the HESS LPD for $I_{tot}$ has an error of $\sigma_{Itot}=0.12$.
-Repeating for $Intensity_{max}$ calculated values, the resultant LPD had an error of $\sigma_{Imax} = 0.24$.
+Due to the trigger cut on HESS cameras of 20 photoelectrons, we are only able to see the LPD from around $r_{core} \textgreater 30m$, at which point the LPD intensity crosses the threshold of 20 p.e.
+All telescope images lying within the maximum DC radius $r_{max}$ are marked in black, where the value of $r_{max}$ varies with energy and first interaction height.
+We expect these events to follow the clear theoretical LPD observed in Figure \ref{fig:lpd}.
+After the first interaction, further emission be determined by a highly variable fragmentation process.
+These events are plotted in red, and will be ignored for LPD fitting purposes.
+
+A parameterisation of the form $y = A \exp (b x) + C $ is fitted to the measurements of $True_{DC}$.
+The fractional deviation $\Delta_{TrueDC} = \frac{signal_{fit} - True_{DC count}}{signal_{fit}}$ can then be found.
+Using the 68th centile of all absolute fractional deviations $\Delta_{TrueDC}$, we find that the HESS LPD for $I_{tot}$ has an error of $\sigma_{Itot}=0.35$.
+Repeating for $Intensity_{max}$ calculated values, the resultant LPD had an error of $\sigma_{Imax} = 0.40$.
 Again, it is clear that the $I_{tot}$ value has a smaller associated error than $Intensity_{max}$.
@@
 The mean fractional deviation between $I_{max}$ and $DC_{count}$ is relatively small, at 0.34.
-In the LPD plot, it becomes clear that the $I_{max}$ value, and thus the $DC_{count}$ value, consistently underestimates the quantity of DC light in an image.
+It is found that the $I_{max}$ value, and by extension the $DC_{count}$ value, consistently underestimates the quantity of DC light in an image.
 This is not surprising, and indicates the degree to which DC light is often split between multiple pixels.
@@
 
-\subsection{Error in calculated $DC_{count}$}
-Having successfully identified the DC pixel in many events, we can find the error $\sigma_{LPD}$ in our calculated $candidate_{DC count}$, through comparison with the correct value $True_{DC}$.
+We must find the error $\sigma_{LPD}$ in our calculated values for $candidate_{DC count}$, through comparison with the correct value $True_{DC}$.
 However, $True_{DC}$ also has an associated error $\sigma_{STA}$, originating in the use of internal random numbers for Sim\textunderscore telarray simulations.
@@
 As we cannot directly measure the actual DC intensity, we must instead measure $\sigma_{TrueDC}$.
-
-A study of 2000 events was conducted, in which each cosmic ray was simulation without night sky background or EAS background.
-Each telescope image simulation was conducted twice, and difference between $I_{1}$ and $I_{2}$ was plotted in \ref{fig:simtelerror}.
-The fractional difference from the mean Intensity of an image was defined as $\Delta = 2 \times \frac{I_{2} - I_{1}}{{I_{2} + I_{1}}}$ .
-It was found that the standard deviation in fractional difference was $\sigma_{STA}=0.06$, meaning that there is an inherent error of 6 \% in measurements of $True_{DC}$.
+Having selected a method for determining $True_{DC}$, we can use the associated value of $\sigma_{STA}=0.06$.
 In later calculations of the error in Intensity, this fractional error can be subtracted in quadrature.
@@
 
-STUFF!
+REDO STATS
 
 Taking account of $\sigma_{STA}$, we deduce that the true associated error in the LPD is $\sigma_{TrueLPD} = \sqrt{(\sigma_{TrueDC}^{2} - \sigma_{STA}^{2})} = 0.11$.
-Thus we conclude that, in an ideal case, any LPD calculated from full shower images would always have a minimum error of 11\%.
+Thus we conclude that, in an ideal case, any LPD measuring pure DC light would always have a minimum error of 11\%.
 This is reasonably high, and can be partially explained by the random nature of atmospheric conditions, among other things.
@@
 However, for high altitude/zenith angles, the DC light may lie partially outside the telescope image.
-To account for this, a new training sample was simulated in CORSIKA with both zenith and azimuth angle fixed at 0.
-Despite intuitive expectation that regressor performance should worsen significantly when it was tested on the use 2000-event testing sample, the more accurate $True_{DC}$ values for the training more than compensated for this.
-
-The training set of data consisted of the true DC pixel in each full shower image.
-A regressor BDT was trained to extrapolate the DC signal, using the variables listed in Table \ref{tab:hess1regressor}.
+To remove all associated uncertainty, a fitted parameterisation was used based on the LPD for $True_{DC}$.
+
+\[ y_{1}(r<r_{max}) = \frac{Z}{26}^{2} \times 5.3 \times \exp(0.013 r)\]
+\[ y_{2}(r > r_{max}) = y_{1}(r_{max}) \times \exp (-0.06( r-r_{max})) \]
+
+For convenience, an offset $C=-6.5$ was omitted, yielding a simple exponential law.
+Counter-intuitively, it does in fact not matter whether the training values bear any close relation to the $True_DC$ values.
+The only values that we can use for reconstruction are our $candidate_{DC count}$, based on the DC candidate pixel and full-shower image.
+As long as these $candidate_{DC count}$ values are proportional to $Z^{2}$, the reconstruction method will remain valid.
+We train the regressor to interpolate the value of $True_{DC}$ using a number of variables, and most importantly, we include the True distance to the Core and the true energy among the regressor variables listed in Table \ref{tab:hess1regressor}.
+
+In theory, any parameterisation would be valid for the regressor to train with.
+It is obvious that, if given accurate core distance values, the regressor will always be able to perfectly replicate the exponential distribution.
+However, we cannot give a trained regressor true values of energy or distance to the core, when the regressor is applied to experimental images.
+Instead, we must give an approximation of these values, estimated through analysis of the full shower.
+Thus, if we were to choose a completely outlandish parameterisation that did not correlate to the images at all, the only useful variable would be the true core distance.
+As we do not exactly know the core distance, we would also have a large uncertainty in $candidate_{DC count}$.
+Because no additional information would be present in the resultant LPD, any reconstruction would not provide reduction in core position or charge resolution measurement.
+
+If suitably trained, the regressor would consider the core position as a factor, but also correlate it with other variable related to the image.
+Then, given an estimate of the core distance, the regressor is able to produce a value of $candidate_{DC count}$ with some small error, that is still proportional to $Z^{2}$.
+The training set of data consisted of one true DC pixel entry in each full shower image.
 To account for the differing hardware, a separate regressor was trained, as before, for the CT5 camera.
-However, initial performance was poor, due to the size of the training dataset.
-Only one pixel per image was usable, leading to a small training dataset.
-Initial performance, as measured by deviation in \ref{fig:corsikalpd}, was initially poor.
-However, an expanded dataset of 5000 events greatly reduced the deviation from $True_{DC}$ values.
-The final BDT was trained with 1000 estimators and a max depth of 3.
 The Feature Importances for the HESS1 and HESS2 regressor are listed in Table \ref{tab:hess1regressor} and Table \ref{tab:hess2regressor} respectively.
@@
 
-\subsection{Full-Shower LPD}
-Having restricted ourselves to high-multiplicity events, we reduce our data sample to mostly images in which air shower lies relatively close to the center of the telescope field of view.
-We can conclude that in many of our images, the air shower will lie mostly within the telescope image.
-In the same way as for DC light, we can look for the existence of a Characteristic LPD describing the Total Shower Intensity, where we define $I_{tot}$=Image Amplitude.
-The results for high-multiplicity events at various energies is shown in Figure \ref{fig:fullshowerlpd}.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{corsikafullshowerlpd}
-\caption{The distribution of HESS 1 Image Amplitude is shown for various energies in the range 36-96 TeV.
-In each case, the exponential fit is indicated, along with the fractional deviation band in green.}
-\label{fig:fullshowerlpd}
-\end{center}
-\end{figure}
-
-For each energy, a clear exponential decay in Image Amplitude is observed.
-The data is fitted with a line of the form $y_{i} (x) =A_{i} \exp (K_{i} x)$.
-The fractional deviation from the fit is found in an analogous way to the DC LPD found in Figure \ref{fig:corsikalpd1}.
-Across all Energies, the mean fractional deviation from the fitted exponential was roughly 0.15.
-For the purposes of reconstruction, an exponential decay with a varying exponent and amplitude will not be particularly useful, because there are two degrees of freedom.
-
-In order to overcome this, we can instead parameterise the exponential fits.
-Across all energies, a fit is made and the exponent coefficients are recorded.
-A plot of the $K_{i}$ exponent values is then made, as shown in Figure  \ref{fig:powerlawlpd}.
-The K coefficients follow a clear linear distribution, to which a line is fitted.
-We obtain an equation to determine the exponent of each power law.
-
-\[ K_{i} = K(E_{i}) = -0.00004 E_{i} + -0.00692 \]
-
-Having retrieved a law for K, each dataset is then fitted a second time.
-The exponent is determined by the Energy, leaving only one degree of freedom for the fit.
-The fitted Amplitudes $A_{i}$ are then recorded, and are also plotted in Figure \ref{fig:powerlawlpd}.
-A clear linear relationship is again observed.
-A straight line is fitted to the data, and we retrieve a second relationship describing the amplitude as a function of the Energy.
-
-\[ A_{i} = A(E_{i}) = 9.4 E_{i} + -204.1 \]
-
-Through combined use of the two equations, we can parameterise the entire Full-Shower LPD using only the Energy.
-These fitted LPDs are also plotted in Figure \ref{fig:fullshowerlpd}.
-The fractional deviation bands are also shown in green, with a mean fractional deviation of roughly 0.15 across the energies.
-The Full Shower LPDs continue to be large enough to trigger telescopes for several hundred meters.
-It is thus likely that, for high-multiplicity events, we will obtain an additional four or five data points from the Full Shower LPD.
-Although the Full Shower LPDs do not depend upon the charge of the primary particle, they will still enable the core position and energy to be effectively constrained.
-This in turn should reduce the uncertainty when determining the charge of the primary particle.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{lpdpowerlaw}
-\caption{The fitted exponents $K_{i}$ are shown above, along with the equation of the Fitted Exponent Line K(E).
-Once the fitted exponents are used, the resultant amplitudes $A_{i}$ are shown below, along with the fitted Amplitude Line A(E).}
-\label{fig:powerlawlpd}
-\end{center}
-\end{figure}
-
 \subsection{Other Stuff Like}
@@
 
-\subsection{Extended Air Shower Background}
-Having successfully parameterised the LPD using CORSIKA simulations, we can replicate it for out Monte Carlo simulation. We have found that the DC LPD is broadly independent of both height and Energy.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=0.9\textheight]{hessheight}
-\caption{The mean first interaction height for all Cherenkov Events is 40km???.
-Events in blue met the multiplicity threshold, with DC light in four telescopes.
-The mean first interaction height for four telescope events in the HESS array is 23km}
-\label{fig:Hessheight}
-\end{center}
-\end{figure}
+\subsection{Full-Shower event reconstruction}
+The full shower image amplitude seen in a telescope depends on the core position and the core energy.
+We have determined a very clear parameterisation of this LPD, along with the expected LPD fractional deviation of $\frac{\sigma_{I}}{I}= 0.15$.
+The received full shower amplitude is simulated under the assumption of a Gaussian distribution around the expected value.
+We can thus reconstruct the core position and energy using a Log Likelihood minimisation.
+Once a Cosmic Ray has reached saturation, the Cherenkov Emission is effectively independent of its energy, barring determination of the first interaction height.
+Consequently, the energy value is solely determined by the full-shower amplitudes.
+
+Having observed the full shower in n telescopes out of five, we consider each of the total photoelectron counts $N_{i, received}$.
+We aim to determine the expectation value of the LPD, $\mu(x, y, Energy$) , which led to the measurement $N_{i, received}$.
+For a given expectation value, we know the corresponding probability of observing $N_{i, received}$ will be the standard Gaussian probability, with a sigma of $\sigma = 0.15 \times \mu$.
+
+\[  P_{i} ( N_{i, Received} \mid X, Y, Energy )  =  \frac{1}{\sqrt{2 \sigma^{2} \pi}} \exp(-\frac{(N_{i, Received} - \mu)^{2}}{2 \sigma^{2}}) \]
+
+To reconstruct the event parameters, we must minimise the probability of a given set of observations.
+We know that the probability of obtaining a set $N_{i,received}$ will simply be the product of the probability of each individual measurement, $\mathbb{P}(x, y, Energy) = \prod_{i=1}^{n} P_{i}(x, y, Energy)$.
+For convenience we minimise the negative log likelihood instead, in which case we find that we can sum over the contribution of each telescope.
+We then minimise the function by varying the core position and energy, to find the most likely values for those parameters.
+
+\[ - \ln(L) = - \sum_{i=1}^{n} \ln(P_{i}) =  \sum_{i=1}^{n} [ \frac{1}{2}\ln(2 \pi) + \ln(\sigma) + \frac{(N_{i, Received} - \mu)^{2}}{2 \sigma^{2}}]\]
+
+The minimsation is done with the iMinuit python package, which calls the MINUIT algorithm to seek a minima in a multi-dimensional parameter space \cite{James75}.
+Due to the discontinuous nature of the likelihood function in the case of non-observation of an air shower, it is sometimes the case that the MINUIT algorithm will find a local rather than global minima.
+To mitigate this problem, we can start the minimisation on points in a lattice of starting values within the parameter space.
+In each case, we would find a local minimum and an assosiated likelihood.
+We can then select the local minimum with the smallest associated likelihood as the global minimum for the entire parameter space.
+
+Using basic Hillas reconstruction techniques we can find a rough estimate of the core position.
+For each telescope, we will obtain an expected direction to shower core, although it will be heavily Gaussian-smeared from the true direction.
+However, combining these values can restrict us to an expected target region.
+We consider a grid of spacing 5m in the xy plane, and with each telescope, consider the reconstructed direction to shower core.
+Allowing a certain angular deviation will give us a target region containing certain likely grid points.
+We progressively increase the angular deviation until we have found the twenty most likely core position points.
+
+In addition, with reference to the energy power law, we consider 50 starting energy values.
+We again use the energy range 35-135 TeV, and as with the initial simulation of the core energy, we convert probabilities to energys.
+In this case, the probability range 0-1 is split into 50 evenly-spaced values, and each of these is converted into a corresponding energy coordinate.
+Thus most of the energy values are found at the lower end of the spectrum, because this is also where the true values for most events will be found.
+
+In combination, we consequently have a total of 1000 minimisations.
+Having run the minimisation algorithm, we thus acheive a full-shower LPD reconstruction, and obtain a measurement of the core energy and starting position.
+The resulting fraction error in energy distribution is shown below in Figure \ref{fig:rawepn}.
+It is clear that the energy reconstruction is fairly good, with a fractional standard deviation of roughly 0.10 when both four and five telescope events are considered.
+We find that the position is also reconstructed, with an accuracy of .
+Having now reconstructed the value of the energy with reasonable accuracy, we can make use of this value when attempting to reconstruct the DC LPD.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{rawepn}
+\caption{The fraction deviation from true energy is shown above.
+For events with five-telescope multiplicity, the fractional error is X but for four-telescope multiplicity, it is Y.
+The expected poissonian error bars are also shown.}
+\label{fig:rawepn}
+\end{center}
+\end{figure}  
+A graph showing the difference between the distance from telescope to true core position, and the distance from telescope to this reconstructed core position.
+The standard deviation from the true core distance  is 10m for 5 telescope events, and 16m for four telescope events.
+A better estimate for the core position will take into account the DC LPD as well as the full LPD.
+
+It is interesting to note that, for both variables, 5-telescope events have a lower deviation that 4-telescope events.
+This is despite the fact that the multiplicity refers solely to the number of identified DC pixels.
+The number of triggered telescopes containing an air shower is almost always five for these events, regardless of whether a DC pixel exists and can be identified.
+We can partially explain this by considering events which are likely to have 5 DC pixels.
+In such a case, the SOMETHING...
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{rawcoredistance}
+\caption{The distance from true core to the core reconstructed with the full-LPD is shown above. For four-telescope events, the standard deviation from true position is Xm. }
+\label{fig:rawcoredistance}
+\end{center}
+\end{figure}
+
+\subsection{Log Likelihood Minimisation}
+In order to fully reconstruct an event, we need to find the x/y core position, the Energy per Nucleon, the first interaction height and the charge.
+However, if one telescope in a five-telescope array does not observe DC light, this data point can be used to constrain the core position.
+Thus, for the LDF method to be applied, we require a minimum of five telescopes, four or more of which must image the DC light.
+We consider the amount of DC light that each telescope receives to be Gaussian, with an expectation of $\mu(X, Y, Z, height, Epn)$ and a standard deviation of $\sigma(\mu)$.
+
+\[  P_{i} ( N_{i, Received} \mid X, Y, Z, height, Epn )  =  \frac{1}{\sqrt{2 \sigma^{2} \pi}} \exp(-\frac{(N_{i, Received} - \mu)^{2}}{2 \sigma^{2}}) \].
+
+We then minimise the Log Likelihood function, assuming n is the total number of telescopes in the array.
+\[ - \ln(L) = - \sum_{i=1}^{n} \ln(P_{i}) =  \sum_{i=1}^{n} [ \frac{1}{2}\ln(2 \pi) + \ln(\sigma) + \frac{(N_{i, Received} - \mu)^{2}}{2 \sigma^{2}}]\]
+
+\subsection{Extracting Charge Resolution}
+Having reconstructed many events, we can then derive the $\sigma_{Z}$ of the dataset, giving us a number to directly compare the quality of event reconstruction.
+However, a simple Gaussian 68\% method will yield only half integer values of $\sigma_{Z}$ and very frequently 0.
+This will be unhelpful for comparisons of minor modifications of reconstruction methods.
+
+Instead, we can assume a Gaussian with tails at the highest and lowest reconstructed charge values in the dataset.
+The size of the dataset can be used to calculate the fraction of events that the extreme values represent, and this probability can be converted into a \textquoteleft number of standard deviations from mean'.
+Dividing the Gaussian total width by the number of standard deviations gives us a value for $\sigma$.
+Although this will in most cases tend to overestimate the spread of the data, it will also be sensitive to all increases in the proportion of correctly reconstructed events.
+
+\subsection{Iterative Scanning Minimisation}
+Through $\sigma_{Z}$ calculation, we find that the LDF method initially provides very poor charge reconstruction.
+This is as a result of varying Threshold Energies and the sharp drop in the LDF above the maximum radius, which means the Log Likelihood is frequently discontinuous within the parameter space.
+Consequently, a Minuit-type minimisation algorithm will only be able to find a local minimum near the starting values for the fit parameters.
+
+To overcome this problem, we can iterate over a series of starting values for the parameters, with the aim of scanning the true minimum among the many minima found.
+To simplify matters, we can scan only the integer Z values over the range $ 20 \leq Z \leq 32 $, rather than considering the charge to be a free floating parameter.
+
+In order to reduce the number of calculations needed, we can consider the core position region derived from camera images, as in Hillas Analysis.
+Each telescope will have a Gaussian smeared central axis indicating the direction of the core.
+We overlay the simulated telescope array with a grid of points with grid width 1m.
+Then we select all points satisfy the condition of lying within the shower axis direction confidence interval for every telescope.
+The angular width of the confidence interval from the shower axis will be determined by the precision of the telescopes.
+
+Having determined the relevant Height and Energy ranges, we can then consider combinations of Energy and Height for which the Energy is above the Cherenkov Emission Threshold (and is saturated!).
+This gives us a second set of starting \textquoteleft Coordinates \textquoteright.
+
+The Z value is fixed and the LL function is then minimised with the assigned starting values, with the other four variables allowed to float freely.
+Minimisation typically scans 13 Z values, 10 core position coordinates, and 50 Height/Energy coordinates, yielding $ 13 \times 10 \times 50 = 6500$ minimisations in total.
+Such a technique is resource intensive but reduces $\sigma_{Z}$ by a factor of 5 or more.
+(CHECK this quantitatively and get a graph yo.
+Want to see some plateauing of sigma Z!).
+
+\subsection{Boosted Decision Trees}
+Using one quarter of a large sample of Monte Carlo data, we can train a Boosted Decision Tree (BDT) for a given telescope multiplicity, using the reconstructed x/y core position, height and energy, as well as the Log Likelihood.
+The BDT is told whether each event is \textquoteleft signal' (correctly reconstructed) or \textquoteleft background' (incorrectly reconstructed).
+
+For every simulated event, this trained BDT can then be used to assign a \textquoteleft Signal Probability'.
+On a second quarter of the dataset we can optimise a cut on the minimum signal probability, in order to maximise the ratio of signal to background.
+We find that the $\sigma_{Z}$ of the remaining \textquoteleft Test' Monte Carlo data is reduced when the same BDT cut is applied.
 

### 2016-06-27 CORSIKA/combineforregressor.py

@@ -16,7 +16,7 @@ cfg = parser.parse_args()
 filepath = "/nfs/astrop/d6/rstein/data/"
 
 i = 1
-j = 5000
+j = 15000
 
 targetfolder = filepath + cfg.jobID +"/"
 
@@ -35,6 +35,8 @@ hess1candidatepixels = []
 hess2candidatepixels = []
 hess1DCsignals = []
 hess2DCsignals = []
+hess1trueZ=[]
+hess2trueZ=[]
 
 targetpath = targetfolder +  "run" + str(i) + "/pickle/eventdata.p"
 
@@ -42,6 +44,15 @@ while (i < j):
 	targetpath = targetfolder +  "run" + str(i) + "/pickle/eventdata.p"
 	if (os.path.isfile(targetpath)):
 		event = pickle.load(open(targetpath, 'rb'))
+		
+		if i < 5001:
+			trueZ = 26
+		elif 5000 < i < 10001:
+			trueZ = 25
+		elif 10000< i:
+			trueZ =27
+		
+		
 		for index in event.simulations.DC.triggerIDs:
 			DCtel =  event.simulations.DC.images[index]
 			fulltel = event.simulations.full.images[index]
@@ -51,9 +62,12 @@ while (i < j):
 				if fulltel.size == "HESS1":
 					hess1candidatepixels.append(fullpixel)
 					hess1DCsignals.append(DCtel.hillas.image_size_amplitude_)
+					hess1trueZ.append(trueZ)
+					
 				elif fulltel.size == "HESS2":
 					hess2candidatepixels.append(fullpixel)
 					hess2DCsignals.append(DCtel.hillas.image_size_amplitude_)
+					hess2trueZ.append(trueZ)
 				else:
 					raise Exception("Name error with size " + fulltel.size)
 					
@@ -70,3 +84,5 @@ pickle.dump(hess1candidatepixels,  open(pickle_dump_dir+"/hess1candidatepixels.p
 pickle.dump(hess2candidatepixels,  open(pickle_dump_dir+"/hess2candidatepixels.p", "wb"))
 pickle.dump(hess1DCsignals,  open(pickle_dump_dir+"/hess1DCsignals.p", "wb"))
 pickle.dump(hess2DCsignals,  open(pickle_dump_dir+"/hess2DCsignals.p", "wb"))
[…]

### 2016-06-27 CORSIKA/corsikatocluster.sh

@@ -94,7 +94,7 @@ echo "MAX_PRINT_ARRAY set to 2100"
 
 mkdir -p /nfs/astrop/d6/rstein/data/$JOB_ID
 
-for (( i=0; i <= 9; i++ ))
+for (( i=0; i <= 29; i++ ))
 do 
  python /nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/CORSIKA/runcorsika.py -rn $((($i*500) + $SGE_TASK_ID)) -td $TMPDIR -jid $JOB_ID
 

### 2016-06-27 CORSIKA/extractpixelsoncluster.sh

@@ -50,7 +50,7 @@
 
 for (( i=0; i <= 9; i++ ))
 do 
- python /nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/CORSIKA/extractpixels.py -rn $((($i*200) + $SGE_TASK_ID)) -jid $1 -bdt $2
+ python /nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/CORSIKA/extractpixels.py -rn $((($i*500) + $SGE_TASK_ID)) -jid $1 -bdt $2
 done
 
 

### 2016-06-27 CORSIKA/lpdfit.py

@@ -13,7 +13,7 @@ sys.path.append('/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/positioning/')
 import lightdensity as ld
 import cherenkovradius as cr
 
-def run(pixel):
+def run(pixel, Z):
 	if hasattr(pixel, "hillasparams") and hasattr(pixel, "dchillasparams"):
 		if hasattr(pixel.hillasparams, "core_distance_to_telescope") and hasattr(pixel.hillasparams, "energy") and hasattr(pixel.dchillasparams, "Hmax_"):
 			coredistance = getattr(pixel.hillasparams, "core_distance_to_telescope")
@@ -27,9 +27,9 @@ def run(pixel):
 		epn = energy/56
 		rmax , theta = cr.run(epn, height, 1, fit="exp")
 		if coredistance > rmax:
-			return ld.f1(coredistance, Z=26)
+			return ld.f1(coredistance, Z=Z)
 		else:
-			return ld.f2(coredistance, Z=26, rmax=rmax)
+			return ld.f2(coredistance, Z=Z, rmax=rmax)
 	else:
 		#~ print "Doesn't have containers"
 		#~ raw_input("prompt")

### 2016-06-27 CORSIKA/powerlawlpd.py

@@ -41,7 +41,7 @@ custom_options = {
 	'format': '%(progress)s%% [%(fill)s%(blank)s]'
 }
 
-for k in range(4):
+for k in range(3):
 	
 	Cvalues=[]
 	sigmas=[]
@@ -283,17 +283,17 @@ for k in range(4):
 		
 		def Afit(x):
 			return Am*x + Ac
-		plt.subplot(3,1,1)
+		plt.subplot(2,1,1)
 		plt.errorbar(data, Avalues, yerr=Aerrors, fmt='o')
 		plt.xlabel("Energy (Tev)")
 		plt.ylabel("Fitted Exponent")
 		
 		plt.plot(data, Afit(data), color="k")
 		Line = "y =" + str('{0:.5f}'.format(Am)) + " x + " + str('{0:.5f}'.format(Ac))
-		plt.annotate(Line, xy=(0.85, 0.9), xycoords="axes fraction",  fontsize=15)
+		plt.annotate(Line, xy=(0.75, 0.9), xycoords="axes fraction",  fontsize=15)
 		
 	elif k==1:
-		plt.subplot(3,1,2)
+		plt.subplot(2,1,2)
 		plt.errorbar(data, Cvalues, yerr=sigmas, fmt='o')
 		plt.xlabel("Energy (Tev)")
 		plt.ylabel("Fitted Amplitude")
@@ -317,26 +317,35 @@ for k in range(4):
 		plt.yscale("log")
 		Line = "y =" + str('{0:.1f}'.format(camplitude)) + " e ^ ( " + str('{0:.3f}'.format(cexponent)) + " x)"
 		plt.annotate(Line, xy=(0.05, 0.9), xycoords="axes fraction",  fontsize=15)
+		#~ 
+		saveto = "/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/CORSIKA/graphs/lpdpowerlaw.pdf"
 		
-	elif k==2:
-		plt.subplot(3,1,3)
-		plt.scatter(hmax, Cdeviation)
-		plt.xlabel("First Interaction Height (m)")
-		plt.ylabel("Fitted Amplitude")
+		print "Saving to", saveto
 		
-		print "Final!", hmax, Cdeviation
+		plt.savefig(saveto)
+		plt.savefig("/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/report/graphs/lpdpowerlaw.pdf")
 		
[…]

### 2016-06-27 CORSIKA/trainextrapolation.py

@@ -46,7 +46,7 @@ def makeBDTentry(pixelentry):
 	return bdtentry
 
 categories = ["hess2","hess1"]
-learningrates = [0.2, 0.5]
+learningrates = [0.2, 0.6]
 
 for i in range(len(categories)):
 	
@@ -57,8 +57,9 @@ for i in range(len(categories)):
 	pickledatafolder = os.path.join(jobfolder, "bdtpickle")
 	filename = pickledatafolder + "/" + category + "candidatepixels.p"
 	signalfilename = pickledatafolder + "/" + category + "DCsignals.p"
+	trueZfilename = pickledatafolder + "/" + category + "trueZ.p"
 
-	if os.path.isfile(filename) and os.path.isfile(signalfilename):
+	if os.path.isfile(filename) and os.path.isfile(signalfilename) and os.path.isfile(trueZfilename):
 		print "Loading training dataset from", filename
 		print "Loading training scores from", signalfilename
 	else:
@@ -69,13 +70,16 @@ for i in range(len(categories)):
 
 	trainset = pickle.load(open(filename, 'rb'))
 	signals= pickle.load(open(signalfilename, 'rb'))
+	trueZ = pickle.load(open(trueZfilename, 'rb'))
 	
 	print category, "training dataset contains", len(trainset), "images"
 	
 	for i in range(len(trainset)):
 		pix = trainset[i]
 		truesignal = signals[i]
-		fitsignal = lf.run(pix)
+		Z = float(trueZ[i])
+		#~ print i, "Z is", Z
+		fitsignal = lf.run(pix, Z)
 		
 		bdtentry = makeBDTentry(pix)
 		

### 2016-06-27 positioning/countsimulation.py

@@ -3,11 +3,12 @@ import lightdensity as ld
 import math
 
 def run(tel, simulatedevent):
-	[sigdensity, sigerror], [bkgdensity, bkgerror] = ld.run(tel.coredistance, simulatedevent.epn, simulatedevent.Z, tel.scaledrmax, simulatedevent.efficiency)
+	[sigdensity, sigerror], [bkgdensity, bkgerror], [recondensity, reconerror] = ld.run(tel.coredistance, simulatedevent.epn, simulatedevent.Z, tel.scaledrmax, simulatedevent.efficiency)
 
 	rawsigcount = tel.area * sigdensity
 	rawbkgcount = tel.area * bkgdensity
+	rawreconcount = tel.area * recondensity
 
 	#~ print int(rawsigcount), int(rawbkgcount), sigerror, bkgerror
-	return rawsigcount, rawbkgcount, sigerror, bkgerror
+	return rawsigcount, rawbkgcount, sigerror, bkgerror, rawreconcount, reconerror
 					

### 2016-06-28 report/draft1.tex
Backup 28/06/16

@@
 \usepackage{amsfonts}
+\usepackage{pgfplotstable, booktabs}
+
+\pgfplotstableset{
+  	every head row/.style={before row=\toprule,after row=\midrule},
+    every last row/.style={after row=\bottomrule}
+	}
+
 \begin{document}
@@
 The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...
+
+We need four-telescope events or something.
 
@@
 
-\section{HESS-type Event Reconstruction}
+\section{HESS-type Event Simulation}
 
@@
 As long as these $candidate_{DC count}$ values are proportional to $Z^{2}$, the reconstruction method will remain valid.
-We train the regressor to interpolate the value of $True_{DC}$ using a number of variables, and most importantly, we include the True distance to the Core and the true energy among the regressor variables listed in Table \ref{tab:hess1regressor}.
+We train the regressor to interpolate the value of $True_{DC}$ using a number of variables, and most importantly, we include the True distance to the Core and the true energy among the regressor variables listed in Table \ref{tab:regressor}.
 
@@
 The training set of data consisted of one true DC pixel entry in each full shower image.
+
+The training sample contains, in equal proportion, elements Manganese (Z=25), Iron (Z=26) and Cobalt (Z=27).
+This to ensure that the regressor is well trained to distinguish between different cosmic ray charges, by providing variation of $Z^{2}$ for training.
+If the regressor is capable of distinguishing between these three elements, then this will serve as a sufficient proof of concept.
+We expect that, were an entire spectrum of cosmic ray elements simulated, a regressor could be trained with similar performance for a large charge range.
+The training of such a BDT was not done as part of this analysis, due to computing time restraints.
+However, in Monte Carlo simulations, the existence of a regressor will be assumed.
+
 To account for the differing hardware, a separate regressor was trained, as before, for the CT5 camera.
-The Feature Importances for the HESS1 and HESS2 regressor are listed in Table \ref{tab:hess1regressor} and Table \ref{tab:hess2regressor} respectively.
-There is again a discrepancy in variable importance between the two BDTs.
+The Feature Importances for the HESS1 and HESS2 regressor are listed in Table \ref{tab:regressor}..
+There is little discrepancy in variable importance between the two BDTs.
 
@@
   \centering
-  \caption{Relative Feature Importance in HESS-1 Regressor BDT training}
-  \label{tab:hess1regressor}
+  \caption{Relative Feature Importance in  Regressor BDT training}
+  \label{tab:regressor}
   \begin{tabular}{ccc}
     \toprule
-    Variable & Relative Importance\\
-    \midrule
-    $Q_{DC}$ & 0.17\\
-    $DC_{Count}$ & 0.16\\
-    Image Amplitude & 0.15\\
-    $Intensity_{N.N.min}$ & 0.14\\
-    $Intensity_{N.N.max}$ & 0.14\\
-    $Intensity$ & 0.13\\
-    $Mean_{N.N}$ & 0.11\\
+    Variable & HESS-1 & HESS-2 \\
+    \midrule
+    Aspect Ratio & 0.12 & 0.12\\
+    $Intensity_{N.N.min}$ & 0.11 & 0.12\\
+    Image Amplitude & 0.11 & 0.11\\
+    $Q_{DC}$ & 0.10 & 0.11\\
+    $r_{core}$ & 0.10 & 0.10\\
+    $Intensity_{N.N.max}$ & 0.10 & 0.10\\
+    $Mean_{N.N}$ & 0.10 & 0.09\\
+    Energy & 0.09 & 0.09\\
+    $DC_{Count}$ & 0.09 & 0.09\\
+    $Intensity$ & 0.08 & 0.08\\
     \bottomrule
@@
 
-\begin{table}[h!]
-  \centering
-  \caption{Relative Feature Importance in HESS-2 Regressor BDT training}
-  \label{tab:hess2regressor}
-  \begin{tabular}{ccc}
-    \toprule
-    Variable & Relative Importance\\
-    \midrule
-    Image Amplitude & 0.20\\
-    $Intensity_{N.N.min}$ & 0.15\\
-    $Q_{DC}$ & 0.15\\
-    $Mean_{N.N}$ & 0.14\\
-    $DC_{Count}$ & 0.13\\
-    $Intensity_{N.N.max}$ & 0.13\\
-    $Intensity$ & 0.13\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-Repeating the comparison for the HESS1 regressor, we find for $\sigma_{rgrfit} = 0.35$, a significant improvement over $\sigma_{DCcount}$.
-Taking into account $\sigma_{STA}$, we find that ultimately $\sigma_{rgr1}=0.34$, a fairly large value that nonetheless should be acceptable in 4-telescope events.
+The features importances are, on the face of it, rather surprising.
+Ultimately, the true values for energy and $r_{core}$ are not the most important variables.
+We can conclude that the regressor has been well taught to indirectly infer the cosmic ray charge, and account for this by correlating values to the true core distance/energy.
+The Aspect Ratio is heavily dependent on distance to core, but also on the charge.
+Thus, in combination with $r_{core}$, the charge can be reasonably inferred.
+Similarly the Image Amplitude is relied upon to infer energy, and in conjunction with the estimated energy, can indicate charge.
+It is encouraging to see that the regressor relies more heavily on Image Amplitude and Aspect Ratio, because these two values are known with a much smaller uncertainty than the core position/energy.
+
+Repeating the comparison for the HESS1 regressor, we find for $\sigma_{rgr} = 0.14$, a significant improvement over $\sigma_{DCcount}$.
+The plotted LPD is seen in Figure \ref{fig:corsikalpd1}.
+Through use of a well-defined law for the training values, we have eliminated the influence of $\sigma_{STA}$ on the training process.
 The comparative performance is recorded in Table \ref{tab:lpderror}.
+
 Instead of rejecting DC pixels which do not meet out $DC_{count}$ and $P_{signal}$ cuts, we can separately measure their deviation from the LPD.
 In this way, we can include the information from these DC pixels in later analysis, while accounting for the larger uncertainty in their LPD measurements.
-For images which do pass only the multiplicity cuts, but not the $P_{signal}$ or $DC_{count}$ cuts, we find that the regressor error is $\sigma_{rejected1}=0.32$.
+For images which do pass only the multiplicity cuts, but not the $P_{signal}$ or $DC_{count}$ cuts, we find that the regressor error is $\sigma_{rejected1}=0.15$.
+We can thus make use of these points, because they follow an almost identical distribution.
+
+STUFF
 
@@
 
-To get a more accurate estimate of the error, the testing set of 2000 events with varying azimuth/zenith was again considered.
-The fractional difference \[  \Delta = \frac{ candidate_{DC count} - True_{DC count}}{True_{DC count}} \] was binned in a histogram format, as shown in Figure \ref{fig:dcdiff}.
-It was observed that the mean was 0.09 and the median was -0.08, meaning the distribution was partially skewed.
-If the absolute deviation from the $True_{DC}$ value is considered, then 68\% of pixels have a fractional deviation less than 0.33.
-Accounting for $\sigma_{STA}$, we find that the $sigma_{LPD}=\sigma_{rgr1}=0.32$, an improvement over the fixed 56Tev directly incident simulation.
-For the high-multiplicity rejected events, we find the regressor has an error of $\sigma_{rejected1}=0.41$.
-
-For HESS2, the mean was 0.22 while the median was -0.09, leading to an even more skewed distribution.
-However the 68\% absolute fractional deviation was 0.29, and with $sigma_{STA}$, we find that $sigma_{LPD}=\sigma_{rgr2}=0.29$, slightly better than for HESS1.
-The improved performance can be explained by the matching energy distribution for the training and testing datasets.
-Higher-energy events have more background EAS light without consequently increased DC light, meaning the signal becomes harder to extract.
-The testing dataset has predominantly low-energy events, with reduced background.
-For the rejected events, we find that $\sigma_{rejected2}=0.63$, with $\sigma_{STA}$ being negligible.
-
-\begin{table}[h!]
-  \centering
-  \caption{Fractional error from $True_{DC}$ for all high-multiplicity test pixels}
-  \label{tab:altlpderror}
-  \begin{tabular}{ccc}
-    \toprule
-    & HESS1 & HESS2\\
-    \midrule
-    $\sigma_{rgr}$ & 0.32 & 0.29\\ 
-    $\sigma_{rejected}$ & 0.41 & 0.63\\ 
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-We can parameterise the error by considering the energy and distance to the core for a selection of DC pixels. We find that, for a fixed energy...
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{DCcounterrorhess1rgrbigtestdata}
-\caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left.
-In the top right the same is shown for events which were rejected.
-The true DC signals for events which passed the cuts is plotted against the reconstructed signals in the lower left, and for rejected events in the lower right.
-As in \ref{fig:cutdistribution}, in all plots a green event is one in which the DC pixel has been correctly identified, while a red event is one that has been incorrectly identified.}
-\label{fig:dcdiff}
-\end{center}
-\end{figure}
-
-\subsection{Other Stuff Like}
-Having obtained a parameterisation of the LPD, and and assoiated error in the case of a HESS-type array, the Charge reconstruction Technique can be applied to a simpified Monte Carlo simulation of the HESS array, developed as part of this analysis.
+\section{Monte Carlo Simulation}
+Having obtained a parameterisation for both the full and DC LPD, as well as the associated error in the case of a HESS-type array, the Charge reconstruction Technique can be applied to a simpified Monte Carlo simulation of the HESS array, developed as part of this analysis.
 Conducting a Monte Carlo simulation using the Gaussian-smeared LPD, we can measure the effectiveness of the LPD-reconstruction technique.
+The simulated Cosmic Rays must be high-multiplicity, and have a realistic distribution of energy and interaction height values.
 
@@
 Using the standard atmospheric tables, the corresponding height value can be found using exponential interpolation.
+The standard atmospheric data is included in the appendix.
 
@@
 
-But you lose the tail..
+Interpolating the value of the height neglects the fact that some cosmic rays which would not interact with the atmosphere before reaching the ground.
+The integrated interaction lengths are equal to about 850 at an altitude comparable to the HESS site.
+There is thus a probability of reaching the ground equal to $P = exp(\frac{-850}{12}) \approx 1.73 \times 10 ^{-31}$.
+It is thus reasonable to ignore this tiny fraction of events, and instead assume that every cosmic ray will interact at some point in the atmosphere.
 
@@
 However, when Cherenkov-Emitting events are considered, we have both a median and mean first interaction height of 30.3km, which clearly agrees with our expectations.
+Considering solely high-multiplicity events, we find that these have a mean height of $h \approx 23 \pm 5$ km, as shown in Figure \ref{fig:Hessheight}.
 
@@
 
-\subsection{First Interaction and Energy Saturation}
-Using the theoretical LPD found from the Frank-Tamm formula, we see that this LPD will have a very abrupt discontinuity.
-
-The mean first interaction height for all Cherenkov Emitting Cosmic Rays in the atmosphere is 40km, and neglecting variations in atmospheric density profiles around the Earth, this can be considered independent of experimental array.
-However, the multiplicity of event is determined by equipment efficiencies, altitude and telescope layout.
-When the HESS layout is simulated, we find that the 4 telescope events have a mean height of $h \approx 23 \pm 5$ km, as shown in \ref{fig:Hessheight}.
+MOAR!!!
 
@@
 We progressively increase the angular deviation until we have found the twenty most likely core position points.
+It is important to note that these core positions are simply starting points for a minimisation.
+The minimisation itself is allowed to float freely anywhere in the simulated target grid of $300 \times 300 = 90000 m^{2}$.
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{rawcoredistance}
+\caption{The distance from true core to the core reconstructed with the full-LPD is shown above. For four-telescope events, the standard deviation from true position is Xm. }
+\label{fig:rawcoredistance}
+\end{center}
+\end{figure}
+
 It is interesting to note that, for both variables, 5-telescope events have a lower deviation that 4-telescope events.
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{rawcoredistance}
+\subsection{Log Likelihood Minimisation}
+Having estimated the rough core position and energy, we would at this point use our regressor to determine the values of $candidate_{DCcount}$, based on the BDT-identified DC pixel and image parameters.
+Having done so, we know that these values would follow the regressor LPD.
+For the Monte-Carlo simulation, this step is bypassed, and the regressor LPD is instead directly simulated with a standard Gaussian smearing.
+Having quantified the expected deviation from the LPD under these conditions, this is a reasonable simplification that massively reduces the computing requirements for event simulation.
+This in turn enables us to consider a greatly expanded dataset for reconstruction attempts.
+
+In order to fully reconstruct the events, we need to find the x/y core position, the Energy per Nucleon, the first interaction height and the charge.
+We again consider the amount of DC light that each telescope receives to be Gaussian, with an expectation of $\mu(X, Y, Z, height, Epn)$ and a standard deviation of $\sigma(\mu)$.
+Ultimately the energy dependence of the LPD is almost negligible over the energy range, because variable $r_{max}$ is only weakly dependent on the energy.
+It thus makes little sense to attempt to reconstruct the energy a second time, when we would expect no discernible improvement over the reconstruction solely based on the Full Shower LPD that was performed before.
+We thus fix the cosmic ray energy as that found before, and instead consider a four-dimensional minimisation in Charge, x and y core position, and first interaction height.
+
+We then minimise the Log Likelihood function, where the total log likelihood for each telescope is equal to a sum of the full-shower LPD log likelihood and the DC LPD log likelihood.
+We are thus minimising a Likelihood function with nine or ten measurements from two broadly independent distributions.
+We consequently expect an improvement in the position reconstruction, as well as a measurement of the charge and the first interaction height.
+
+As before, we find that the discontinuous LPD leads to a frequent identification of local rather than global minima.
+To overcome this problem, we can iterate over a series of starting values for the parameters, with the aim of scanning the true minimum among the many minima found.
+In addition to the grid of likely positions identified for the Full-Shower LPD minimisation, we can can scan the integer Z values over the range $ 20 \leq Z \leq 32 $.
+It should be emphasised that the charge Z is treated as a free-floating parameter during the minimisation, and is able to vary freely within the range 16-36.
+Similarly, three first interaction heights in the range 20-30 km are scanned, but the value is able to vary freely in the range 15-65 km.
+It is purely due to computer resource restraints that \textquoteleft likely coordinates' in the parameter space are scanned as a starting point for a minimisation, rather than a uniformly distributed scan.
+Despite the simplifications, each minimisation process will still undergo $12 \times 20 \times 3 = 720$ iterations before a final reconstruction is complete.
+
+\subsection{Variable Resolution}
+If we compare the deviation from true core distance to each telescope, we can quantify the improvcement in core position reconstruction from minimisation based solely on the full-shower LPD.
+This is shown in Figure \ref{fig:coredistance}, and is directly comparable with the preliminary results in Figure \ref{fig:rawcoredistance}.
+As expected, the core distance resolution is reduced to X and Ym, and clear improvement over the previous measurements of core position.
+
+As an alternative metric for assessing reconstruction accuracy, we can calculate the absolute distance from the reconstructed core to the true core.
+The results of a binning of this distribution are shown in Figure \ref{fig:position}.
+It is found that, for both four and five telescope events, the core reconstruction is approximately $\sigma_{core} \approx 10m$.
+Most core positions are reconstructed less than 10m from the true position.
+This is extremely good, especially in comparison to the Hillas Reconstruction, where a core resolution of Y is more typical AND CITE!.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{coredistance}
 \caption{The distance from true core to the core reconstructed with the full-LPD is shown above. For four-telescope events, the standard deviation from true position is Xm. }
-\label{fig:rawcoredistance}
-\end{center}
-\end{figure}
-
-\subsection{Log Likelihood Minimisation}
-In order to fully reconstruct an event, we need to find the x/y core position, the Energy per Nucleon, the first interaction height and the charge.
-However, if one telescope in a five-telescope array does not observe DC light, this data point can be used to constrain the core position.
-Thus, for the LDF method to be applied, we require a minimum of five telescopes, four or more of which must image the DC light.
-We consider the amount of DC light that each telescope receives to be Gaussian, with an expectation of $\mu(X, Y, Z, height, Epn)$ and a standard deviation of $\sigma(\mu)$.
-
-\[  P_{i} ( N_{i, Received} \mid X, Y, Z, height, Epn )  =  \frac{1}{\sqrt{2 \sigma^{2} \pi}} \exp(-\frac{(N_{i, Received} - \mu)^{2}}{2 \sigma^{2}}) \].
-
-We then minimise the Log Likelihood function, assuming n is the total number of telescopes in the array.
-\[ - \ln(L) = - \sum_{i=1}^{n} \ln(P_{i}) =  \sum_{i=1}^{n} [ \frac{1}{2}\ln(2 \pi) + \ln(\sigma) + \frac{(N_{i, Received} - \mu)^{2}}{2 \sigma^{2}}]\]
+\label{fig:coredistance}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{position}
+\caption{The distance from true core position to the reconstructed core position is shown above. For four-telescope events, the standard deviation from true position is Xm.}
+\label{fig:position}
+\end{center}
+\end{figure}
 
@@
 Although this will in most cases tend to overestimate the spread of the data, it will also be sensitive to all increases in the proportion of correctly reconstructed events.
-
-\subsection{Iterative Scanning Minimisation}
-Through $\sigma_{Z}$ calculation, we find that the LDF method initially provides very poor charge reconstruction.
-This is as a result of varying Threshold Energies and the sharp drop in the LDF above the maximum radius, which means the Log Likelihood is frequently discontinuous within the parameter space.
-Consequently, a Minuit-type minimisation algorithm will only be able to find a local minimum near the starting values for the fit parameters.
-
-To overcome this problem, we can iterate over a series of starting values for the parameters, with the aim of scanning the true minimum among the many minima found.
-To simplify matters, we can scan only the integer Z values over the range $ 20 \leq Z \leq 32 $, rather than considering the charge to be a free floating parameter.
-
-In order to reduce the number of calculations needed, we can consider the core position region derived from camera images, as in Hillas Analysis.
-Each telescope will have a Gaussian smeared central axis indicating the direction of the core.
-We overlay the simulated telescope array with a grid of points with grid width 1m.
-Then we select all points satisfy the condition of lying within the shower axis direction confidence interval for every telescope.
-The angular width of the confidence interval from the shower axis will be determined by the precision of the telescopes.
-
-Having determined the relevant Height and Energy ranges, we can then consider combinations of Energy and Height for which the Energy is above the Cherenkov Emission Threshold (and is saturated!).
-This gives us a second set of starting \textquoteleft Coordinates \textquoteright.
-
-The Z value is fixed and the LL function is then minimised with the assigned starting values, with the other four variables allowed to float freely.
-Minimisation typically scans 13 Z values, 10 core position coordinates, and 50 Height/Energy coordinates, yielding $ 13 \times 10 \times 50 = 6500$ minimisations in total.
-Such a technique is resource intensive but reduces $\sigma_{Z}$ by a factor of 5 or more.
-(CHECK this quantitatively and get a graph yo.
-Want to see some plateauing of sigma Z!).
 
@@
 \subsection{Saturation Region Energies}
+Hillas reconstruction better
+Combine with Hillas reconstruction
 
@@
 Such an array may have a grid spacing of 20-50m, although further study is needed to determine the ideal layout.
+
+To get a more accurate estimate of the error, the testing set of 2000 events with varying azimuth/zenith was again considered.
+The fractional difference \[  \Delta = \frac{ candidate_{DC count} - True_{DC count}}{True_{DC count}} \] was binned in a histogram format, as shown in Figure \ref{fig:dcdiff}.
+It was observed that the mean was 0.09 and the median was -0.08, meaning the distribution was partially skewed.
+If the absolute deviation from the $True_{DC}$ value is considered, then 68\% of pixels have a fractional deviation less than 0.33.
+Accounting for $\sigma_{STA}$, we find that the $sigma_{LPD}=\sigma_{rgr1}=0.32$, an improvement over the fixed 56Tev directly incident simulation.
+For the high-multiplicity rejected events, we find the regressor has an error of $\sigma_{rejected1}=0.41$.
+
+For HESS2, the mean was 0.22 while the median was -0.09, leading to an even more skewed distribution.
+However the 68\% absolute fractional deviation was 0.29, and with $sigma_{STA}$, we find that $sigma_{LPD}=\sigma_{rgr2}=0.29$, slightly better than for HESS1.
+The improved performance can be explained by the matching energy distribution for the training and testing datasets.
+Higher-energy events have more background EAS light without consequently increased DC light, meaning the signal becomes harder to extract.
+The testing dataset has predominantly low-energy events, with reduced background.
+For the rejected events, we find that $\sigma_{rejected2}=0.63$, with $\sigma_{STA}$ being negligible.
+
+\begin{table}[h!]
+  \centering
+  \caption{Fractional error from $True_{DC}$ for all high-multiplicity test pixels}
+  \label{tab:altlpderror}
+  \begin{tabular}{ccc}
+    \toprule
+    & HESS1 & HESS2\\
+    \midrule
+    $\sigma_{rgr}$ & 0.32 & 0.29\\ 
+    $\sigma_{rejected}$ & 0.41 & 0.63\\ 
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{DCcounterrorhess1rgrbigtestdata}
+\caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left.
+In the top right the same is shown for events which were rejected.
+The true DC signals for events which passed the cuts is plotted against the reconstructed signals in the lower left, and for rejected events in the lower right.
+As in \ref{fig:cutdistribution}, in all plots a green event is one in which the DC pixel has been correctly identified, while a red event is one that has been incorrectly identified.}
+\label{fig:dcdiff}
+\end{center}
+\end{figure}
+\section{Bibliography}
 \bibliographystyle{unsrt}
 \bibliography{report}
+\section{Appendix}
+\subsection{Atmospheric Data Table for CORSIKA (Windhoek, Namibia)}
+\pgfplotstabletypeset{data/atmprof10.dat}
 \end{document}

### 2016-06-28 positioning/minimise.py

@@ -32,7 +32,7 @@ def min(fullsimulation, layout, gridwidth, raweff):
 	argumentx = "limit_x = (-300, 300), error_x = 100000, "
 	argumenty = "limit_y = (-300, 300), error_y = 100000, "
 	argumentZ = "limit_Z = (16,36), error_Z = 2, "
-	argumentheight = "limit_height = (17500, 70000), error_height=(100000), "
+	argumentheight = "limit_height = (15000, 65000), error_height=(100000), "
 	argumentE = "limit_Epn = (232, 4000), error_Epn=1000, "
 	argumenterror = "print_level=0, errordef = 100"
 
@@ -50,7 +50,7 @@ def min(fullsimulation, layout, gridwidth, raweff):
 	
 	minangle = 0.0
 	j = 0
-	
+	#~ 
 	while j < 20:
 		coordinates = []
 		j = 0
@@ -69,7 +69,7 @@ def min(fullsimulation, layout, gridwidth, raweff):
 							j+=1
 		if minangle > 20:
 			j=200
-		
+		#~ 
 	for [x, y] in coordinates:							
 			for e in evals:
 				m = eval("Minuit(full,  " + "Epn=" + str(e) + ", " + argumentE + "x="+ str(x) + ", " + argumentx + "y="+ str(y) + ", " + argumenty+ argumenterror + ")")
@@ -125,7 +125,7 @@ def min(fullsimulation, layout, gridwidth, raweff):
 			Ethreshold = float(cr.runemin(ri))
 			if float(Epn) > float(Ethreshold):
 				ehvals.append([Epn, height])
-	
+	#~ 
 	xycount = len(coordinates)			
 	ehcount = len(ehvals)
 	zcount = len(zvalues)
@@ -133,7 +133,8 @@ def min(fullsimulation, layout, gridwidth, raweff):
 	
 	print ehvals
 		
-	print measured.DCmultiplicity, "Detections -> ", xycount, "Valid Core Positions (", minangle, "Degrees from recorded axis)", ehcount, "Valid Height/Epn Combinations", zcount, "Charge Values", xycount*ehcount*zcount, "Total Minimisations"
+	print measured.DCmultiplicity, "Detections -> "
+	print xycount, "Valid Core Positions (", minangle, "Degrees from recorded axis)", ehcount, "Valid Height/Epn Combinations", zcount, "Charge Values", xycount*ehcount*zcount, "Total Minimisations"
 	
[…]

### 2016-06-28 positioning/optimisez.py

@@ -81,6 +81,8 @@ def run(statsset, mindetections):
 				bdtcuts.append(BDTcut)
 				meansigmas.append(meansigma)
 				
+				
+				
 				if float(frac) > float(0.2):
 					if float(24) < float(meanz) < float(28):
 						if float(meansigma) < float(lowestsigma):

### 2016-06-28 positioning/plotcoredistance.py

@@ -74,8 +74,11 @@ def run(statsset, mindetections, cuts):
 			sigma = 0.5*(upperz-lowerz)
 			
 			fraction = float(passing)/float(full)
-			info += str("For N = " + str(j) + " we require BDT >  " + str('{0:.2f}'.format(bdtmin)) + "\n ")
-			info += str("Fraction passing is " + str('{0:.2f}'.format(fraction)) + "\n")
+			if fraction < 1.0:
+				info += str("For N = " + str(j) + " we require BDT >  " + str('{0:.2f}'.format(bdtmin)) + "\n ")
+				info += str("Fraction passing is " + str('{0:.2f}'.format(fraction)) + "\n")
+			else:
+				info += str("For N = " + str(j) + ":\n ")
 			info += ('Lower = ' + str('{0:.2f}'.format(lowerz)) + " \n")
 			info += ('Median = ' + str('{0:.2f}'.format(meanz)) + " \n")
 			info += ('Upper = ' + str('{0:.2f}'.format(upperz)) + " \n")
@@ -123,13 +126,15 @@ def run(statsset, mindetections, cuts):
 	plt.title("Distance Reconstruction")
 	plt.legend()
 	
+	plt.annotate(info, xy=(0.05, 0.6), xycoords="axes fraction",  fontsize=15)
 	if cuts == None:
 		plt.savefig('/d6/rstein/Hamburg-Cosmic-Rays/report/graphs/rawcoredistance.pdf')
 		path = '/d6/rstein/Hamburg-Cosmic-Rays/positioning/graphs/rawcoredistance.pdf'
 	else:
+		plt.savefig('/d6/rstein/Hamburg-Cosmic-Rays/report/graphs/coredistance.pdf')
 		path = '/d6/rstein/Hamburg-Cosmic-Rays/positioning/graphs/coredistance.pdf'
 	
-	plt.annotate(info, xy=(0.05, 0.6), xycoords="axes fraction",  fontsize=15)
+	
 	plt.savefig(path)
 	print "saving to", path
 	plt.close()

### 2016-06-28 positioning/plotposition.py

@@ -61,8 +61,11 @@ def run(statsset, mindetections, cuts):
 			sigma = specificcount[upper]
 			
 			fraction = float(passing)/float(full)
-			info += str("For N = " + str(j) + " we require BDT >  " + str('{0:.2f}'.format(bdtmin)) + "\n ")
-			info += str("Fraction passing is " + str('{0:.2f}'.format(fraction)) + "\n")
+			if fraction < 1.0:
+				info += str("For N = " + str(j) + " we require BDT >  " + str('{0:.2f}'.format(bdtmin)) + "\n ")
+				info += str("Fraction passing is " + str('{0:.2f}'.format(fraction)) + "\n")
+			else:
+				info += str("For N = " + str(j) + ":\n ")
 			info += ('Median = ' + str('{0:.2f}'.format(meanz)) + " \n")
 			info += ('Sigma = ' + str('{0:.2f}'.format(sigma)) + "\n \n")
 	
@@ -108,13 +111,14 @@ def run(statsset, mindetections, cuts):
 	plt.title("Distance Reconstruction")
 	plt.legend()
 	
+	plt.annotate(info, xy=(0.75, 0.6), xycoords="axes fraction",  fontsize=15)
 	if cuts == None:
 		plt.savefig('/d6/rstein/Hamburg-Cosmic-Rays/report/graphs/rawposition.pdf')
 		path = '/d6/rstein/Hamburg-Cosmic-Rays/positioning/graphs/rawposition.pdf'
 	else:
+		plt.savefig('/d6/rstein/Hamburg-Cosmic-Rays/report/graphs/position.pdf')
 		path = '/d6/rstein/Hamburg-Cosmic-Rays/positioning/graphs/position.pdf'
 	
-	plt.annotate(info, xy=(0.75, 0.6), xycoords="axes fraction",  fontsize=15)
 	plt.savefig(path)
 	print "saving to", path
 	plt.close()

### 2016-06-29 report/draft1.tex
Backup 29/06/16

@@
 \section{Preface}
-I basically just did everything. It was great.
+The basis of this thesis work can be divided into two halves.
+The first half is the simulation of cosmic ray HESS camera images, and analysis work based on these images.
+The second half is a Monte Carlo study simulating air shower intensities, based entirely on function fitted from the HESS camera images.
+
+It is important to note that the simulation of cosmic ray air showers for the first part of my thesis was performed using the CORSIKA software \cite{Heck98}, and the resultant HESS camera images were produced using the Sim\textunderscore Tel array software \cite{Bernlohr08}.
+I claim no credit for the complex simulations that these packages have enabled me to perform.
+
+Additionally, a significant portion of this work relies on Supervised machine learning that was performed using the SciKit learn package \cite{scikit-learn}.
+Although I wrote the relevant Python scripts to facilitate data categorisation and algorithm training, the package acts as a black box to convert training data into a functioning Boosted Decision Tree.
+I would like to make clear that I am indebted to those who produced this package, without whom this analysis could not have been performed.
+
+Aside from this, all other work in this thesis is my own. I wrote all necessary code for the Monte Carlo simulation, and it was conducted entirely by me. Similarly
+
+Thank Dieter, and Attilla, and...
 \newpage
@@
 \section{Introduction}
+Cosmic Rays are abundant in our galaxy, and enter the Earth's upper atmosphere from every direction.
+Their flux is governed by a well-defined energy power law, which is almost unchanged across more than 10 orders of magnitude \cite{Blasi:2013rva}.
+Cosmic Rays are in fact not rays but rather charged particles, primarily protons, which have been accelerated by various galactic or stellar processes.
+The exact cosmic ray composition is energy dependent, and provides information regarding the source of cosmic rays.
+Heavy cosmic rays, the most common of which is iron, vary substantially in relative abundance for different energy scales.
+
+Being highly-energetic charged particles, Cosmic rays will often travel through the atmosphere faster than the local speed of light.
+Consequently, many Cosmic Rays will emit Cherenkov light over substantial distances, and this light will be visible on the ground.
 There are numerous Telescope Arrays which image the Cherenkov Light emitted by Cosmic Rays in the atmosphere, including the HESS, MAGIC and VERITAS Experiments.
-All rely on Hillas Analysis with extracted parameters from each of the camera images being used to reconstruct the events, but heavy atmospheric blurring means that charge resolution is very poor.
+Although the number of emitted photons is comparatively small, the Cherenkov light is still brighter than the night sky background because the telescopes are able to capture images with an exceptionally short recording time, equal to 80ns for the HESS array \cite{Funk:2004ie}.
+The Cherenkov photons all arrive almost simultaneously, so have a high intensity over the short time window during which the image is formed.
+
+All telescope arrays rely on Hillas Analysis with extracted parameters from each of the camera images being used to reconstruct the events, but heavy atmospheric blurring means that charge resolution is very poor.
 For Iron Nucleus events, we would expect to reconstruct \[Z \approx 26 \pm 5 \] with a core position resolution of roughly $d \approx 20 m $ \cite{hess07}.
-
-Cosmic Rays that are imaged by these telescopes have energies between $13 $TeV and $200 $TeV.
-At present, no study of the relative abundance of different cosmic ray elemental abundances exists at these energies.
-It could provide important clues regarding the mechanism of Cosmic Ray formation and propagation in the galaxy, but current charge resolution from Hillas Analysis is not small enough to undertake such a study.
-
-Instead of Hillas Analysis, we consider a new method for event reconstruction, in which we fit the known Direct Cherenkovn (DC) Light observed by each telescope to a characteristic Lateral Photon Distribution (LPD) function.
-This new technique is valid both for currently running experiments, as well as planned experiments such as the Cherenkov Telescope Array (CTA).
-It uses only the information from the DC Pixel identified in the shower images.
+The Cosmic Rays imaged by these telescopes have energies between $13-200 $TeV, and at present, no study of the relative abundance of different cosmic ray elemental abundances exists at these energies.
+If the telescope arrays could be used to spectroscopically analyse the Cosmic rays, it could provide important clues regarding the mechanism of Cosmic Ray formation and propagation in the galaxy.
+However, current charge resolution from Hillas Analysis is not small enough to undertake such a study.
+The principal goal of this thesis is to enable spectroscopic analysis with Cherenkov Telescope arrays, by improving the charge resolution of reconstructed events.
 
@@
 Thus, if the LPD method can achieve this core position resolution, the precision will be sufficient to extract the abundances of the different Cosmic Ray Elements.
-This the prime motivation for the new LPD technique.
-
-In order to reconstruct events using the LPD method, we require saturation of the Cosmic Ray Energy, and that the event can be seen by at least 4 telescopes.
-
-The Cosmic Rays follow a well-defined power law where $ \frac{dN(E)}{dt} \propto E^{-\gamma} $ and experimentally $ \gamma = 2.7 \pm ?
-$.
-Consequently higher energy Cosmic Rays are heavily suppressed.
-The Energy Threshold for Cherenkov Light Emission as a function of height is illustrated in \ref{fig:generalenergy}.
+
+Instead of Hillas Analysis, we will consider a new method for event reconstruction, in which we fit the known Direct Cherenkov (DC) Light observed by each telescope to a characteristic Lateral Photon Distribution (LPD) function.
+This new technique is valid both for currently running experiments, as well as planned experiments such as the Cherenkov Telescope Array (CTA).
+It uses only the information from the DC Pixel identified in the shower images.
+Possible improvement in core resolution is the prime motivation for the new LPD technique.
+
+To understand why an LPD exists, it is important to recall that Cherenkov emission begins when a charged particle passes the local speed of light in a medium.
+We know that the refractive index of air is proportional to the density of air.
+Thus, the minimum velocity needed for Cherenkov Emission is lower for low atmospheric altitudes, because the air is denser.
+If the velocity is sufficient, we will observe photon emission from the particle at the Cherenkov Angle $\theta_{c}$.
+
+\[ \cos(\theta_{c}) = \frac{1}{\eta \beta}  \Longrightarrow \beta_{min} \geq \frac{1}{\eta}\]
+
+We obviously require that the Cherenkov Angle is real, so then require $\cos(\theta_{c}) \leq 1$.
+The minimum required velocity $\beta_{min}$ is thus equal to the inverse of the local refractive index $\eta$.
+The velocity of a particle is a function of its energy, determined with the relations $\gamma = \frac{E}{m_{0} c^{2}}$ and $\beta^{2} = 1 - \frac{1}{\gamma ^{2}}$.
+Thus, we find that the minimum velocity ultimately leads to an Energy per unit mass threshold.
+If we assume that the slight difference in proton and neutron mass is negligible here, than we can determine a local energy per nucleon threshold that will be valid for all Cosmic Rays passing a given atmospheric altitude.
+
+The Energy per Nucleon Threshold for Cherenkov Light Emission as a function of height is illustrated in \ref{fig:generalenergy}.
 Once the Energy of a Cosmic Ray exceeds the local Cherenkov Energy Threshold of the atmosphere, the Nucleus will begin emitting a ring of Cherenkov Light.
+Then for a given Telescope Array altitude above sea level and a given height h, simple trigonometry yields the final radius of emission on the ground:
+\[ Radius(h) = \tan (\theta_{C}(h)) \times (h - altitude_{array})\]
+
+The refractive index as a function of height is shown in as seen in Figure \ref{fig:lpd}, using standard values listed in the appendix.
+Because the refractive index of air increases very quickly as the height decreases, the Cherenkov Angle $\theta_{C}$ will also increase rapidly with decreasing height.
+Thus, although the displacement $(h - altitude_{array})$ decreases as the height, the radius on the ground increases as height decreases.
+Consequently the upper atmosphere emission contributes to the inner LDF, while the lower atmosphere emission contributes to the outer LDF.
+As the cosmic ray travels down through the atmosphere, Cherenkov Emission continuously illuminates new areas on the ground that were previously unlit, without re-illuminating inner regions.
+
+Emission continues until the first interaction with the atmosphere, occurring at a randomly distributed height we call $h_{int}$.
+The maximum radius of the DC light will then be $r_{max} = Radius(h_{int})$.
+This is extremely useful, because for all distances up to $r_{max}$, the LPD will be completely independent of the emission height.
+One full parameterisation of the LPD will thus be valid for all heights, provided the maximum radius is known.
 
@@
 If we divide the number of emitted photons by the area of the annulus between the ring radii at $h$ and $h - \Delta_{h}$, we retrieve the LDF shown in \ref{fig:lpd}, which varies with $ \rho_{DC}  = f(r) \times Z^{2}$ .
-Thus the amplitude of the LDF is proportional to the charge of the Cosmic Ray, enabling the Charge to be determined from the DC emission.
-This is the basis for charge reconstruction in the LDF method.
+Thus the amplitude of the LDF is proportional to the square of the Cosmic Ray charge, enabling us to reconstruct this number from the DC emission.
+This proportionality is the basis for charge reconstruction in the LDF method.
 
@@
 \includegraphics[height=0.9\textheight]{simulatedlpd}
-\caption{The LPD obtained from simulation of an Iron Nucleus up to a first interaction height of 25km for a range of Core Energies.
+\caption{Above, the refractive index is shown with both linear and exponential interpolation between the known values.
+The LPD obtained from simulation of an Iron Nucleus up to a first interaction height of 25km for a range of Core Energies.
 An altitude of 1.8km for the experimental array is assumed.
@@
 
-The Refractive Index of the atmosphere, and thus the Cherenkov angle $\theta_{C}$, increases as the altitude decreases.
 The refractive index at a series of heights, based on data from the HESS site, is shown \ref{fig:lpd}.
@@
 
-Emission continues until the first interaction with the atmosphere, occurring at a randomly distributed height we call $h$.
-Then for a given Telescope Array altitude above sea level, simple trigonometry yields the radius of the LDF on the ground:
-\[ Radius(height = altitude_{array}) = \tan [\theta_{C}(h)] \times (h - altitude_{array})\]
-
-Thus the upper atmosphere emission contributes to the inner LDF, while the lower atmosphere emission contributes to the outer LDF.
-As the cosmic ray travels down through the atmosphere, Cherenkov Emission continuously illuminates new areas on the ground that were previously unlit, without re-illuminating inner regions.
-This is extremely useful, because it means that for all distances up to the maximum radius, the LPD will be completely independent of the emission height.
-One full parameterisation of the LPD will thus be valid for all heights, provided the maximum radius is known.
-
-We can also see ground emission radius as a function of height in \ref{fig:generalenergy}.
+We can also see ground emission radius as a function of height in Figure \ref{fig:generalenergy}.
 We find that the high-radius emission (occurring near the first interaction region) varies little between different high energies.
 We deem this to be \textquoteleft Saturated Emission\textquoteright.
-
-To accurately quantify Saturated Emission, we can compare the photon density to the theoretical maximum photon density, corresponding to an infinite-energy particle with $\beta =1$.
+To accurately quantify Saturated Emission, we can compare the photon density to the theoretical maximum photon density, corresponding to an infinite-energy particle with $\beta =1$ in Figure \ref{fig:lpd}.
 The illustrated maximum is useful as a reference, although because the atmosphere is not modelled beyond an altitude of 120km, the small-radius emission is not accurately simulated entirely correctly.
 However, real cosmic rays in the considered energy regime will all cross the emission threshold and begin emission at an altitude much lower than 120km, so can be considered accurately modelled.
-Absorption WAS/WAS NOT modelled.
-
-However, in the 4 telescope height region, the Cherenkov Threshold Energy is $ E_{Threshold} \approx 0.35$ TeV per Nucleon as shown in \ref{fig:lpd}!
-The saturation in for these heights occurs roughly at 0.7 TeV per Nucleon or something...
-
-We need four-telescope events or something.
+
+The salient point is that there is a clear characteristic photon distribution that, for energies above 25 TeV at least, is almost constant except for a varying endpoint.
+However, we will not be able to directly measure this LPD.
+Instead, a telescope images containing air showers must be analysed, and from these images, we can infer the quantity of DC light present amongst a large degree of background.
+Extensive simulations of Camera images will be performed, in order to quantify the resultant LPD extracted from the telescope images.
+After determining a likely experimental LPD, Monte Carlo events can be simulated, and then reconstructed.
+
+To reconstruct an event, we will need to find the \textquoteleft Core position' of the Cosmic Ray, which is defined as the position on the ground through which the Cosmic Ray would pass if it continued in a straight line to the ground.
+In addition, we will need to determine the Energy, first interaction height, and the charge.
+We would normally require at least five data points in order to reconstruct these variables.
+However, it is possible to use the non-observation of light in one telescope to constrain the core position.
+Thus, we require that an  event was be seen by at least four telescopes for a five-telescope array such as HESS.
 
@@
 On the basis of efficiency calculations in DC pixel identification, it is clear that 2.2\% of Iron Ray events will produce high-multiplicity DC pixels accepted by the BDT.
-Thus, we will ultimately obtain an hourly flux of $F(35-135TeV) = 4.4 \times 10^{-4} s^{-1} = 1.58 h^{-1}$ high-multiplicity Iron events.
+Thus, we will ultimately obtain an hourly flux of $F(35-135TeV) = 4.84 \times 10^{-3} s^{-1} = 17.4 h^{-1}$ high-multiplicity Iron events.
 
@@
 \[ F(R) = F(En(R)-135TeV) = \int_{En(R)}^{135} \phi_{0} E^{-2.76} dE =\frac{\phi_{0}}{1.76}[En(R)^{-1.76} - 135^{-1.76}]= R \times F(35-135TeV)\] \[\Longrightarrow  En(R) = (\frac{1.76\times R \times F(35-135TeV)}{\phi_{0}} +135^{-1.76})^{\frac{-1}{1.76}} \]
+
+RATES!!!
 
@@
 The resulting fraction error in energy distribution is shown below in Figure \ref{fig:rawepn}.
-It is clear that the energy reconstruction is fairly good, with a fractional standard deviation of roughly 0.10 when both four and five telescope events are considered.
+Under the assumption of a gaussian distribution, we can calculate the mean fractional deviation as half of the distance between the 16th and 84th centiles of data.
+We sort each fractional deviation, and expect that 68\% of events will lie between these values.
+Using this method, it is clear that the energy reconstruction is fairly good, with a fractional standard deviation of roughly 0.10 when both four and five telescope events are considered.
 We find that the position is also reconstructed, with an accuracy of .
@@
 A graph showing the difference between the distance from telescope to true core position, and the distance from telescope to this reconstructed core position.
-The standard deviation from the true core distance  is 10m for 5 telescope events, and 16m for four telescope events.
+Using the same 68\% method, the standard deviation from the true core distance  is 10m for 5 telescope events, and 16m for four telescope events.
 A better estimate for the core position will take into account the DC LPD as well as the full LPD.
@@
 
-As an alternative metric for assessing reconstruction accuracy, we can calculate the absolute distance from the reconstructed core to the true core.
-The results of a binning of this distribution are shown in Figure \ref{fig:position}.
-It is found that, for both four and five telescope events, the core reconstruction is approximately $\sigma_{core} \approx 10m$.
-Most core positions are reconstructed less than 10m from the true position.
-This is extremely good, especially in comparison to the Hillas Reconstruction, where a core resolution of Y is more typical AND CITE!.
-
 \begin{figure}
@@
 
+As an alternative metric for assessing reconstruction accuracy, we can calculate the absolute distance from the reconstructed core to the true core.
+The results of a binning of this distribution are shown in Figure \ref{fig:position}.
+Because we consider absolute distance, this value can never be negative.
+Thus, we calculate a one-sided distribution standard deviation, and consider the value of an event in the 68th centile to be equal to the standard deviation.
+It is found that, for both four and five telescope events, the core reconstruction is approximately $\sigma_{core} \approx 10m$.
+Most reconstructed core positions thus lie less than 10m from the true position.
+This is extremely good, especially in comparison to the Hillas Reconstruction, where a core resolution of Y is more typical AND CITE!
+
 \begin{figure}
@@
 
-\subsection{Extracting Charge Resolution}
-Having reconstructed many events, we can then derive the $\sigma_{Z}$ of the dataset, giving us a number to directly compare the quality of event reconstruction.
-However, a simple Gaussian 68\% method will yield only half integer values of $\sigma_{Z}$ and very frequently 0.
-This will be unhelpful for comparisons of minor modifications of reconstruction methods.
-
-Instead, we can assume a Gaussian with tails at the highest and lowest reconstructed charge values in the dataset.
-The size of the dataset can be used to calculate the fraction of events that the extreme values represent, and this probability can be converted into a \textquoteleft number of standard deviations from mean'.
-Dividing the Gaussian total width by the number of standard deviations gives us a value for $\sigma$.
-Although this will in most cases tend to overestimate the spread of the data, it will also be sensitive to all increases in the proportion of correctly reconstructed events.
+We can similarly consider the resolution of reconstructed height.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{rawheight}
+\caption{The distance from true core position to the reconstructed core position is shown above. For four-telescope events, the standard deviation from true position is Xm.}
+\label{fig:height}
+\end{center}
+\end{figure}
+
+Having taken into account our various variable uncertainties, we can also consider our most important variable.
+In Figure \ref{fig:rawZ} the reconstructed charge number is binned in integers, illustrating the element that each reconstructed event would be assigned to.
+As we would hope, there is a very clear peak centered on Z=26, and the median charge value lies very close to this value.
+The distributions are broadly symettric, and have a charge resoultion of $\sigma_{Z} = 1.1$ and $\sigma_{Z} = 2.2$ for five and four telescope events respectively.
+Unsurprisingly, the charge resolution is better for five-telescope events, but both cases represent a significant improvement over the existing charge resolution obtained through Hillas analysis.
+With the reasonably high event rate, we could certainly expect to see such a peak in the existing HESS data, and the uncertainty well be small enough to enable spectroscopic analysis.
+Obtaining such a peak is a vindication of the LPD method, and demonstrates its superior performance for event reconstruction.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{rawZ}
+\caption{The distance from true core position to the reconstructed core position is shown above. For four-telescope events, the standard deviation from true position is Xm.}
+\label{fig:rawZ}
+\end{center}
+\end{figure}
 
@@
 We find that the $\sigma_{Z}$ of the remaining \textquoteleft Test' Monte Carlo data is reduced when the same BDT cut is applied.
-
-\subsection{Reconstructed Charge Resolution}
-In the preliminary HESS simulation, it was found that the 4 telescope event reconstruction had a charge resolution of $\sigma_{Z} = 1.4$.
-However, requiring that the BDT signal probability satisfied $P > 0.81$ removed $75 \%$ of events, while reducing the Charge resolution to $\sigma_{Z} = 0.9$ .
-With this cut, core position resolution was $d \approx 1.4 m $.
-For 5 telescope events, it was found that the charge resolution was also $\sigma_{Z} = 1.4$.
-However, requiring that the signal probability satisfied $P > 0.05$ removed $53 \%$ of events, including all wrongly reconstructed ones.
-This placed an upper limit on the charge resolution of $\sigma_{Z} < 0.35$ .
-With this cut, core position resolution was $d \approx 0.8 m $.
 
@@
 Combine with Hillas reconstruction
+Apply to HESS data
+calibrate with position of Iron peak
 

### 2016-07-01 report/draft1.tex
Backup 01/07/16

@@
-\documentclass{article}
+\documentclass[11pt]{article}
 \usepackage{graphicx}
@@
 \section{Introduction}
-Cosmic Rays are abundant in our galaxy, and enter the Earth's upper atmosphere from every direction.
+Cosmic Rays are abundant in our solar system, entering the Earth's upper atmosphere from every direction.
+Cosmic Rays are in fact not rays but rather charged particles, primarily protons, which have been accelerated by various galactic or stellar processes.
 Their flux is governed by a well-defined energy power law, which is almost unchanged across more than 10 orders of magnitude \cite{Blasi:2013rva}.
-Cosmic Rays are in fact not rays but rather charged particles, primarily protons, which have been accelerated by various galactic or stellar processes.
-The exact cosmic ray composition is energy dependent, and provides information regarding the source of cosmic rays.
-Heavy cosmic rays, the most common of which is iron, vary substantially in relative abundance for different energy scales.
-
-Being highly-energetic charged particles, Cosmic rays will often travel through the atmosphere faster than the local speed of light.
-Consequently, many Cosmic Rays will emit Cherenkov light over substantial distances, and this light will be visible on the ground.
+The exact Cosmic Ray composition is energy dependent, and provides information regarding their sources.
+Heavy Cosmic Rays, the most common of which is iron, vary substantially in relative abundance for different energy scales.
+
+Being highly-energetic charged particles, Cosmic Rays will often travel through the atmosphere faster than the local speed of light.
+Consequently, many will emit substantial Cherenkov light, and this light will often be visible on the ground.
 There are numerous Telescope Arrays which image the Cherenkov Light emitted by Cosmic Rays in the atmosphere, including the HESS, MAGIC and VERITAS Experiments.
-Although the number of emitted photons is comparatively small, the Cherenkov light is still brighter than the night sky background because the telescopes are able to capture images with an exceptionally short recording time, equal to 80ns for the HESS array \cite{Funk:2004ie}.
-The Cherenkov photons all arrive almost simultaneously, so have a high intensity over the short time window during which the image is formed.
-
-All telescope arrays rely on Hillas Analysis with extracted parameters from each of the camera images being used to reconstruct the events, but heavy atmospheric blurring means that charge resolution is very poor.
+Although the number of emitted photons is comparatively small, the Cherenkov light is still distinguishable from the night sky background because the telescopes are able to capture images with an exceptionally short recording time.
+The Cherenkov photons all arrive almost simultaneously, so have a high intensity during the short time window when the image is formed.
+For the HESS array, this window is equal to 80ns \cite{Funk:2004ie}.
+
+All such telescope arrays currently rely on Hillas Analysis to fully reconstruct the events, including the  charge Z of the Cosmic Ray.
+Hillas Analysis relies on extracted parameters from each of the camera images, but heavy atmospheric blurring of these images means that charge resolution is very poor.
 For Iron Nucleus events, we would expect to reconstruct \[Z \approx 26 \pm 5 \] with a core position resolution of roughly $d \approx 20 m $ \cite{hess07}.
-The Cosmic Rays imaged by these telescopes have energies between $13-200 $TeV, and at present, no study of the relative abundance of different cosmic ray elemental abundances exists at these energies.
-If the telescope arrays could be used to spectroscopically analyse the Cosmic rays, it could provide important clues regarding the mechanism of Cosmic Ray formation and propagation in the galaxy.
+The Cosmic Rays imaged by these telescopes have energies in TeV scale, and at present, no study of the relative abundance of different cosmic ray elemental abundances exists at these energies.
+If the telescope arrays could be used to spectroscopically analyse the Cosmic Rays, it could provide important clues regarding the mechanism of Cosmic Ray formation and propagation in the galaxy.
 However, current charge resolution from Hillas Analysis is not small enough to undertake such a study.
@@
 
-A theoretical study by Kieda in 2001 \cite{kieda01} suggested that for a core position resolution of $d \approx 5 $ m, we could expect to see a charge resolution of $ \sigma_{Z} \approx 1 $ for elements of $Z = 20$ or higher.
+A theoretical study by Kieda in 2001 \cite{kieda01} suggested that, with a core position resolution of $d \approx 5 $ m, we could expect to see a charge resolution of $ \sigma_{Z} \approx 1 $ for elements of $Z = 20$ or higher.
 In this case the core position resolution would be the limiting value.
@@
 
-To understand why an LPD exists, it is important to recall that Cherenkov emission begins when a charged particle passes the local speed of light in a medium.
+To fully reconstruct an event, we will need to find the charge, energy and the core position coordinates.
+In addition, we will need to determine the height of the first atmospheric interaction.
+We would normally require at least five data points in order to reconstruct these variables.
+However, it is possible to use the non-observation of light in one telescope to constrain the core position.
+Thus, we require that an event was be seen by at least four telescopes for a five-telescope array such as HESS.
+
+\section{DC Pixel Identification}
+Cosmic Rays will emit Direct Cherenkov (DC) light in the upper atmosphere, before generating an Extended Air Shower (EAS) through interaction with the lower atmosphere.
+In telescope images, the DC light is usually concentrated in a single  \textquoteleft DC pixel'.
+Identifying this pixel is challenging, because the brighter EAS Cherenkov light background often overlaps with the DC pixel.
+In order to apply the LPD method to data, we must first identify the DC pixel in a shower image, and determine the number of DC photoelectrons present.
+
+\subsection{Theoretical LPD}
+To understand why DC light has a characteristic distribution, it is important to recall that Cherenkov emission begins when a charged particle passes the local speed of light in a medium.
 We know that the refractive index of air is proportional to the density of air.
@@
 
-\[ \cos(\theta_{c}) = \frac{1}{\eta \beta}  \Longrightarrow \beta_{min} \geq \frac{1}{\eta}\]
+\[ \cos(\theta_{c}) = \frac{1}{\eta \beta}  \Longrightarrow \beta \geq \frac{1}{\eta}\]
 
@@
 
-The salient point is that there is a clear characteristic photon distribution that, for energies above 25 TeV at least, is almost constant except for a varying endpoint.
+We see that there is a clear characteristic photon distribution which, for energies above 25 TeV, is almost constant except for a varying endpoint.
 However, we will not be able to directly measure this LPD.
@@
 
-To reconstruct an event, we will need to find the \textquoteleft Core position' of the Cosmic Ray, which is defined as the position on the ground through which the Cosmic Ray would pass if it continued in a straight line to the ground.
-In addition, we will need to determine the Energy, first interaction height, and the charge.
-We would normally require at least five data points in order to reconstruct these variables.
-However, it is possible to use the non-observation of light in one telescope to constrain the core position.
-Thus, we require that an  event was be seen by at least four telescopes for a five-telescope array such as HESS.
-
-\section{DC Pixel Identification}
-\textbf{Cosmic Rays will emit Direct Cherenkov (DC) light in the upper atmosphere, before generating an Extended Air Shower (EAS) through interaction with the lower atmosphere. }
-
-In telescope images, the DC light is usually concentrated in a single  \textquoteleft DC pixel'.
-Identifying this pixel is challenging, because the brighter EAS Cherenkov light background often overlaps with the DC pixel.
-In order to apply the LPD method to data, we must first identify the DC pixel in a shower image, and determine the number of DC photoelectrons present.
-
-We define the variable $Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity}$ as the ratio of the largest neighbouring pixel intensity to the intensity of a given pixel.
+\subsection{Image Simulation}
+We can find the DC pixel by defining the variable $Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity}$ as the ratio of the largest neighbouring pixel intensity to the intensity of a given pixel.
 In previous experiments, the DC pixel candidate was identified by applying a number of cuts to pixels in an image \cite{hess07}, and from the subset of pixels passing the specified cuts, selecting the pixel with the smallest $Q_{DC}$ as the \textquoteleft DC candidate'.
@@
 
-\subsection{Image Simulation}
-The full simulation of air showers was performed using the CORSIKA package, with a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
+The full simulation of air showers was performed using the CORSIKA package with a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
+This Atmospheric Profile is included in the Appendix.
 In total, 5000 training events and a further 10000 testing events were simulated.
-The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi(E) \propto E^{-2.7}$.
+The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a flux spectrum $\phi(E) \propto E^{-2.7}$.
 For each set of simulated event, 4 unique random number seeds were used to generate the shower.
@@
 
+\subsection{Low-Energy Emission}
+In the theoretical simulation of the LPD, we noted that the distribution in Figure \ref{fig:lpd} is only saturated in the region of around 35 TeV.
+Below this, the LPD is more heavily dependent on Energy, and thus our basic assumption of a characteristic equation will no longer be valid.
+To account for this, an additional simulation of 15000 Iron events was conducted in the energy range 5-135TeV.
+The BDT remained the same, and the same initial cuts were replicated as before.
+The same was also done for Protons in the same energy range.
+The results are summarised in Table \ref{tab:fullironacceptance}.
+
+\begin{table}[h!]
+  \centering
+  \caption{Comparison of Proton and Iron Acceptance}
+  \label{tab:fullironacceptance}
+  \begin{tabular}{ccc}
+    \toprule
+    & HESS1  & HESS2 \\
+    \midrule
+    Proton Pixels Accepted after All Cuts(\%) & 0.21 & 0.19\\
+    Sample Purity (\%) & 1.74 & 0.00 \\
+    \midrule
+    Iron Pixels Accepted after All Cuts(\%) & 0.17 & 0.11\\
+    Sample Purity (\%) & 80.00 & 80.00 \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+We find that, for Iron Events, the acceptance rate falls by a factor of approximately 15.
+The relative proportion of HESS 1 to HESS 2 acceptance is broadly maintained at a factor of roughly 1.5, although the sample purity falls somewhat.
+If we account for the differing intergrated flux rate, we can calculate the ratio of expected high-multiplicity event rate $\Gamma_{HM}(E)$ for the ranges 5-135 TeV and 35-135 TeV.
+
+\[ \frac{\Gamma_{HM}(5-135)}{\Gamma_{HM}(35-135)} = \frac{5^{-1.7} - 135^{-1.7}}{35^{-1.7} - 135^{-1.7}} 
+= 30.3 \]
+
+Thus, if we have thirtyfold increase in event rate, but only one-fifteenth the acceptance rate, we would ultimately expect that we would have twice as many Iron Events if the full energy range of 5-135 TeV was included.
+However, the low-energy proton acceptance is much higher.
+Thus, were we to include events in this energy range, we would again retrieve a sample dominated by protons that will not be correctly reconstructed.
+The energy distribution of the Protons and Iron Events are shown in FIG.
+To remove this contamination from protons and non-saturated Iron events, we thus apply one additional Energy cut on the data sample.
+We simply require that the reconstructed Energy is greater than 30TeV.
+This will, assuming a rough energy resolution of around 15\% in reconstruction, remove the majority of these low-energy events.
+(WILL CONFIRM ONCE HISTOGRAMS ARE RETRIEVED).
+
 \section{HESS-type Event Simulation}
@@
 We can consider an identical $90000 m^{2}$ target region for core position simulation.
-The HESS telescope additionally has a solid and field of view of 5 degrees (0.09 rad),meaning an expected telescope array Iron Flux of $F(35-135TeV) = 0.22 s^{-1}$.
+The HESS telescope additionally has a solid and field of view of 5 degrees (0.006 steradians),meaning an expected telescope array Iron Flux of $F(35-135TeV) = 0.0154 s^{-1}$.
 On the basis of efficiency calculations in DC pixel identification, it is clear that 2.2\% of Iron Ray events will produce high-multiplicity DC pixels accepted by the BDT.
-Thus, we will ultimately obtain an hourly flux of $F(35-135TeV) = 4.84 \times 10^{-3} s^{-1} = 17.4 h^{-1}$ high-multiplicity Iron events.
+Thus, we will ultimately obtain an hourly flux of $F(35-135TeV) = 3.40 \times 10^{-4} s^{-1} = 1.22 h^{-1}$ high-multiplicity Iron events.
 
@@
 Due to the requirement of night operation under favourable weather conditions, the HESS phase 2 experiment has collected approximately 5000 hours of data.
-On the basis of our high-multiplicity flux rate, we can assume that a rough expected event count would be roughly 7900 high-multiplicity iron events.
+On the basis of our high-multiplicity flux rate, we can assume that a rough expected event count would be roughly 6100 high-multiplicity iron events.
 The Monte Carlo simulations will be run with approximately this number of events.
@@
 Thus R=0 corresponds to an Energy of 135TeV yielding no Integrated Flux, while R=1 would correspond to an Energy of 35TeV and the full Integrated Flux.
-THus the simulated Cosmic Rays will obey the power law, with high-energy events being realistically suppressed.
-
-\[ F(R) = F(En(R)-135TeV) = \int_{En(R)}^{135} \phi_{0} E^{-2.76} dE =\frac{\phi_{0}}{1.76}[En(R)^{-1.76} - 135^{-1.76}]= R \times F(35-135TeV)\] \[\Longrightarrow  En(R) = (\frac{1.76\times R \times F(35-135TeV)}{\phi_{0}} +135^{-1.76})^{\frac{-1}{1.76}} \]
-
-RATES!!!
+Thus the simulated Cosmic Rays will obey the power law, with high-energy events being realistically suppressed.
+
+\[ F(R) = \int_{En(R)}^{135} \phi_{0} E^{-2.76} dE =\frac{\phi_{0}}{1.76}[En(R)^{-1.76} - 135^{-1.76}]= R \times F(35-135TeV)\] \[\Longrightarrow  En(R) = (\frac{1.76\times R \times F(35-135TeV)}{\phi_{0}} +135^{-1.76})^{\frac{-1}{1.76}} \]
 
@@
 \end{table}
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{DCcounterrorhess1rgrbigtestdata}
-\caption{The difference between true and reconstructed DC signal for events passing the cuts is shown in the top left.
-In the top right the same is shown for events which were rejected.
-The true DC signals for events which passed the cuts is plotted against the reconstructed signals in the lower left, and for rejected events in the lower right.
-As in \ref{fig:cutdistribution}, in all plots a green event is one in which the DC pixel has been correctly identified, while a red event is one that has been incorrectly identified.}
-\label{fig:dcdiff}
-\end{center}
-\end{figure}
 \section{Bibliography}
@@
 \subsection{Atmospheric Data Table for CORSIKA (Windhoek, Namibia)}
+\begin{center}
+\begin{small}
 \pgfplotstabletypeset{data/atmprof10.dat}
+\end{small}
+\end{center}
 \end{document}

### 2016-07-01 positioning/classes.py

@@ -259,7 +259,7 @@ class telescope():
 	
 		
 		
-bdtvariables =["epn", "minuslldc", "minusllfull", "fullmultiplicity", "truemultiplicity", "rayxpos", "rayypos", "height"]
+bdtvariables =["epn", "fullmultiplicity", "truemultiplicity", "rayxpos", "rayypos", "height"]
 
 def makeBDTentry(simevent):
 	bdtentry =[]

### 2016-07-01 positioning/optimisez.py

@@ -89,12 +89,14 @@ def run(statsset, mindetections):
 				upperz = specificcount[upper]
 				meansigma = (upperz-lowerz) * 0.5
 				
-				bdtcuts.append(BDTcut)
-				meansigmas.append(meansigma)
+
 				
-				if float(frac) > float(0.2):
+				if float(1.0) > float(frac) > float(0.50):
+					bdtcuts.append(BDTcut)
+					meansigmas.append(meansigma)
 					if float(24) < float(meanz) < float(28):
 						if float(meansigma) < float(lowestsigma):
+
 							lowestsigma=meansigma
 							optimumbdt=BDTcut
 							optimumpassing = passing
@@ -122,7 +124,7 @@ def run(statsset, mindetections):
 	plt.gca().set_ylim(bottom=-0.05)
 	plt.gca().set_xlim(left=-0.05)
 	
-	plt.annotate(annotation, xy=(0.0, 0.9), xycoords="axes fraction",  fontsize=10)
+	plt.annotate(annotation, xy=(0.5, 0.8), xycoords="axes fraction",  fontsize=10)
 	
 	plt.legend()
 	plt.savefig('/d6/rstein/Hamburg-Cosmic-Rays/positioning/graphs/Zcuts.pdf')

### 2016-07-01 report/draft1.tex
Backup 02/07/16

@@
 \usepackage{pgfplotstable, booktabs}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 Thus, we require that an event was be seen by at least four telescopes for a five-telescope array such as HESS.
+An illustration of the HESS array is shown in Figure \ref{fig:hessdiagram}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[height=0.3\textheight]{hessdiagram}
+\caption{A diagram illustrating the HESS array \cite{hess07}.
+The four small telescopes are shown, but not the larger central telescope.
+The smaller Cherenkov ring is seen alongside the broader EAS light.
+A simplified camera image is also shown, and can be compared to a full image seen in Figure \ref{fig:fulltelimage}.}
+\label{fig:hessdiagram}
+\end{center}
+\end{figure}
 
 \section{DC Pixel Identification}
-Cosmic Rays will emit Direct Cherenkov (DC) light in the upper atmosphere, before generating an Extended Air Shower (EAS) through interaction with the lower atmosphere.
+In a Comsic Ray event, the \textquoteleft Primary Particle' will emit Direct Cherenkov (DC) light in the upper atmosphere, before generating an Extended Air Shower (EAS) through interaction with the lower atmosphere.
+The primary particle is the Cosmic Ray itself, while the EAS refers to all daughter particle of the primary particle.
 In telescope images, the DC light is usually concentrated in a single  \textquoteleft DC pixel'.
@@
 If the velocity is sufficient, we will observe photon emission from the particle at the Cherenkov Angle $\theta_{c}$.
-
-\[ \cos(\theta_{c}) = \frac{1}{\eta \beta}  \Longrightarrow \beta \geq \frac{1}{\eta}\]
-
 We obviously require that the Cherenkov Angle is real, so then require $\cos(\theta_{c}) \leq 1$.
 The minimum required velocity $\beta_{min}$ is thus equal to the inverse of the local refractive index $\eta$.
+
+\[ \cos(\theta_{c}) = \frac{1}{\eta \beta}  \Longrightarrow \beta \geq \frac{1}{\eta}\]
+
 The velocity of a particle is a function of its energy, determined with the relations $\gamma = \frac{E}{m_{0} c^{2}}$ and $\beta^{2} = 1 - \frac{1}{\gamma ^{2}}$.
 Thus, we find that the minimum velocity ultimately leads to an Energy per unit mass threshold.
-If we assume that the slight difference in proton and neutron mass is negligible here, than we can determine a local energy per nucleon threshold that will be valid for all Cosmic Rays passing a given atmospheric altitude.
-
-The Energy per Nucleon Threshold for Cherenkov Light Emission as a function of height is illustrated in \ref{fig:generalenergy}.
+If we assume that the slight difference in proton and neutron mass is negligible here, than any atmospheric altitude will have a local Energy per Nucleon threshold, and this threshold will be the same for all Cosmic Rays.
+
+The Energy per Nucleon Threshold for Cherenkov Light Emission as a function of height is illustrated in Figure \ref{fig:generalenergy}.
 Once the Energy of a Cosmic Ray exceeds the local Cherenkov Energy Threshold of the atmosphere, the Nucleus will begin emitting a ring of Cherenkov Light.
-Then for a given Telescope Array altitude above sea level and a given height h, simple trigonometry yields the final radius of emission on the ground:
+Then, for a given Telescope Array altitude above sea level and a given height h, simple trigonometry yields the final radius of emission on the ground:
 \[ Radius(h) = \tan (\theta_{C}(h)) \times (h - altitude_{array})\]
@@
 
-We see that there is a clear characteristic photon distribution which, for energies above 25 TeV, is almost constant except for a varying endpoint.
-However, we will not be able to directly measure this LPD.
+For energies above 25 TeV, we see that there is a clear characteristic photon distribution which is almost independent of Energy except for a varying endpoint.
+The LPD displays many discontinuities, which can be explained by the interpolation of Refractive Index.
+Exponential Interpolation will not provide a function that is smooth for second or third derivatives, and consequently, the LPD is not smooth.
+In reality, there will be a funtion describing the Refractive Index as a function of height, but it will depend on many variables such as Temperature.
+This will be the dominant cause of variations to the LPD, and thus, uncertainty in the LPD from Refractive Index Interpolation will be sub-dominant.
+
+In any case, we will not be able to directly measure this LPD.
 Instead, a telescope images containing air showers must be analysed, and from these images, we can infer the quantity of DC light present amongst a large degree of background.
@@
 \subsection{Image Simulation}
-We can find the DC pixel by defining the variable $Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity}$ as the ratio of the largest neighbouring pixel intensity to the intensity of a given pixel.
-In previous experiments, the DC pixel candidate was identified by applying a number of cuts to pixels in an image \cite{hess07}, and from the subset of pixels passing the specified cuts, selecting the pixel with the smallest $Q_{DC}$ as the \textquoteleft DC candidate'.
-Due to the low pass rate for cuts, we obtain a small low-contamination dataset, while the majority of telescope images are left without a DC pixel candidate.
-An improved method would aim to increase the number of correctly identified DC pixels, while still enabling cuts which discriminate well between correctly and incorrectly identified DC pixels.
-
-Classifiers provide an alternative method of identification, making use of supervised machine learning to find rules for categorising pixels.
-To train a classifier, we require a set of training pixels, as well as the correct class for each pixel.
-Once trained, a classifier can then be used to predict the class of a pixel.
-
 The CORSIKA package \cite{Heck98} was used to generate Cosmic Ray events, and the Sim\textunderscore telarray package  \cite{Bernlohr08} was used to generate corresponding HESS array telescope images.
 Simulation with EAS background was used to produce training pixel sets, while corresponding simulation without EAS background was used to find the true DC pixel in each training image.
-As part of a new method developed for this analysis, a Boosted Decision Tree (BDT) classifier was trained with the data to identify DC pixels.
-Once trained, the BDT was applied to a separate \textquoteleft testing' set of simulated telescope images.
-As before, the true DC pixel was determined from a second EAS-free simulation.
-Thus, the accuracy of BDT identification for test telescope images was calculated.
-
-The full simulation of air showers was performed using the CORSIKA package with a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
-This Atmospheric Profile is included in the Appendix.
+
+The full simulation of air showers was performed using CORSIKA with a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia.
+This is included in the Appendix.
 In total, 5000 training events and a further 10000 testing events were simulated.
@@
 The length of each cross arm was $85m$.
-The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis.Due to hardware differences between CT5 and the original HESS 1 telescopes, we analyse HESS1 and HESS2 images separately.
+The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis.
+Due to hardware differences between CT5 and the original HESS 1 telescopes, we analyse HESS1 and HESS2 images separately.
+
 To determine the true class of each pixel, a simulation was initially run with an energy cut of 10 PeV on all muons and electrons.
@@
 This gave a complete EAS image including identical DC light.
+The difference is well-illustrated in Figures \ref{fig:DCtelimage} and \ref{fig:fulltelimage}.
 
@@
 \begin{figure}
-\newgeometry{a4paper, portrait, margin=1.5in}
+\newgeometry{a4paper, portrait, margin=1.0in}
 \centering
@@
 \includegraphics[trim=80 120 80 150,clip,width=\textwidth]{graphDC}
-\caption{A typical camera image without the EAS shower.
+\caption{An ideal camera image without the EAS shower.
 The DC light is visible in every telescope, indicated by the white arrow.
 The DC pixel is circled in white.
-The largest telescope image is from CT5, but was not used in analysis.}
+The largest telescope image is from CT5, and is analysed separately.}
 \label{fig:DCtelimage}
@@
 \includegraphics[trim=80 120 80 150,clip,width=\textwidth]{graphfull}
-\caption{The same shower as in \ref{fig:DCtelimage} is shown here with the inclusion of the EAS shower.
+\caption{This is a typical camera image.
+The same shower as in Figure \ref{fig:DCtelimage} is shown here with the inclusion of the EAS shower.
 The DC light is pixels indicated with a white arrow and circle.
 The shower center of gravity is marked by a white cross.}
-\label{fig:cutdistribution2}
+\label{fig:fulltelimage}
 \end{minipage}
@@
 \subsection{Classic HESS1 DC Pixel Identification}
-As a basis for comparison, the original HESS cuts listed in Table \ref{tab:table1} were replicated for the set of test data.
+We can find the DC pixel in am image by defining the variable $Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity}$ as the ratio of the largest neighbouring pixel intensity to the intensity of a given pixel.
+In previous experiments, the DC pixel candidate was identified by applying a number of cuts to pixels in an image \cite{hess07}, and from the subset of pixels passing the specified cuts, selecting the pixel with the smallest $Q_{DC}$ as the \textquoteleft DC candidate'.
+Due to the low pass rate for cuts, we obtain a small low-contamination dataset, while the majority of telescope images are left without a DC pixel candidate.
+
+As a basis for comparison, these original HESS cuts listed in Table \ref{tab:qdccuts} were replicated for the set of test data.
 For every HESS1 image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a dynamic cut, $Q_{DC} < 0.14 \times \log(\frac{I_{tot}}{161 \times \cos \theta})$.
-Among those pixels passing all cuts, the one with the smallest $Q_{DC}$ was selected as the DC pixel candidate for the image.
 Because many images had no pixel that passed all cuts, the $Q_{DC}$ method was frequently unable to identify a DC pixel.
@@
 Increasing the acceptance rate will be essential for enabling spectroscopic analysis of cosmic rays, by providing more events to analyse.
+An improved method would aim to increase the number of correctly identified DC pixels, while still enabling cuts which discriminate well between correctly and incorrectly identified DC pixels.
 
@@
 \subsection{Boosted Decision Tree DC Identification}
-As an alternative to use of $Q_{DC}$, a new method of DC pixel identification was developed as part of this analysis by using a BDT trained with the Scikit Learn Python package \cite{scikit-learn}.
-Using the training set of 2000 CORSIKA events, and randomly split further, with 90\% in a learning subset and 10\% in a subset to check for overtraining.
+Classifiers provide an alternative method of DC pixel identification, making use of supervised machine learning to find rules for categorising pixels.
+To train a classifier, we require a set of training pixels, as well as the correct class for each pixel.
+Once trained, a classifier can then be used to predict the class of a pixel.
+As part of a new method developed for this analysis, a Boosted Decision Tree (BDT) classifier was trained to identify DC pixels using the Scikit Learn Python package \cite{scikit-learn}.
+
+A Decision Tree is a simple method of classification, in which a number of branching decisions are used to place events into one of many \textquoteleft leaves'.
+A leaf lies at the end of every decision chain, and will be associated with one of the possible classes.
+Any event being assigned to a particular leaf will then be classified as belonging to that leaf's class.
+Each branch and leaf has a sample, which indicates the number of training events that are placed in there.
+As part of the machine learning process, branches are constructed to maximise leaf purity.
+A hypothetical perfect branch would split a mixed sample into two pure leaves.
+
+It will almost always be possible to construct a tree, such that each event was placed in its own, unique leaf.
+The performance of a tree would be perfect for the training set.
+However, if applied to a separate testing sample, the performance would be significantly worse.
+The tree would not be classifying data, but rather simply remembering the structure of the training data.
+We describe such a tree as being overtrained.
+
+In general, larger training sets prevent overtraining by making it more difficult to uniquely distinguish the individual events.
+The maximum depth of a tree is the number of branches a decision chain can pass through before it must end on a leaf.
+The minimum leaf sample is the minimum number that every leaf has sample must exceed.
+Either of these quantities can be used to restrict overtraining of a Decision Tree.
+
+A graphical representation of a Decision Tree is given in Figure \ref{fig:decisiontree}.
+Decision Tree training is highly unpredictable, meaning similar datasets can produce wildly differing trees.
+Thus Boosted Decision Trees are used to provide a more stable method of classification.
+The training of a Boosted Decision Tree is in some sense an averaging process, where many different Decision Trees are trained.
+One starting Decision Tree is produced, with each event having an equal weighting.
+After each iteration of tree production, any misidentified events in a tree are given a higher weighting for the training of the next tree \cite{Roe:2004na}.
+Over time, this leads to an improved learning process by focussing more on those events that are more difficult to classify.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{decisiontreehess1}
+\caption{An example of a decision tree for the HESS 1 telescope system.
+The left direction is followed if the branch condition is true, while the right direction is followed if the condition is false.
+Red leaves contain non-DC pixels, while blue leaves represent DC pixels.
+The sample of each leaf is listed.
+Darker boxes have purer samples, while lighter boxes are more mixed.}
+\label{fig:decisiontree}
+\end{center}
+\end{figure}
+
+In this case, the training set consisted of pixels from 5000 CORSIKA events.
+It was randomly split further, with 90\% in a learning subset and 10\% in a subset to check for overtraining.
 Within the learning subset, every HESS 1 image was used, provided it was triggered in both EAS-free and full-shower simulations.
@@
 A class of 0 was assigned to every non-DC pixel, and a class of 1 was assigned to every DC pixel.
-Having created a dataset, the BDT was then trained with a maximum depth of 8, and with 100 trees generated.
+Having created a dataset, the BDT was then trained with a maximum depth of 8, and with 1000 trees generated.
 The data was provided in the form of individual pixel entries, rather than as discrete sets for images or events.
@@
     \midrule
-    $DC_{Count}$ & 0.33\\
+    $DC_{Signal}$ & 0.33\\
     $Mean_{N.N}$ & 0.24\\
@@
 The relative importance of each \textquoteleft feature' is automatically calculated by the Scikit Learn package, and is also recorded in table \ref{tab:hess1classifier}.
-The variable $DC_{Count}$ was consistently the most importance variable across many combinations of included variables and BDT training parameters.
+The variable $DC_{Signal}$ was consistently the most importance variable across many combinations of included variables and BDT training parameters.
 It was found that, under the conditions listed above, the BDT was 99.94 \% accurate for the learning pixel subset, and 99.94 \%  accurate for the overtraining-check pixel subset.
@@
 A cut was applied, requiring $P_{signal} > 0.5$ for the DC candidate to be accepted.
-A second cut requiring $DC_{Count} > 150$ removed many incorrectly identified events.
+A second cut requiring $DC_{Signal} > 150$ removed many incorrectly identified events.
 Application of this combined cut greatly increases the successful identification rate.
@@
     \midrule
-    Pixels Accepted and Correctly Identified (\%)  & 1.81 & 16.01\\
-   Pixels Accepted and Incorrectly Identified (\%)  & 0.52& 4.22\\
+    Accepted Pixels Correctly Identified (\%)  & 1.81 & 16.01\\
+   Accepted Pixels Incorrectly Identified (\%)  & 0.52& 4.22\\
     Sample Purity (\%)  & 77.8 & 79.2 \\
@@
 The original HESS study predated the construction of the larger CT5 telescope, and thus focused exclusively in the four HESS-1 telescopes.
-Although the cuts in \ref{tab:qdccuts} were not optimised for the differing pixel size and angular viewing region of CT5, they were replicated to provide a basis for comparison.
+Although the cuts in Table \ref{tab:qdccuts} were not optimised for the differing pixel size and angular viewing region of CT5, they were replicated to provide a basis for comparison.
 Based on CT5 images from the training sample, an increased 5.6\% of DC pixels were correctly identified and passed the required cut.
@@
 Thus, the number of DC pixels successfully identified using the $Q_{DC}$ method is still a valid benchmark for comparative BDT performance.
-A true accuracy rate closer to the HESS 1 rate of 90\% could be expected.
-Due to the distinctiveness of the CT5 telescope, direct application of the HESS1 classifier to the CT5 telescope yields poorer BDT performance.
-To improve CT5 pixel identification, a separate HESS2 BDT was instead trained with the same variables as above.
+A true accuracy rate closer to the HESS 1 rate of 90\% could be expected, at the expense of a depressed acceptance rate.
+Due to the distinctiveness of the CT5 telescope hardware, direct application of the HESS1 classifier to the CT5 telescope yields poorer BDT performance.
+Discrepancies in To improve CT5 pixel identification, a separate HESS2 BDT was instead trained with the same variables as above.
 The relative feature importance is listed in Table \ref{tab:hess2classifier}.
@@
 The classifier was thus not significantly overtrained.
-Applying the new classifier lede to an improvement in CT5 classification, with 17.9 \% of pixels being correctly identified and accepted, and an accuracy of 66.1\%.
-Despite this improvement, a clear gap emerged between the between the performance of HESS1 classifier on old telescopes, and the performance of the HESS2 classifier on CT5.
-Part of this discrepancy can be explained by the HESS2 learning dataset, which has just one DC pixel per event rather than the four HESS1 DC pixels.
-Additionally, HESS 2 images will have roughly 2600 non-DC pixels per event, versus 3600 DC pixels per event for HESS 1 images.
-The HESS2 classifier was thus trained on significantly fewer DC pixels, so we would expect to see the clear performance gap in comparison to the HESS1 classifier.
+Applying the new classifier lede to an improvement in CT5 classification, with 18.52 \% of pixels being correctly identified and accepted, and an accuracy of 80.6\%.
+With this improvement, there is a no significant gap between the between the performance of HESS1 classifier on old telescopes, and the performance of the HESS2 classifier on CT5.
 
@@
     \midrule
-    Pixels Accepted and Correctly Identified (\%) & 5.59 & 18.52 \\
-   Pixels Accepted and Incorrectly Identified (\%) & 14.75 & 4.44 \\
+    Accepted Pixels Correctly Identified (\%) & 5.59 & 18.52 \\
+    Accepted Pixels Incorrectly Identified (\%) & 14.75 & 4.44 \\
     Sample Purity (\%) & 27.5 & 80.6 \\
@@
 A \textquoteleft high-multiplicity event' is one in which we have telescope multiplicity $>3$.
-If we only consider high-multiplicity events, we can determine the $Q_{DC}$ performance for use in LPD reconstruction.
-After applying this cut, there were was just one single high-multiplicity event found using the $Q_{DC}$ method.
-This meant that just 0.01\% of all pixels were accepted, although with a sample purity of 100\%.
+If we only consider high-multiplicity-$Q_{DC}$ events, we can determine how frequently the $Q_{DC}$ method provides events suitable for LPD reconstruction.
+After applying the multiplicity cut, there were was just one single high-multiplicity event found using the $Q_{DC}$ method out of the 10000 testing events.
+This meant that just 0.01\% of all pixels were accepted, albeit with a sample purity of 100\%.
 Because the final sample consisted of just three HESS1 pixels, and one HESS2 pixel, the associated Poissonian error in acceptance rates and accuracy rates will be extremely large.
 
-Through we application of the two HESS classifiers, we can find the comparative high-multiplicity BDT performance.
-If we only consider high-multiplicity BDT events, the fraction of correctly identified HESS1 DC pixels falls to 2.2\%, while the fraction of incorrectly identified pixels passing the cuts falls to 0.2\%.
-The sample purity increases slightly to 91.2\%.
-In the case of the high-multiplicity HESS2 images, the BDT performance gap narrows somewhat.
-In total 1.9\% of pixels are correctly identified and accepted, although the accuracy rate is only increased to 80.7\%.
+Through application of the two HESS classifiers, we can find the comparative high-multiplicity-BDT performance.
+If we only consider high-multiplicity-BDT events, the fraction of correctly identified HESS 1 DC pixels falls to 2.20\%, while the fraction of incorrectly identified pixels passing the cuts falls to 0.43\%.
+The sample purity increases slightly to 83.8\%.
+In total 1.61\% of the HESS 2 pixels are correctly identified and accepted, although the accuracy rate is increased to 88.0\%.
 The relatively high fraction of passing events is in excess of the random expectation of $0.16^{4}=0.07\%$ and $0.19^{4}=0.13\%$ for HESS1 and HESS2.
@@
 The same is true for the $Q_{DC}$ high multiplicity rates.
-As well as general BDT accuracy improving after high-multiplicity cuts, the performance gap over the $Q_{DC}$ method is vastly increased for high-multiplicity events.
-As a result of the two-hundred-fold increase in acceptance rate for high multiplicity events, the expected data sample size will increase dramatically.
-This should enable spectroscopic analysis of Cosmic Ray Elements to be conducted after a much shorter experimental run time that for the $Q_{DC}$ method.
+
+The minor discrepancy in performance between HESS1 and HESS2 can partially be explained by the geometry of the HESS array.
+Any event  with a core position near the central CT5 telescope is likely to trigger the four outer telescopes.
+However, the dim inner LPD is unlikely to be seen in the big central telescope.
+In the event of a core position near one of the corner telescopes, CT5 and at least three of the other telescopes are likely to have a clear DC signal.
+Thus the effective area for high multiplicity events including CT5 is smaller than for those involving the HESS1 telescopes.
+
+Despite the minor performance difference, the BDT method is clearly superior in both cases.
+On top the gains in BDT accuracy when considering only high-multiplicity events high multiplicity events, we also find the relative performance gap over the $Q_{DC}$ method is vastly increased.
+As a result of the two-hundred-fold increase in acceptance rate for high-multiplicity-BDT events against high-multiplicity-$Q_{DC}$ events, the expected data sample size will increase dramatically.
+This should enable spectroscopic analysis of Cosmic Ray elements to be conducted after a much shorter experimental run time that for the $Q_{DC}$ method.
+Use of the BDT identification method will be assumed throughout the rest of this paper, and a high-multiplicity event will be intended to mean a high-multiplicity-BDT event.
 
@@
     \midrule
-    High Multiplicity Pixels Accepted and Correctly Identified (\%)& 0.01 & 2.20 & 0.01 & 1.61\\
-    High Multiplicity Pixels Accepted and Incorrectly Identified (\%)  & 0.00 & 0.43 & 0.01 & 0.22\\
+    High Multiplicity Accepted Pixels Correctly Identified (\%)& 0.01 & 2.20 & 0.01 & 1.61\\
+    High Multiplicity Accepted Pixels Incorrectly Identified (\%)  & 0.00 & 0.43 & 0.01 & 0.22\\
     Sample Purity (\%)& 100.0 & 83.8 & 100.0 & 88.0\\
@@
 \subsection{Proton Background}
-It is important to discriminate between the heavy cosmic ray elements, such as iron, and the much more abundant proton events.
+It is important to discriminate between the heavy Cosmic Ray elements, such as Iron, and the much more abundant proton events.
 Protons tend to emit negligible DC light, so will contaminate any data sample with events that cannot be reconstructed using the LPD method.
-To determine the acceptance rate for proton events, a simulation was conducted with 5000 proton events in CORSIKA.
+To determine the acceptance rate for proton events, a simulation was conducted with 5000 proton events in CORSIKA with the same parameters as the Iron train/test data.
 For HESS1, the raw acceptance rate was 15.1\% while the sample purity of 32.2\%.
@@
 Once multiplicity cuts are applied, the acceptance rate falls steeply to just 2.9\%.
-With the factor 10 discrepancy in flux, the number of proton and iron images will be comparable.
+With the factor 10 discrepancy in flux, the number of proton and iron images would be comparable.
 Of those passing the cuts, 24.5\% are correctly identified.
@@
 We aim to remove proton pixels but not iron pixels.
-Applying a cut requiring Aspect Ratio $> 0.35$ eliminated all accepted proton events for HESS1 and HESS2.
+Applying a cut requiring Aspect Ratio $> 0.40$ eliminated all accepted proton events for HESS1 and HESS2.
 With 17792 total HESS1 images, just 6195 images were triggered by DC light.
 Of all 17792 images, there were none passing all of the required cuts.
-We can place a poissonian upper limit on the acceptance rate of $< 0.02 \%$.
-Of the for 4448 HESS2 images, just 2169 contained DC light.
-As no image passed all cuts, we place an upper limit of $< 0.07\%$.
-
-Using poissonian statistics, we can place a 95\% confidence upper limit on the rate of accepted, high-multiplicity $Q_{DC}$ events.
+
+Using poissonian statistics, we can place a 95\% confidence upper limit on the acceptance rate.
 By virtue of passing a multiplicity cut, the number of accepted pixels must be at least 4, or none.
 It is thus more appropriate to instead consider the total number of events for calculations of an upper limit.
-There were 4711 fully triggered events, of which none were \textquoteleft High multiplicity Events'.
+There were 4711 fully triggered events, of which none was a \textquoteleft High Multiplicity Event'.
 We find a value for the mean $\lambda$ such that the probability of not observing a high multiplicity event is less than 5\%.
@@
 
-Thus, we can conclude that if the mean was greater that if the mean $\lambda>3$, we would have expected to observe at least one event with a 95\% probability.
+Thus, we can conclude that if the mean $\lambda$ was greater than 3, we would have expected to observe at least one event with a 95\% probability.
 As we did not observe an event, we conclude that the mean high multiplicity event rate is less than $\frac{3}{4711}=0.06\%$.
 
-For HESS1 iron events, the total acceptance rate falls slightly from 2.4\% to 2.3\%, while the sample purity decreases slightly to 89.0\%.
-For HESS2, the total acceptance rate falls slightly from 2.4\% to 2.3 \%, while the sample purity decreases slightly to 79.8\%.
-Iron images form at least 75\% of a sample, because most proton images are at least one hundred times less likely to be accepted.
-Use of this BDT method is thus assumed throughout the rest of this analysis.
+For HESS1 iron events, the total acceptance rate falls slightly from 2.4\% to 2.3\%, while the sample purity increases slightly to 84.3\%.
+For HESS2, the total acceptance rate falls slightly from 2.4\% to 2.3 \%, while the sample purity also increases slightly to 88.2\%.
+Iron images form at least 80\% of a sample, because most proton images are at least fifty times less likely to be accepted.
+These results are summarised in Table \ref{tab:protonacceptance}.
 
@@
 We must remove the white proton pixels passing all other cuts, without removing dark green iron pixels passing all other cuts.
-A cut requiring Aspect Ratio $> 0.35$ should remove a large proportion of proton images without reducing the pass rate for iron nucleii.}
+A cut requiring Aspect Ratio $> 0.40$ should remove a large proportion of proton images without reducing the pass rate for iron nucleii.}
 \label{fig:aspectratio}
@@
     \midrule
-    Proton Pixels Accepted (\%) & 15.10 & 32.68\\
+    Accepted Proton Pixels (\%) & 15.10 & 32.68\\
     Sample Purity (\%) & 10.1 & 5.1 \\
     \midrule
-    High Multiplicity Proton Pixels Accepted (\%) & 0.83 & 1.03\\
+    High Multiplicity Accepted Proton Pixels (\%) & 0.83 & 1.03\\
     Sample Purity (\%) & 6.8 & 4.3 \\
     \midrule
-    Proton Pixels Accepted after All Cuts(\%) & $< 0.06$ & $< 0.06$\\
+    Accepted Proton Pixels after All Cuts(\%) & $< 0.06$ & $< 0.06$\\
     Sample Purity (\%) & / & / \\
     \midrule
-    Iron Pixels Accepted after All Cuts(\%) & 2.44 & 1.66\\
+    Accepted Iron Pixels after All Cuts(\%) & 2.44 & 1.66\\
     Sample Purity (\%) & 84.3 & 88.2 \\
@@
 Below this, the LPD is more heavily dependent on Energy, and thus our basic assumption of a characteristic equation will no longer be valid.
-To account for this, an additional simulation of 15000 Iron events was conducted in the energy range 5-135TeV.
+However, we also know that any data sample will be dominated by lower-energy events as a result of the power law $\phi(E) \propto E^{-2.7}$.
+To account for this, an additional simulation of 15000 Iron events was conducted in the energy range 5-135TeV to give a realistic model for performance.
 The BDT remained the same, and the same initial cuts were replicated as before.
 The same was also done for Protons in the same energy range.
+
+We find that, for Iron Events, the acceptance rate falls by a factor of approximately 15.
+The relative proportion of HESS 1 to HESS 2 acceptance is broadly maintained at a factor of roughly 1.5, although the sample purity falls somewhat.
+If we account for the differing intergrated flux rate, we can calculate the ratio of expected high-multiplicity event rate $\Gamma_{HM}(E)$ for the ranges 5-135 TeV and 35-135 TeV.
+
+\[ \frac{\Gamma_{HM}(5-135)}{\Gamma_{HM}(35-135)} = \frac{5^{-1.7} - 135^{-1.7}}{35^{-1.7} - 135^{-1.7}} 
+= 30.3 \]
+
+Thus, if we have thirtyfold increase in event rate, but only one-fifteenth the acceptance rate, we would ultimately expect that we would have twice as many Iron Events if the full energy range of 5-135 TeV was included.
+However, the low-energy proton acceptance is much higher.
+Thus, were we to include all events in this energy range, we would again retrieve a sample dominated by protons.
 The results are summarised in Table \ref{tab:fullironacceptance}.
@@
 
-We find that, for Iron Events, the acceptance rate falls by a factor of approximately 15.
-The relative proportion of HESS 1 to HESS 2 acceptance is broadly maintained at a factor of roughly 1.5, although the sample purity falls somewhat.
-If we account for the differing intergrated flux rate, we can calculate the ratio of expected high-multiplicity event rate $\Gamma_{HM}(E)$ for the ranges 5-135 TeV and 35-135 TeV.
-
-\[ \frac{\Gamma_{HM}(5-135)}{\Gamma_{HM}(35-135)} = \frac{5^{-1.7} - 135^{-1.7}}{35^{-1.7} - 135^{-1.7}} 
-= 30.3 \]
-
-Thus, if we have thirtyfold increase in event rate, but only one-fifteenth the acceptance rate, we would ultimately expect that we would have twice as many Iron Events if the full energy range of 5-135 TeV was included.
-However, the low-energy proton acceptance is much higher.
-Thus, were we to include events in this energy range, we would again retrieve a sample dominated by protons that will not be correctly reconstructed.
-The energy distribution of the Protons and Iron Events are shown in FIG.
-To remove this contamination from protons and non-saturated Iron events, we thus apply one additional Energy cut on the data sample.
-We simply require that the reconstructed Energy is greater than 30TeV.
-This will, assuming a rough energy resolution of around 15\% in reconstruction, remove the majority of these low-energy events.
-(WILL CONFIRM ONCE HISTOGRAMS ARE RETRIEVED).
-
-\section{HESS-type Event Simulation}
-
-\subsection{Extended Air Shower Background}
-Having successfully parameterised the LPD using CORSIKA simulations, we can replicate it for out Monte Carlo simulation. We have found that the DC LPD is broadly independent of both height and Energy.
-
-\begin{figure}
-\begin{center}
-\includegraphics[height=0.9\textheight]{hessheight}
-\caption{The mean first interaction height for all Cherenkov Events is 40km???.
-Events in blue met the multiplicity threshold, with DC light in four telescopes.
-The mean first interaction height for four telescope events in the HESS array is 23km}
-\label{fig:Hessheight}
-\end{center}
-\end{figure}
+Fortunately, there is a large degree of separability for Iron and Proton Events based on their Energy.
+The energy distribution of the Protons and Iron Events are shown in Figures \ref{fig:protonenergy} and \ref{fig:ironenergy}.
+The Iron distribution is slightly unusual, in that it is terminated above roughly 13 TeV, although lower energy events are much more frequent.
+This can be explained by the fact that the Cherenkov Emission Threshold is specified by the Energy per Nucleon, and Iron Nucleii have 56 nucleons.
+Thus, in almost all cases, Iron Nucleii below this Energy will interact with the atmosphere before they emit Cherenkov Light.
+The BDT is unlikely to identify 4 DC pixels with a sufficient $P_{signal}$ in an event without any real DC light, and thus no low-Energy High-Multiplicity Iron events are found.
+
+To remove the proton contamination from protons and non-saturated Iron events, we thus apply one additional Energy cut on the data sample.
+The majority of accepted protons have an Energy of less than 10 TeV, and the largest recorded Energy was 21.6 TeV.
+We can thus require that the reconstructed Energy is greater than 30TeV.
+This will, assuming a rough energy resolution of around 15\% in reconstruction, easily remove all of the proton background.
+We will also remove roughly half of the Iron events, but as shown in Figure \ref{fig:lpd}, this low-energy half of events will mostly contain non-saturated DC emission that would be harder to reconstruct.
+
+\begin{figure}
+	\centering
+	\begin{subfigure}[b]{0.9\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{energyfullprotons}
+		\caption{}
+		\label{fig:protonenergy}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.9\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{energyfulliron}
+		\caption{}
+		\label{fig:ironenergy}
+	\end{subfigure}
+	\caption{The Energy of Proton events passing all cuts is shown above in \ref{fig:protonenergy}.
+It is clear that the majority come from the low energy regime, and none have an energy greater than 22 TeV in.
+The Energy of Iron events passing all cuts is shown below in \ref{fig:ironenergy}.
+The majority come from the region above 20 TeV.}
+\end{figure}
+
+\section{Parameterisation of the LPD}
+Having identified DC pixels in a reliable way without accompanying background events, we can now consider the resultant LPD.
+We must parameterise this function before we are able to reconstruct events.
+We can also account for additional information provided in the EAS light.
 
@@
 We can conclude that in many of our images, the air shower will lie mostly within the telescope image.
-In the same way as for DC light, we can look for the existence of a Characteristic LPD describing the Total Shower Intensity, where we define $I_{tot}$=Image Amplitude.
+In the same way as for DC light, we can firstly look for the existence of a Characteristic LPD describing the EAS Intensity, where we define $I_{tot}$=Image Amplitude.
 The results for high-multiplicity events at various energies is shown in Figure \ref{fig:fullshowerlpd}.
@@
 The data is fitted with a line of the form $y_{i} (x) =A_{i} \exp (K_{i} x)$.
-The fractional deviation from the fit is found in an analogous way to the DC LPD found in Figure \ref{fig:corsikalpd1}.
+The fractional deviation from the fit is found for each point by calculating $\Delta_{EAS} = \frac{fit_{EAS} - I_{tot}}{fit_{EAS}}$.
+We can then take the 68\% interval values for fractional deviation to give a fractional uncertainty $\sigma_{EAS}$.
 Across all Energies, the mean fractional deviation from the fitted exponential was roughly 0.15.
@@
 
-In order to overcome this, we can instead parameterise the exponential fits.
+In order to overcome this, we can instead try to parameterise the exponential fits.
 Across all energies, a fit is made and the exponent coefficients are recorded.
@@
 The fitted Amplitudes $A_{i}$ are then recorded, and are also plotted in Figure \ref{fig:powerlawlpd}.
-A clear exponential relationship is again observed.
+A clear relationship is again observed, in this an exponential law.
 A straight line is fitted to the logarithm of the data values, and we retrieve a second relationship describing the amplitude as a function of the Energy.
@@
 
+\[ y (x, E) = 73.9 \times \exp (0.025 E -(0.00004 E + 0.00692)x) \]
+
 Although the Full Shower LPDs do not depend upon the charge of the primary particle, they will still enable the core position and energy to be effectively constrained.
 We can use the Full Shower LPD to obtain a rough estimate for the core position, and thus a rough estimate of the distance from each telescope to the core.
-similarly the core energy can be estimated.
+Similarly the core energy can be estimated.
 Although this reconstruction will be inferior to one accounting for both LPDs, we can make use of the preliminary core position estimate to aid our calculation of $True_{DC}$.
@@
 \subsection{Determining $True_{DC}$}
-Determining the value of $True_{DC}$ is essential for determining the error in our LPD measurements.
+Before we can extract the DC LPD from telescope imagesTo determine the value of $True_{DC}$ is essential for determining the error in our LPD measurements.
 However, there are two natural ways of quantifying $True_{DC}$.
@@
 \end{figure}
-
-REDO STATS
 
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[height=0.9\textheight]{hessheight}
+\caption{The mean first interaction height for all Cherenkov Events is 40km???.
+Events in blue met the multiplicity threshold, with DC light in four telescopes.
+The mean first interaction height for four telescope events in the HESS array is 23km}
+\label{fig:Hessheight}
+\end{center}
+\end{figure}
+
 Another parameter exponentially interpolated using the data tables is the optical depth to the surface, $\tau$.
@@
 calibrate with position of Iron peak
+Real data
 

### 2016-07-01 CORSIKA/aspectratio.py

@@ -8,7 +8,7 @@ from telescopeclasses import *
 from matplotlib import rc
 
 parser = argparse.ArgumentParser()
-parser.add_argument("-jid", "--jobID", default="testdata")
+parser.add_argument("-jid", "--jobID", default="bigtestdata")
 
 cfg = parser.parse_args()
 
@@ -21,7 +21,7 @@ hess2ars =[[],[]]
 for f in range(len(files)):
 	filepath = "/nfs/astrop/d6/rstein/data/"
 	i = 1
-	j = 5000
+	j = 15000
 	
 	folder = files[f]
 	

### 2016-07-01 CORSIKA/combineforenergystatistics.py

@@ -69,13 +69,15 @@ while (i < j):
 	
 print energy
 
-plt.hist(energy, log=True, histtype='bar')
+print cfg.jobID.split("full")[1]
+
+plt.hist(energy, histtype='bar')
 figure = plt.gcf() # get current figure
-figure.set_size_inches(20, 15)
-plt.xlabel("True Energy (TeV)")
-plt.ylabel("Count")
-plt.title("Energy Distribution of Accepted Events")
-plt.ylim(bottom=0.8)
+figure.set_size_inches(20, 10)
+plt.xlabel("True Energy (TeV)", fontsize=20)
+plt.ylabel("Count", fontsize=20)
+plt.title("Energy Distribution of Accepted " + cfg.jobID.split("full")[1], fontsize=25)
 plt.savefig("/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/CORSIKA/graphs/energy"+str(cfg.jobID)+".pdf")
+plt.savefig("/nfs/astrop/d6/rstein/Hamburg-Cosmic-Rays/report/graphs/energy"+str(cfg.jobID)+".pdf")
 plt.close()
 					

### 2016-07-03 report/draft1.tex
Backup 03/07/16

@@
 Thus, we calculate a one-sided distribution standard deviation, and consider the value of an event in the 68th centile to be equal to the standard deviation.
-It is found that, for both four and five telescope events, the core reconstruction is approximately $\sigma_{core} \approx 10m$.
+It is found that, for both four and five telescope events, the core reconstruction is approximately $\sigma_{core} \approx 10m$ and $\sigma_{core} \approx 20m$ respectively.
 Most reconstructed core positions thus lie less than 10m from the true position.
 This is extremely good, especially in comparison to the Hillas Reconstruction, where a core resolution of Y is more typical AND CITE!
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{position}
+\caption{The distance from true core position to the reconstructed core position is shown above. For four-telescope events, the standard deviation from true position is Xm.}
+\label{fig:rawposition}
+\end{center}
+\end{figure}
+
+We can similarly consider the resolution of reconstructed height.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{rawheight}
+\caption{The distance from true core position to the reconstructed core position is shown above. For four-telescope events, the standard deviation from true position is Xm.}
+\label{fig:rawheight}
+\end{center}
+\end{figure}
+
+Having taken into account our various variable uncertainties, we can also consider our most important variable.
+In Figure \ref{fig:rawZ} the reconstructed charge number is binned in integers, illustrating the element that each reconstructed event would be assigned to.
+As we would hope, there is a very clear peak centered on Z=26, and the median charge value lies very close to this value.
+The distributions are broadly symmetric, and have a charge resolution of $\sigma_{Z} = 1.1$ and $\sigma_{Z} = 2.2$ for five and four telescope events respectively.
+Unsurprisingly, the charge resolution is better for five-telescope events, but both cases represent a significant improvement over the existing charge resolution obtained through Hillas analysis.
+With the reasonably high event rate, we could certainly expect to see such a peak in the existing HESS data, and the uncertainty may be small enough to enable spectroscopic analysis.
+Obtaining such a peak is a vindication of the LPD method, and demonstrates its superior performance for event reconstruction.
+However, the value of $\sigma_{Z}$ for 4-telescope events is still large.
+It is also clear in Figure \ref{fig:rawZ} that the distribution is somewhat truncated by the imposed minimisation reconstruction range of 16-36.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{rawZ}
+\caption{The distance from true core position to the reconstructed core position is shown above. For four-telescope events, the standard deviation from true position is Xm.}
+\label{fig:rawZ}
+\end{center}
+\end{figure}
+
+\subsection{Boosted Decision Trees}
+There is one additional possibility for improved event reconstruction.
+We recall that, by virtue of being a high multiplicity event, we will already be restricting ourselves to a fairly limited core position and energy range.
+We can train a BDT to distinguish between events that are likely to be well constructed, and those that are likely to be poorly constructed.
+
+Once an event has been reconstructed, we can define the expected multiplicity as the number of telescopes we would expect to see DC light in, given the reconstructed values for Energy per Nucleon, charge and core position.
+Using this value, alongside the core position coordinates and the energy, we train a BDT for each telescope multiplicity.
+Using a second set of Monte carlo data, simulated under the same conditions, we train both a 4-tel and a 5-tel BDT.
+The relative importance of variables is shown in table \ref{tab:reconbdt}.
+
+\begin{table}[h!]
+  \centering
+  \caption{Feature Importances for the reconstruction BDTs, ordered by 4-tel importance}
+  \label{tab:reconbdt}
+  \begin{tabular}{ccc}
+    \toprule
+    Variable & 4-tel & 5-tel\\
+    \midrule
+    Energy per Nucleon & 0.29 & 0.30\\
+    Core y Position & 0.27 & 0.31\\
+    Core x Position & 0.26 & 0.31\\ 
+    Expected Multiplicity & 0.19 & 0.07\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+It is interesting to note that, although the energy and core position always have similar importance, the expected multiplicity is far more important for the 4-tel BDT.
+This implies that many poorly reconstructed events have core positions that would lead to an altered multiplicity.
+If a telescope is not triggered, it is currently ignored for the purpose of reconstruction.
+Consequently events can be reconstructed with core positions that we know to be false.
+We apply each BDT to the Monte Carlo data with matching multiplicity, to identify events that are likely to be reconstructed.
+The BDT score distribution is shown in Figure \ref{fig:reconBDTdistribution}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{Likelihood}
+\caption{The BDT score distribution is shown for the Monte Carlo test data.
+Events are colour-coded by how well the Charge number was reconstructed.
+We see that the majority of bad red events have a lower BDT score in the 4-tel graph.
+In each graph, the think black line indicates the eventual cut made to the data.}
+\label{fig:reconBDTdistribution}
+\end{center}
+\end{figure}
+
+Having obtained a BDT score variables $P_{4tel}$ and $P_{5tel}$, we can then optimise cuts on this variable.
+The two BDTs will be optimised independently.
+Our aim is to reduce the value of $\sigma_{Z}$ to provide a narrower reconstructed peak.
+This should enable more effective spectroscopic analysis.
+At the same time, we wish to maintain as high a pass rate as possible, to reduce the expected random Poissonian Error in the dataset.
+We know that the Poissonian Error of a distribution scales with $\frac{1}{\sqrt{N}}$.
+Ultimately we expect to obtain a spectrum of overlapping Gaussians corresponding to each element, and fit for the relative height of each Gaussian.
+To balance the competing priorities of large N and small $\sigma_{Z}$ which will enable the Gaussian peaks to be resolved, we can define a new scaled variable $\mathbf{\tilde{\sigma_{Z}}} = \frac{\sigma_{Z}}{\sqrt{(f)}}$.
+Here, instead of N, we are scaling with the passing fraction of events $f = \frac{N_{passing}}{N_{total}}$.
+The quantity $\mathbf{\tilde{\sigma_{Z}}}$ is then found for a range of BDT cut values, and the minimum found.
+The values of $\sigma_{Z}$ and $\mathbf{\tilde{\sigma_{Z}}}$ are shown in Figure \ref{fig:Zcuts}.
+Ultimately, a cut of $P_{4tel} > 0.15$ and $P_{5tel} > 0.22$ was chosen, corresponding to $\sigma_{Z}=0.88$ and $\sigma_{Z}=1.04$ respectively.
+The respective passing fraction was 0.92 and 0.53.
+The improvement for 5 telescope events is minor, but for 4 telescope events there is a significant reduction in charge resolution.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{Zcuts}
+\caption{The BDT score distribution is shown for the Monte Carlo test data.
+Events are colour-coded by how well the Charge number was reconstructed.
+We see that the majority of bad red events have a lower BDT score in the 4-tel graph.
+In each graph, the think black line indicates the eventual cut made to the data.}
+\label{fig:Zcuts}
+\end{center}
+\end{figure}
+
+We can plot the distribution of reconstructed core positions, with the BDT score as a color scale.
+We see that a clear pattern emerges, with distinct differences between 4-tel and 5-tel events.
+For 4-tel events, the core positions are widely distributed in the simulated region.
+However, there are many cores clustered around each of the 5 telescopes.
+This makes sense, as cores close to a telescope are likely to produce negligible DC light in that telescope.
+However, once the $P_{4tel}$ cut is applied, the majority of events lying outside the square of small telescopes are removed.
+Also, interestingly, most events lying near one of the smaller telescopes are removed, giving each telescope a noticeable halo containing few or no events.
+This suggests that, if an event lies close to one telescope, the distance to the opposite diagonal telescope is likely to be too large to produce a DC signal.
+Thus, we would instead expect a 3-tel event.
+We know that the first interaction height is reconstructed extremely poorly, and thus the exact $r_{max}$ values for these LPDs is uncertain.
+It is likely that, given this, the height is being misreconstructed to allow the LPD to extend fare enough to trigger the most distant telescope.
+
+However, there is a region of high $P_{4tel}$ points lying directly beyond the halo, in the inner region.
+Events in this location are likely to be too dim to trigger the nearest telescope, while still being close enough to trigger the remaining telescope.
+This region also encroaches partially on the four telescope halos that would otherwise be completely circular.
+We are left with a clear square region of high-score events lying within the telescope square.
+There is then a less distinct halo surrounding the central CT5 telescope.
+This halo represents events that would be distant enough from the center to trigger the CT5, but central enough to also trigger the outer 4 telescopes.
+within this halo, there is a dense region of reconstructed events lying very close to the CT5 telescope, where they are close enough to not trigger it but are still able to trigger the outer 4 telescopes.
+
+The distribution of 5-tel events is much easier to explain.
+As each telescope must be triggered there is a clear halo surrounding each telescope.
+Certain events are reconstructed with a higher radius from the center, and these are mostly removed by the $P_{5tel}$ cuts.
+We are left with a ring surrounding CT5 of high scoring events.
+The relatively loose cut is extremely effective at reducing almost outlying events that are far from the centre, while leaving almost all other events.
+Future reconstruction techniques could aim to make use of this information by restricting the core position to these regions of expected high-multiplicity.
+However, this was not done as part of this analysis.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{bdtmap}
+\caption{A geometric representation the reconstructed events is shown.
+Each coordinate corresponding to a reconstructed position in metres.
+The 5 HESS telescopes are represented by black rings.
+Above we see all events, while below we see only events passing their respective BDT cuts.
+In the left column we see the 4-telescope events, while in the right column, we see 5-telescope events.}
+\label{fig:bdtmap}
+\end{center}
+\end{figure}
+
+We can assess the impact of the $P_{4tel}$ and $P_{5tel}$ cuts on the distribution of reconstructed Energy.
+We would expect that the true energy distribution would begin at around 10-15 TeV, when Cherenkov Emission becomes possible.
+The number of events would increase with energy up to a maximum around 25 TeV when Emission becomes saturated, and would then decline in accordance with the $E^{-2.7}$ flux rate.
+The reconstructed Energy distribution does, as expect, follow this pattern.
+This suggests that our method for Energy reconstruction is reasonable, and this is further confirmation of the reasonably precise energy resolution shown in Figure \ref{fig:rawepn}.
+The Energy distribution is shown in Figure \ref{fig:energy}, alongside the post-cuts distribution.
+As might be expected, the loose $P_{5tel}$ cuts produce little noticeable difference to the distribution.
+However, there is a clear curtailing of the lower Energy events after the $P_{4tel}$ cut has been applied.
+This is as might be expected, because events that are not saturated in Energy are unlikely to be reconstructed well.
+Ultimately, the post cut distributions of 4-tel events appears similar to the 5-tel distribution, albeit with a greater overall frequency.
+In contrast, the pre-cuts 4-tel events had a noticeable broader distribution extending further into the very low and very high energy regimes.
+The results broadly vindicate our decision to apply an Energy Cut on reconstructed events that was implemented to remove protons.
+Were the lower Energy Iron events to have been included in our simulations, we would have needed to remove them through the BDT method because they are unlikely to be reconstructed well.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{energymap}
+\caption{The reconstructed Energy distribution is shown. Above, all events are included. Below, only those events passing the $P_{4tel}$ and $P_{5tel}$ cuts are included}
+\label{fig:energy}
+\end{center}
+\end{figure}
+
+\subsection{Final Variable resolution}
+After application of the BDT cut to the Monte Carlo datasets, the distributions in Energy, Core Position and
+Charge are repeated.
+Unsurprisingly, the loose cuts for $P_{5tel}$ mean that 5-tel performance is only slightly improved, while the 4-tel performance is more significantly improved.
+For 5-tel events, the core position reduces from $\sigma_{core} = 9.2m$ to $\sigma_{core} = 8.6m$, while for 4-tel events, the improvement is a substantial reduction from $\sigma_{core} = 17.0m$ to $\sigma_{core} = 10.0m$.
+Ultimately our resultant core resolutions are broadly similar for both multiplicities, and represent a significant improvement over previous Hillas-reconstructed core positions.
+
+With regards to energy, the removal of many low-energy events by the 4-tel BDT leads to a clear improvement in resolution.
+This is evident in Figure \ref{fig:epn}.
+The 5-tel resolution improves slight from $\frac{\sigma_{E}}{E} = 0.06$ to $\frac{\sigma_{E}}{E} = 0.05$ and the 4-tel resolution improves more noticeably from $\frac{\sigma_{E}}{E} = 0.12$ to $\frac{\sigma_{E}}{E} = 0.06$.
+We again see that the harsher $P_{4tel}$ cuts leads to a convergence of 4-tel and 5-tel resolution.
+
+This trend continues for the charge resolution, where we see a sharp improvement for 4-tel events.
+Whereas in Figure \ref{fig:rawZ} the distribution is clearly partially truncated by the imposed range of $16 < Z < 36$, we see no such problem once $P_{4tel}$ cuts have been applied.
+Ultimately the 5-tel resolution improves from $\sigma_{Z}=0.95$ to $\sigma_{Z}=0.87$, while the 4-tel resolution improves from $\sigma_{Z}=2.11$ to $\sigma_{Z}=1.05$.
+In doing this, we have achieved our stated aim of obtaining a charge reconstruction method capable of producing large datasets with a charge resolution of roughly  $\sigma_{Z} \approx 1$.
+The LPD method is this shown to be sufficiently good to enable spectroscopic analysis of Heavy Cosmic Rays.
 
@@
 
-Having taken into account our various variable uncertainties, we can also consider our most important variable.
-In Figure \ref{fig:rawZ} the reconstructed charge number is binned in integers, illustrating the element that each reconstructed event would be assigned to.
-As we would hope, there is a very clear peak centered on Z=26, and the median charge value lies very close to this value.
-The distributions are broadly symettric, and have a charge resoultion of $\sigma_{Z} = 1.1$ and $\sigma_{Z} = 2.2$ for five and four telescope events respectively.
-Unsurprisingly, the charge resolution is better for five-telescope events, but both cases represent a significant improvement over the existing charge resolution obtained through Hillas analysis.
-With the reasonably high event rate, we could certainly expect to see such a peak in the existing HESS data, and the uncertainty well be small enough to enable spectroscopic analysis.
-Obtaining such a peak is a vindication of the LPD method, and demonstrates its superior performance for event reconstruction.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{rawZ}
-\caption{The distance from true core position to the reconstructed core position is shown above. For four-telescope events, the standard deviation from true position is Xm.}
-\label{fig:rawZ}
-\end{center}
-\end{figure}
-
-\subsection{Boosted Decision Trees}
-Using one quarter of a large sample of Monte Carlo data, we can train a Boosted Decision Tree (BDT) for a given telescope multiplicity, using the reconstructed x/y core position, height and energy, as well as the Log Likelihood.
-The BDT is told whether each event is \textquoteleft signal' (correctly reconstructed) or \textquoteleft background' (incorrectly reconstructed).
-
-For every simulated event, this trained BDT can then be used to assign a \textquoteleft Signal Probability'.
-On a second quarter of the dataset we can optimise a cut on the minimum signal probability, in order to maximise the ratio of signal to background.
-We find that the $\sigma_{Z}$ of the remaining \textquoteleft Test' Monte Carlo data is reduced when the same BDT cut is applied.
-
-However, the simulated number of hours for the data was 1200?
-hours, and comparisons with HESS data show just 12 4-telescope events rather than 600.
-Thus, although the technique is valid and effective for HESS, the count rate will limit the potential to conduct any statistical analysis from this experiment.
-
-\section{Optimised Telescope Array}
-NO Background!!!!!
-\subsection{Count Rates}
-
-In order to improve the count rate of high-multiplicity events, we can consider a 3x3 array of Cherenkov Telescopes, which we want to use for identifying Cosmic Ray Elements accurately.
-In \ref{fig:optmiselayout} we see that the \textquoteleft High Multiplicity Count Rate' of events observed by 4 or more telescopes falls with increasing grid separation.
-We can clearly see that the optimum grid spacing will likely lie in the 20-50m region to provide a reasonable count rate.
-Competing with this effect is the reliance of LDF reconstruction on sampling the entire lateral distribution.
-Thus the reconstruction quality will decrease as Grid Width decreases.
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{epn}
+\caption{The fraction deviation from true energy is shown above.
+For events with five-telescope multiplicity, the fractional error is X but for four-telescope multiplicity, it is Y.
+The expected poissonian error bars are also shown.}
+\label{fig:epn}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{Z}
+\caption{The reconstructed charge for the cut dataset is shown, with a clear peak around the true value of Z=26.}
+\label{fig:Z}
+\end{center}
+\end{figure}
+
+\section{Further Improvements}
+There are many potential avenues that would improve or expand upon the work conducted as part of this analysis.
+The development of a new method of DC pixel identification is likely to prove particularly useful, as it performs more accurately and vastly more efficiently that existing methods of DC pixels.
+
+\subsection{Hillas Reconstruction}
+The LPD reconstruction method was developed to replace the current method of Hillas Reconstruction, owing to the latter's poor position resolution.
+Rather counter-intuitively, despite the demonstrated superiority of the LPD method, the result of this analysis may well be to strengthen the use of Hillas Analysis.
+The exact process for Hillas Reconstruction relies on deriving the Major and Minor axis of a shower image, and calculating pairwise intersection points of the major axes between telescopes to find the shower direction.
+Due to the blurriness of the shower images, there is significant uncertainty in placing of the major axis.
+However, we know that the major axis will pass through both the shower centre of gravity and the DC light.
+The shower centre of gravity is much easier to determine despite image blurring, and thus has a much lower uncertainty.
+Previously, difficulty in identifying DC pixels meant that this centre of gravity was not particularly useful.
+However, through use of the BDT-identified DC pixels, it should be possible to much more reliable place the major axis in a shower image.
+We can thus expect that, with the BDT, Hillas reconstruction may have a significantly improved core position resolution.
+Further analysis in this area will be conducted by other members of our research group.
+In the reasonable assumption that this does produce much better position resolution, we will have third independent method to determine the core position as well as the two LPDs.
+We could then conduct a likelihood minimisation encompassing this new information alongside the existing LPDs.
+We would expect our final core position resolution, and thus charge resolution, to improve even further as a result of these extra measurements.
+
+\subsection{Actual Data}
+The obvious next step to take as part of this analysis would be to apply the reconstruction Method to real HESS data.
+We would hope to obtain a distribution similar to that in Figure \ref{fig:Z}, to which we could fit Gaussians centered on each integer value of Charge.
+In this way, we could calculate the relative abundance of the different Heavy Cosmic rays.
+Comparing the width of these Gaussians would confirm whether or not our reconstruction method was optimistic in our various assumptions for error.
+Additionally, on the basis of the calculated expectation rate for Iron Events we could compare to see if this agrees
+with the data.
+An excessive experimental count rate would likely indicate that additional sources of background, such as protons, are passing the various cuts.
+To compensate for this, additional cuts would need to be designed and applied, which would likely lead to reductions in expected Iron acceptance rate.
+
+In the event that the experimental method proves successful, it should be possible to use the exact position of the iron peak as a method of calibration for atmospheric absorption.
+An underestimate of the absorption would lead to an iron peak that was shifted to a charge number lower than 26, due to a lower than unexpected photon count.
+Similarly, the reverse would apply if the modelled atmospheric absorption was an overestimate.
+As these is much associated uncertainty in the atmospheric properties, this would be a useful measurement to perform.
+
+\subsection{High Speed Telescopes}
+By definition, a Cherenkov-Emitting Cosmic ray will be travelling faster than the light that it emits.
+The EAS shower will thus arrive on the ground shortly before the DC light.
+There are currently several ultra-high-speed Cherenkov telescopes capable of resolving the received light into narrow time bands.
+It should thus be possible for the telescope to directly measure the DC light in one image, and the EAS shower in another image.
+We can imagine the possible impact that such a telescope array would have on the reconstruction process.
+Directly measuring this light will provide a direct measurement of $True_{DC}$ for use in shower reconstruction.
+Although we saw that the value of $True_{DC}$ has a relatively large associated error, it could be used in various ways.
+Firstly, it could be used as an additional measurement to give a third LPD to be minimised.
+These extra $True_{DC}$ measurements could be included in any likelihood minimisation.
+Secondly, we could use the observation or non-observation of DC light to more reliably constrain the core position of DC light.
+At present, our reconstruction method can have a BDT-identified DC pixel even though there may not actually be DC light in the image.
+Thirdly, the $True_{DC}$ variable could be passed to the regressor that was trained on the full shower images.
+It is possible that this information may correlate well to other variables, and enable better regressor LPD reconstruction.
+
+\subsection{Optimised Telescope Array}
+The reconstruction process that was developed is generally applicable to all telescope arrays that image Cherenkov Light.
+This includes the Cherenkov Telescope Array (CTA), a planned array that is likely to have many more telescopes than HESS.
+As we have seen, the reconstruction process only works well for high-multiplicity events, but these represent only a small fraction of all HESS events.
+We can imagine how the expected Iron event rate might increase, were an alternate telescope array used.
+As the design for CTA has not been agreed, we can imagine what an optimum arrangement for CTA might be, for the purpose measure DC light using the method described here.
+To this end, we can consider a 3x3 array of Cherenkov Telescopes, which we want to use for identifying Cosmic Ray Elements accurately.
+We can vary the grid spacing, and determine the effect on expected count rate.
+In Figure \ref{fig:optmiselayout} we see the expected distribution of event multiplicities for varying grid width.
+While the overall detected event rate increases as grid width increases, we find that that the \textquoteleft High Multiplicity Count Rate' of events observed by 4 or more telescopes decreases with increasing grid separation.
+Competing with this effect is the reliance of LPD reconstruction on sampling the entire lateral distribution.
+Thus the reconstruction quality for a given multiplicity will likely decrease as Grid Width decreases.
+Nonetheless, it appears that the optimum grid spacing will likely lie in the 20-50m region to provide a reasonable count rate.
+This is likely to fully sample an LPD of typical radius $r_{max} \approx 100$, while clearly maintaining a reasonably high count rate.
+
 Further study of $\sigma_{Z}$ in this region is required to determine the optimum layout (not necessarily be a grid) for event reconstruction.
@@
 \end{figure}
-
-\subsection{Saturation Region Energies}
-Hillas reconstruction better
-Combine with Hillas reconstruction
-Apply to HESS data
-calibrate with position of Iron peak
-Real data
-
-\subsection{High Speed Telescopes}
-By definition, the EAS shower will arrive on the ground shortly before the DC light.
-There are currently several high-speed Cherenkov telescopes capable of distinguishing between these, allowing a background-free LDF to be fitted.
-Additional study of alternative energy regimes and layouts will also be considered for the case of a high-speed imaging telescope array.
 

### 2016-07-03 positioning/optimisez.py

@@ -11,7 +11,7 @@ def run(statsset, mindetections):
 	datasimset = pickle.load(open(statsset, 'rb'))
 	detectorcount = datasimset[0].ndetectors
 
-	plt.figure()
+	fig = plt.figure()
 
 	Z = 26
 	
@@ -20,13 +20,18 @@ def run(statsset, mindetections):
 	
 	optimumcuts = []
 	
+	ax1 = plt.subplot(2,1,1)
+	ax2 = plt.subplot(2,1,2)
+	
 	for j in range (detectorcount, mindetections -1, -1):	
 		print "Ndetections", j
 		lowestsigma = 10
+		lowestscalesigma=10
 		optimumbdt = 0.0
 		optimumpassing = 1.0
 		
 		meansigmas=[]
+		scalesigmas=[]
 		
 		bdtcuts =[]
 		
@@ -72,11 +77,11 @@ def run(statsset, mindetections):
 			if total > 0:
 			
 				frac = float(passing)/float(full)					
-				meanz = np.mean(specificcount)
-				meanz2 = np.mean(sqvals)
-				var = meanz2 - (meanz**2)
-				
-				meansigma=math.sqrt(var)
+				#~ meanz = np.mean(specificcount)
+				#~ meanz2 = np.mean(sqvals)
+				#~ var = meanz2 - (meanz**2)
+				#~ 
+				#~ meansigma=math.sqrt(var)
 				
 				specificcount.sort()
 		
@@ -88,46 +93,53 @@ def run(statsset, mindetections):
 				meanz = specificcount[mid]
 				upperz = specificcount[upper]
 				meansigma = (upperz-lowerz) * 0.5
+				scalesigma = meansigma/math.sqrt(frac)
 				
-
-				
-				if float(1.0) > float(frac) > float(0.50):
+				if float(frac) > float(0.01):
 					bdtcuts.append(BDTcut)
 					meansigmas.append(meansigma)
+					scalesigmas.append(scalesigma)
 					if float(24) < float(meanz) < float(28):
-						if float(meansigma) < float(lowestsigma):
-
+						if float(scalesigma) < float(lowestscalesigma):
 							lowestsigma=meansigma
+							lowestscalesigma = scalesigma
 							optimumbdt=BDTcut
 							optimumpassing = passing
-						
-		plt.plot(bdtcuts, meansigmas, label=line)
[…]

### 2016-07-03 positioning/plotheight.py

@@ -75,7 +75,7 @@ def run(statsset, mindetections, cuts):
 	
 	plt.annotate(info, xy=(0.8, 0.4), xycoords="axes fraction",  fontsize=10)
 	
-	n, bins, _ = plt.hist(fullcount, bins=15, label=labels, histtype='bar', stacked=True)
+	n, bins, _ = plt.hist(fullcount, bins=25, label=labels, histtype='stepfilled', stacked=True)
 	
 	mid = (bins[1:] + bins[:-1])*0.5
 	if isinstance(n[0], np.ndarray):

### 2016-07-03 positioning/plotlikelihood.py

@@ -59,7 +59,7 @@ def run(statsset, mindetections, cuts=None):
 								wrong.append(float(recon.BDTscore))
 			
 		total = len(correct)
-		info += "For BDT > " + str(bdtmin) + " Values \n"
+		info += "For BDT > " + str('{0:.2f}'.format(bdtmin)) + " Values \n"
 		for i in range(0, 3):
 			category = [correct, close, wrong][i]
 			name = ["correct", "close", "wrong"][i]
@@ -77,11 +77,11 @@ def run(statsset, mindetections, cuts=None):
 				plotlabel.append(label)
 			else:
 				passfrac = 0
-			info += ('For ' + str(name) + ' then ' + str(passfrac) + " events pass \n")
+			info += (str(label) + ' - ' + str('{0:.0f}'.format(100*passfrac)) + "% pass \n")
 	
 		if len(plot) > 0:
-			plt.hist(plot, color = plotcolour, bins = 50, stacked=True, label=plotlabel, histtype='bar')
-			plt.axvline(x=bdtmin,  color='r')
+			plt.hist(plot, color = plotcolour, range=[0,1], bins = 25, stacked=True, label=plotlabel, histtype='stepfilled')
+			plt.axvline(x=bdtmin,  color='k', linewidth=4)
 		
 		#~ for val in llcuts:
 			#~ plt.axvline(x=(val+0.01), linestyle='--', color='m', label="LL Cut")
@@ -89,13 +89,13 @@ def run(statsset, mindetections, cuts=None):
 		plt.xlabel('BDT Score')
 		plt.ylabel('Count', labelpad=0)
 		plt.legend()
-		plt.annotate(info, xy=(0.65, 0.45), xycoords="axes fraction",  fontsize=10)
+		plt.annotate(info, xy=(0.65, 0.75), xycoords="axes fraction",  fontsize=10)
 		title = str(j) + " Telescope Detections"
 		plt.title(title)
 	
 	figure = plt.gcf() # get current figure
-	figure.set_size_inches(20, 15)
+	figure.set_size_inches(15, 10)
 	plt.suptitle('BDT prediction of signal probability', fontsize=20)
-	
+	plt.savefig('/d6/rstein/Hamburg-Cosmic-Rays/report/graphs/Likelihood.pdf')
 	plt.savefig('/d6/rstein/Hamburg-Cosmic-Rays/positioning/graphs/Likelihood.pdf')
 	plt.close()

### 2016-07-03 positioning/plotposition.py

@@ -36,11 +36,11 @@ def run(statsset, mindetections, cuts):
 					if recon.BDTscore != None:
 						if float(bdtmin) < float(recon.BDTscore):
 							passing += 1
-							if cuts == None:
-								distance = math.sqrt(((recon.fullrayxpos-true.rayxpos)**2)+(recon.fullrayypos-true.rayypos)**2)
-								
-							else:
-								distance = math.sqrt(((recon.rayxpos-true.rayxpos)**2)+(recon.rayypos-true.rayypos)**2)
+							#~ if cuts == :
+								#~ distance = math.sqrt(((recon.fullrayxpos-true.rayxpos)**2)+(recon.fullrayypos-true.rayypos)**2)
+								#~ 
+							#~ else:
+							distance = math.sqrt(((recon.rayxpos-true.rayxpos)**2)+(recon.rayypos-true.rayypos)**2)
 							specificcount.append(distance)
 
 		total = len(specificcount)
@@ -73,7 +73,7 @@ def run(statsset, mindetections, cuts):
 	
 	
 	
-	n, bins, _ = plt.hist(fullcount, bins=20, label=labels, histtype='bar', stacked=True)
+	n, bins, _ = plt.hist(fullcount, bins=25, label=labels, histtype='stepfilled', stacked=True)
 
 	mid = (bins[1:] + bins[:-1])*0.5
 	

### 2016-07-06 report/final.tex
Post-Thesis Backup 06/07/16

--- 2016-07-03 report/draft1.tex
@@
 \usepackage{subcaption}
+\usepackage{setspace}
+\usepackage{afterpage}
+\newcommand\blankpage{%
+    \null
+    \thispagestyle{empty}%
+    \addtocounter{page}{-1}%
+    \newpage}
+\onehalfspacing
 
@@
 \begin{document}
+\afterpage{\blankpage}
 \begin{titlepage}
@@
 \section*{Abstract}
-Between impact with the upper atmosphere and decay into a charged particle shower, heavy cosmic ray elements such as Iron emit Cherenkov Light at an angle determined by the Refractive Index of the air and the energy per nucleon.
-This direct Cherenkov Light forms a characteristic circular light distribution on the Earth's surface with an intensity proportional to the square of the cosmic ray charge.
-A new method has been developed to reconstruct this charge number, by fitting the received Cherenkov Photons to the characteristic Lateral Photon Distribution.
-The expected performance for various existing and planned installations will be discussed.
+Between entry into the upper atmosphere and interaction with the lower atmosphere to produce a charged particle shower, heavy Cosmic Ray elements such as Iron will emit Cherenkov Light.
+This Direct Cherenkov (DC) Light forms a characteristic circular light distribution on the Earth's surface with an intensity proportional to the square of the cosmic ray charge.
+While the air showers will cover much of a telescope image, this DC light is usually concentrated in a single DC pixel.
+A new method of identifying these DC pixels was developed using a Boosted Decision Tree (BDT), leading to an eightfold increase in acceptance rate and a decrease in misidentification.
+A second new method was developed to reconstruct this charge number, by fitting the received Cherenkov Photons to the characteristic Lateral Photon Distribution (LPD).
+The reconstruction requires at least four DC pixels to be found simultaneously, with the new BDT identification method leading to a two-hundred-fold increase in such events being found.
+A likelihood minimisation enabled successful reconstruction of the Charge Z of such events.
+A charge resolution of $\sigma_{Z} \approx 1$ was observed, compared to a resolution of  $\sigma_{Z} \approx 5$ that existing techniques are capable of.
 
 \section*{Zusammenfassung}
-Between impact with the upper atmosphere and decay into a charged particle shower, heavy cosmic ray elements such as Iron emit Cherenkov Light at an angle determined by the Refractive Index of the air and the energy per nucleon.
-This direct Cherenkov Light forms a characteristic circular light distribution on the Earth's surface with an intensity proportional to the square of the cosmic ray charge.
-A new method has been developed to reconstruct this charge number, by fitting the received Cherenkov Photons to the characteristic Lateral Photon Distribution.
-The expected performance for various existing and planned installations will be discussed.
+Nach dem Eintritt in den oberen Atmosph\"{a}re und vor die Interaktion mit den unteren Atmosph\"{a}re, die eine Teilchenkaskade produziert, emmitiert schwere Kosmischiche Strahlung wie Eisern das Cherenkov-Licht.
+Dieses Direkt Cherenkov (DC) Licht produziert eine charakteristische kreisformige lichtkurze auf die Erdefl\"{a}che, die eine Intensit\"{a}t proportional zur Kernladungszahl zum Quadrat hat.
+Obwohl die Teilchenkaskade die Meisten des Telescopbilds besetzt, dieses Cherenkov-Licht wird normalerweise in einem einzelen Bildpunkt konzentriert.
+Ein neues Verfahren, das diesen DC-Bildpunkten mit einem Boosted Decision Tree (BDT) identifiziert, ist entwickelt.
+Es hat nicht nur zu einen achtmaligen Zunehmung der Akzeptiertenquote, sondern auch zu eine Verbessung der Misidentifikationsquote gef\"{u}hrt.
+Noch ein neues Verfahren, das die Ladungszahl durch einem Fit des Cherenkov-Lichts zum characteristische LPD rekonstruktiert, ist entwickelt.
+Solche Rekonstruktion braucht gleichzeitig mindestens 4 DC-Bildpunkten, die das neues BDT-Verfahren zeihundertmal so oft finden kann.
+Dadurch ist eine W\"{a}hrscheinlichkeitsminimierung
+m\"{o}glich, die zum Rekonstruktion der Laudungszahl f\"{u}hrt.
+Letztendlich beobachten wir eine Ladungszahlaufl\"{o}sung von $\sigma_{Z} \approx 1$, die vergleichbar mit den heutigen Aufl\"{o}sung von $\sigma_{Z} \approx 5$ ist.
 \newpage
@@
 \section{Preface}
+This analysis was conducted in the Astroteilchenphysik group of Universit\"{a}t Hamburg between October 2015 and July 1016.
+It was supervised by Professor Dieter Horns who, in addition to invaluable guidance and never-ending patience, proposed both the original aim of the project and the concept of LPD reconstruction.
+It was further supported by Attila Abramowski, whose overlapping field of research provided invaluable opportunities for discussion and comparison.
+
 The basis of this thesis work can be divided into two halves.
-The first half is the simulation of cosmic ray HESS camera images, and analysis work based on these images.
+The first half is the simulation of Cosmic Ray HESS camera images, and analysis work based on these images.
 The second half is a Monte Carlo study simulating air shower intensities, based entirely on function fitted from the HESS camera images.
-
-It is important to note that the simulation of cosmic ray air showers for the first part of my thesis was performed using the CORSIKA software \cite{Heck98}, and the resultant HESS camera images were produced using the Sim\textunderscore Tel array software \cite{Bernlohr08}.
+It is important to note that the simulation of Cosmic Ray air showers for the first part of my thesis was performed using the CORSIKA software \cite{Heck98}, and the resultant HESS camera images were produced using the Sim\textunderscore Telarray software \cite{Bernlohr08}.
 I claim no credit for the complex simulations that these packages have enabled me to perform.
@@
 
-Aside from this, all other work in this thesis is my own. I wrote all necessary code for the Monte Carlo simulation, and it was conducted entirely by me. Similarly
-
-Thank Dieter, and Attilla, and...
+Furthermore, a part of this analysis was based on comparison with existing methods for reconstructing Cosmic Ray Charge Number that were performed by the HESS collaboration \cite{hess07}.
+Their groundwork based on the first phase of the HESS array was both a guide and a standard for my efforts at reconstruction.
+
+Aside from this, all other work described here is my own.
+In particular, I wrote scripts to read the Sim\textunderscore Telarray output, convert raw voltages to calibrated pixels Intensities, and to plot the HESS camera images such as that found in Figure \ref{fig:DCtelimage}.
+Furthermore, I wrote all necessary code for the Monte Carlo simulation, and it was conducted solely for this analysis.
 \newpage
@@
 The exact Cosmic Ray composition is energy dependent, and provides information regarding their sources.
-Heavy Cosmic Rays, the most common of which is iron, vary substantially in relative abundance for different energy scales.
+Heavy Cosmic Rays, the most common of which is Iron, vary substantially in relative abundance for different energy scales.
 
@@
 However, it is possible to use the non-observation of light in one telescope to constrain the core position.
-Thus, we require that an event was be seen by at least four telescopes for a five-telescope array such as HESS.
+Thus, we will seek events seen by at least four telescopes for a five-telescope array such as HESS.
 An illustration of the HESS array is shown in Figure \ref{fig:hessdiagram}.
@@
 Because the refractive index of air increases very quickly as the height decreases, the Cherenkov Angle $\theta_{C}$ will also increase rapidly with decreasing height.
-Thus, although the displacement $(h - altitude_{array})$ decreases as the height, the radius on the ground increases as height decreases.
-Consequently the upper atmosphere emission contributes to the inner LDF, while the lower atmosphere emission contributes to the outer LDF.
+Thus, although the displacement $(h - altitude_{array})$ decreases with height, the radius on the ground will nonetheless increase as height decreases.
+Consequently the upper atmosphere emission contributes to the inner LPD, while the lower atmosphere emission contributes to the outer LPD.
 As the cosmic ray travels down through the atmosphere, Cherenkov Emission continuously illuminates new areas on the ground that were previously unlit, without re-illuminating inner regions.
@@
 The maximum radius of the DC light will then be $r_{max} = Radius(h_{int})$.
-This is extremely useful, because for all distances up to $r_{max}$, the LPD will be completely independent of the emission height.
+This is extremely useful, because for all distances up to $r_{max}$, the LPD will be completely independent of the interaction height.
 One full parameterisation of the LPD will thus be valid for all heights, provided the maximum radius is known.
@@
 
-A full simulation of the LPD was undertaken, with the assumption that $\Delta_{E} \approx 0.7$ independent of Energy.
+A full simulation of the LPD was undertaken, with the assumption that $\Delta_{E} \approx 0.7 eV$ independent of Energy.
 Although this is certainly an oversimplification of the true picture, it will allow us to understand the variation of the LPD with height.
@@
 
-If we divide the number of emitted photons by the area of the annulus between the ring radii at $h$ and $h - \Delta_{h}$, we retrieve the LDF shown in \ref{fig:lpd}, which varies with $ \rho_{DC}  = f(r) \times Z^{2}$ .
-Thus the amplitude of the LDF is proportional to the square of the Cosmic Ray charge, enabling us to reconstruct this number from the DC emission.
-This proportionality is the basis for charge reconstruction in the LDF method.
+If we divide the number of emitted photons by the area of the annulus between the ring radii at $h$ and $h - \Delta_{h}$, we retrieve the LPD shown in Figure \ref{fig:lpd}, which varies with $ \rho_{DC}  = f(r) \times Z^{2}$ .
+Thus the amplitude of the LPD is proportional to the square of the Cosmic Ray charge, enabling us to reconstruct this number from the DC emission.
+This proportionality is the basis for charge reconstruction in the LPD method.
 
@@
 The red and green and magenta line show the emission radius at 3.57 and 0.75 and 0.23 TeV per Nucleon respectively.
-The Green line is sufficiently close to the background to be saturated at 24km, while the magenta line is not.}
+The Green 0.7 TeV line is sufficiently close to the background to be saturated at 24km, while the magenta line is not.}
 \label{fig:generalenergy}
@@
 \caption{Above, the refractive index is shown with both linear and exponential interpolation between the known values.
-The LPD obtained from simulation of an Iron Nucleus up to a first interaction height of 25km for a range of Core Energies.
+The LPD obtained from simulation of an Iron Nucleus up to a first interaction height of 20km for a range of Core Energies.
 An altitude of 1.8km for the experimental array is assumed.
@@
 Despite the exponential interpolation, discontinuities in the second derivative of the refractive index prevent the LPD from being smooth in the simulation.
-This is unimportant, because in reality the variation due to atmospheric conditions and random noise will smear out any discontinuities in the LDF.
+This is unimportant, because in reality the variation due to atmospheric conditions and random noise will smear out any discontinuities in the LPD.
 
@@
 \subsection{Classic HESS1 DC Pixel Identification}
-We can find the DC pixel in am image by defining the variable $Q_{DC} = \frac{Intensity_{N.N.max}}{Intensity}$ as the ratio of the largest neighbouring pixel intensity to the intensity of a given pixel.
+We can find the DC pixel in an image with the variable $Q_{DC}$.
 In previous experiments, the DC pixel candidate was identified by applying a number of cuts to pixels in an image \cite{hess07}, and from the subset of pixels passing the specified cuts, selecting the pixel with the smallest $Q_{DC}$ as the \textquoteleft DC candidate'.
@@
 In the original analysis, an additional cut $r_{core} \textgreater 40m$ was applied.
-However, the uncertainty in determining the core position through Hillas Analysis is typically of the order of $\pm 30m$.
-Consequently, this particular cut was omitted.
+However, the uncertainty in determining the core position through Hillas Analysis is typically of the order of $\pm 20m$.
+Consequently, this particular cut was omitted, though it would only serve to further reduce the DC pixel acceptance rate.
 
@@
 The maximum depth of a tree is the number of branches a decision chain can pass through before it must end on a leaf.
-The minimum leaf sample is the minimum number that every leaf has sample must exceed.
-Either of these quantities can be used to restrict overtraining of a Decision Tree.
+The minimum leaf sample is the minimum number that every leaf sample must exceed.
+Either of these quantities can also be used to restrict overtraining of a Decision Tree.
 
@@
 The results are summarised in Table \ref{tab:qdcbdtcomparison1}.
-The BDT method represents a clear improvement in DC pixel identification over the previous $Q_{DC}$ method, and corresponds to a fifteen-fold increase in identified pixels.
+The BDT method represents a clear improvement in DC pixel identification over the previous $Q_{DC}$ method, and corresponds to an eightfold increase in identified pixels.
 
@@
 Based on CT5 images from the training sample, an increased 5.6\% of DC pixels were correctly identified and passed the required cut.
-A further 11.3 \% of all pixels passed the cuts, despite being misidentified.
-This represented a very heavy decrease in sample purity to just 33.0\%.
+A further 14.8 \% of all pixels passed the cuts, despite being misidentified.
+This represented a very heavy decrease in sample purity to just 27.5\%.
 We can assume that better optimised CT5 cuts could remove many of these misidentified events, though it is unlikely that any significant improvement in the number of correctly identified DC pixels would be possible.
 Thus, the number of DC pixels successfully identified using the $Q_{DC}$ method is still a valid benchmark for comparative BDT performance.
-A true accuracy rate closer to the HESS 1 rate of 90\% could be expected, at the expense of a depressed acceptance rate.
+A true accuracy rate closer to the HESS 1 rate of 80\% could be expected, at the expense of a depressed acceptance rate.
 Due to the distinctiveness of the CT5 telescope hardware, direct application of the HESS1 classifier to the CT5 telescope yields poorer BDT performance.
-Discrepancies in To improve CT5 pixel identification, a separate HESS2 BDT was instead trained with the same variables as above.
+To improve CT5 pixel identification, a separate HESS2 BDT was instead trained with the same variables as above.
 The relative feature importance is listed in Table \ref{tab:hess2classifier}.
@@
 Despite the minor performance difference, the BDT method is clearly superior in both cases.
-On top the gains in BDT accuracy when considering only high-multiplicity events high multiplicity events, we also find the relative performance gap over the $Q_{DC}$ method is vastly increased.
+On top the gains in BDT accuracy when considering only high-multiplicity events, we also find the relative performance gap over the $Q_{DC}$ method is vastly increased.
 As a result of the two-hundred-fold increase in acceptance rate for high-multiplicity-BDT events against high-multiplicity-$Q_{DC}$ events, the expected data sample size will increase dramatically.
@@
   \centering
-  \caption{Comparison of high-multiplicity performance Performance}
+  \caption{Comparison of high-multiplicity performance}
   \label{tab:highmultiplicitycomparison}
@@
 Applying a cut requiring Aspect Ratio $> 0.40$ eliminated all accepted proton events for HESS1 and HESS2.
-With 17792 total HESS1 images, just 6195 images were triggered by DC light.
-Of all 17792 images, there were none passing all of the required cuts.
+With 18844 total HESS1 images, just 6195 images were triggered by DC light.
+Of all 18844 images, there were none passing all of the required cuts.
 
@@
 
-Thus, if we have thirtyfold increase in event rate, but only one-fifteenth the acceptance rate, we would ultimately expect that we would have twice as many Iron Events if the full energy range of 5-135 TeV was included.
-However, the low-energy proton acceptance is much higher.
+Thus, if we have thirtyfold increase in event rate, but only one-fifteenth of the original acceptance rate, we would ultimately expect that we would have twice as many Iron Events if the full energy range of 5-135 TeV was included.
+However, the low-energy proton acceptance is much higher than before at 0.21\%.
 Thus, were we to include all events in this energy range, we would again retrieve a sample dominated by protons.
@@
 The majority of accepted protons have an Energy of less than 10 TeV, and the largest recorded Energy was 21.6 TeV.
-We can thus require that the reconstructed Energy is greater than 30TeV.
+We can thus require that the reconstructed Energy is greater than 35TeV.
 This will, assuming a rough energy resolution of around 15\% in reconstruction, easily remove all of the proton background.
@@
 \section{Parameterisation of the LPD}
-Having identified DC pixels in a reliable way without accompanying background events, we can now consider the resultant LPD.
+Having identified DC pixels in a way that is both reliable and consistently removes background events, we can now consider the resultant LPD.
 We must parameterise this function before we are able to reconstruct events.
-We can also account for additional information provided in the EAS light.
+We can also make use of the additional information provided by the EAS light in each shower image.
 
@@
 Having restricted ourselves to high-multiplicity events, we reduce our data sample to mostly images in which air shower lies relatively close to the center of the telescope field of view.
-We can conclude that in many of our images, the air shower will lie mostly within the telescope image.
-In the same way as for DC light, we can firstly look for the existence of a Characteristic LPD describing the EAS Intensity, where we define $I_{tot}$=Image Amplitude.
+We can conclude that in many of our images, the air shower should be mostly contained within the telescope image.
+In the same way as for DC light, we can firstly look for the existence of a Characteristic LPD describing the EAS Intensity, which we define as $I_{tot}$=Image Amplitude.
 The results for high-multiplicity events at various energies is shown in Figure \ref{fig:fullshowerlpd}.
@@
 The data is fitted with a line of the form $y_{i} (x) =A_{i} \exp (K_{i} x)$.
-The fractional deviation from the fit is found for each point by calculating $\Delta_{EAS} = \frac{fit_{EAS} - I_{tot}}{fit_{EAS}}$.
-We can then take the 68\% interval values for fractional deviation to give a fractional uncertainty $\sigma_{EAS}$.
-Across all Energies, the mean fractional deviation from the fitted exponential was roughly 0.15.
 For the purposes of reconstruction, an exponential decay with a varying exponent and amplitude will not be particularly useful, because there are two degrees of freedom.
@@
 The fitted Amplitudes $A_{i}$ are then recorded, and are also plotted in Figure \ref{fig:powerlawlpd}.
-A clear relationship is again observed, in this an exponential law.
+A clear relationship is again observed, this time an exponential law.
 A straight line is fitted to the logarithm of the data values, and we retrieve a second relationship describing the amplitude as a function of the Energy.
@@
 These fitted LPDs are also plotted in Figure \ref{fig:fullshowerlpd}.
-The fractional deviation bands are also shown in green, with a mean fractional deviation of roughly 0.15 across the energies.
+The fractional deviation from the fit is found for each point by calculating $\Delta_{EAS} = \frac{fit_{EAS} - I_{tot}}{fit_{EAS}}$.
+We can then take the 68\% centile values to give us a $\sigma$-fraction width, and thus a fractional standard deviation $\frac{\sigma_{EAS}}{fit_{EAS}}$.
+The fractional standard deviation bands are shown in green, with a mean value of $\frac{\sigma_{EAS}}{fit_{EAS}}=0.15$ across the energies.
+We will make an approximation by assuming this value is a constant, though this is not strictly true.
 The Full Shower LPDs continue to be large enough to trigger telescopes for several hundred meters.
@@
 Although this reconstruction will be inferior to one accounting for both LPDs, we can make use of the preliminary core position estimate to aid our calculation of $True_{DC}$.
-This in turn should reduce the uncertainty when determining the charge of the primary particle.
+The information from the full-shower LPD will also be incorporated into our final likelihood minimisation, when we reconstruct the events.
 
@@
 \subsection{Determining $True_{DC}$}
-Before we can extract the DC LPD from telescope imagesTo determine the value of $True_{DC}$ is essential for determining the error in our LPD measurements.
+Before we can extract the DC LPD from telescope images, we must first decide how to measure the quantity of DC light, $True_{DC}$.
+Determining the value of $True_{DC}$ is essential for determining the error in our LPD measurements.
 However, there are two natural ways of quantifying $True_{DC}$.
@@
 As a result of the smaller angular region covered by each CT5 pixel, this happens much more frequently for HESS2 than for HESS1.
-A countervailing argument is the susceptibility of the Image Amplitude measurement to edge effects.
+On the other hand, Image Amplitude measurement is susceptible to edge effects.
 A DC pixel lying near the image edge will be unaffected by this fact, but the total image amplitude may decline because dimmer pixels move over the image edge.
@@
 A study of 2000 events was conducted, in which each cosmic ray was simulation without night sky background or EAS background.
-Each telescope image simulation was conducted twice, and difference between $I_{1}$ and $I_{2}$ was plotted as in \ref{fig:simtelerror}.
+Each telescope image simulation was conducted twice, and difference between $I_{1}$ and $I_{2}$ was plotted as in Figure \ref{fig:simtelerror}.
 The fractional difference from the mean Intensity of an image was defined as $\Delta = 2 \times \frac{I_{2} - I_{1}}{{I_{2} + I_{1}}}$.
 
-For $I_{tot}$, it was found that the standard deviation in fractional difference was $\sigma_{Itot}=0.06$, meaning that there is an inherent error of 6 \% in measurements of $True_{DC}$.
+For $I_{tot}$, it was found that the standard deviation in fractional difference was $\frac{\sigma_{Itot}}{I_{tot}}=0.06$, meaning that there is an inherent error of 6 \% in measurements of $True_{DC}$.
+This is reasonably low, and can be predominantly explained by the random nature of Photomultiplier Tubes (PMTs) that are used to measure the Photon Intensity in each pixel.
 In later calculations of the error in Intensity, this fractional error can be subtracted in quadrature.
 The distribution did not vary between HESS1 and HESS2 telescopes.
-For the alternative $Intensity_{max}$ measurement, the standard deviation was $\sigma_{Imax}=0.09$ for HESS1 and $\sigma_{Imax}=0.12$, a clear increase.
+For the alternative $Intensity_{max}$ measurement, the fractional standard deviation was $\frac{\sigma_{Imax}}{I_{max}}=0.09$ for HESS1 and $\frac{\sigma_{Imax}}{I_{max}}=0.12$ for HESS2, a clear increase.
 This implies that the $I_{tot}$ measurements are more reliable.
@@
 The fractional deviation $\Delta_{TrueDC} = \frac{signal_{fit} - True_{DC count}}{signal_{fit}}$ can then be found.
-Using the 68th centile of all absolute fractional deviations $\Delta_{TrueDC}$, we find that the HESS LPD for $I_{tot}$ has an error of $\sigma_{Itot}=0.35$.
-Repeating for $Intensity_{max}$ calculated values, the resultant LPD had an error of $\sigma_{Imax} = 0.40$.
-Again, it is clear that the $I_{tot}$ value has a smaller associated error than $Intensity_{max}$.
-
-It is interesting to note that the values of $I_{max}$ and $DC_{count}$ are strongly correlated with one another.
-The mean fractional deviation between $I_{max}$ and $DC_{count}$ is relatively small, at 0.34.
+Using the 68th centile of all absolute fractional deviations $\Delta_{TrueDC}$, we find that the HESS LPD for $I_{tot}$ has an error of $\frac{\sigma_{Itot}}{I_{tot}}=0.48$.
+Repeating for $Intensity_{max}$ calculated values, the resultant LPD had an error of $\frac{\sigma_{Imax}}{I_{max}} = 0.51$.
+Again, it is clear that $I_{tot}$ has a smaller associated error than $I_{max}$.
+
+It is interesting to note that the values of $I_{max}$ and $DC_{count}$ are correlated with one another, more than with $I_{tot}$.
+The fractional standard deviation between $I_{max}$ and $DC_{count}$ is relatively small, at 0.34.
 It is found that the $I_{max}$ value, and by extension the $DC_{count}$ value, consistently underestimates the quantity of DC light in an image.
@@
 
-We must find the error $\sigma_{LPD}$ in our calculated values for $candidate_{DC count}$, through comparison with the correct value $True_{DC}$.
-However, $True_{DC}$ also has an associated error $\sigma_{STA}$, originating in the use of internal random numbers for Sim\textunderscore telarray simulations.
-If we neglect to account for this $\sigma_{STA}$, our final $\sigma_{calculated}$ will be an overestimate that also includes the random fluctuation of $True_{DC}$ around the actual DC intensity.
-As we cannot directly measure the actual DC intensity, we must instead measure $\sigma_{TrueDC}$.
+However, we know that in reality $True_{DC}$ will also have an associated error $\sigma_{STA}$.
+This error originates in the use of internal random numbers for Sim\textunderscore telarray simulations, and means that a given air shower is not completely reproducible.
 Having selected a method for determining $True_{DC}$, we can use the associated value of $\sigma_{STA}=0.06$.
@@
 
-Taking account of $\sigma_{STA}$, we deduce that the true associated error in the LPD is $\sigma_{TrueLPD} = \sqrt{(\sigma_{TrueDC}^{2} - \sigma_{STA}^{2})} = 0.11$.
-Thus we conclude that, in an ideal case, any LPD measuring pure DC light would always have a minimum error of 11\%.
-This is reasonably high, and can be partially explained by the random nature of atmospheric conditions, among other things.
-
-The same exercise was repeated using the value of $DC_{Count}$ for the BDT candidate pixels in a full shower image, if the pixel had passed both the $DC_{Count}$ and $P_{signal}$ cuts.
-This provides a more reasonable estimate of the expected LPD error likely to be obtained experimentally, and includes the additional complication of having incorrectly identified pixels in the dataset.
-As before, the absolute fractional deviation of each pixel from the fit of the $True_{DC}$ LPD was found.
-Due to consistent underestimate of the $True_{DC}$ value using the simple $DC_{Count}$ method, the error was much larger, with $\sigma_{DCcount}=0.57$ and the $\sigma_{STA}$ being negligible in comparison.
-This representative error is extremely large, and will pose significant problems for event reconstruction.
+Taking account of $\frac{\sigma_{STA}}{I_{tot}}$, we deduce that the true associated error in the LPD is $\frac{\sigma_{TrueLPD}}{{True_{DC}}} = \sqrt{(\frac{\sigma_{TrueDC}}{True_{DC}}^{2} - \frac{\sigma_{STA}}{{True_{DC}}}^{2})} = 0.48$.
+Thus, we conclude that the error $\sigma_{STA}$ is broadly negligible, and in an ideal case, any LPD measuring pure DC light would always have a minimum error of 48\%.
+This is extremely large, and suggests that the atmospheric emission height may play a strong role in absorption of DC light.
+We had previously assumed that the amplitude of the LPD might not really be dependent of height.
+
+This suspicion was tested through a second simulation of 56 TeV Iron Events with a fixed interaction height of 20km.
+In this case, the recorded fractional standard deviation was $\frac{\sigma_{TrueDC}}{True_{DC}}=0.14$, a very significant improvement.
+This clearly confirms that there is a significant degree of LPD dependence of height, and that this far exceeds variations from small changes in charge number.
+Whether this will prevent us from using the LPD technique to reconstruct events depends on whether the measurements we make of the DC light will be independent of height.
+It may be possible to account for the varying interaction height.
+
+One way of measuring the emitted DC light would be to use the variable $DC_{Count}$.
+The same fractional standard deviation calculations for varying first interaction height was repeated with this variable for the BDT candidate pixels in a full shower image, if the pixel had passed both the $DC_{Count}$ and $P_{signal}$ cuts.
+This provides a more reasonable estimate of the expected LPD error we are likely to be obtained experimentally, and also includes the additional complication of having incorrectly identified pixels in the dataset.
+As before, the fractional standard deviation of each pixel from the fit of the $True_{DC}$ LPD was found.
+Due to consistent underestimate of the $True_{DC}$ value using the simple $DC_{Count}$ method, the error was much larger, with $\frac{\sigma_{DCcount}}{DC_{count}}=0.43$ and the $\sigma_{STA}$ again being negligible in comparison.
+Interestingly, this is a slight improvement over the value of $True_{DC}$.
+It is likely that this is explained by the atmospheric absorption as a source of measurement uncertainty.
+Although the quantity of received DC light will be dependent on atmospheric absorbance, so will the EAS Shower Intensity that is present in the neighboring pixels.
+Thus, when subtracting the mean neighbouring Intensity of the DC pixel, the variation in $True_{DC}$ will be somewhat reduced.
+Despite the minor improvement, this representative error is extremely large, and will pose significant problems for event reconstruction.
 
@@
 
-Accurate measurement of the value of $True_{DC}$ is hindered because the DC light can be split into multiple pixels.
-Instead of the brightest pixel intensity the total Image Amplitude in the EAS free image was used.
-However, for high altitude/zenith angles, the DC light may lie partially outside the telescope image.
-To remove all associated uncertainty, a fitted parameterisation was used based on the LPD for $True_{DC}$.
+Training of a BDT is significantly impeded by the huge uncertainty in $True_{DC}$.
+A BDT regressor is unlikely to be able to improve upon the error in the original training values.
+To remove all associated uncertainty, a fitted parameterisation was used based on the LPD for $True_{DC}$ rather than the actual values of $True_{DC}$.
+The parameterisation, most importantly, will be independent of first interaction height.
 
@@
 
-For convenience, an offset $C=-6.5$ was omitted, yielding a simple exponential law.
-Counter-intuitively, it does in fact not matter whether the training values bear any close relation to the $True_DC$ values.
-The only values that we can use for reconstruction are our $candidate_{DC count}$, based on the DC candidate pixel and full-shower image.
-As long as these $candidate_{DC count}$ values are proportional to $Z^{2}$, the reconstruction method will remain valid.
-We train the regressor to interpolate the value of $True_{DC}$ using a number of variables, and most importantly, we include the True distance to the Core and the true energy among the regressor variables listed in Table \ref{tab:regressor}.
-
+We train the regressor to interpolate the value of y(r) using a number of variables, and most importantly, we include the True distance to the Core and the true energy among the regressor variables.
+These values will be exactly known for the purposes of training, and known with a roughly 10\% uncertainty when an event is reconstructed.
+The full variable list in given in Table \ref{tab:regressor}.
+
+For convenience, an offset $C=-6.5$ in y(r) was omitted, yielding a simple exponential law.
+Counter-intuitively, it does in fact not matter whether the training values bear any direct relation to the $True_{DC}$ values.
+The only values that we need for reconstruction are our $DC_{rgr}$ values, based on the DC candidate pixel and full-shower image.
+As long as these $DC_{rgr}$ values are proportional to $Z^{2}$, the reconstruction method will remain valid.
 In theory, any parameterisation would be valid for the regressor to train with.
@@
 Thus, if we were to choose a completely outlandish parameterisation that did not correlate to the images at all, the only useful variable would be the true core distance.
-As we do not exactly know the core distance, we would also have a large uncertainty in $candidate_{DC count}$.
+As we do not exactly know the core distance, we would also have a large uncertainty in $DC_{rgr}$.
 Because no additional information would be present in the resultant LPD, any reconstruction would not provide reduction in core position or charge resolution measurement.
@@
 If suitably trained, the regressor would consider the core position as a factor, but also correlate it with other variable related to the image.
-Then, given an estimate of the core distance, the regressor is able to produce a value of $candidate_{DC count}$ with some small error, that is still proportional to $Z^{2}$.
-The training set of data consisted of one true DC pixel entry in each full shower image.
-
+Then, given an estimate of the core distance, the regressor is able to produce a value of $DC_{rgr}$ with some small error, that is still proportional to $Z^{2}$.
+To be successful, we require the BDT to make of use of many other variables in addition to $DC_{count}$.
+If the BDT can do so, it will have a far smaller related uncertainty than the values of $True_{DC}$ by also taking the varying interaction height into account.
+
+The training set of data for the BDT consisted of one true DC pixel entry in each full shower image.
 The training sample contains, in equal proportion, elements Manganese (Z=25), Iron (Z=26) and Cobalt (Z=27).
@@
 If the regressor is capable of distinguishing between these three elements, then this will serve as a sufficient proof of concept.
-We expect that, were an entire spectrum of cosmic ray elements simulated, a regressor could be trained with similar performance for a large charge range.
+We expect that, were an entire spectrum of Cosmic Ray elements simulated, a regressor could be trained with similar performance for a large charge range.
 The training of such a BDT was not done as part of this analysis, due to computing time restraints.
@@
 
-To account for the differing hardware, a separate regressor was trained, as before, for the CT5 camera.
-The Feature Importances for the HESS1 and HESS2 regressor are listed in Table \ref{tab:regressor}..
+As before, a separate BDT was trained to account for the differences in hardware for the CT5 camera.
+The Feature Importances for the HESS1 and HESS2 regressor are listed in Table \ref{tab:regressor}.
 There is little discrepancy in variable importance between the two BDTs.
@@
 
-Repeating the comparison for the HESS1 regressor, we find for $\sigma_{rgr} = 0.14$, a significant improvement over $\sigma_{DCcount}$.
+Repeating the comparison for the HESS1 regressor, we find for $\frac{\sigma_{rgr}}{DC_{rgr}} = 0.14$, a significant improvement over $\sigma_{DCcount}$.
 The plotted LPD is seen in Figure \ref{fig:corsikalpd1}.
@@
 In this way, we can include the information from these DC pixels in later analysis, while accounting for the larger uncertainty in their LPD measurements.
-For images which do pass only the multiplicity cuts, but not the $P_{signal}$ or $DC_{count}$ cuts, we find that the regressor error is $\sigma_{rejected1}=0.15$.
-We can thus make use of these points, because they follow an almost identical distribution.
-
-STUFF
+For images which do pass only the multiplicity cuts, but not the $P_{signal}$ or $DC_{count}$ cuts, we find that the regressor error is $\frac{\sigma_{rejected}}{DC_{rgr}}=0.15$.
+It would be interesting to incorporate the information from these pixels into reconstruction, but doing so would remove our ability to constrain the core.
+Further study could attempt to use the rejected pixels, though the performance of the regressor on images without DC light would first need to be thoroughly tested to account for the possibility that rejected pixels belong top images without DC light.
+Because the BDT regressor functions as a Black Box, it is difficult to know how it is using the information from camera images to calculate $DC_{rgr}$.
+To ensure the validity of our Monte Carlo simulation, we will omit the rejected pixels as part of this analysis.
 
@@
   \centering
-  \caption{Fractional error from fitted 56-TeV LPD distribution up to $r_{core}=90$, accounting for $\sigma_{STA}$}
+  \caption{Fractional error from fitted 56-TeV LPD distribution}
   \label{tab:lpderror}
@@
     \midrule
-    $\sigma_{TrueDC}$ & 0.13 & 0.29\\
-    $\sigma_{DCcount}$ & 0.69 & 0.91\\
-    $\sigma_{rgr}$ & 0.27 & 0.53\\ 
-    $\sigma_{rejected}$ & 0.32 & 0.43\\ 
+    $\sigma_{TrueDC}$ & 0.48 & 0.61\\
+    $\sigma_{DCcount}$ & 0.43 & 0.58\\
+    $\sigma_{rgr}$ & 0.14 & 0.16\\ 
+    $\sigma_{rejected}$ & 0.15 & 0.17\\ 
     \bottomrule
@@
 \subsection{Iron Flux and Energy}
-Iron nucleii, like all Cosmic Rays, follow a well-defined power law where $\phi(E) = \frac{dN(E)}{dt} = \phi_{0} E^{-\gamma} $ for some constant k.
+Iron nucleii, like all Cosmic Rays, follow a well-defined power law where $\phi(E) = \frac{dN(E)}{dt} = \phi_{0} (\frac{E}{TeV})^{-\gamma} $ for some constant $\gamma$ \cite{hess07}.
 Using the SIBYLL model for Cosmic Ray Simulation, we assume that $ \gamma = 2.76 \pm 0.11 $ and $\phi_{0}=0.029 \pm 0.01 m^{-2} s^{-1} sr^{-1} TeV ^{-1}$ \cite{hess07}.
@@
 
-\[ F(35-135TeV) = \int_{35}^{135} \phi_{0} E^{-2.76} dE = \frac{\phi_{0}}{1.76}[35^{-1.76} - 135^{-1.76}] = 2.86 \times 10^{-5} m^{-2} s^{-1} sr^{-1}\]
+\[ F(35-135TeV) = \int_{35}^{135} \phi_{0} (\frac{E}{TeV})^{-\gamma} dE = \frac{\phi_{0}}{1.76}[35^{-1.76} - 135^{-1.76}] = 2.86 \times 10^{-5} m^{-2} s^{-1} sr^{-1}\]
 
@@
 The HESS telescope additionally has a solid and field of view of 5 degrees (0.006 steradians),meaning an expected telescope array Iron Flux of $F(35-135TeV) = 0.0154 s^{-1}$.
-On the basis of efficiency calculations in DC pixel identification, it is clear that 2.2\% of Iron Ray events will produce high-multiplicity DC pixels accepted by the BDT.
+On the basis of efficiency calculations in DC pixel identification, it is clear that 2.3\% of Iron Ray events will produce high-multiplicity DC pixels accepted by the BDT.
 Thus, we will ultimately obtain an hourly flux of $F(35-135TeV) = 3.40 \times 10^{-4} s^{-1} = 1.22 h^{-1}$ high-multiplicity Iron events.
@@
 The energy E is defined as the lower bound of the integral which would produce the chosen integrated flux F.
+R can also be interpreted fraction of events that will have a larger energy than the simulated cosmic ray does.
 Thus R=0 corresponds to an Energy of 135TeV yielding no Integrated Flux, while R=1 would correspond to an Energy of 35TeV and the full Integrated Flux.
-Thus the simulated Cosmic Rays will obey the power law, with high-energy events being realistically suppressed.
+The simulated Cosmic Rays will therefore obey a realistic power law, with high-energy events being suppressed.
 
@@
 Cosmic Rays survival in from the top of the atmosphere follows an exponential decay with the number of 'interaction lengths' passed.
-
 The mean free path $\ell$ of a Cosmic Ray is a function of atmospheric cross section and number density, which are themselves functions of  height, so that $\ell(h) = \frac{1}{\sigma(h) n(h)}$.
@@
 \includegraphics[height=0.9\textheight]{hessheight}
-\caption{The mean first interaction height for all Cherenkov Events is 40km???.
+\caption{The mean first interaction height for all Cherenkov Events is 40km.
 Events in blue met the multiplicity threshold, with DC light in four telescopes.
-The mean first interaction height for four telescope events in the HESS array is 23km}
+The mean first interaction height for all Cherenkov events is 30km, while for high-multiplicity events in the HESS array it is 23km.}
 \label{fig:Hessheight}
@@
 
-Another parameter exponentially interpolated using the data tables is the optical depth to the surface, $\tau$.
+Another parameter that could be exponetially the optical depth to the surface, $\tau$.
 The Cherenkov Light, mostly emitted in the visible blue part of the EM spectrum, experiences relatively little atmospheric absorption.
@@
 For a given emitted intensity $I_{0}$ we find that the corresponding I received on the ground decays exponentially with optical depth, so that $\frac{I}{I_{0}}=e^{-\tau}$ with $\tau=\int_{0}^{l}ds$.
-
-MOAR!!!
+However, the CORSIKA parameterisation has already accounted for any influence of atmospheric absorption.
+It is likely that this, in part, contributed to the value of $\sigma_{DCrgr}$.
 
@@
 \caption{The fraction deviation from true energy is shown above.
-For events with five-telescope multiplicity, the fractional error is X but for four-telescope multiplicity, it is Y.
+For events with five-telescope multiplicity, the fractional error is 0.06 but for four-telescope multiplicity, it is 0.12.
 The expected poissonian error bars are also shown.}
@@
 \end{figure}
+
 A graph showing the difference between the distance from telescope to true core position, and the distance from telescope to this reconstructed core position.
@@
 \includegraphics[width=\textwidth]{rawcoredistance}
-\caption{The distance from true core to the core reconstructed with the full-LPD is shown above. For four-telescope events, the standard deviation from true position is Xm. }
+\caption{The distance from true core to the core reconstructed with the full-LPD is shown above.
+For 4-tel events the standard deviation from true core distance is 16.4m while for 5-tel events, it is 9.7m.}
 \label{fig:rawcoredistance}
@@
 We can partially explain this by considering events which are likely to have 5 DC pixels.
-In such a case, the SOMETHING...
+In such a case, the core is likely to be restricted to a central ring in the region between CT5 and the outer telescopes.
+This relatively strong confinement reduces the potential for misreconstruction of the core position, and this indirectly improves reconstruction of the other variables.
 
@@
 This is shown in Figure \ref{fig:coredistance}, and is directly comparable with the preliminary results in Figure \ref{fig:rawcoredistance}.
-As expected, the core distance resolution is reduced to X and Ym, and clear improvement over the previous measurements of core position.
+As expected, the core distance resolution is reduced to 13.5m and 6.1m, which is a clear improvement over the previous measurements of core position.
 
@@
 \includegraphics[width=\textwidth]{coredistance}
-\caption{The distance from true core to the core reconstructed with the full-LPD is shown above. For four-telescope events, the standard deviation from true position is Xm. }
+\caption{The distance from true core to the core reconstructed with both the full shower LPD and the DC LPD is shown above.
+For 4-tel events the standard deviation from true core distance is 13.5m, while for 5-tel events, it is a much smaller 6.1m.
+In both cases, there is clear improvement over the full-shower-only reconstruction in Figure \ref{fig:rawcoredistance}.}
 \label{fig:coredistance}
@@
 As an alternative metric for assessing reconstruction accuracy, we can calculate the absolute distance from the reconstructed core to the true core.
-The results of a binning of this distribution are shown in Figure \ref{fig:position}.
+The results of a binning of this distribution are shown in Figure \ref{fig:rawposition}.
 Because we consider absolute distance, this value can never be negative.
 Thus, we calculate a one-sided distribution standard deviation, and consider the value of an event in the 68th centile to be equal to the standard deviation.
-It is found that, for both four and five telescope events, the core reconstruction is approximately $\sigma_{core} \approx 10m$ and $\sigma_{core} \approx 20m$ respectively.
-Most reconstructed core positions thus lie less than 10m from the true position.
-This is extremely good, especially in comparison to the Hillas Reconstruction, where a core resolution of Y is more typical AND CITE!
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{position}
-\caption{The distance from true core position to the reconstructed core position is shown above. For four-telescope events, the standard deviation from true position is Xm.}
+It is found that, for both four and five telescope events, the core reconstruction is approximately $\sigma_{core} = 9.1m$ and $\sigma_{core} 17.0m$ respectively.
+Considered together, we conclude that most high-multiplicity reconstructed core positions thus lie less than 15m from the true position.
+This is reasonably good, especially in comparison to the Hillas Reconstruction, where a core position resolution of $\sigma_{core} \approx 20m$ is more typical.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\textwidth]{rawposition}
+\caption{The distance from true core position to the reconstructed core position is shown above.
+For 4-tel events, the standard deviation from true position is 17.0m, while for 5-tel events, it is just 9.2m.}
 \label{fig:rawposition}
@@
 
-We can similarly consider the resolution of reconstructed height.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{rawheight}
-\caption{The distance from true core position to the reconstructed core position is shown above. For four-telescope events, the standard deviation from true position is Xm.}
-\label{fig:rawheight}
-\end{center}
-\end{figure}
+In contrast the fractional height standard deviation is of the order of 0.35.
+This is fairly bad but not at all unexpected, because the regressor LPD was designed to be independent of height.
+It is only the termination of the LPD that is height dependent, and thus it is both hard to measure but also broadly unimportant.
+The reconstructed height has a tendency to lie close to the starting values for height in the reconstruction process, namely 20, 25 and 30km.
+As seen in Figure \ref{fig:generalenergy}, the value for $r_{max}$ varies relatively little between these energies, provided that emission is saturated.
+On the basis of Energy cuts to remove protons, we are restricting ourselves to Energies of roughly 35TeV or more.
+As seen in Figures \ref{fig:lpd} and \ref{fig:generalenergy}, this is clearly sufficient for saturated emission.
+In fact, the extremely poor height resolution can be taken as a mark of success in that our event reconstruction is now almost completely independent of height, and therefore can't be used to reconstruct the height.
 
@@
 \includegraphics[width=\textwidth]{rawZ}
-\caption{The distance from true core position to the reconstructed core position is shown above. For four-telescope events, the standard deviation from true position is Xm.}
+\caption{The reconstructed charge is shown.
+For 4-tel events, the median charge is 26.0 with a standard deviation of 2.1, while for 5-tel events, the median charge is 26.0 with a standard deviation of 0.95.}
 \label{fig:rawZ}
@@
 However, there are many cores clustered around each of the 5 telescopes.
+It is important to recall that the BDT is never explicitly told about the position or number of telescopes, though the distinct features at each telescope tell us that their existence has clearly been inferred by the BDT.
+This suggests that the BDT is functioning as we would hope, and has learned indirectly where the telescopes lie.
+
 This makes sense, as cores close to a telescope are likely to produce negligible DC light in that telescope.
@@
 The Energy distribution is shown in Figure \ref{fig:energy}, alongside the post-cuts distribution.
+The full simulated distribution of $\phi(E) \propto E^{-2.7}$ is indicated alongside the reconstructed distributions.
+There is already a noticeable similarity between the Simulated and Reconstructed Energy distributions, albeit with a broadening due to the Energy resolution of roughly 10\%.
+
 As might be expected, the loose $P_{5tel}$ cuts produce little noticeable difference to the distribution.
@@
 Ultimately, the post cut distributions of 4-tel events appears similar to the 5-tel distribution, albeit with a greater overall frequency.
-In contrast, the pre-cuts 4-tel events had a noticeable broader distribution extending further into the very low and very high energy regimes.
+Both are lie closer to the simulated distribution once cuts have been applied.
+In contrast, the pre-cuts 4-tel events had a noticeable broader distribution extending further into the very low and very high energy regimes even when compared to the 5-tel rather than simulated distribution.
 The results broadly vindicate our decision to apply an Energy Cut on reconstructed events that was implemented to remove protons.
 Were the lower Energy Iron events to have been included in our simulations, we would have needed to remove them through the BDT method because they are unlikely to be reconstructed well.
+Having applied the BDT cuts, we see that the 5-tel distribution broadly follows the simulated distribution with a relative height of 0.6\%, while the 4-tel events follow the simulated distribution with a relative height of 1.8\%.
 
@@
 Unsurprisingly, the loose cuts for $P_{5tel}$ mean that 5-tel performance is only slightly improved, while the 4-tel performance is more significantly improved.
-For 5-tel events, the core position reduces from $\sigma_{core} = 9.2m$ to $\sigma_{core} = 8.6m$, while for 4-tel events, the improvement is a substantial reduction from $\sigma_{core} = 17.0m$ to $\sigma_{core} = 10.0m$.
+For 5-tel events, the core position reduces from $\sigma_{core} = 9.2m$ to $\sigma_{core} = 8.7m$, while for 4-tel events, the improvement is a substantial reduction from $\sigma_{core} = 17.0m$ to $\sigma_{core} = 10.0m$.
 Ultimately our resultant core resolutions are broadly similar for both multiplicities, and represent a significant improvement over previous Hillas-reconstructed core positions.
+Considered as a target region, we see that we have a roughly fourfold reduction in bounding area likely to contain the core.
 
@@
 We again see that the harsher $P_{4tel}$ cuts leads to a convergence of 4-tel and 5-tel resolution.
+The height resolution remains poor, but continues to not hinder the charge reconstruction.
 
@@
 Whereas in Figure \ref{fig:rawZ} the distribution is clearly partially truncated by the imposed range of $16 < Z < 36$, we see no such problem once $P_{4tel}$ cuts have been applied.
-Ultimately the 5-tel resolution improves from $\sigma_{Z}=0.95$ to $\sigma_{Z}=0.87$, while the 4-tel resolution improves from $\sigma_{Z}=2.11$ to $\sigma_{Z}=1.05$.
+Ultimately the 5-tel resolution improves from $\sigma_{Z}=0.95$ to $\sigma_{Z}=0.88$, while the 4-tel resolution improves from $\sigma_{Z}=2.11$ to $\sigma_{Z}=1.05$.
 In doing this, we have achieved our stated aim of obtaining a charge reconstruction method capable of producing large datasets with a charge resolution of roughly  $\sigma_{Z} \approx 1$.
@@
 \includegraphics[width=\textwidth]{position}
-\caption{The distance from true core position to the reconstructed core position is shown above. For four-telescope events, the standard deviation from true position is Xm.}
+\caption{The distance from true core position to the reconstructed core position is shown above.
+For 4-tel events, the standard deviation from true position is 10.0m, while for 5-tel events, it is 8.7m.There is a clear improvement over the distribution in Figure \ref{fig:rawposition}.}
 \label{fig:position}
-\end{center}
-\end{figure}
-
-We can similarly consider the resolution of reconstructed height.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=\textwidth]{rawheight}
-\caption{The distance from true core position to the reconstructed core position is shown above. For four-telescope events, the standard deviation from true position is Xm.}
-\label{fig:height}
 \end{center}
@@
 \caption{The fraction deviation from true energy is shown above.
-For events with five-telescope multiplicity, the fractional error is X but for four-telescope multiplicity, it is Y.
-The expected poissonian error bars are also shown.}
+For events with five-telescope multiplicity, the fractional error is 0.05 but for four-telescope multiplicity, it is 0.06.
+The expected poissonian error bars are also shown.
+There is a clear improvement over the distribution in Figure \ref{fig:rawepn}.}
 \label{fig:epn}
@@
 \includegraphics[width=\textwidth]{Z}
-\caption{The reconstructed charge for the cut dataset is shown, with a clear peak around the true value of Z=26.}
+\caption{The reconstructed charge for the cut dataset is shown, with a clear peak around the true value of Z=26.
+There is a noticeable improvement over Figure \ref{fig:rawZ}, with a new resolution of 1.1 and 0.9 for 4-tel and 5-tel events respectively.}
 \label{fig:Z}
@@
 In the event that the experimental method proves successful, it should be possible to use the exact position of the iron peak as a method of calibration for atmospheric absorption.
-An underestimate of the absorption would lead to an iron peak that was shifted to a charge number lower than 26, due to a lower than unexpected photon count.
+An underestimate of the CORSIKA absorption used in training would lead to an iron peak that was shifted to a charge number lower than 26, due to a lower than unexpected photon count.
 Similarly, the reverse would apply if the modelled atmospheric absorption was an overestimate.
@@
 This is likely to fully sample an LPD of typical radius $r_{max} \approx 100$, while clearly maintaining a reasonably high count rate.
-
-Further study of $\sigma_{Z}$ in this region is required to determine the optimum layout (not necessarily be a grid) for event reconstruction.
+Further study of $\sigma_{Z}$ in this region is required to determine the optimum layout for event reconstruction, which is not necessarily a grid.
+Additional study in this area would be required to confidently predict what an optimum Cherenkov Array for Heavy Charge measurement might look like.
 
@@
 \section{Conclusion}
-Preliminary results suggest that the LDF reconstruction technique will significantly improve charge reconstruction, to a level sufficient for cosmic ray abundance studies.
+Preliminary results suggest that the LPD reconstruction technique will significantly improve charge reconstruction, to a level sufficient for cosmic ray abundance studies.
 However, reliance on high-multiplicity events means that although applicable to current experiments such as HESS, a new optimised telescope array would be required for a statistical analysis.
@@
 
-To get a more accurate estimate of the error, the testing set of 2000 events with varying azimuth/zenith was again considered.
-The fractional difference \[  \Delta = \frac{ candidate_{DC count} - True_{DC count}}{True_{DC count}} \] was binned in a histogram format, as shown in Figure \ref{fig:dcdiff}.
-It was observed that the mean was 0.09 and the median was -0.08, meaning the distribution was partially skewed.
-If the absolute deviation from the $True_{DC}$ value is considered, then 68\% of pixels have a fractional deviation less than 0.33.
-Accounting for $\sigma_{STA}$, we find that the $sigma_{LPD}=\sigma_{rgr1}=0.32$, an improvement over the fixed 56Tev directly incident simulation.
-For the high-multiplicity rejected events, we find the regressor has an error of $\sigma_{rejected1}=0.41$.
-
-For HESS2, the mean was 0.22 while the median was -0.09, leading to an even more skewed distribution.
-However the 68\% absolute fractional deviation was 0.29, and with $sigma_{STA}$, we find that $sigma_{LPD}=\sigma_{rgr2}=0.29$, slightly better than for HESS1.
-The improved performance can be explained by the matching energy distribution for the training and testing datasets.
-Higher-energy events have more background EAS light without consequently increased DC light, meaning the signal becomes harder to extract.
-The testing dataset has predominantly low-energy events, with reduced background.
-For the rejected events, we find that $\sigma_{rejected2}=0.63$, with $\sigma_{STA}$ being negligible.
-
-\begin{table}[h!]
-  \centering
-  \caption{Fractional error from $True_{DC}$ for all high-multiplicity test pixels}
-  \label{tab:altlpderror}
-  \begin{tabular}{ccc}
-    \toprule
-    & HESS1 & HESS2\\
-    \midrule
-    $\sigma_{rgr}$ & 0.32 & 0.29\\ 
-    $\sigma_{rejected}$ & 0.41 & 0.63\\ 
-    \bottomrule
-  \end{tabular}
-\end{table}
+The stated aim of this study was the Reconstruction of Charge Number of Heavy Cosmic Rays using Cherenkov Light.
+Broken down further, this analysis aimed to identify DC pixels in camera Images, to make a measurement of the DC light, and to reconstruct the charge of the Cosmic Ray with an error or roughly $\sigma_{Z}=1$ or less.
+On all of these counts, it is fair to say that the project was successful.
+
+On the first count, the use of BDTs was overwhelmingly successful for identifying DC pixels.
+On a single Image basis, the BDT method produced an eightfold increase in accepted pixels with an accompanying decrease in the proportion of misidentified pixels.
+More importantly, the BDTs produced a two-hundred-fold increase in the acceptance of high-multiplicity events upon which this analysis depends.
+Combining the acceptance rates, we find that 2.3\% of all Iron Cosmic Rays with an Energy greater than 35 TeV will belong to a high-multiplicity image set.
+This gives an expected high-multiplicity Iron event rate of $1.22 \, h^{-1}$, rather than the alternative rate of $6.1 \times 10 ^{-3} \, h^{-1}= 1.02 \, week^{-1}$ that we would achieve with traditional $Q_{DC}$ identification.
+Ultimately, any attempted to analyse experimental data will suffer from vastly insufficient statistics unless the BDT method is applied for DC pixels.
+This technique will have wide-ranging uses outside of this analysis, among these will hopefully be a significant improvement in Hillas reconstruction.
+
+The second goal was achieved through use of a second set of BDTs, in this case regressors, to extract values for $DC_{rgr}$ from images using DC pixels.
+It was found that the actual quantity of DC light $True_{DC}$ varied quite significantly with the first interaction height.
+The time required to produce the five simulations seen in Figure \ref{fig:lpd} was approximately two minutes, and we might thus expect a calculation involving a thoroughly simulated LPD to last 10-20 seconds.
+The exact calculation time would be energy dependent.
+If we were to fully simulate the LPD for each iteration of the LPD, in order to realistically simulate the interaction height dependence,  we can see how long we might expect a minimisation of several thousand iterations to take.
+Each minimisation is itself only one of several hundred, making clear that such  fully simulating the LPD as part of a minimisation process is completely infeasible.
+
+Our only viable alternative is to develop a technique for measuring $True_{DC}$ without fully simulating the entire LPD.
+Fortunately, the BDT regressor was able to  do exactly this.
+The fractional standard deviation was reduced of the BDT was just $\frac{\sigma_{rgr}}{DC_{rgr}} = 0.14$ for a sample of mixed interaction heights, as opposed to $\frac{\sigma_{TrueDC}}{True_{DC}} = 0.48$ when the actual DC light was measured.
+With 4 or 5 LPD measurements, this BDT regressor was capable of giving an amplitude proportional to $Z^{2}$ with sufficient precision to enable reconstruction.
+The regressor was able to the necessary precision by correlating a number of image and pixel variables such as the Image Amplitude and Aspect Ratio.
+The BDT must indirectly be inferring the charge number, but by providing this information in the form of an LPD rather than a simple number, we are able to reconstruct the charge using all available information.
+It would be interesting to explore the possibility of a BDT that would directly calculate the charge number of a Cosmic Ray based on a given Image, but this was not done as part of this analysis.
+
+Our last goal was to reconstruct the charge number of Cosmic Rays.
+To be more specific, the reconstructed charge number should have a reasonably good resolution, while still having a reasonably high acceptance rate that means a spectroscopic analysis of heavy Cosmic Rays would be possible.
+Through a combination of two well-defined LPDs, it was possible to reconstruct events using a likelihood minimisation.
+This resulted in many high-multiplicity events, but the vast majority were 4-tel events with a charge resolution of $\sigma_{Z} = 2.2$.
+However, a third BDT was again able to significantly improve these results.
+In particular, 4-tel events were very easy to separate on the basis of their reconstructed energy and core position into groups of \textquoteleft Good' and \textquoteleft Bad' reconstructions.
+Using only those events which were deemed by the BDT to probably be well reconstructed, we noticeably reduce the charge resolution.
+Ultimately we are left with $\sigma_{Z}=1.05$ and $\sigma_{Z}=0.87$ for 4-tel and 5-tel events respectively.
+The resolutions, alongside the pass rate of 0.54 and 0.96, should be good enough to allow measurement of Cosmic Ray composition.
+
+Having successfully reconstructed a relatively large and narrow Iron peak, it is safe to say that this analysis was a clear proof of concept.
+It remains to be seen whether the technique can be applied to real HESS data so effectively as the simulations suggest, but there is sufficient evidence to be optimistic.
+At the very least, the use of BDTs have provided significant improvements in the viability of LPD-based reconstruction.
+\newpage
+\section{Acknowledgements}
+I would firstly like to thank Professor Dieter Horns, who served as a supervisor without flaw.
+I would particularly like to thank him for encouraging  me to present part of this work at a conference, as well as for occasionally providing Ice Cream to group members in the summer.
+Both were highly appreciated.
+
+In addition, I would like to thank Attila Abramowski for our many discussions about the HESS experiment and DC light.
+He was patient enough share his experience, which often served as a much-needed sanity check on my results.
+
+More generally, I would like to thank every member of the group, all of whom invariably made me feel welcome.
+I've really enjoyed my time as part of this group and they were the reason why.
+I feel luckily to have found a research group full of such genuinely nice people.
+(Apologies for Brexit!)
+\newpage
 \section{Bibliography}
@@
 \begin{small}
+\setstretch{1.0}
 \pgfplotstabletypeset{data/atmprof10.dat}

### 2016-12-07 report/updated.tex
Final Thesis Update 07/12/16

--- 2016-07-06 report/final.tex
@@
 \geometry{a4paper, portrait, margin=1.0in}
-\usepackage{gensymb}
 \usepackage{booktabs}
@@
 
+        \day4
+        \month 7
+        \year 2016
         \today
@@
 The first half is the simulation of Cosmic Ray HESS camera images, and analysis work based on these images.
-The second half is a Monte Carlo study simulating air shower intensities, based entirely on function fitted from the HESS camera images.
+The second half is a Monte Carlo study simulating air shower intensities, with event reconstruction based on function-fitting to these intensities.
 It is important to note that the simulation of Cosmic Ray air showers for the first part of my thesis was performed using the CORSIKA software \cite{Heck98}, and the resultant HESS camera images were produced using the Sim\textunderscore Telarray software \cite{Bernlohr08}.
@@
 
-Additionally, a significant portion of this work relies on Supervised machine learning that was performed using the SciKit learn package \cite{scikit-learn}.
+Additionally, a significant portion of this work relies on supervised machine learning that was performed using the SciKit learn package \cite{scikit-learn}.
 Although I wrote the relevant Python scripts to facilitate data categorisation and algorithm training, the package acts as a black box to convert training data into a functioning Boosted Decision Tree.
@@
 For Iron Nucleus events, we would expect to reconstruct \[Z \approx 26 \pm 5 \] with a core position resolution of roughly $d \approx 20 m $ \cite{hess07}.
-The Cosmic Rays imaged by these telescopes have energies in TeV scale, and at present, no study of the relative abundance of different cosmic ray elemental abundances exists at these energies.
+The Cosmic Rays imaged by these telescopes have energies in TeV scale, and at present, no study of the relative cosmic ray elemental abundances exists at these energies.
 If the telescope arrays could be used to spectroscopically analyse the Cosmic Rays, it could provide important clues regarding the mechanism of Cosmic Ray formation and propagation in the galaxy.
@@
 
-The refractive index as a function of height is shown in as seen in Figure \ref{fig:lpd}, using standard values listed in the appendix.
+The refractive index as a function of height is shown in Figure \ref{fig:lpd}, using standard values listed in the appendix.
 Because the refractive index of air increases very quickly as the height decreases, the Cherenkov Angle $\theta_{C}$ will also increase rapidly with decreasing height.
@@
 Above threshold, Cherenkov Emission is determined by the Frank Tamm formula \cite{ppreview}.
-Under the assumption of constant magnetic permittivity and a zenith angle of $90\degree$, and with  the vertical distance travelled in meters $\Delta_{h}$ and the emission energy range in eV $\Delta_{E}$, we can find an approximate Cherenkov Emission formula.
+Under the assumption of constant magnetic permittivity and a zenith angle of $90^{\circ}$, and with  the vertical distance travelled in meters $\Delta_{h}$ and the emission energy range in eV $\Delta_{E}$, we can find an approximate Cherenkov Emission formula.
 \[ \frac{d^{2}N_{photons}}{dEdh} = \frac{\alpha Z^{2}}{\hbar c} \sin^{2} \theta_{c}(E) \approx 370 Z^{2} \sin^{2} \theta_{c}(E)\, cm^{-1}eV^{-1} \]
@@
 
-If we divide the number of emitted photons by the area of the annulus between the ring radii at $h$ and $h - \Delta_{h}$, we retrieve the LPD shown in Figure \ref{fig:lpd}, which varies with $ \rho_{DC}  = f(r) \times Z^{2}$ .
+If we divide the number of emitted photons by the area of the annulus between the ring radii at $h$ and $h - \Delta_{h}$, we retrieve the LPD shown in Figure \ref{fig:lpd}, which varies with $ \rho_{DC}  = f(r) \times Z^{2}$.
 Thus the amplitude of the LPD is proportional to the square of the Cosmic Ray charge, enabling us to reconstruct this number from the DC emission.
@@
 
-The refractive index at a series of heights, based on data from the HESS site, is shown \ref{fig:lpd}.
+The refractive index at a series of heights, based on data from the HESS site, is also shown \ref{fig:lpd}.
 Exponentials are fitted between points to provide interpolation, and a comparison can be made to a linear interpolation that is also plotted.
@@
 An altitude of 1800m was assumed, again corresponding to the HESS site.
-The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$.
+The simulated zenith angle ranged from $0^{\circ} < \theta < 2 ^{\circ}$, while the simulated azimuth angle ranges from $-2^{\circ} < \phi < 2 ^{\circ}$.
 The four smaller HESS-phase-1 telescopes were arranged in a cross along the x/y axis with the larger HESS-phase-2 \textquoteleft CT5' telescope placed at the center.
@@
 \includegraphics[width=\textwidth]{hess1statsbigtestdata}
-\caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000.
-Events below this are unlikely to be identified correctly because the DEC light is too faint.
-In the top right- the distribution of the dataset is shown, once all the non-$Q_{DC}$ cuts have been applied.
-In the bottom left, the BDT score distribution is shown before any cuts.
-On the bottom right, we see the same distribution after both signal and BDT score cuts are applied.
-All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.}
+\caption{The DC signal in the shower-free pixel is shown in the top right, following an exponential decay.
+Events below roughly 200 are unlikely to be identified correctly because the DC light is too faint to be seen against the background.
+In the top left, the BDT score distribution is shown before any cuts.
+In the lower left, we see the same distribution after both signal and BDT score cuts are applied.
+For comparison, the lower right graph shows the alternative distribution of $Q_{DC}$-reconstructed events.
+All green events are ones in which the DC pixel has been correctly identified, while grey events are ones that have been incorrectly identified.}
 \label{fig:cutdistribution}
@@
 It would be interesting to incorporate the information from these pixels into reconstruction, but doing so would remove our ability to constrain the core.
-Further study could attempt to use the rejected pixels, though the performance of the regressor on images without DC light would first need to be thoroughly tested to account for the possibility that rejected pixels belong top images without DC light.
+Further study could attempt to use the rejected pixels, though the performance of the regressor on images without DC light would first need to be thoroughly tested to account for the possibility that rejected pixels belong to images without DC light.
 Because the BDT regressor functions as a Black Box, it is difficult to know how it is using the information from camera images to calculate $DC_{rgr}$.
@@
 \section{Monte Carlo Simulation}
-Having obtained a parameterisation for both the full and DC LPD, as well as the associated error in the case of a HESS-type array, the Charge reconstruction Technique can be applied to a simpified Monte Carlo simulation of the HESS array, developed as part of this analysis.
+Having obtained a parameterisation for both the full and DC LPD, as well as the associated error in the case of a HESS-type array, the charge reconstruction technique can be applied to a simplified Monte Carlo simulation of the HESS array, developed as part of this analysis.
 Conducting a Monte Carlo simulation using the Gaussian-smeared LPD, we can measure the effectiveness of the LPD-reconstruction technique.
@@
 \includegraphics[height=0.9\textheight]{generalheight}
-\caption{The integrated interaction lengths increases as height decreases.
+\caption{Above, the integrated interaction lengths increases as height decreases.
 Thus the decay probability follows a exponentially increasing distribution.
+In the centre, the survival and decay fractions are illustrated as a function of height.
+The median occurs around 40km, where the two lines intersect.
+Below, the fraction of interacting particles in each height band is shown in a histogram.
 The mean first interaction height for all events is roughly 40km above sea level.}
@@
 This parameter is free-floating, and can only be determined through experimental study of Cosmic Rays.
-Experimental results indicate an approximate cross section of $\sigma_{Fe-air} = 2000mb$ and a corresponding thus $x_{0} \approx 12 g cm^{-2}$ \cite{Montanus2013}.
+Experimental results indicate an approximate cross section of $\sigma_{Fe-air} = 2000mb$ and thus a corresponding value of $x_{0} \approx 12 g cm^{-2}$ \cite{Montanus2013}.
 
@@
 
-Another parameter that could be exponetially the optical depth to the surface, $\tau$.
+Another parameter that could be modelled is $\tau$, the optical depth to the surface.
 The Cherenkov Light, mostly emitted in the visible blue part of the EM spectrum, experiences relatively little atmospheric absorption.
-The major of Rayleigh scattering-based atmospheric absorption occurs in the lower part of the troposphere, and thus the atmospheric absorption is almost independent of emission up to first interaction height.
+The major component of Rayleigh-scattering-based atmospheric absorption occurs in the lower part of the troposphere, and thus the atmospheric absorption is almost independent of emission up to first interaction height.
 For a given emitted intensity $I_{0}$ we find that the corresponding I received on the ground decays exponentially with optical depth, so that $\frac{I}{I_{0}}=e^{-\tau}$ with $\tau=\int_{0}^{l}ds$.
@@
 Using this method, it is clear that the energy reconstruction is fairly good, with a fractional standard deviation of roughly 0.10 when both four and five telescope events are considered.
-We find that the position is also reconstructed, with an accuracy of .
 Having now reconstructed the value of the energy with reasonable accuracy, we can make use of this value when attempting to reconstruct the DC LPD.
@@
 Thus, we calculate a one-sided distribution standard deviation, and consider the value of an event in the 68th centile to be equal to the standard deviation.
-It is found that, for both four and five telescope events, the core reconstruction is approximately $\sigma_{core} = 9.1m$ and $\sigma_{core} 17.0m$ respectively.
+It is found that, for both four and five telescope events, the core reconstruction is approximately $\sigma_{core} = 9.1m$ and $\sigma_{core}=17.0m$ respectively.
 Considered together, we conclude that most high-multiplicity reconstructed core positions thus lie less than 15m from the true position.
@@
 Having taken into account our various variable uncertainties, we can also consider our most important variable.
-In Figure \ref{fig:rawZ} the reconstructed charge number is binned in integers, illustrating the element that each reconstructed event would be assigned to.
+In Figure \ref{fig:rawZ} the reconstructed charge number is binned, illustrating the expected experimental results.
 As we would hope, there is a very clear peak centered on Z=26, and the median charge value lies very close to this value.
@@
 We see that the majority of bad red events have a lower BDT score in the 4-tel graph.
-In each graph, the think black line indicates the eventual cut made to the data.}
+In each graph, the thick black line indicates the eventual cut made to the data.}
 \label{fig:reconBDTdistribution}
@@
 The values of $\sigma_{Z}$ and $\mathbf{\tilde{\sigma_{Z}}}$ are shown in Figure \ref{fig:Zcuts}.
-Ultimately, a cut of $P_{4tel} > 0.15$ and $P_{5tel} > 0.22$ was chosen, corresponding to $\sigma_{Z}=0.88$ and $\sigma_{Z}=1.04$ respectively.
+Ultimately, a cut of $P_{4tel} > 0.21$ and $P_{5tel} > 0.15$ was chosen, corresponding to $\sigma_{Z}=0.88$ and $\sigma_{Z}=1.04$ respectively.
 The respective passing fraction was 0.92 and 0.53.
@@
 \includegraphics[width=\textwidth]{Zcuts}
-\caption{The BDT score distribution is shown for the Monte Carlo test data.
-Events are colour-coded by how well the Charge number was reconstructed.
-We see that the majority of bad red events have a lower BDT score in the 4-tel graph.
-In each graph, the think black line indicates the eventual cut made to the data.}
+\caption{Above, the raw values for $\sigma_{Z}$ are shown as a function of the BDT cuts for 4-tel and 5-tel events.
+Below, the scaled values of $\mathbf{\tilde{\sigma_{Z}}}$ are shown.
+For 4-tel events, there is a clear minimum for $P_{4tel} > 0.21$, while for 5-tel events, there is a broader minimum at $P_{5tel} > 0.15$.}
 \label{fig:Zcuts}
@@
 We know that the first interaction height is reconstructed extremely poorly, and thus the exact $r_{max}$ values for these LPDs is uncertain.
-It is likely that, given this, the height is being misreconstructed to allow the LPD to extend fare enough to trigger the most distant telescope.
+It is likely that, given this, the height is being misreconstructed to allow the LPD to extend far enough to trigger the most distant telescope.
 
@@
 Ultimately, the post cut distributions of 4-tel events appears similar to the 5-tel distribution, albeit with a greater overall frequency.
-Both are lie closer to the simulated distribution once cuts have been applied.
+Both lie closer to the simulated distribution once cuts have been applied.
 In contrast, the pre-cuts 4-tel events had a noticeable broader distribution extending further into the very low and very high energy regimes even when compared to the 5-tel rather than simulated distribution.
@@
 \subsection{Actual Data}
-The obvious next step to take as part of this analysis would be to apply the reconstruction Method to real HESS data.
+The obvious next step to take as part of this analysis would be to apply the reconstruction method to real HESS data.
 We would hope to obtain a distribution similar to that in Figure \ref{fig:Z}, to which we could fit Gaussians centered on each integer value of Charge.
@@
 Similarly, the reverse would apply if the modelled atmospheric absorption was an overestimate.
-As these is much associated uncertainty in the atmospheric properties, this would be a useful measurement to perform.
+As there is much associated uncertainty in the atmospheric properties, this would be a useful measurement to perform.
 
@@
 The BDT must indirectly be inferring the charge number, but by providing this information in the form of an LPD rather than a simple number, we are able to reconstruct the charge using all available information.
-It would be interesting to explore the possibility of a BDT that would directly calculate the charge number of a Cosmic Ray based on a given Image, but this was not done as part of this analysis.
+It would be interesting to explore the possibility of a BDT that would directly calculate the charge number of a Cosmic Ray based on a given image, but this was not done as part of this analysis.
 
